### 2011-12-16 paper.tex
First dump of LaTeX code, mainly the example directly from the journals homepage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This is the article LaTeX template for RSC journals
%Copyright The Royal Society of Chemistry 2010
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[8.5pt,twoside,twocolumn]{article}
\oddsidemargin -1.2cm
\evensidemargin -1.2cm
\textwidth 18cm
\headheight 1.0in
\topmargin -3.5cm
\textheight 22cm
\usepackage[super,sort&compress,comma]{natbib} 
\usepackage{mhchem}
\usepackage{times,mathptmx}
% \usepackage{times}
% feel free not to use mathptmx if it causes difficulties
\usepackage{sectsty}
\usepackage{balance}

\usepackage{graphicx} %eps figures can be used instead
\usepackage{lastpage}
\usepackage[format=plain,justification=raggedright,singlelinecheck=false,font=small,labelfont=bf,labelsep=space]{caption} 
\usepackage{fancyhdr}
\pagestyle{fancy}

\begin{document}

\thispagestyle{plain}
\fancypagestyle{plain}{
\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
\renewcommand{\headrulewidth}{1pt}}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand\footnoterule{\vspace*{1pt}% 
\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
\setcounter{secnumdepth}{5}

\makeatletter 
\def\subsubsection{\@startsection{subsubsection}{3}{10pt}{-1.25ex plus -1ex minus -.1ex}{0ex plus 0ex}{\normalsize\bf}} 
\def\paragraph{\@startsection{paragraph}{4}{10pt}{-1.25ex plus -1ex minus -.1ex}{0ex plus 0ex}{\normalsize\textit}} 
\renewcommand\@biblabel[1]{#1}            
\renewcommand\@makefntext[1]% 
{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
\makeatother 
\renewcommand{\figurename}{\small{Fig.}~}
\sectionfont{\large}
\subsectionfont{\normalsize}

\fancyfoot{}
\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
\fancyhead{}
\renewcommand{\headrulewidth}{1pt} 
\renewcommand{\footrulewidth}{1pt}
\setlength{\arrayrulewidth}{1pt}
\setlength{\columnsep}{6.5mm}
\setlength\bibsep{1pt}

\twocolumn[
  \begin{@twocolumnfalse}
\noindent\LARGE{\textbf{Oscillations in CO-oxidation Catalysts at Atmospheric Pressures$^\dag$}}
\vspace{0.6cm}

\noindent\large{\textbf{Full Name,$^{\ast}$\textit{$^{a}$} Full Name,\textit{$^{b\ddag}$} and
Full Name\textit{$^{a}$}}}\vspace{0.5cm}
%Please note that \ast indicates the corresponding author(s) but no footnote text is required.

\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
First published on the web Xth XXXXXXXXXX 200X}}}

\noindent \textbf{\small{DOI: 10.1039/b000000x}}
\vspace{0.6cm}
%Please do not change this text.

\noindent \normalsize{The abstract should be a single paragraph which summarises the content of the article. Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].}
\vspace{0.5cm}
 \end{@twocolumnfalse}
  ]

\section{Introduction}

\section{Experimental Methods}

\section{This is the section heading style}
%Footnotes
\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}

%Please use \dag to cite the ESI in the main text of the article.
%If you article does not have ESI please remove the the \dag symbol from the title and the above footnotetext.

\footnotetext{\textit{$^{a}$~Address, Address, Town, Country. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: xxxx@aaa.bbb.ccc}}
\footnotetext{\textit{$^{b}$~Address, Address, Town, Country. }}

%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required

\footnotetext{\ddag~Additional footnotes to the title and authors can be included \emph{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P. Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}

The main text of the article\cite{Mena2000} should appear here.

\subsection{This is the subsection heading style}
Section headings can be typeset with and without numbers.\cite{Abernethy2003}

\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.

\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.

\section{Equations}

Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:

 \[ A = \pi r^2 \]

\begin{equation}
  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
\end{equation}

\section{Graphics and tables}
\subsection{Graphics}
Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).\cite{Cotton1999}

\begin{figure}[h]
\centering
  \includegraphics[height=3cm]{example}
  \caption{An example figure caption}
  \label{fgr:example}
\end{figure}

% an example of a two-column figure
%\begin{figure*}
  %\centering
  %\includegraphics[height=3cm]{example.jpg}
  %\caption{An example figure caption, an image from the \textit{Physical Chemistry Chemical Physics} cover gallery.}
  %\label{fgr:example}
%\end{figure*}

\subsection{Tables}
Tables typeset in RSC house style do not include vertical lines. Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table. Table captions do not end in a full point.\cite{Arduengo1992,Eisenstein2005}

\begin{table}[h]
\small
  \caption{\ An example of a caption to accompany a table}
  \label{tbl:example}
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
    \hline
    Header one/units & Header two & Header three \\
    \hline
    1 & 2 & 3 \\
    4 & 5 & 6 \\
    7 & 8 & 9 \\
    10 & 11 & 12 \\
    \hline
  \end{tabular*}
\end{table}

Adding notes to tables can be complicated.  Perhaps the easiest
method is to generate these manually.

% an example of a two-column table
%\begin{table*}
%\small
  %\caption{\ An example of a caption to accompany a table, table captions do not end in a full point}
  %\label{tbl:example}
  %\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllll}
    %\hline
    %Header one & Header two & Header three & Header four & Header five & Header six  & Header seven\\
    %\hline
    %1 & 2 & 3 & 4 & 5 & 6  & 7\\
    %8 & 9 & 10 & 11 & 12 & 13 & 14 \\
    %15 & 16 & 17 & 18 & 19 & 20 & 21\\
    %\hline
  %\end{tabular*}
%\end{table*}

You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
The \texttt{mhchem} package can also be used so
that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.

\section{Conclusions}
The conclusions section should come at the end of article. For the reference section, the style file rsc.bst can be used to generate the correct reference style.\footnote[4]{Footnotes should appear here. These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
 %For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols. e.g.  \footnote[num]{your text} the corresponding author \ast counts as footnote 1, ESI as footnote 2, e.g. if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] etc. Please also cite the ESI within the main body of the text using \dag.

%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.

%\balance

%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
%\renewcommand\refname{Notes and references}

\footnotesize{
\bibliography{rsc} %your .bib file
\bibliographystyle{rsc} %the RSC's .bst file
}

\end{document}

### 2011-12-16 paper.tex
End-of-the-day commit, only details added since last commit

@@
 \section{Experimental Methods}
+The measurents are done in a silicon-fabricated microreactor, developed here at CINF (REF!)....
+
+\section{Results}
+Several different samples deposited at various diffent sizes and amounts all show the oscillating bahaviour.
+Repeatability is high regarding running long experiments on a single sample, but very low from sample to sample.
+
+\section{Discussion}
+....
 

### 2011-12-17 python_figures/single_full_oscillation.py
End-of-day commit, started first figure

@@ -1,0 +1,48 @@
+import matplotlib
+#matplotlib.use('svg')
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import numpy as np
+import MySQLdb
+
+try:
+    db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+except:
+    db = MySQLdb.connect(host="127.0.0.1", port=9995, user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+
+
+cursor = db.cursor()
+
+data = {}
+#Mass28
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactorNG where measurement = 572")
+data['M28'] = np.array(cursor.fetchall())
+
+#Mass44
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactorNG where measurement = 573")
+data['M44'] =  np.array(cursor.fetchall())
+
+#Temperature
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactorNG where measurement = 578")
+data['TEMPERATURE'] = np.array(cursor.fetchall())
+
+
+fig = plt.figure()
+
+axis = fig.add_subplot(1,1,1)
+axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
+axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'b-')
+axis.set_ylim(0.2,1.2)
+axis2 = axis.twinx()
+axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'k-')
+axis2.set_ylim(150,210)
+axis.set_xlim(1000,1133)
+axis.grid(True)    
+
+axis.set_ylabel('SEM Current / nA', fontsize=20)
+axis2.set_ylabel('Temperature', fontsize=20)
+axis.set_xlabel('Time/minutes', fontsize=20)
+
+#plt.tight_layout()
+plt.show()
+#plt.savefig('../svg_figures/oscillations_gas_dependence.svg')

### 2012-01-09 paper.tex
Added two figures and started the reference list

@@
 \usepackage{mhchem}
+\usepackage[utf8]{inputenc}
 \usepackage{times,mathptmx}
@@
 
-\noindent\large{\textbf{Full Name,$^{\ast}$\textit{$^{a}$} Full Name,\textit{$^{b\ddag}$} and
-Full Name\textit{$^{a}$}}}\vspace{0.5cm}
+\noindent\large{\textbf{Robert Jensen$^{\ast}$\textit{$^{a}$}, Thomas Andersen\textit{$^{b\ddag}$}, Anders Nierhoff\textit{$^{b\ddag}$}, Søren Dahl\textit{$^{b\ddag}$}, Ole Hansen\textit{$^{b\ddag}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
 %Please note that \ast indicates the corresponding author(s) but no footnote text is required.

### 2012-01-09 python_figures/oscillations_gas_dependence.py

@@ -59,8 +59,8 @@ for i in range(0,steps-1):
     axis_array[i].tick_params(direction='in', length=6, width=2, colors='k',labelsize=14,axis='both',pad=5)
     axis2_array[i].tick_params(direction='in', length=6, width=2, colors='k',labelsize=14,axis='y',pad=5)
     
-axis_array[2].set_ylabel('SEM Current / nA', fontsize=20)
-axis2_array[2].set_ylabel('CO/O2 Ratio', fontsize=20)
+axis_array[4].set_ylabel('SEM Current / nA', fontsize=20)
+axis2_array[4].set_ylabel('CO/O2 Ratio', fontsize=20)
 axis_array[4].set_xlabel('Time/h', fontsize=20)
 
 

### 2012-01-09 python_figures/summary_of_long_measurement.py

@@ -64,12 +64,6 @@ axis.set_xlabel('Time/minutes', fontsize=20)
 
 
 
-
-
-
-
-
-
 #plt.tight_layout()
 plt.show()
 #plt.savefig('../svg_figures/oscillations_gas_dependence.svg')

### 2012-01-10 paper.tex
Adjusted to literature.bib
Added some very preliminary content and an extra reference

@@
 \section{Introduction}
+Oxidation of CO is a classic model system for testing catalytic properties of various materials.
+It was shown already in 1985 (REF) that this reaction will show oscilaltory behaviour under UHV conditions due to surface reconstructions having large influence on the catalytic activity of the surface.
+However, this is a phenomenon that is only observed under UHV-condition, under higher pressures these kinds of reconstructions will happen.
+In this paper we show sustained catalytic oscilations on Platinum nano particles that due to their sometimes extremely long time-scales cannot be a surface phenomenon, but must involve a bulk oxidation of the nanoparticle.
 
 \section{Experimental Methods}
-The measurents are done in a silicon-fabricated microreactor, developed here at CINF (REF!)....
+The measurents are done in a silicon-fabricated microreactor, developed here at CINF \cite{Henriksen2009}.
+The reactor consists of a two inlets, a long mixing zone for the incoming gases and a reactor of total volume of $240\,$nL.
+The reactor is able to operate at a pressure range og 0-2.5\,bar.
+The gases is supplied through ordinary flow controllers capable of controlling flow in the range of a few mL/min.
+The flow is reduced to a value capable of being fed into a mass-spectrometer by passing most of the flow through an outlet connected to a pressure controller.
+A small part of the flow is led into the reactor chamber and via a $5.4\,\mu$m wide capillary further into UHV chamber equiped with a quadropole mass spectrometer.
+The design ensures that all gas exposed to the catalyst under investigation is also measured in the mass spectrometer ensures a very high sensitivity of the device.
+When an evacuated microreactor is mounted, the base pressure of the UHV chambe is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.
+
+The reactor is heated by a Pt heating element evaporated on the backside that at the same time acts as an RTD to measure the temperature.
+
+\section{Sample preparation}
+The samples was made by depositing a very small amount of size-selcted clusters from a quadropole cluster source (REF!) onto the microreactores.
+Typical sizes are in the order of 3-9\,nm and the coverage is kept at approximately 0.1\% geometric coverage, found by measuring the current from the charged clusters landing on the reactor.
+After deposition the reactor is anonicly bonded to a pyrex lid while keeping the reactor area cold by mounting the reactor on a cooling block and heating the rest of the sample to $\sim350\,^\circ$C \cite{Vesborg2010}
 
 \section{Results}
+The experiments was carried out 
 Several different samples deposited at various diffent sizes and amounts all show the oscillating bahaviour.
@@
 \section{Discussion}
-....
+Due to long timescales involved which are much larger than any typically orcurring timescales for such a small system, there can be little doubt that this phenomenon involves some kind of reaction involving the bulk of the nano particles.
 
@@
 \footnotesize{
-\bibliography{rsc} %your .bib file
+\bibliography{literature} %your .bib file
 \bibliographystyle{rsc} %the RSC's .bst file

### 2012-01-11 paper.tex
Added some content, 3 figures and included the references

@@
 
-\noindent\large{\textbf{Robert Jensen$^{\ast}$\textit{$^{a}$}, Thomas Andersen\textit{$^{b\ddag}$}, Anders Nierhoff\textit{$^{b\ddag}$}, Søren Dahl\textit{$^{b\ddag}$}, Ole Hansen\textit{$^{b\ddag}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
+\noindent\large{\textbf{Robert Jensen\textit{$^{b}$}, Thomas Andersen\textit{$^{b}$}, Anders Nierhoff\textit{$^{b}$}, Søren Dahl\textit{$^{b}$}, Ole Hansen\textit{$^{b}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
 %Please note that \ast indicates the corresponding author(s) but no footnote text is required.
@@
 
+%\section{This is the section heading style}
 \section{Introduction}
+
+%Footnotes
+\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
+
+%Please use \dag to cite the ESI in the main text of the article.
+%If you article does not have ESI please remove the the \dag symbol from the title and the above footnotetext.
+
+\footnotetext{\textit{$^{a}$~DTU Physics, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
+\footnotetext{\textit{$^{b}$~DTU Physics, Fysikvej 312, 2800 Lyngby, Denmark}}
+
+%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
+
+%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \emph{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
+Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}
+
 Oxidation of CO is a classic model system for testing catalytic properties of various materials.
@@
 In this paper we show sustained catalytic oscilations on Platinum nano particles that due to their sometimes extremely long time-scales cannot be a surface phenomenon, but must involve a bulk oxidation of the nanoparticle.
+Similar phenomeon of oscillations of CO oxidation Pt has been seen earlier on thin-films \cite{Lund2000}, single crystals \cite{Hendriksen2005} and in macroscopic flow-reactors \cite{Singh2010}, but to our knowledge never before on nano particles.
 
@@
 \section{Results}
-The experiments was carried out 
+The experiments was carried out ....
+
+The period of the oscillations ranges from a few seconds (the time-constant of the reactor) up to more than an hour.
+A typical slow is oscillation is seen in figure~\ref{fgr:full_oscillation} where we see the typical pattern going from almost no activity slowly up towards $\sim$50\% conversion at which point the sample light off to full conversion almost instantiously where after a short peiod of time the sample again de-activates.
+% an example of a two-column figure, remember that the graphics should be included where it is first referenced
+\begin{figure*}
+  \centering
+  \includegraphics[height=7cm]{single_full_oscillation.png}
+  \caption{A full oscillation first showing a steep ignition of the sample followed by an almost imidiately de-activation of the sample.
+For the next 65\,minutes the sample slowly recovers activity until it again lights off completely.}
+  \label{fgr:full_oscillation}
+\end{figure*}
+
+If a sample is leaved for long periods of time, it keep performing sustained oscillations, but with longer and longer periods.
+In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods.
+Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days.
+% an example of a single-column figure, remember that the graphics should be included where it is first referenced
+\begin{figure}[h]
+\centering
+  \includegraphics[height=7cm]{summary_of_long_measurement.png}
+  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample a total for 439 oscillations in 4 days.}
+  \label{fgr:long_measurement}
+\end{figure}
+
+Extracts of the mass-spectrometry from the very beginning, the middle and towards the end of the experiments is shown in figure~\ref{fgr:extracts}, it is evident that the oscillations are getting more and more irregular as times goes on, towards the end, it is also clearly visible how the smaller oscillations are taking place at a much higher frequency than the full on-off cycles, which is most likely the explanation for the increasing scatter in the period summary.
+% an example of a two-column figure, remember that the graphics should be included where it is first referenced
+\begin{figure*}
+  \centering
+  \includegraphics[height=7cm]{extracts_from_very_long_oscillation.png}
+  \caption{Extracts from the 4 day long experiment.}
+  \label{fgr:extracts}
+\end{figure*}
+
 Several different samples deposited at various diffent sizes and amounts all show the oscillating bahaviour.
@@
 
-\section{This is the section heading style}
-%Footnotes
-\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
+%\subsection{This is the subsection heading style}
+%Section headings can be typeset with and without numbers.\cite{Gong2004} \cite{Hendriksen2010}
 
-%Please use \dag to cite the ESI in the main text of the article.
-%If you article does not have ESI please remove the the \dag symbol from the title and the above footnotetext.
+%\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.
 
-\footnotetext{\textit{$^{a}$~Address, Address, Town, Country. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: xxxx@aaa.bbb.ccc}}
-\footnotetext{\textit{$^{b}$~Address, Address, Town, Country. }}
-
-%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
-
-\footnotetext{\ddag~Additional footnotes to the title and authors can be included \emph{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
-Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}
-
-The main text of the article\cite{Mena2000} should appear here.
-
-\subsection{This is the subsection heading style}
-Section headings can be typeset with and without numbers.\cite{Abernethy2003}
-
-\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.
-
-\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.
+%\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.
 
@@
 \subsection{Graphics}
-Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).\cite{Cotton1999}
-
-\begin{figure}[h]
-\centering
-  \includegraphics[height=3cm]{example}
-  \caption{An example figure caption}
-  \label{fgr:example}
-\end{figure}
-
-% an example of a two-column figure
-%\begin{figure*}
-  %\centering
-  %\includegraphics[height=3cm]{example.jpg}
-  %\caption{An example figure caption, an image from the \textit{Physical Chemistry Chemical Physics} cover gallery.}
-  %\label{fgr:example}
-%\end{figure*}
+Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).
 
@@
 Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table.
-Table captions do not end in a full point.\cite{Arduengo1992,Eisenstein2005}
+Table captions do not end in a full point.
 

### 2012-01-11 python_figures/extracts_from_very_long_oscillation.py

@@ -1,6 +1,6 @@
 import matplotlib
 #matplotlib.use('svg')
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
@@ -53,14 +53,6 @@ for i in range(0,3):
     axis2_array[i].set_ylabel('Temperature', fontsize=20)
     axis_array[i].set_xlabel('Time/minutes', fontsize=20)
 
-
-
-
-
-
-
-
-
 #plt.tight_layout()
-plt.show()
-#plt.savefig('../svg_figures/oscillations_gas_dependence.svg')
+#plt.show()
+plt.savefig('../extracts_from_very_long_oscillation.png')

### 2012-01-11 python_figures/single_full_oscillation.py

@@ -1,6 +1,6 @@
 import matplotlib
 #matplotlib.use('svg')
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
@@ -46,5 +46,5 @@ axis2.set_ylabel('Temperature', fontsize=20)
 axis.set_xlabel('Time/minutes', fontsize=20)
 
 #plt.tight_layout()
-plt.show()
-#plt.savefig('../svg_figures/oscillations_gas_dependence.svg')
+#plt.show()
+plt.savefig('../single_full_oscillation.png')

### 2012-01-11 python_figures/summary_of_long_measurement.py

@@ -4,7 +4,7 @@
 
 import matplotlib
 #matplotlib.use('svg')
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
@@ -46,6 +46,8 @@ periods.append(0)
 for i in range(1,len(oscillations)):
     periods.append(oscillations[i]-oscillations[i-1])
 
+#print len(periods)
+
 fig = plt.figure()
 
 axis = fig.add_subplot(1,1,1)
@@ -65,5 +67,5 @@ axis.set_xlabel('Time/minutes', fontsize=20)
 
 
 #plt.tight_layout()
-plt.show()
-#plt.savefig('../svg_figures/oscillations_gas_dependence.svg')
+#plt.show()
+plt.savefig('../summary_of_long_measurement.png')

### 2012-01-11 python_figures/extracts_from_very_long_oscillation.py
Added preliminary figure showing a measure of the duty cycle of oscillations

@@ -1,6 +1,6 @@
 import matplotlib
 #matplotlib.use('svg')
-matplotlib.use('Agg')
+#matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
@@ -54,5 +54,5 @@ for i in range(0,3):
     axis_array[i].set_xlabel('Time/minutes', fontsize=20)
 
 #plt.tight_layout()
-#plt.show()
-plt.savefig('../extracts_from_very_long_oscillation.png')
+plt.show()
+#plt.savefig('../extracts_from_very_long_oscillation.png')

### 2012-01-11 python_figures/duty_cycles_long_measurement.py
Added preliminary figure showing a measure of the duty cycle of oscillations

@@ -1,0 +1,89 @@
+
+#This will be a simple implementation of a program that summaries the oscillation period as a function of oscillation number
+#We will also need a simple program that summarises duty cycle as a function of oscillation
+
+import matplotlib
+#matplotlib.use('svg')
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import numpy as np
+import MySQLdb
+
+def average(values):
+    """Computes the arithmetic mean of a list of numbers.
+
+    >>> print average([20, 30, 70])
+    40.0
+    """
+    return sum(values, 0.0) / len(values)
+
+
+try:
+    db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+except:
+    db = MySQLdb.connect(host="127.0.0.1", port=9995, user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+
+
+cursor = db.cursor()
+
+data = {}
+#Mass28
+cursor.execute("SELECT x/60000,y*1e9 FROM xy_values_microreactor where measurement = 6133")
+data['M28'] = np.array(cursor.fetchall())
+
+#Mass44
+cursor.execute("SELECT x/60000,y*1e9 FROM xy_values_microreactor where measurement = 6135")
+data['M44'] =  np.array(cursor.fetchall())
+
+#Limit: everytime M44 goes above 4.5nA we start a new oscillation
+i = 0
+old_m44 = 0
+mass_indexes = []
+oscillations = [] #Holds the switching times
+for row in data['M44']:
+    i = i+1
+    if (row[1] > (4.5)) and (old_m44<4.5):
+        oscillations.append(row[0])
+        old_m44 = row[1]
+        mass_indexes.append(i)
+        
+    if (i%10==0):
+        old_m44 = row[1]
+    
+    
+periods = []
+periods.append(0)
+m44_average = []
+m44_average.append(0)
+m28_average = []
+m28_average.append(0)
+for i in range(1,len(oscillations)):
+    periods.append(oscillations[i]-oscillations[i-1])
+    
+    m44_average.append(average(data['M44'][mass_indexes[i-i]:mass_indexes[i],1]))
+    m28_average.append(average(data['M28'][mass_indexes[i-i]:mass_indexes[i],1]))
+
+#print len(periods)
+
[…]

### 2012-01-12 paper.tex
Worked on the introduction and experimental sections

@@
   \begin{@twocolumnfalse}
-\noindent\LARGE{\textbf{Oscillations in CO-oxidation Catalysts at Atmospheric Pressures$^\dag$}}
+\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure$^\dag$}}
 \vspace{0.6cm}
@@
 
-Oxidation of CO is a classic model system for testing catalytic properties of various materials.
-It was shown already in 1985 (REF) that this reaction will show oscilaltory behaviour under UHV conditions due to surface reconstructions having large influence on the catalytic activity of the surface.
-However, this is a phenomenon that is only observed under UHV-condition, under higher pressures these kinds of reconstructions will happen.
-In this paper we show sustained catalytic oscilations on Platinum nano particles that due to their sometimes extremely long time-scales cannot be a surface phenomenon, but must involve a bulk oxidation of the nanoparticle.
-Similar phenomeon of oscillations of CO oxidation Pt has been seen earlier on thin-films \cite{Lund2000}, single crystals \cite{Hendriksen2005} and in macroscopic flow-reactors \cite{Singh2010}, but to our knowledge never before on nano particles.
+Because of its industrial importance CO oxidation on transition metal surfaces has been widely studied as both industrial catalyst and as a model system for testing catalytic properties of materials (REF, Ertl?).
+Despite intensive studies this reaction is still not understood and shows interesting new and interesting features.
+
+It has previously been shown (REF) that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and bare metal surface.
+CO oxidation oscillations on has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.
 
 \section{Experimental Methods}
-The measurents are done in a silicon-fabricated microreactor, developed here at CINF \cite{Henriksen2009}.
-The reactor consists of a two inlets, a long mixing zone for the incoming gases and a reactor of total volume of $240\,$nL.
-The reactor is able to operate at a pressure range og 0-2.5\,bar.
-The gases is supplied through ordinary flow controllers capable of controlling flow in the range of a few mL/min.
-The flow is reduced to a value capable of being fed into a mass-spectrometer by passing most of the flow through an outlet connected to a pressure controller.
-A small part of the flow is led into the reactor chamber and via a $5.4\,\mu$m wide capillary further into UHV chamber equiped with a quadropole mass spectrometer.
-The design ensures that all gas exposed to the catalyst under investigation is also measured in the mass spectrometer ensures a very high sensitivity of the device.
-When an evacuated microreactor is mounted, the base pressure of the UHV chambe is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.
+\subsection{$\mu$-reactors}
+Reaction data was performed in silicon-based microreactors developed in-house \cite{Henriksen2009}.
+The reactor consists of a two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume.
+The reactor is sealed from atmosphere by anodic bonding of a pyrex lid to the silicon reactor is able to operate at a pressure range of 0-2.5\,bar.
+The reaction gases is supplied through flow controllers capable of controlling flow in the range of a 1-10 mL/min.
+The capillary flow fed into a quadropole mass-spectrometer while any extra gas from the inlets are passed through the outlet connected to a pressure controller to control the reactor pressure.
+The design ensures that all gas exposed to the catalyst under investigation is measured by the mass spectrometer ensuring a high sensitivity of the device.
+When an evacuated microreactor is mounted, the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.
 
-The reactor is heated by a Pt heating element evaporated on the backside that at the same time acts as an RTD to measure the temperature.
+The reactor is heated by joule heating of platinum strip evaporated on the backside of the reactor volume.
+The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume.
 
-\section{Sample preparation}
-The samples was made by depositing a very small amount of size-selcted clusters from a quadropole cluster source (REF!) onto the microreactores.
-Typical sizes are in the order of 3-9\,nm and the coverage is kept at approximately 0.1\% geometric coverage, found by measuring the current from the charged clusters landing on the reactor.
-After deposition the reactor is anonicly bonded to a pyrex lid while keeping the reactor area cold by mounting the reactor on a cooling block and heating the rest of the sample to $\sim350\,^\circ$C \cite{Vesborg2010}
+\subsection{Platinum nanoparticle deposition}
+Platinum nanoparticles were deposited from a size-selected cluster source (REF!).
+Clusters are produced by impinging argon ions on a metal target and condensing these in a cold gas.
+The cluster are subsequently size-selected by a quadropole mass selection filter.
+Typical sizes are 3-9\,nm and the coverage is kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor.
+After deposition the reactor is anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles.
 

### 2012-01-16 paper.tex
Figures are now MUCH closer to be of publishable quality

@@
   \centering
-  \includegraphics[height=7cm]{single_full_oscillation.png}
+  \includegraphics[width=17cm]{single_full_oscillation.png}
   \caption{A full oscillation first showing a steep ignition of the sample followed by an almost imidiately de-activation of the sample.
-For the next 65\,minutes the sample slowly recovers activity until it again lights off completely.}
+For the next 65 minutes the sample slowly recovers activity until it again lights off completely.}
   \label{fgr:full_oscillation}
@@
 
-If a sample is leaved for long periods of time, it keep performing sustained oscillations, but with longer and longer periods.
+If a sample is leaved for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods.
 In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods.
@@
 \centering
-  \includegraphics[height=7cm]{summary_of_long_measurement.png}
-  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample a total for 439 oscillations in 4 days.}
+  \includegraphics[width=9cm]{summary_of_long_measurement.png}
+  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
   \label{fgr:long_measurement}
@@
 % an example of a two-column figure, remember that the graphics should be included where it is first referenced
-\begin{figure*}
+\begin{figure}[h]
   \centering
-  \includegraphics[height=7cm]{extracts_from_very_long_oscillation.png}
+  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
   \caption{Extracts from the 4 day long experiment.}
   \label{fgr:extracts}
-\end{figure*}
+\end{figure}
 

### 2012-01-16 python_figures/extracts_from_very_long_oscillation.py

@@ -1,6 +1,6 @@
 import matplotlib
 #matplotlib.use('svg')
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
@@ -27,32 +27,46 @@ cursor.execute("SELECT x/60000,y FROM xy_values_microreactor where measurement =
 data['TEMPERATURE'] = np.array(cursor.fetchall())
 
 fig = plt.figure()
+fig.subplots_adjust(bottom=0.1) # Make room for x-label
+fig.subplots_adjust(right=0.85) # Make room for right y-label
+#ratio = 0.61803398              # Golden mean
+ratio = 1
+fig_width = 9
+fig_width = fig_width /2.54     # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
+
 axis_array = []
 axis2_array = []
 
 limit = []
-limit.append((700,900))
-limit.append((2800,3000))
-limit.append((5800,6000))
+#limit.append((700,900))
+limit.append((700,800))
+#limit.append((2800,3000))
+limit.append((2800,2900))
+#limit.append((5800,6000))
+limit.append((5900,6000))
 
 for i in range(0,3):
     axis_array.append(fig.add_subplot(3,1,i+1))
     axis_array[i].plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
-    axis_array[i].plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'b-')
+    axis_array[i].plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
     axis_array[i].set_ylim(0,7)
     axis2_array.append(axis_array[i].twinx())
-    axis2_array[i].plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'k-')
-    axis2_array[i].set_ylim(181,230)
+    axis2_array[i].plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'b-')
+    axis2_array[i].set_ylim(181,229)
     axis_array[i].set_xlim(limit[i])
+    axis_array[i].set_yticks((1,3,5))
     
-    axis_array[i].tick_params(direction='in', length=6, width=2, colors='k',labelsize=14,axis='both',pad=5)
[…]

### 2012-01-16 python_figures/single_full_oscillation.py

@@ -28,23 +28,38 @@ data['TEMPERATURE'] = np.array(cursor.fetchall())
 
 
 fig = plt.figure()
+fig.subplots_adjust(bottom=0.2) # Make room for x-label
+
+#ratio = 0.61803398           # Golden mean
+ratio = 0.4                  # This figure should be very wide to span two columns
+fig_width = 17
+fig_width = fig_width /2.54        # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
 
 axis = fig.add_subplot(1,1,1)
 axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
-axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'b-')
+axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
 axis.set_ylim(0.1,1.2)
 axis2 = axis.twinx()
-axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'k-')
+axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'b-')
 axis2.set_ylim(160,205)
+axis2.set_yticks((170,180,190,200))
 axis.set_xlim(1001,1133)
 axis.grid(True)    
 
-axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=14,axis='both',pad=5)
+arrow = dict(facecolor='black', shrink=0.085,width=1)
+axis.annotate('M28', xy=(1040, 0.83),  xycoords='data', xytext=(1058, 0.93), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('M44', xy=(1040, 0.41),  xycoords='data', xytext=(1058, 0.27), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('Temp.', xy=(1070, 1.08),  xycoords='data', xytext=(1095, 0.93), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 
-axis.set_ylabel('SEM Current / nA', fontsize=20)
-axis2.set_ylabel('Temperature', fontsize=20)
-axis.set_xlabel('Time/minutes', fontsize=20)
[…]

### 2012-01-16 python_figures/summary_of_long_measurement.py

@@ -49,23 +49,30 @@ for i in range(1,len(oscillations)):
 #print len(periods)
 
 fig = plt.figure()
+fig.subplots_adjust(bottom=0.2) # Make room for x-label
+ratio = 0.61803398              # Golden mean
+fig_width = 9
+fig_width = fig_width /2.54     # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
+
 
 axis = fig.add_subplot(1,1,1)
-axis.plot(oscillations, periods, 'bo')
+axis.plot(oscillations, periods, 'b.')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
 #axis.set_ylim(0,7)
 #axis.set_xlim(0,500)
 
-axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=14,axis='both',pad=5)
+axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=10,axis='both',pad=3)
 axis.grid(True)    
 
 #axis.set_ylabel('SEM Current / nA', fontsize=20)
-axis.set_ylabel('Oscillations periods / minutes', fontsize=20)
-axis.set_xlabel('Time/minutes', fontsize=20)
+axis.set_ylabel('Oscil. period / minutes', fontsize=10)
+axis.set_xlabel('Time/minutes', fontsize=10)
 
 
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../summary_of_long_measurement.png')
+plt.savefig('../summary_of_long_measurement.png',dpi=300)

### 2012-02-02 paper.tex
Added content and a figure to the experimental section. Moved a reference from the complete list to the actual reference list

@@
 
-\noindent \normalsize{The abstract should be a single paragraph which summarises the content of the article.
-Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].}
+\noindent \normalsize{High-quality mass spectrometry of the oscillatory behaviour of CO oxidation on supported Pt-nanoparticles is presented.
+It is demonstrated that the oscillations can continue self-sustained for several days.
+It is demonstrated that the oscillations exhibits a well defined frequency which is slowly developing towards lower freqeuncy.}
+%Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
 \vspace{0.5cm}
@@
 
-It has previously been shown (REF) that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and bare metal surface.
+It has previously been shown that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and bare metal surface.
 CO oxidation oscillations on has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.
@@
 Reaction data was performed in silicon-based microreactors developed in-house \cite{Henriksen2009}.
-The reactor consists of a two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume.
-The reactor is sealed from atmosphere by anodic bonding of a pyrex lid to the silicon reactor is able to operate at a pressure range of 0-2.5\,bar.
-The reaction gases is supplied through flow controllers capable of controlling flow in the range of a 1-10 mL/min.
-The capillary flow fed into a quadropole mass-spectrometer while any extra gas from the inlets are passed through the outlet connected to a pressure controller to control the reactor pressure.
+The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume.
+The reactor is sealed from atmosphere by anodic bonding a pyrex lid to the silicon reactor, it is able to operate at a pressure range of 0-2.5\,bar.
+The reaction gases is supplied through flow controllers capable of controlling flow in the range of 0-10 mL/min.
+The capillary flow is fed into a quadropole mass-spectrometer while any extra gas from the inlets are passed directly through to the outlet connected to a pressure controller to control the reactor pressure.
 The design ensures that all gas exposed to the catalyst under investigation is measured by the mass spectrometer ensuring a high sensitivity of the device.
@@
 The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume.
+An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement doing operation.
+
+The system is fully automized, allowing for measurements of several days without human intervention. This allows for very self-consistent measurements of many samples.
+
+A typical oscillation maesurement is done by mounting a sample in setup directly after cluster deposition and anodic bonding.
+A typical measurement will involve an initial light-off CO-oxidation measurement, where the temperature is slowly increased up until the sample ignites and achieves full conversion of the CO.
+At the typical conditions (O:CO ratio of typically $\sim13$ and Pt-coverage of $\sim0.1\%$) lighoff happens around 180$^\circ$C, the ramp is typically continued up to 260$^\circ$C whereafter the temperature is lowered at the same rate as the heating (typically 3$^\circ$C/min).
+A typical initial treatment is seen in figurefigure~\ref{fgr:initial_treatment} Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
+Sustained oscillations is then achieved by following the same heathing ramp up to a fixed temperature and then the temperature is kept constant for the remaing period of the measurement.
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{initial_treatment.png}
+  \caption{A typical example of the initial treatment of a new sample.}
+  \label{fgr:initial_treatment}
+\end{figure}
 
@@
 \section{Results}
-The experiments was carried out ....
+During the experiments we have tried a large number of samples, and it is evident that the oscillation phenomenon is rather easy to reproduce.
+In agreement with litterature\cite{Singh2010} (FLERE REFS), we find that a very high oxygen concentration (on the order of 13:1) is needed to get the oscillations running, most likely because the much higher sticking coefficient of CO would otherwise result in a completely CO poisoned sample doing the low-reactivity region of the cycle.
+In our setup we also found that we need a very low coverage on the order 0.1\% of nano-particles to achive consistent oscillations.
+This is for sure an artifact of our very small reactor, since other groups have seen oscillations on both extended thin-films \cite{Singh2010} as well as on single crystals (REF TIL FRENKEN).
 
 The period of the oscillations ranges from a few seconds (the time-constant of the reactor) up to more than an hour.
-A typical slow is oscillation is seen in figure~\ref{fgr:full_oscillation} where we see the typical pattern going from almost no activity slowly up towards $\sim$50\% conversion at which point the sample light off to full conversion almost instantiously where after a short peiod of time the sample again de-activates.
+A slow is oscillation is seen in figure~\ref{fgr:full_oscillation} where we see the typical pattern going from almost no activity slowly up towards $\sim$50\% conversion at which point the sample light off to full conversion almost instantiously where after a short peiod of time the sample again de-activates.
 % an example of a two-column figure, remember that the graphics should be included where it is first referenced
@@
 
-If a sample is leaved for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods.
+If a sample is leaved at constant temperature for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods.
 In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods.
@@
 
-Extracts of the mass-spectrometry from the very beginning, the middle and towards the end of the experiments is shown in figure~\ref{fgr:extracts}, it is evident that the oscillations are getting more and more irregular as times goes on, towards the end, it is also clearly visible how the smaller oscillations are taking place at a much higher frequency than the full on-off cycles, which is most likely the explanation for the increasing scatter in the period summary.
+Extracts of the mass-spectrometry from the very beginning, the middle and towards the end of the experiments is shown in figure~\ref{fgr:extracts}, it is evident that the oscillations are getting more and more irregular as times goes on.
+Towards the end, it is also clearly visible how  oscillations with smaller amplitude are taking place at a much higher frequency than the full on-off cycles, which is most likely the explanation for the increasing scatter in the period summary, sometimes the smaller oscillations will trigger a full switch, and sometimes it will not, thus introducing more short-period oscillations despite the trend of slower and slower oscillations.
 % an example of a two-column figure, remember that the graphics should be included where it is first referenced
@@
 
-Several different samples deposited at various diffent sizes and amounts all show the oscillating bahaviour.
-Repeatability is high regarding running long experiments on a single sample, but very low from sample to sample.
-
 \section{Discussion}
 Due to long timescales involved which are much larger than any typically orcurring timescales for such a small system, there can be little doubt that this phenomenon involves some kind of reaction involving the bulk of the nano particles.
+Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.
 
@@
 
-\section{Equations}
+%\section{Equations}
 
-Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:
+%Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:
 
- \[ A = \pi r^2 \]
+% \[ A = \pi r^2 \]
 
-\begin{equation}
-  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
-\end{equation}
+%\begin{equation}
+%  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
+%\end{equation}
 
-\section{Graphics and tables}
-\subsection{Graphics}
-Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).
+%\section{Graphics and tables}
+%\subsection{Graphics}
+%Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).
 
-\subsection{Tables}
-Tables typeset in RSC house style do not include vertical lines.
+%\subsection{Tables}
+%Tables typeset in RSC house style do not include vertical lines.
 Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table.
@@
 
-\begin{table}[h]
-\small
-  \caption{\ An example of a caption to accompany a table}
-  \label{tbl:example}
-  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
-    \hline
-    Header one/units & Header two & Header three \\
-    \hline
-    1 & 2 & 3 \\
-    4 & 5 & 6 \\
-    7 & 8 & 9 \\
-    10 & 11 & 12 \\
-    \hline
-  \end{tabular*}
-\end{table}
+%\begin{table}[h]
+%\small
+%  \caption{\ An example of a caption to accompany a table}
+%  \label{tbl:example}
+%  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
+%    \hline
+%    Header one/units & Header two & Header three \\
+%    \hline
+%    1 & 2 & 3 \\
+%    4 & 5 & 6 \\
+%    7 & 8 & 9 \\
+%    10 & 11 & 12 \\
+%    \hline
+%  \end{tabular*}
+%\end{table}
 
-Adding notes to tables can be complicated.  Perhaps the easiest
-method is to generate these manually.
+%Adding notes to tables can be complicated.  Perhaps the easiest
+%method is to generate these manually.
 
@@
 
-You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
-The \texttt{mhchem} package can also be used so
-that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.
+%You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
+%The \texttt{mhchem} package can also be used so
+%that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.
 
-\section{Conclusions}
-The conclusions section should come at the end of article.
+%\section{Conclusions}
+%The conclusions section should come at the end of article.
 For the reference section, the style file rsc.bst can be used to generate the correct reference style.\footnote[4]{Footnotes should appear here.

### 2012-02-02 python_figures/initial_treatment.py

@@ -1,0 +1,64 @@
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import numpy as np
+import MySQLdb
+
+try:
+    db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+except:
+    db = MySQLdb.connect(host="127.0.0.1", port=9995, user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+
+
+cursor = db.cursor()
+
+data = {}
+#Mass28
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactor where measurement = 6133")
+data['M28'] = np.array(cursor.fetchall())
+
+#Mass44
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactor where measurement = 6135")
+data['M44'] =  np.array(cursor.fetchall())
+
+#Temperature
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactor where measurement = 6139")
+data['TEMPERATURE'] = np.array(cursor.fetchall())
+
+
+fig = plt.figure()
+fig.subplots_adjust(bottom=0.2) # Make room for x-label
+fig.subplots_adjust(right=0.85) # Make room for second y-label
+
+ratio = 0.61803398           # Golden mean
+fig_width = 9
+fig_width = fig_width /2.54        # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
+
+axis = fig.add_subplot(1,1,1)
+axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
+axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
+axis.set_ylim(0,8)
+axis2 = axis.twinx()
+axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'b-')
+axis2.set_ylim(0,300)
+#axis2.set_yticks((170,180,190,200))
+axis.set_xlim(100,800)
+axis.grid(True)    
+
+arrow = dict(facecolor='black', shrink=0.085,width=1)
+axis.annotate('M28', xy=(260, 2.6),  xycoords='data', xytext=(185, 3.5), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
[…]

### 2012-02-02 paper.tex
Added a bit of content to the results section

@@
 During the experiments we have tried a large number of samples, and it is evident that the oscillation phenomenon is rather easy to reproduce.
-In agreement with litterature\cite{Singh2010} (FLERE REFS), we find that a very high oxygen concentration (on the order of 13:1) is needed to get the oscillations running, most likely because the much higher sticking coefficient of CO would otherwise result in a completely CO poisoned sample doing the low-reactivity region of the cycle.
+In agreement with litterature\cite{Singh2010,Hendriksen2005}, we find that a very high oxygen concentration (on the order of 13:1) is needed to get the oscillations running, most likely because the much higher sticking coefficient of CO would otherwise result in a completely CO poisoned sample doing the low-reactivity region of the cycle.
 In our setup we also found that we need a very low coverage on the order 0.1\% of nano-particles to achive consistent oscillations.
-This is for sure an artifact of our very small reactor, since other groups have seen oscillations on both extended thin-films \cite{Singh2010} as well as on single crystals (REF TIL FRENKEN).
+This is for sure an artifact of our very small reactor, since other groups have seen oscillations on both extended thin-films \cite{Singh2010} as well as on single crystals\cite{Hendriksen2005}.
 
@@
 
+Most measurements where done at 1\,bar, however no clear pressure dependence is seen within a pressure range of at least 0.1\,bar to 1\,bar, the oscillations neither change their period nor qualitative behaviour significantly.
+Similarly, only a rather weak dependence on the CO pressure is seen.
+Oscillations is barely visible in the mass-spectrometry from a CO-concentration of $\sim0.025$ and is then seen up to concentrations of $\sim0.175$.
+A tendendcy towards slower oscillations for higher CO-concentrations is seen, but the effect is not very large.
+
 If a sample is leaved at constant temperature for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods.
@@
 Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days.
+Analysing the on/off ratio of the oscillations doing the full period of time shows that the ratio is unaffected across the entire period of the measurement, the oscillations are qualititively almost identical even though the period is changed by a factor of 10 doing the measurement.
 % an example of a single-column figure, remember that the graphics should be included where it is first referenced
@@
 Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.
+
+The exact mechanisum of CO oxidation on Pt is still under debate, but concesus seems to be, that the most active phase is a skin of Pt-oxide on top of metallic Pt. ..... .... ... ...
+
+The phenomenon of increasing oscillation period over time is completely consistent across all measured samples, and it must originate from a real physical phenomen.
+A possible explanation of the phenomenon could be sintering or roughening of the clusters.
 

### 2012-02-07 paper.tex
Include changes on paper.tex

--- 2012-02-02 paper.tex
@@
 
-\noindent \normalsize{High-quality mass spectrometry of the oscillatory behaviour of CO oxidation on supported Pt-nanoparticles is presented.
-It is demonstrated that the oscillations can continue self-sustained for several days.
-It is demonstrated that the oscillations exhibits a well defined frequency which is slowly developing towards lower freqeuncy.}
+\noindent \normalsize{In the current paper high-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented.
+The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio.
+The frequency of the oscillations tends to increase in with time while the duty cycle remains constant.}
 %Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
@@
 
-\footnotetext{\textit{$^{a}$~DTU Physics, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
-\footnotetext{\textit{$^{b}$~DTU Physics, Fysikvej 312, 2800 Lyngby, Denmark}}
+\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
+\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}
 
@@
 
-Because of its industrial importance CO oxidation on transition metal surfaces has been widely studied as both industrial catalyst and as a model system for testing catalytic properties of materials (REF, Ertl?).
-Despite intensive studies this reaction is still not understood and shows interesting new and interesting features.
+CO oxidation is one of the most studied reactions due to its importance in both automotive catalysis and in the removal of trace CO in hydrogen streams.
+A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
+Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active (under-coordinated?) sites.
 
-It has previously been shown that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and bare metal surface.
-CO oxidation oscillations on has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.
+Here we report oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure.
+It has previously been shown that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
+CO oxidation oscillations has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.
 
 \section{Experimental Methods}
-\subsection{$\mu$-reactors}
-Reaction data was performed in silicon-based microreactors developed in-house \cite{Henriksen2009}.
+\subsection{Reactor setup}
+The experiments were performed in silicon-based $\mu$-reactors \cite{Henriksen2009}.
 The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume.
-The reactor is sealed from atmosphere by anodic bonding a pyrex lid to the silicon reactor, it is able to operate at a pressure range of 0-2.5\,bar.
+The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar.
 The reaction gases is supplied through flow controllers capable of controlling flow in the range of 0-10 mL/min.
-The capillary flow is fed into a quadropole mass-spectrometer while any extra gas from the inlets are passed directly through to the outlet connected to a pressure controller to control the reactor pressure.
-The design ensures that all gas exposed to the catalyst under investigation is measured by the mass spectrometer ensuring a high sensitivity of the device.
-When an evacuated microreactor is mounted, the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and when operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar.
+The capillary flow is fed into a quadropole mass-spectrometer for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller to control the reactor pressure.
+The design ensures that all gases exposed to the catalyst under investigation is measured by the mass spectrometer ensuring an extremely high sensitivity of the system.
 
-The reactor is heated by joule heating of platinum strip evaporated on the backside of the reactor volume.
+Before any measurements are performed the reactor is pumped by a turbopump minimizing contaminants in the system.
+When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar in the mass spectrometer chamber.
+
+The reactor is heated by joule heating of a platinum strip evaporated on the backside of the reactor volume.
 The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume.
-An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement doing operation.
+An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
 
-The system is fully automized, allowing for measurements of several days without human intervention. This allows for very self-consistent measurements of many samples.
-
-A typical oscillation maesurement is done by mounting a sample in setup directly after cluster deposition and anodic bonding.
-A typical measurement will involve an initial light-off CO-oxidation measurement, where the temperature is slowly increased up until the sample ignites and achieves full conversion of the CO.
-At the typical conditions (O:CO ratio of typically $\sim13$ and Pt-coverage of $\sim0.1\%$) lighoff happens around 180$^\circ$C, the ramp is typically continued up to 260$^\circ$C whereafter the temperature is lowered at the same rate as the heating (typically 3$^\circ$C/min).
-A typical initial treatment is seen in figurefigure~\ref{fgr:initial_treatment} Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
-Sustained oscillations is then achieved by following the same heathing ramp up to a fixed temperature and then the temperature is kept constant for the remaing period of the measurement.
-\begin{figure}[h]
-\centering
-  \includegraphics[width=9cm]{initial_treatment.png}
-  \caption{A typical example of the initial treatment of a new sample.}
-  \label{fgr:initial_treatment}
-\end{figure}
+The gas handling including flow and pressured controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention.
+This allows for very self-consistent measurements of many samples.
 
@@
 
+BEMÆRK!
+Denne tekst er nakket fra et tidligere paper (Carbon,2011).
+Pre-formed mass-selected platinum particles were soft-landed onto the reactor at room temperature using an inert gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
+The particles are formed by gas-phase condensation from a ﬂux of platinum atoms that are sputtered from a 99.99\,\% pure Ru target using a magnetron sputter source.
+The magnetron is housed in a liquid nitrogen cooled enclosure with a 3 mm diameter aperture at one end.
+Argon gas is ﬂown into the volume around the magnetron at a rate of 10–120 sccm and is pumped away via the aperture so that a local pressure of 0.1–1 mbar is obtained inside the gas-aggregation zone during operation.
+The cooled argon gas thermalises the sputtered platinum atoms so that they condense into clusters, which further coalesce to form nanoparticles.
+The size of the nanoparticles is determined by a number of factors such as magnetron sputter power (typically 20–40 W), rate of gas flow, distance between the target and the exit aperture and the diameter of the exit aperture.
+Platinum nanoparticles with diameters in the range of 2–16 nm can be produced using the source \cite{Nielsen2010,Nielsen2009}.
+The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further reﬁned by a skimmer.
+The nanoparticle beam is then passed through a quadrupole mass ﬁlter where the ionised fraction (60–80\,\%) of the nanoparticles can be ﬁltered according to their mass-to-charge ratio.
+
 \section{Results}
-During the experiments we have tried a large number of samples, and it is evident that the oscillation phenomenon is rather easy to reproduce.
-In agreement with litterature\cite{Singh2010} (FLERE REFS), we find that a very high oxygen concentration (on the order of 13:1) is needed to get the oscillations running, most likely because the much higher sticking coefficient of CO would otherwise result in a completely CO poisoned sample doing the low-reactivity region of the cycle.
-In our setup we also found that we need a very low coverage on the order 0.1\% of nano-particles to achive consistent oscillations.
-This is for sure an artifact of our very small reactor, since other groups have seen oscillations on both extended thin-films \cite{Singh2010} as well as on single crystals (REF TIL FRENKEN).
+An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding.
+Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
+At O$_2$:CO ratio of $\sim13$ and a geometrical Pt-coverage of $\sim0.1\,\%$ lightoff occurs at approximately 180\,$^\circ$C.
+The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating.
+After the initial lightoff the sample is cooled to room temperature.
+When at low temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur.
+A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen.
+Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{initial_treatment.png}
+  \caption{A typical example of the initial treatment of a new sample.
+After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
+  \label{fgr:initial_treatment}
+\end{figure}
+The quantitative same behavior has been reproduced on a large number of samples where oscillations also occur.
+Generally the oscillations have been seen on samples in a wide coverage and particle size regime, however, a geometrical nanoparticle coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.
 
-The period of the oscillations ranges from a few seconds (the time-constant of the reactor) up to more than an hour.
-A slow is oscillation is seen in figure~\ref{fgr:full_oscillation} where we see the typical pattern going from almost no activity slowly up towards $\sim$50\% conversion at which point the sample light off to full conversion almost instantiously where after a short peiod of time the sample again de-activates.
-% an example of a two-column figure, remember that the graphics should be included where it is first referenced
+The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim$7\,s.) up to more than an hour.
+An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
+After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
+After the deactivation the sample quickly regains $\sim$30\,\% conversion.
+Hereafter the conversion increases linearly with time until approximately 50 \,\% conversion is reached.
+Shortly after reaching 50 \,\% conversion the sample again ignites and covert all CO to CO$_$2.
+After a short full conversion period the sample again deactivates and the cycle repeats itself.
 \begin{figure*}
@@
   \includegraphics[width=17cm]{single_full_oscillation.png}
-  \caption{A full oscillation first showing a steep ignition of the sample followed by an almost imidiately de-activation of the sample.
-For the next 65 minutes the sample slowly recovers activity until it again lights off completely.}
+  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample.
+For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.}
   \label{fgr:full_oscillation}
 \end{figure*}
+Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations.
+In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found.
+The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}.
+Similarly, only a weak dependence on the CO/O$_$2 pressure was observed.
+At a CO/O$_$2 ratio of $\sim0.025$ only very small amplitude oscillations were observed.
+Increasing the CO/O$_$2 to $\sim0.175$ showed a clear oscillations with a clear increase in oscillation amplitude compared to lower CO concentrations as observed by the mass spectrometer data.
+Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.
 
-If a sample is leaved at constant temperature for long periods of time, it keeps performing sustained oscillations, but with longer and longer periods.
-In the beginning the period is very stable and sligtly increasing but after a few days, the periods becomes more and more noisy although still maintaining the trend of longer and longer periods.
-Figure~\ref{fgr:full_oscillation} shows a summary of the periods of a sample oscillating for 4 days.
-% an example of a single-column figure, remember that the graphics should be included where it is first referenced
+After the initial lightoff experiment the nanoparticles show stable self-sustained oscillation.
+After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}.
+Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time.
+Hereafter the oscillations is more irregular which is evident from Figure~\ref{fgr:long_measurement}.
+At experiment end the oscillation period is between 45 and 20 minutes.
 \begin{figure}[h]
@@
 
-Extracts of the mass-spectrometry from the very beginning, the middle and towards the end of the experiments is shown in figure~\ref{fgr:extracts}, it is evident that the oscillations are getting more and more irregular as times goes on.
-Towards the end, it is also clearly visible how  oscillations with smaller amplitude are taking place at a much higher frequency than the full on-off cycles, which is most likely the explanation for the increasing scatter in the period summary, sometimes the smaller oscillations will trigger a full switch, and sometimes it will not, thus introducing more short-period oscillations despite the trend of slower and slower oscillations.
-% an example of a two-column figure, remember that the graphics should be included where it is first referenced
+Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from a four day measurement.
+Here data from shortly after the initial treatment, after 2800\,min.
+of oscillation time and after 5900\,min.
+are shown.
+After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
+Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
 \begin{figure}[h]
@@
   \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
-  \caption{Extracts from the 4 day long experiment.}
+  \caption{Extracts from the 4 day long experiment.
+The oscillation period become more irregular with time while the on/off ratio remains constant.
+Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
   \label{fgr:extracts}
@@
 
+The oscillation period becomes more irregular with progressing experiment time although the on/off ratio remains constant during the entire experiment time.
+Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure \ref{fgr:full_oscillation}.
+A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered.
+At approximately 50\,\% conversion lightoff occurs and the sample is in full conversion.
+
 \section{Discussion}
-Due to long timescales involved which are much larger than any typically orcurring timescales for such a small system, there can be little doubt that this phenomenon involves some kind of reaction involving the bulk of the nano particles.
-Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.
+The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175.
+Richer CO mixtures than 0.175 could did produce any oscillations in our system.
+The very oxygen rich mixture needed to provoke oscillations agrees with literature \cite{Singh2010,Hendriksen2005}.
+The is most likely due to the much higher sticking coefficient of CO on platinum which poisons the nanoparticles during the low reactivity region of the cycle.
+
+Although a range of different CO/O$_2$ ratios were tried no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system.
+This is not, however, believed to be a property of the platinum thin film but a property of the small reactor used in this study.
+This is supported by literature where oscillations have been observed on both extended thin-films \cite{Singh2010} as well as on single crystals \cite{Hendriksen2005} at atmospheric pressure.
+
+Due to long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds.
+It is hence hypothesized that the oscillations is a feature related to the nanoparticles.
+The particles are maybe oxidized?
+Subsurface, totally oxidized etc.
+Digt en smuk historie om dette...
+
+%Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.
+
+The oscillation period increases with time and becomes increasingly less stable as shown in Figure \ref{fgr:extracts} is consistent across all measured samples.
+The large scattter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
+Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
+A possible explanation of the phenomenon could be sintering or roughening of the clusters.
+Skriv noget mere her...
 

### 2012-02-07 paper.tex
Corrected a few typos and added some references

@@
 
-BEMÆRK!
+BEMAERK!
 Denne tekst er nakket fra et tidligere paper (Carbon,2011).
 Pre-formed mass-selected platinum particles were soft-landed onto the reactor at room temperature using an inert gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
-The particles are formed by gas-phase condensation from a ﬂux of platinum atoms that are sputtered from a 99.99\,\% pure Ru target using a magnetron sputter source.
-The magnetron is housed in a liquid nitrogen cooled enclosure with a 3 mm diameter aperture at one end.
-Argon gas is ﬂown into the volume around the magnetron at a rate of 10–120 sccm and is pumped away via the aperture so that a local pressure of 0.1–1 mbar is obtained inside the gas-aggregation zone during operation.
+The particles are formed by gas-phase condensation from a flux of platinum atoms that are sputtered from a 99.99\% pure Ru target using a magnetron sputter source.
+The magnetron is housed in a liquid nitrogen cooled enclosure with a 3\,mm diameter aperture at one end.
+Argon gas is flown into the volume around the magnetron at a rate of 10-120 sccm and is pumped away via the aperture so that a local pressure of 0.1-1 mbar  is obtained inside the gas-aggregation zone during operation.
 The cooled argon gas thermalises the sputtered platinum atoms so that they condense into clusters, which further coalesce to form nanoparticles.
@@
 Platinum nanoparticles with diameters in the range of 2–16 nm can be produced using the source \cite{Nielsen2010,Nielsen2009}.
-The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further reﬁned by a skimmer.
-The nanoparticle beam is then passed through a quadrupole mass ﬁlter where the ionised fraction (60–80\,\%) of the nanoparticles can be ﬁltered according to their mass-to-charge ratio.
+The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further refined by a skimmer.
+The nanoparticle beam is then passed through a quadrupole mass filter where the ionised fraction (60-80\%) of the nanoparticles can be filtered according to their mass-to-charge ratio.
 
@@
 Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
-At O$_2$:CO ratio of $\sim13$ and a geometrical Pt-coverage of $\sim0.1\,\%$ lightoff occurs at approximately 180\,$^\circ$C.
+At O$_2$:CO ratio of $\sim13$ and a geometrical Pt-coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C.
 The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating.
@@
 
-The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim$7\,s.) up to more than an hour.
+The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
 An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
 After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
-After the deactivation the sample quickly regains $\sim$30\,\% conversion.
-Hereafter the conversion increases linearly with time until approximately 50 \,\% conversion is reached.
-Shortly after reaching 50 \,\% conversion the sample again ignites and covert all CO to CO$_$2.
+After the deactivation the sample quickly regains $\sim$30\% conversion.
+Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached.
+Shortly after reaching 50\% conversion the sample again ignites and covert all CO to CO$_2$.
 After a short full conversion period the sample again deactivates and the cycle repeats itself.
@@
 The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}.
-Similarly, only a weak dependence on the CO/O$_$2 pressure was observed.
-At a CO/O$_$2 ratio of $\sim0.025$ only very small amplitude oscillations were observed.
-Increasing the CO/O$_$2 to $\sim0.175$ showed a clear oscillations with a clear increase in oscillation amplitude compared to lower CO concentrations as observed by the mass spectrometer data.
+Similarly, only a weak dependence on the CO/O$_2$ pressure was observed.
+At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed.
+Increasing the CO/O$_2$ to $\sim0.175$ showed a clear oscillations with a clear increase in oscillation amplitude compared to lower CO concentrations as observed by the mass spectrometer data.
 Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.
@@
 The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175.
-Richer CO mixtures than 0.175 could did produce any oscillations in our system.
+Richer CO mixtures than 0.175 did not produce any oscillations in our system.
 The very oxygen rich mixture needed to provoke oscillations agrees with literature \cite{Singh2010,Hendriksen2005}.
@@
 Digt en smuk historie om dette...
+It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theoretical studies \cite{Gong2004} that the activity of Pt towards CO oxidation at high pressures is highly dependent on the oxidation state of the surface.
 

### 2012-02-08 paper.tex
A quick proof-read of the paper

@@
 \section{Experimental Methods}
-\subsection{Reactor setup}
-The experiments were performed in silicon-based $\mu$-reactors \cite{Henriksen2009}.
+\subsection{Reactor}
+The experiments were performed in silicon-based 20x15 mm $\mu$-reactors \cite{Henriksen2009}.
 The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume.
 The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar.
-The reaction gases is supplied through flow controllers capable of controlling flow in the range of 0-10 mL/min.
-The capillary flow is fed into a quadropole mass-spectrometer for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller to control the reactor pressure.
-The design ensures that all gases exposed to the catalyst under investigation is measured by the mass spectrometer ensuring an extremely high sensitivity of the system.
+The reaction gases is supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min.
+The capillary flow is fed into a quadropole mass-spectrometer for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
+The design makes sure that all gases exposed to the catalyst under investigation is measured by the mass spectrometer ensuring an extremely high sensitivity of the system.
 
-Before any measurements are performed the reactor is pumped by a turbopump minimizing contaminants in the system.
-When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operating at $1\,$bar in the reactor the pressure is $\sim5\times10^{-7}\,$mbar in the mass spectrometer chamber.
+Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.
+When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the mass spectrometer chamber.
 
 The reactor is heated by joule heating of a platinum strip evaporated on the backside of the reactor volume.
-The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor volume.
+The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor.
 An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
@@
 \subsection{Platinum nanoparticle deposition}
-Platinum nanoparticles were deposited from a size-selected cluster source (REF!).
-Clusters are produced by impinging argon ions on a metal target and condensing these in a cold gas.
-The cluster are subsequently size-selected by a quadropole mass selection filter.
-Typical sizes are 3-9\,nm and the coverage is kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor.
-After deposition the reactor is anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles.
+Platinum nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
+Platinum clusters were formed by gas-phase condensation of platinum atoms produced by impinging argon ions on a 99.99\,\% platinum target in a magnetron sputter source.
+After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
+Using this setup platinum nanoparticles with diameters in the range of 2–16 nm can be produced \cite{Nielsen2010,Nielsen2009}.
+The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor.
+The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition.
+After deposition the reactors were anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
 
-BEMAERK!
+%BEMAERK!
 Denne tekst er nakket fra et tidligere paper (Carbon,2011).
@@
 Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
-At O$_2$:CO ratio of $\sim13$ and a geometrical Pt-coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C.
-The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating.
+At O$_2$:CO ratio of $\sim0.08$ and a geometrical platinum coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C.
+The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp.
 After the initial lightoff the sample is cooled to room temperature.
-When at low temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur.
+When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur.
 A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen.
@@
 \end{figure*}
-Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations.
+
+Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations as a function of pressure.
 In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found.
@@
 At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed.
-Increasing the CO/O$_2$ to $\sim0.175$ showed a clear oscillations with a clear increase in oscillation amplitude compared to lower CO concentrations as observed by the mass spectrometer data.
+Increasing the CO/O$_2$ to $\sim0.175$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
 Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.
@@
 Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time.
-Hereafter the oscillations is more irregular which is evident from Figure~\ref{fgr:long_measurement}.
+Hereafter the oscillations is more irregular which as shown in Figure~\ref{fgr:long_measurement}.
 At experiment end the oscillation period is between 45 and 20 minutes.
@@
 Richer CO mixtures than 0.175 did not produce any oscillations in our system.
-The very oxygen rich mixture needed to provoke oscillations agrees with literature \cite{Singh2010,Hendriksen2005}.
-The is most likely due to the much higher sticking coefficient of CO on platinum which poisons the nanoparticles during the low reactivity region of the cycle.
+CO/O$_2$ ratios lower than 0.175 were needed to provoke oscillations in our system.
+This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
+The low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on platinum which poisons the nanoparticle surface during the low reactivity region of the cycle.
+Once poisoned, an increase in temperature would be necessary to ignite the reaction again.
 
@@
 
-Due to long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds.
-It is hence hypothesized that the oscillations is a feature related to the nanoparticles.
+Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds.
+It is hence concluded that the oscillations is a feature related to the nanoparticles.
 The particles are maybe oxidized?
@@
 Digt en smuk historie om dette...
-It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theoretical studies \cite{Gong2004} that the activity of Pt towards CO oxidation at high pressures is highly dependent on the oxidation state of the surface.
+It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theoretical studies \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
 
@@
 
-The oscillation period increases with time and becomes increasingly less stable as shown in Figure \ref{fgr:extracts} is consistent across all measured samples.
+The oscillation period increases with time and becomes increasingly less stable as shown in Figure \ref{fgr:extracts}.
+This phenomena is consistent across all measured samples with approximately the oscillation period evolution with time.
 The large scattter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.

### 2012-02-11 paper.tex
Added a (not 100% complete) figure showing the extreme temperature dependence

@@
   \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample.
-For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.}
+For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.
+This extremely long oscillation period is not commonly seen and was a result of carefull parameter tuning.
+Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.}
   \label{fgr:full_oscillation}
@@
 The oscillation period becomes more irregular with progressing experiment time although the on/off ratio remains constant during the entire experiment time.
-Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure \ref{fgr:full_oscillation}.
+Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure~\ref{fgr:full_oscillation}.
 A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered.
 At approximately 50\,\% conversion lightoff occurs and the sample is in full conversion.
+
+A very destinct temperature dependence is seen on the oscillation frequency, an example is given in Figure~\ref{fgr:temperature_dependence}.
+The exact magnitude is not completely consistent between samples, but the effect is always large.
+This is in good agreement with \cite{Hendriksen2010} where a strong temperature dependence was predicted but not actually demonstrated.
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{temperature_dependence.png}
+  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C.
+Before the temperature step, the oscillation period was apprixmately 500\,s, after the step, the period is approximately 5000\,s}
+  \label{fgr:temperature_dependence}
+\end{figure}
 

### 2012-02-11 python_figures/temperature_dependence.py

@@ -1,0 +1,64 @@
+import matplotlib
+#matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import numpy as np
+import MySQLdb
+
+try:
+    db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+except:
+    db = MySQLdb.connect(host="127.0.0.1", port=9995, user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
+
+
+cursor = db.cursor()
+
+data = {}
+#Mass28
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactorNG where measurement = 572")
+data['M28'] = np.array(cursor.fetchall())
+
+#Mass44
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactorNG where measurement = 573")
+data['M44'] =  np.array(cursor.fetchall())
+
+#Temperature
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactorNG where measurement = 578")
+data['TEMPERATURE'] = np.array(cursor.fetchall())
+
+
+fig = plt.figure()
+fig.subplots_adjust(bottom=0.2) # Make room for x-label
+fig.subplots_adjust(right=0.85) # Make room for second y-label
+
+ratio = 0.61803398           # Golden mean
+fig_width = 9
+fig_width = fig_width /2.54        # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
+
+axis = fig.add_subplot(1,1,1)
+axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
+axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
+axis.set_ylim(0.1,1.3)
+axis2 = axis.twinx()
+axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'b-')
+axis2.set_ylim(150,210)
+#axis2.set_yticks((170,180,190,200))
+axis.set_xlim(700,1000)
+axis.grid(True)    
+
+arrow = dict(facecolor='black', shrink=0.085,width=1)
+axis.annotate('M28', xy=(830, 0.85),  xycoords='data', xytext=(800, 0.95), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
[…]

### 2012-02-11 paper.tex
Added a very long and boring part to the discussion. This will very much need to be trimmed!

@@
 Here we report oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure.
-It has previously been shown that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
-CO oxidation oscillations has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.
+Oscilating reactions on Platiunum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions doing the oscillations\cite{Ertl2008}.
+This mechanism is however not relevant at atmospheric pressures (REF?) and thus another physical mechanism must be governing the oscillations at high pressures.
+It has previously been shown already in 1982\cite{SALES1982} that CO oxidation at around 1\,bar will show oscillatory behavior on single crystals off Pt, Pd and Ir.
+Later studies has come a long way to explain the phenomenen on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
+CO oxidation oscillations has also been observed on Pt on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.
 
@@
 After deposition the reactors were anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
+Doing the experiments, samples from 3\,nm to 9\,nm has been measured, all showing oscillations.
 
@@
 \end{figure}
-The quantitative same behavior has been reproduced on a large number of samples where oscillations also occur.
+The qualitative same behavior has been reproduced on a large number of samples where oscillations also occur.
 Generally the oscillations have been seen on samples in a wide coverage and particle size regime, however, a geometrical nanoparticle coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.
 
-The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
+The oscillations are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
 An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
@@
 After a short full conversion period the sample again deactivates and the cycle repeats itself.
+The ratio between periods of high and low conversion are very different among samples, but for a given sample the ratio normally does not change even though the oscillation period consistently becomes longer and longer as the experiment progresses.
 \begin{figure*}
@@
 
-Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations as a function of pressure.
-In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found.
+In the setup we are able to change the the pressure in the reactor volume to observe any change in behavior of the oscillations as a function of pressure.
+In the pressure range of 0.1\,bar to 1\,bar no change that could be attributed to the pressure was found.
 The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}.
@@
 Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds.
-It is hence concluded that the oscillations is a feature related to the nanoparticles.
-The particles are maybe oxidized?
-Subsurface, totally oxidized etc.
-Digt en smuk historie om dette...
+It is hence concluded that the oscillations is a feature related to the catalyst.
 It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theoretical studies \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
+A detailed propsal for the reaction mechanism on Pd has been developed\cite{Hendriksen2010} and our data is to a very large degree consistent with this model.
+According to the model, the bare metal surface is less active than the oxidized surface, and further it is proposed that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface.
+The oscillating behaviour now arises because the reaction on the oxidized surface will increase surface roughness and the reaction on the reduced surface will decrease surface roughness.
+Thus the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and thus lower the rate.
+After some time the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.
+In this study, we measure on Pt nanoparticles which compared to a single crystal or a thin film, is a very rough surface.
+Thus it is to be expected that the particles will initially favor the reduced state, however as the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time, the reaction itself will smoothen the particles, further pushing towards an oxidation of the particles.
+Gradually as the particles towards the outlet oxidizes the turn-over will increasing and the general CO concentration will go down, further promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrase in CO.
+At a given point the CO concentration will become low enough that a ligh-off like phenomeneon will set in and the sample will show full conversion.
+In this state, most of the particles will be in the oxidzed high-activity state.
+As all particles are now oxidized, the will all become more and more roughened and gradually an increasing amount will go back to the reduced state.
+Thus less and less oxidized particles will be responsible for most of the activity and thus the roughness will increase faster and faster for these remaing active particles.
+Just before the overall activity drops, one must expect that only a very small fraction of the particles actually participates in the reaction and therefore the de-activation will happen very suddenly once these few particles eventually becomes sufficiently rough, that they will reduce and lose activity.
 
-%Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.
-
-The oscillation period increases with time and becomes increasingly less stable as shown in Figure \ref{fgr:extracts}.
-This phenomena is consistent across all measured samples with approximately the oscillation period evolution with time.
+The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}.
+This phenomena is consistent across all measured samples.
 The large scattter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
 Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
-A possible explanation of the phenomenon could be sintering or roughening of the clusters.
-Skriv noget mere her...
+A possible explanation of the phenomenon could be sintering or roughening of the clusters, but it is not possible at this time to tell what is the exact mechanism.
 

### 2012-02-12 paper.tex
Small corrections throughout the manuscript. The discussion is now at least decently self-consistent.

@@
 A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
-Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active (under-coordinated?) sites.
+Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active sites.
 
@@
 Oscilating reactions on Platiunum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions doing the oscillations\cite{Ertl2008}.
-This mechanism is however not relevant at atmospheric pressures (REF?) and thus another physical mechanism must be governing the oscillations at high pressures.
-It has previously been shown already in 1982\cite{SALES1982} that CO oxidation at around 1\,bar will show oscillatory behavior on single crystals off Pt, Pd and Ir.
+This mechanism is however not relevant at atmospheric pressures and thus another physical mechanism must be governing the oscillations at high pressures.
+It has previously been shown already in 1982\cite{SALES1982} that CO oxidation at around 1\,bar will show oscillatory behavior on single crystals of Pt, Pd and Ir.
 Later studies has come a long way to explain the phenomenen on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
@@
 Platinum nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
-Platinum clusters were formed by gas-phase condensation of platinum atoms produced by impinging argon ions on a 99.99\,\% platinum target in a magnetron sputter source.
+Platinum clusters were formed by gas-phase condensation of platinum atoms produced by impinging argon ions on a 99.99\% platinum target in a magnetron sputter source.
 After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
@@
 
-The oscillations are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
+The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
 An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
@@
 In the pressure range of 0.1\,bar to 1\,bar no change that could be attributed to the pressure was found.
-The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}.
+The oscillations does not change frequency nor qualitative behavior whith changing pressure.
 Similarly, only a weak dependence on the CO/O$_2$ pressure was observed.
@@
 Richer CO mixtures than 0.175 did not produce any oscillations in our system.
-CO/O$_2$ ratios lower than 0.175 were needed to provoke oscillations in our system.
 This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
@@
 
-Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds.
+Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.
 It is hence concluded that the oscillations is a feature related to the catalyst.
@@
 Gradually as the particles towards the outlet oxidizes the turn-over will increasing and the general CO concentration will go down, further promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrase in CO.
-At a given point the CO concentration will become low enough that a ligh-off like phenomeneon will set in and the sample will show full conversion.
-In this state, most of the particles will be in the oxidzed high-activity state.
-As all particles are now oxidized, the will all become more and more roughened and gradually an increasing amount will go back to the reduced state.
+At a given point the CO concentration will become low enough that a ligh-off like phenomeneon will set in and the sample will show full conversion, if not all particles where oxidized at this point, they will oxidize much faster after light-off due to the much lower CO-concentration, the increased rate will not be visible in the mass-spectromery since reactor is allready in full conversion.
+As most of the particles are now oxidized, the will all become more and more roughened and gradually an increasing amount will go back to the reduced state.
 Thus less and less oxidized particles will be responsible for most of the activity and thus the roughness will increase faster and faster for these remaing active particles.
@@
 A possible explanation of the phenomenon could be sintering or roughening of the clusters, but it is not possible at this time to tell what is the exact mechanism.
+
+\section{Conclusion}
+We have for the first time demonstrated oscillationg CO oxidation on Pt nanoparticles, measured with high-quality mass-spectrometry.
+We have shown that the phenomenon is happining for a wide range of sizes of nanoparticles and for a relatively large span i CO-concentration.
 

### 2012-02-13 paper.tex
Minor corrections

--- 2012-02-11 paper.tex
@@
 The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio.
-The frequency of the oscillations tends to increase in with time while the duty cycle remains constant.}
+The frequency of the oscillations tends to increase in with time while the duty cycle remains constant.
+Jeg synes, at vi skal skrive abstractet om.
+Det skal i alle være længere og mere præcist.}
 %Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
@@
 A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
-Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active (under-coordinated?) sites.
+Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active sites.
 
 Here we report oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure.
-It has previously been shown that CO oxidation will show oscillatory behavior on single crystals on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
-CO oxidation oscillations has also been observed on thin-films \cite{Lund2000} and in macroscopic flow reactors \cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.
+Oscillating reactions on platinum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions during the oscillations\cite{Ertl2008}.
+It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures shows oscillatory behavior on single crystals of Pt, Pd and Ir.
+Recent studies have proposed a mechanism on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
+CO oxidation oscillations has also been observed on Pt thin-films\cite{Lund2000} and in macroscopic flow reactors\cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.
 
@@
 \subsection{Reactor}
-The experiments were performed in silicon-based 20x15 mm $\mu$-reactors \cite{Henriksen2009}.
-The reactor consists of two inlets, a long mixing zone for the reaction gases to allow for diffusional mixing, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for probing the gases from the reactor volume.
+The experiments were performed in silicon-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}.
+The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu m$ wide capillary used for sniffing gases from the reactor volume.
 The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar.
@@
 
-The gas handling including flow and pressured controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention.
-This allows for very self-consistent measurements of many samples.
+The gas handling including flow and pressured controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention allowing for self-consistent measurements of many samples.
 
@@
 \end{figure}
-The quantitative same behavior has been reproduced on a large number of samples where oscillations also occur.
-Generally the oscillations have been seen on samples in a wide coverage and particle size regime, however, a geometrical nanoparticle coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.
+The qualitative same behavior has been reproduced on a large number of samples where oscillations also occur.
+Generally the oscillations have been seen on samples from 3\,nm to 9\,nm and in a wide coverage regime.
+A geometrical coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.
 
-The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
+The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
 An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
@@
 Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached.
-Shortly after reaching 50\% conversion the sample again ignites and covert all CO to CO$_2$.
+Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$.
 After a short full conversion period the sample again deactivates and the cycle repeats itself.
+The ratio between periods of high and low conversion are very different among samples, but for a given sample the ratio normally does not change even though the oscillation period consistently becomes longer as the experiment progresses.
 \begin{figure*}
@@
 
-Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations as a function of pressure.
-In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found.
-The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}.
+The pressure dependence of the oscillations were also investigated.
+In the pressure range of 0.1\,bar to 1\,bar no change that could be attributed to the pressure was found.
+The oscillations does not change frequency nor qualitative behavior with changing pressure.
 Similarly, only a weak dependence on the CO/O$_2$ pressure was observed.
@@
 Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time.
-Hereafter the oscillations is more irregular which as shown in Figure~\ref{fgr:long_measurement}.
+Hereafter the oscillations are more irregular as shown in Figure~\ref{fgr:long_measurement}.
 At experiment end the oscillation period is between 45 and 20 minutes.
@@
 
-A very destinct temperature dependence is seen on the oscillation frequency, an example is given in Figure~\ref{fgr:temperature_dependence}.
-The exact magnitude is not completely consistent between samples, but the effect is always large.
-This is in good agreement with \cite{Hendriksen2010} where a strong temperature dependence was predicted but not actually demonstrated.
 \begin{figure}[h]
@@
   \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C.
-Before the temperature step, the oscillation period was apprixmately 500\,s, after the step, the period is approximately 5000\,s}
+Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s}
   \label{fgr:temperature_dependence}
 \end{figure}
+A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}.
+By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10.
 
 \section{Discussion}
+This mechanism is, however, not relevant at atmospheric pressures and thus another physical mechanism must be governing the oscillations at high pressures.
+
 The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175.
 Richer CO mixtures than 0.175 did not produce any oscillations in our system.
-CO/O$_2$ ratios lower than 0.175 were needed to provoke oscillations in our system.
 This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
@@
 
-Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds.
-It is hence concluded that the oscillations is a feature related to the nanoparticles.
-The particles are maybe oxidized?
-Subsurface, totally oxidized etc.
-Digt en smuk historie om dette...
-It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theoretical studies \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
+Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.
+It is hence concluded that the oscillations is a feature related to the catalyst.
+It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theory \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
+A detailed proposal for the reaction mechanism on Pd has been developed \cite{Hendriksen2010} and our data is consistent with this model.
+According to the proposed model, the bare metal surface is less active than the oxidized surface.
+It is further suggested that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface.
+The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness.
+Thus the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and thus lower the rate.
+After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.
+In this study, we measure on Pt nanoparticles which, compared to a single crystal or a thin film, is a very rough surface.
+It is to be expected that the particles will initially favor the reduced state.
+As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time, the reaction itself will smoothen the particles, further pushing towards an oxidation of the particles.
+Gradually as the particles towards the outlet oxidizes the turn-over will increase and the general CO concentration will decrease, further promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.
+At a given point the CO concentration will become low enough that a light-off like phenomenon will set in and the sample will show full conversion.
+If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration.
+The increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion.
+As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state.
+Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles.
+Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the de-activation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.
 
-%Due to the nature of our reactor system, it is almost impossible to gain extra insight through traditional surface science techniques, but it has eaelier been showed that in other experimental setups, it is possible to apply both SPM microscopy \cite{Hendriksen2005} as well as infrared spectroscopy \cite{Carlsson2006}.
-
-The oscillation period increases with time and becomes increasingly less stable as shown in Figure \ref{fgr:extracts}.
-This phenomena is consistent across all measured samples with approximately the oscillation period evolution with time.
-The large scattter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
+The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}.
+This phenomena is consistent across all measured samples.
+The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
 Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
 A possible explanation of the phenomenon could be sintering or roughening of the clusters.
-Skriv noget mere her...
+
+%This is in good agreement with \cite{Hendriksen2010} where a strong temperature dependence was predicted but not actually demonstrated.
+
+\section{Conclusion}
+We have for the first time demonstrated oscillating CO oxidation on Pt nanoparticles measured with high-quality mass-spectrometry.
+We have shown oscillations wide range of sizes of nanoparticles and a large span i CO-concentration.
+Burde vi ikke skrive lidt mere om, hvad vi egentlig præsenter?
+Vi viser egentlig ikke så meget med størrelseafhængighed og CO-koncentrations-eksperimenter.
 

### 2012-02-13 paper.tex
Updated various parts of the manuscript

@@
 
-\noindent \normalsize{In the current paper high-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented.
+\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented.
 The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio.
-The frequency of the oscillations tends to increase in with time while the duty cycle remains constant.
-Jeg synes, at vi skal skrive abstractet om.
-Det skal i alle være længere og mere præcist.}
-%Any references in the abstract should be written out in full \textit{e.g.} [Surname \textit{et al., Journal Title}, 2000, \textbf{35}, 3523].
+The frequency of the oscillations is very well defined and show clear tendency to increase in with time.
+A plausible mechanism for the oscillations is proposed based on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
 \vspace{0.5cm}
@@
 Oscillating reactions on platinum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions during the oscillations\cite{Ertl2008}.
+This mechanism is, however, not relevant at atmospheric pressures and thus another physical mechanism must be governing the oscillations at high pressures.
 It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures shows oscillatory behavior on single crystals of Pt, Pd and Ir.
@@
 \end{figure}
-The qualitative same behavior has been reproduced on a large number of samples where oscillations also occur.
-Generally the oscillations have been seen on samples from 3\,nm to 9\,nm and in a wide coverage regime.
-A geometrical coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.
+The qualitative same behavior has been reproduced on a large number of samples, many of them showing oscillations.
+We have tried with particles with sized between 3\,nm and 9\,nm, but no clear size dependence was seen, most of the experiments presented here was done with 3\,nm particles.
+A geometrical coverage of 0.1\% gave the most consistent oscillations.
+Higher coverages also showed oscillations, but often only on the inital heating and cooling ramps, but only very rarely did they show prolonged oscillations at constant temperature.
 
 The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
-An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
+Once a sample start to oscillate consistently, it will keep performing self-sustained oscillations for as long as the experiemnt is allowed to run.
+We have not seen a single sample stop oscillating once the self-sustained oscillations had started.
+An example of a very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
 After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
@@
   \includegraphics[width=17cm]{single_full_oscillation.png}
-  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample.
+  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation.
 For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.
@@
 
-After the initial lightoff experiment the nanoparticles show stable self-sustained oscillation.
 After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}.
@@
 
-Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from a four day measurement.
+Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four day measurement.
 Here data from shortly after the initial treatment, after 2800\,min.
@@
 A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered.
-At approximately 50\,\% conversion lightoff occurs and the sample is in full conversion.
+At approximately 50\% conversion lightoff occurs and the sample is in full conversion.
 
@@
 By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10.
-
-\section{Discussion}
-This mechanism is, however, not relevant at atmospheric pressures and thus another physical mechanism must be governing the oscillations at high pressures.
+The magnitude of the change is not completely consistent across all measured samples, but all samples do show a very large temperature dependency, in some cases a change of a few degrees will consistently turn on and off the oscillations.
 
@@
 
+\section{Discussion}
 Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.
@@
 It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theory \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
-A detailed proposal for the reaction mechanism on Pd has been developed \cite{Hendriksen2010} and our data is consistent with this model.
+A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et.
+al.}\cite{Hendriksen2010} and our data is consistent with this model.
+
 According to the proposed model, the bare metal surface is less active than the oxidized surface.
@@
 After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.
+
 In this study, we measure on Pt nanoparticles which, compared to a single crystal or a thin film, is a very rough surface.
@@
 Gradually as the particles towards the outlet oxidizes the turn-over will increase and the general CO concentration will decrease, further promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.
-At a given point the CO concentration will become low enough that a light-off like phenomenon will set in and the sample will show full conversion.
+
+Even though the temperature is kept constant, the light-off temperature will decrease as the CO-concentration increases, and at a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion.
 If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration.
-The increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion.
+The further increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion.
 As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state.
@@
 
-%This is in good agreement with \cite{Hendriksen2010} where a strong temperature dependence was predicted but not actually demonstrated.
+An interesting feature in the data, is the very large temperature dependence.
+This property was actually predicted by Hendriksen et.
+al \cite{Hendriksen2010} when they proposed the model, and to our knowledge, this is the first time the temperature dependence is measured.
 
@@
 We have for the first time demonstrated oscillating CO oxidation on Pt nanoparticles measured with high-quality mass-spectrometry.
-We have shown oscillations wide range of sizes of nanoparticles and a large span i CO-concentration.
-Burde vi ikke skrive lidt mere om, hvad vi egentlig præsenter?
-Vi viser egentlig ikke så meget med størrelseafhængighed og CO-koncentrations-eksperimenter.
+We have found that the samples will increasing the oscillation period over time and show a dramatic temperature dependence.
+Oscillations has been seen on a wide range of nanoparticles from 3\,nm to 9\,nm and within a large CO-concentration window, however, it is evident that very oxygen rich conditions is needed for the oscillations to happen.
 

### 2012-02-13 paper.tex
Proof-reading

@@
 \usepackage[super,sort&compress,comma]{natbib} 
-\usepackage{mhchem}
+\usepackage[version=3]{mhchem}
 \usepackage[utf8]{inputenc}
@@
 
-\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behaviour of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure is presented.
+\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behavior of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure has been performed.
 The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio.
-The frequency of the oscillations is very well defined and show clear tendency to increase in with time.
-A plausible mechanism for the oscillations is proposed based on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
+The frequency of the oscillations is very well defined and increases with time.
+The oscillation frequency is furthermore strongly temperature temperature dependent with increasing temperature resulting in increasing frequency.
+A plausible mechanism for the oscillations is proposed based on a oxidation/reduction cycle of the nanoparticles which change the change rate of CO oxidation on the particles.}  %on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
 \vspace{0.5cm}
@@
 After deposition the reactors were anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
-
-%BEMAERK!
-Denne tekst er nakket fra et tidligere paper (Carbon,2011).
-Pre-formed mass-selected platinum particles were soft-landed onto the reactor at room temperature using an inert gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
-The particles are formed by gas-phase condensation from a flux of platinum atoms that are sputtered from a 99.99\% pure Ru target using a magnetron sputter source.
-The magnetron is housed in a liquid nitrogen cooled enclosure with a 3\,mm diameter aperture at one end.
-Argon gas is flown into the volume around the magnetron at a rate of 10-120 sccm and is pumped away via the aperture so that a local pressure of 0.1-1 mbar  is obtained inside the gas-aggregation zone during operation.
-The cooled argon gas thermalises the sputtered platinum atoms so that they condense into clusters, which further coalesce to form nanoparticles.
-The size of the nanoparticles is determined by a number of factors such as magnetron sputter power (typically 20–40 W), rate of gas flow, distance between the target and the exit aperture and the diameter of the exit aperture.
-Platinum nanoparticles with diameters in the range of 2–16 nm can be produced using the source \cite{Nielsen2010,Nielsen2009}.
-The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further refined by a skimmer.
-The nanoparticle beam is then passed through a quadrupole mass filter where the ionised fraction (60-80\%) of the nanoparticles can be filtered according to their mass-to-charge ratio.
 
@@
   \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C.
-Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s}
+Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
   \label{fgr:temperature_dependence}
@@
 By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10.
-The magnitude of the change is not completely consistent across all measured samples, but all samples do show a very large temperature dependency, in some cases a change of a few degrees will consistently turn on and off the oscillations.
+The magnitude of the change is not completely consistent across all measured samples but all samples do show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.
 
@@
 
-According to the proposed model, the bare metal surface is less active than the oxidized surface.
+According to the proposed model the bare metal surface is less active than the oxidized surface.
 It is further suggested that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface.
 The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness.
-Thus the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and thus lower the rate.
+Thus, the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and lower the rate.
 After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.
 
-In this study, we measure on Pt nanoparticles which, compared to a single crystal or a thin film, is a very rough surface.
+In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface.
 It is to be expected that the particles will initially favor the reduced state.
-As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time, the reaction itself will smoothen the particles, further pushing towards an oxidation of the particles.
-Gradually as the particles towards the outlet oxidizes the turn-over will increase and the general CO concentration will decrease, further promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.
+As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time the reaction itself will smoothen the particles further pushing towards an oxidation of the particles.
+Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.
 
-Even though the temperature is kept constant, the light-off temperature will decrease as the CO-concentration increases, and at a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion.
+Even though the temperature is kept constant the light-off temperature will decrease as the CO-concentration increases.
+At a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion.
 If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration.
@@
 
-An interesting feature in the data, is the very large temperature dependence.
-This property was actually predicted by Hendriksen et.
-al \cite{Hendriksen2010} when they proposed the model, and to our knowledge, this is the first time the temperature dependence is measured.
+An interesting feature in the data is the very large temperature dependence.
+This property agrees well an earlier suggested model \cite{Hendriksen2010} and is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure is measured.
 
 \section{Conclusion}
-We have for the first time demonstrated oscillating CO oxidation on Pt nanoparticles measured with high-quality mass-spectrometry.
-We have found that the samples will increasing the oscillation period over time and show a dramatic temperature dependence.
-Oscillations has been seen on a wide range of nanoparticles from 3\,nm to 9\,nm and within a large CO-concentration window, however, it is evident that very oxygen rich conditions is needed for the oscillations to happen.
+Self-sustained CO oxidation oscillations at atmospheric pressure on Pt nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-quality mass-spectrometry.
+It was found that the samples increased the oscillation period over time and showed a strong temperature dependence.
+A model is proposed where the nanoparticles go through repetitive oxidation/reduction cycles which change the change rate of CO oxidation on the particles.
 

### 2012-02-14 paper.tex
Minor corrections

@@
 
-\thispagestyle{plain}
-\fancypagestyle{plain}{
-\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
-\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
-\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
-\renewcommand{\headrulewidth}{1pt}}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\renewcommand\footnoterule{\vspace*{1pt}% 
-\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
-\setcounter{secnumdepth}{5}
+%\thispagestyle{plain}
+%\fancypagestyle{plain}{
+%\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
+%\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
+%\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
+%\renewcommand{\headrulewidth}{1pt}}
+%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+%\renewcommand\footnoterule{\vspace*{1pt}% 
+%\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
+%\setcounter{secnumdepth}{5}
 
@@
 
-\fancyfoot{}
-\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
-\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
-\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
-\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
-\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
+%\fancyfoot{}
+%\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
+%\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
+%\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
+%\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
+%\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
 \fancyhead{}
@@
 
-\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
-First published on the web Xth XXXXXXXXXX 200X}}}
+%\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
+%First published on the web Xth XXXXXXXXXX 200X}}}
 
-\noindent \textbf{\small{DOI: 10.1039/b000000x}}
+%\noindent \textbf{\small{DOI: 10.1039/b000000x}}
 \vspace{0.6cm}
@@
 %Footnotes
-\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
+%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
 
@@
 
-\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
-\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}
+%\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
+%\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}
 
@@
 
-Here we report oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure.
-Oscillating reactions on platinum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions during the oscillations\cite{Ertl2008}.
-This mechanism is, however, not relevant at atmospheric pressures and thus another physical mechanism must be governing the oscillations at high pressures.
+Here we report on oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure.
+Oscillating reactions on platinum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
+This mechanism is, however, not relevant at atmospheric pressures and thus another mechanism is governing the oscillations at high pressures.
 It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures shows oscillatory behavior on single crystals of Pt, Pd and Ir.
@@
 \end{figure}
-The qualitative same behavior has been reproduced on a large number of samples, many of them showing oscillations.
-We have tried with particles with sized between 3\,nm and 9\,nm, but no clear size dependence was seen, most of the experiments presented here was done with 3\,nm particles.
-A geometrical coverage of 0.1\% gave the most consistent oscillations.
+The qualitative same behavior has been reproduced on a large number of samples.
+Nanoparticles with sizes ranging from 3\,nm and 9\,nm, have been tested but no clear size dependence was seen.
+3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations.
 Higher coverages also showed oscillations, but often only on the inital heating and cooling ramps, but only very rarely did they show prolonged oscillations at constant temperature.
@@
 The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
-Once a sample start to oscillate consistently, it will keep performing self-sustained oscillations for as long as the experiemnt is allowed to run.
-We have not seen a single sample stop oscillating once the self-sustained oscillations had started.
-An example of a very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
+Once a sample start to oscillate consistently it will perform self-sustained oscillations for as long as the experiment is allowed to run.
+We have not observed a single sample stop oscillating once the self-sustained oscillations had started.
+
+An example of a single very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
 After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
@@
 In the pressure range of 0.1\,bar to 1\,bar no change that could be attributed to the pressure was found.
-The oscillations does not change frequency nor qualitative behavior with changing pressure.
+The oscillations do not change frequency nor qualitative behavior at different reactor pressures.
 Similarly, only a weak dependence on the CO/O$_2$ pressure was observed.
@@
 Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four day measurement.
-Here data from shortly after the initial treatment, after 2800\,min.
+Data from shortly after the initial treatment, after 2800\,min.
 of oscillation time and after 5900\,min.
-are shown.
+is shown.
 After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
@@
 Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles.
-Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the de-activation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.
+Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the deactivation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.
 
@@
 An interesting feature in the data is the very large temperature dependence.
-This property agrees well an earlier suggested model \cite{Hendriksen2010} and is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure is measured.
+This property agrees well an earlier suggested model \cite{Hendriksen2010} and is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
 

### 2012-02-15 python_figures/initial_treatment.py
Updated the initial_treatment figure

@@ -1,8 +1,11 @@
 import matplotlib
 matplotlib.use('Agg')
 import matplotlib.pyplot as plt
+import matplotlib.gridspec as gridspec
 import numpy as np
 import MySQLdb
+from matplotlib.patches import Rectangle
+
 
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
@@ -27,16 +30,27 @@ data['TEMPERATURE'] = np.array(cursor.fetchall())
 
 
 fig = plt.figure()
-fig.subplots_adjust(bottom=0.2) # Make room for x-label
+fig.subplots_adjust(bottom=0.1) # Make room for x-label
 fig.subplots_adjust(right=0.85) # Make room for second y-label
 
-ratio = 0.61803398           # Golden mean
+#ratio = 0.61803398           # Golden mean
+ratio = 0.9
 fig_width = 9
 fig_width = fig_width /2.54        # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
 
-axis = fig.add_subplot(1,1,1)
+
+gs = gridspec.GridSpec(2, 2)
+
+gs.update(wspace=0.1,hspace=0.4)
+
+axis = plt.subplot(gs[0, :])
+#axis = fig.add_subplot(2,2,1)
+
+
+p = axis.axvspan(460, 490, facecolor='red', alpha=0.25)
+p = axis.axvspan(710, 740, facecolor='yellow', alpha=0.35)
 axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
 axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
 axis.set_ylim(0,8)
@@ -46,6 +60,8 @@ axis2.set_ylim(0,300)
 #axis2.set_yticks((170,180,190,200))
 axis.set_xlim(100,800)
 axis.grid(True)    
+
+
 
 arrow = dict(facecolor='black', shrink=0.085,width=1)
 axis.annotate('M28', xy=(260, 2.6),  xycoords='data', xytext=(185, 3.5), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
[…]

### 2012-02-15 paper.tex
Initial corrections after Ibs comments

@@
 
-\noindent\large{\textbf{Robert Jensen\textit{$^{b}$}, Thomas Andersen\textit{$^{b}$}, Anders Nierhoff\textit{$^{b}$}, Søren Dahl\textit{$^{b}$}, Ole Hansen\textit{$^{b}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
+\noindent\large{\textbf{Robert Jensen\textit{$^{a}$}, Thomas Andersen\textit{$^{a}$}, Anders Nierhoff\textit{$^{a}$}, Thomas Pedersen\textit{$^{b}$}, Ole Hansen\textit{$^{b}$}, Søren Dahl\textit{$^{a}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
 %Please note that \ast indicates the corresponding author(s) but no footnote text is required.
@@
 
-The pressure dependence of the oscillations were also investigated.
-In the pressure range of 0.1\,bar to 1\,bar no change that could be attributed to the pressure was found.
-The oscillations do not change frequency nor qualitative behavior at different reactor pressures.
-Similarly, only a weak dependence on the CO/O$_2$ pressure was observed.
-At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed.
-Increasing the CO/O$_2$ to $\sim0.175$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
-Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.
-
 After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}.
@@
 A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}.
-By changing the temperature 5$^\circ$C the oscillation period is changed by more than a factor of 10.
+By changing the temperature 5$^\circ$C the oscillation period was changed by more than a factor of 10.
 The magnitude of the change is not completely consistent across all measured samples but all samples do show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.
@@
 
-Although a range of different CO/O$_2$ ratios were tried no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system.
-This is not, however, believed to be a property of the platinum thin film but a property of the small reactor used in this study.
-This is supported by literature where oscillations have been observed on both extended thin-films \cite{Singh2010} as well as on single crystals \cite{Hendriksen2005} at atmospheric pressure.
+The pressure dependence of the oscillations were also investigated.
+In the pressure range of 0.1\,bar to 1\,bar no change that could be attributed to the pressure was found.
+The oscillations do not change frequency nor qualitative behavior at different reactor pressures.
+Similarly, only a weak dependence on the CO/O$_2$ pressure was observed.
+At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed.
+Increasing the CO/O$_2$ to $\sim0.175$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
+Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.
+
+Although oscillations have been observed on extended platinum thin films \cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric pressure no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
 
@@
 According to the proposed model the bare metal surface is less active than the oxidized surface.
-It is further suggested that a high concentration of steps will thermodynamically favor the reduced surface and a low concentration of steps will favor the oxidized surface.
+It is further suggested due to the general high adsorption energy of CO on metal surfaces that CO stabilizes a metal surface stable at low CO concentrations on high-density stepped surfaces.
+Contrary, a low concentration of steps will favour an oxidized surface.
 The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness.
@@
 It is to be expected that the particles will initially favor the reduced state.
-As the reaction runs, the conditions toward the outlet of the reactor will become more reducing and at the same time the reaction itself will smoothen the particles further pushing towards an oxidation of the particles.
+As the reaction runs, the conditions toward the outlet of the reactor will become more oxidizing and at the same time the reaction itself will smoothen the particles further pushing towards an oxidation of the particles.
 Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.
 
-Even though the temperature is kept constant the light-off temperature will decrease as the CO-concentration increases.
+Even though the temperature is kept constant the light-off temperature will decrease as the CO-concentration decreases.
 At a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion.
@@
 This property agrees well an earlier suggested model \cite{Hendriksen2010} and is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
+
+Noget om turnover frequency??
 

### 2012-02-18 python_figures/duty_cycles_long_measurement.py
Lots of work on the figures

@@ -4,7 +4,7 @@
 
 import matplotlib
 #matplotlib.use('svg')
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
@@ -66,24 +66,30 @@ for i in range(1,len(oscillations)):
 #print len(periods)
 
 fig = plt.figure()
+fig.subplots_adjust(bottom=0.2) # Make room for x-label
+ratio = 0.61803398              # Golden mean
+fig_width = 9
+fig_width = fig_width /2.54     # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
 
 axis = fig.add_subplot(1,1,1)
-axis.plot(oscillations, m28_average, 'ro')
-axis.plot(oscillations, m44_average, 'bo')
+axis.plot(oscillations, m28_average, 'r-')
+axis.plot(oscillations, m44_average, 'b-')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
 #axis.set_ylim(0,7)
 #axis.set_xlim(0,500)
 
-axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=14,axis='both',pad=5)
+axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=5)
 axis.grid(True)    
 
 #axis.set_ylabel('SEM Current / nA', fontsize=20)
-axis.set_ylabel('Integrated charge (a.u.) / oscillation', fontsize=20)
-axis.set_xlabel('Time/minutes', fontsize=20)
+axis.set_ylabel('Integrated charge (a.u.) / oscil.', fontsize=8)
+axis.set_xlabel('Time/minutes', fontsize=8)
 
 
 
 #plt.tight_layout()
 plt.show()
-#plt.savefig('../summary_of_long_measurement.png')
+plt.savefig('../duty_cycles_long_measurement_supplemental.png',dpi=300)

### 2012-02-18 python_figures/extracts_from_very_long_oscillation.py

@@ -60,7 +60,7 @@ for i in range(0,3):
     
     axis_array[i].tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=2)
     axis2_array[i].tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='y',pad=2)
-    axis_array[i].grid(True)    
+    axis_array[i].grid(False)    
 
 axis_array[1].set_ylabel('SEM Current / nA', fontsize=8)
 axis2_array[1].set_ylabel('Temperature', fontsize=8)

### 2012-02-18 python_figures/initial_treatment.py

@@ -54,19 +54,21 @@ p = axis.axvspan(710, 740, facecolor='yellow', alpha=0.35)
 axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
 axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
 axis.set_ylim(0,8)
+axis.set_yticks((2,4,6))
 axis2 = axis.twinx()
 axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'b-')
 axis2.set_ylim(0,300)
-#axis2.set_yticks((170,180,190,200))
+axis2.set_yticks((50,150,250))
 axis.set_xlim(100,800)
-axis.grid(True)    
+axis.grid(False)    
 
 
 
-arrow = dict(facecolor='black', shrink=0.085,width=1)
+#arrow = dict(facecolor='black', shrink=0.085,width=1)
+arrow = dict(facecolor='black',arrowstyle='->')
 axis.annotate('M28', xy=(260, 2.6),  xycoords='data', xytext=(185, 3.5), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
-axis.annotate('M44', xy=(460, 4.4),  xycoords='data', xytext=(390, 5.6), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
-axis.annotate('Temp.', xy=(440, 6.8),  xycoords='data', xytext=(270, 7.2), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('M44', xy=(440, 4.4),  xycoords='data', xytext=(390, 5.6), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('Temp.', xy=(440, 6.6),  xycoords='data', xytext=(270, 7.2), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
[…]

### 2012-02-18 python_figures/oscillations_gas_dependence.py

@@ -1,9 +1,10 @@
 import matplotlib
 #matplotlib.use('svg')
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
+import math
 
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
@@ -41,8 +42,17 @@ for row in data['CO_FLOW']:
 
 steps = len(flow_sections)
 
-
 fig = plt.figure()
+fig.subplots_adjust(bottom=0.05) # Make room for x-label
+fig.subplots_adjust(right=0.85) # Make room for right y-label
+#ratio = 0.61803398              # Golden mean
+ratio = 2
+fig_width = 13
+fig_width = fig_width /2.54     # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
+
+
 axis_array = []
 axis2_array = []
 
@@ -50,20 +60,29 @@ for i in range(0,steps-1):
     axis_array.append(fig.add_subplot((steps-1)/2,2,i+1))
     axis_array[i].plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
     axis_array[i].plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'b-')
-    axis_array[i].set_ylim(0,0.1*(i+1)*1.85)
+    #axis_array[i].set_ylim(0,0.1*(i+1)*1.85)
+    axis_array[i].set_ylim(0,1.5)
+    axis_array[i].set_yticks((0.25,0.5,0.75,1,1.25))
     axis2_array.append(axis_array[i].twinx())
     axis2_array[i].plot(data['CO_FLOW'][:,0], data['CO_FLOW'][:,1]/(4+data['CO_FLOW'][:,1]), 'k-')
     axis2_array[i].set_ylim(0.01,0.25)
     
-    axis_array[i].set_xlim(flow_sections[i],flow_sections[i+1])
-    axis_array[i].tick_params(direction='in', length=6, width=2, colors='k',labelsize=14,axis='both',pad=5)
-    axis2_array[i].tick_params(direction='in', length=6, width=2, colors='k',labelsize=14,axis='y',pad=5)
+    if i%2 == 1:
+        axis_array[i].set_yticks(())    
+    else:
+        axis2_array[i].set_yticks(())    
[…]

### 2012-02-18 python_figures/oscillations_gas_dependence_summary.py

@@ -1,6 +1,6 @@
 import matplotlib
 #matplotlib.use('svg')
-#matplotlib.use('Agg')
+matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
@@ -71,27 +71,31 @@ periods.append(0)
 for i in range(1,len(oscillations)):
     periods.append(oscillations[i]-oscillations[i-1])
 
+
 fig = plt.figure()
+fig.subplots_adjust(bottom=0.2) # Make room for x-label
+ratio = 0.61803398              # Golden mean
+fig_width = 9
+fig_width = fig_width /2.54     # width in cm converted to inches
+fig_height = fig_width*ratio
+fig.set_size_inches(fig_width,fig_height)
+
 
 print len(oscillations)
 print len(periods)
 
 axis = fig.add_subplot(1,1,1)
-axis.plot(oscillations, periods, 'bo')
+axis.plot(oscillations, periods, 'b.')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
-#axis.set_ylim(0,7)
-#axis.set_xlim(0,500)
+axis.set_ylim(0,50)
+axis.set_xlim(0,3100)
 
-axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=14,axis='both',pad=5)
+axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=3)
 axis.grid(True)    
 
-#axis.set_ylabel('SEM Current / nA', fontsize=20)
-axis.set_ylabel('Oscillations periods / minutes', fontsize=20)
-axis.set_xlabel('Time/minutes', fontsize=20)
-
-
-
+axis.set_ylabel('Oscillations periods / minutes', fontsize=8)
+axis.set_xlabel('Time/minutes', fontsize=8)
 
 
 
@@ -100,7 +104,7 @@ axis.set_xlabel('Time/minutes', fontsize=20)
 
 #plt.tight_layout()
 plt.show()
-#plt.savefig('../svg_figures/oscillations_gas_dependence.svg')
+plt.savefig('../oscillations_gas_dependence_supplemental.png',dpi=300)
 
 
 

### 2012-02-18 python_figures/single_full_oscillation.py

@@ -48,7 +48,8 @@ axis2.set_yticks((170,180,190,200))
 axis.set_xlim(1001,1133)
 axis.grid(True)    
 
-arrow = dict(facecolor='black', shrink=0.085,width=1)
+#arrow = dict(facecolor='black', shrink=0.085,width=1)
+arrow = dict(facecolor='black',arrowstyle='->')
 axis.annotate('M28', xy=(1040, 0.83),  xycoords='data', xytext=(1058, 0.93), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 axis.annotate('M44', xy=(1040, 0.41),  xycoords='data', xytext=(1058, 0.27), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 axis.annotate('Temp.', xy=(1070, 1.08),  xycoords='data', xytext=(1095, 0.93), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)

### 2012-02-18 python_figures/summary_of_long_measurement.py

@@ -59,20 +59,22 @@ fig.set_size_inches(fig_width,fig_height)
 
 axis = fig.add_subplot(1,1,1)
 axis.plot(oscillations, periods, 'b.')
+axis.plot([750,6000],[1.8,17],'k-')
+axis.plot([750,5000],[5,43],'k-')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
 #axis.set_ylim(0,7)
 #axis.set_xlim(0,500)
 
-axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=10,axis='both',pad=3)
+axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=3)
 axis.grid(True)    
 
 #axis.set_ylabel('SEM Current / nA', fontsize=20)
-axis.set_ylabel('Oscil. period / minutes', fontsize=10)
-axis.set_xlabel('Time/minutes', fontsize=10)
+axis.set_ylabel('Oscil. period / minutes', fontsize=8)
+axis.set_xlabel('Time/minutes', fontsize=8)
 
 
 
 #plt.tight_layout()
-#plt.show()
+plt.show()
 plt.savefig('../summary_of_long_measurement.png',dpi=300)

### 2012-02-18 python_figures/temperature_dependence_supplemental.py

@@ -14,15 +14,15 @@ cursor = db.cursor()
 
 data = {}
 #Mass28
-cursor.execute("SELECT x/60000,y FROM xy_values_microreactorNG where measurement = 572")
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactor where measurement = 6303")
 data['M28'] = np.array(cursor.fetchall())
 
 #Mass44
-cursor.execute("SELECT x/60000,y FROM xy_values_microreactorNG where measurement = 573")
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactor where measurement = 6305")
 data['M44'] =  np.array(cursor.fetchall())
 
 #Temperature
-cursor.execute("SELECT x/60000,y FROM xy_values_microreactorNG where measurement = 578")
+cursor.execute("SELECT x/60000,y FROM xy_values_microreactor where measurement = 6309")
 data['TEMPERATURE'] = np.array(cursor.fetchall())
 
 
@@ -39,19 +39,19 @@ fig.set_size_inches(fig_width,fig_height)
 axis = fig.add_subplot(1,1,1)
 axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
 axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
-axis.set_ylim(0.1,1.3)
+axis.set_ylim(0,8)
 axis2 = axis.twinx()
 axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'b-')
-axis2.set_ylim(150,210)
-#axis2.set_yticks((170,180,190,200))
-axis.set_xlim(700,1000)
+axis2.set_ylim(140,225)
+axis2.set_yticks((190,200,210,220))
+axis.set_xlim(30,250)
 axis.grid(False)    
 
 arrow = dict(facecolor='black',arrowstyle='->')
 #arrow = dict(facecolor='black', shrink=0.085,width=1)
-axis.annotate('M28', xy=(830, 0.85),  xycoords='data', xytext=(800, 0.95), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
-axis.annotate('M44', xy=(830, 0.4),  xycoords='data', xytext=(800, 0.25), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
[…]

### 2012-02-18 python_figures/initial_treatment.py
Spiced up the colors on the initial_treatment figure

@@ -49,8 +49,8 @@ axis = plt.subplot(gs[0, :])
 #axis = fig.add_subplot(2,2,1)
 
 
-p = axis.axvspan(460, 490, facecolor='red', alpha=0.25)
-p = axis.axvspan(710, 740, facecolor='yellow', alpha=0.35)
+p = axis.axvspan(460, 490, facecolor='#b6fa77', alpha=0.25)
+p = axis.axvspan(710, 740, facecolor='#28cfe9', alpha=0.35)
 axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
 axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
 axis.set_ylim(0,8)
@@ -80,7 +80,7 @@ axis.set_xlabel('Time/minutes', fontsize=8)
 
 
 axis = plt.subplot(gs[1,0])
-p = axis.axvspan(460, 490, facecolor='red', alpha=0.25)
+p = axis.axvspan(460, 490, facecolor='#b6fa77', alpha=0.25)
 axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
 axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
 axis.set_ylim(0,6)
@@ -102,7 +102,7 @@ axis.grid(False)
 
 axis = plt.subplot(gs[1,1])
 #axis = fig.add_subplot(2,2,1)
-p = axis.axvspan(710, 740, facecolor='yellow', alpha=0.35)
+p = axis.axvspan(710, 740, facecolor='#28cfe9', alpha=0.35)
 axis.plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
 axis.plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
 axis.set_ylim(0,6)

### 2012-02-19 paper.tex
Minor corrections as well as a small update of the discussion

@@
 The frequency of the oscillations is very well defined and increases with time.
-The oscillation frequency is furthermore strongly temperature temperature dependent with increasing temperature resulting in increasing frequency.
-A plausible mechanism for the oscillations is proposed based on a oxidation/reduction cycle of the nanoparticles which change the change rate of CO oxidation on the particles.}  %on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
+The oscillation frequency is furthermore strongly temperature dependent with increasing temperature resulting in increasing frequency.
+A plausible mechanism for the oscillations is proposed based on a oxidation/reduction cycle of the nanoparticles which change the rate of CO oxidation on the particles.}  %on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
 \vspace{0.5cm}
@@
 The experiments were performed in silicon-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}.
-The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu m$ wide capillary used for sniffing gases from the reactor volume.
+The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for sniffing gases from the reactor volume.
 The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar.
@@
 After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
-Using this setup platinum nanoparticles with diameters in the range of 2–16 nm can be produced \cite{Nielsen2010,Nielsen2009}.
+Using this setup platinum nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2010,Nielsen2009}.
 The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor.
@@
 The qualitative same behavior has been reproduced on a large number of samples.
-Nanoparticles with sizes ranging from 3\,nm and 9\,nm, have been tested but no clear size dependence was seen.
+Nanoparticles with sizes ranging from 3\,nm to 9\,nm, have been tested but no clear size dependence was seen.
 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations.
@@
 
-The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175.
-Richer CO mixtures than 0.175 did not produce any oscillations in our system.
-This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
-The low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on platinum which poisons the nanoparticle surface during the low reactivity region of the cycle.
-Once poisoned, an increase in temperature would be necessary to ignite the reaction again.
-
 The pressure dependence of the oscillations were also investigated.
@@
 At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed.
-Increasing the CO/O$_2$ to $\sim0.175$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
+Increasing the CO/O$_2$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
 Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.
+Richer CO mixtures than 0.175 did not produce any oscillations in our system.
+This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
+The needed low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on platinum which poisons the nanoparticle surface during the low reactivity region of the cycle.
 
-Although oscillations have been observed on extended platinum thin films \cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric pressure no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
+Although oscillations have previously been observed on extended platinum thin films \cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric pressure no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
 
@@
 Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the deactivation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.
+It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of (Talværdier kommer lige om lidt...) ???/site/s corresponding to as little as ???
+nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
 
@@
 This property agrees well an earlier suggested model \cite{Hendriksen2010} and is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
-
-Noget om turnover frequency??
 

### 2012-02-20 paper.tex
Revised

@@
 
-\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behavior of CO oxidation on silicon dioxide supported Pt-nanoparticles at atmospheric pressure has been performed.
+\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behavior of CO oxidation on SiO$_2$ supported Pt-nanoparticles at atmospheric pressure has been acquired.
 The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio.
@@
 
-Here we report on oscillatory behavior of CO oxidation on size-selected platinum nanoparticles supported on a silicon dioxide substrate at atmospheric pressure.
-Oscillating reactions on platinum at UHV-conditions has been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
+Here we report on oscillatory behavior of CO oxidation on size-selected Pt nanoparticles supported on a SiO$_2$ substrate at atmospheric pressure.
+Oscillating reactions on Pt at UHV-conditions has been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
 This mechanism is, however, not relevant at atmospheric pressures and thus another mechanism is governing the oscillations at high pressures.
@@
 Recent studies have proposed a mechanism on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
-CO oxidation oscillations has also been observed on Pt thin-films\cite{Lund2000} and in macroscopic flow reactors\cite{Singh2010} but never on size selected platinum nanoparticles at atmospheric pressures for prolonged periods of time.
+CO oxidation oscillations has also been observed on Pt thin-films\cite{Lund2000} and in macroscopic flow reactors\cite{Singh2010} but never on size selected Pt nanoparticles at atmospheric pressures for prolonged periods of time.
 
@@
 \subsection{Reactor}
-The experiments were performed in silicon-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}.
+The experiments were performed in Si-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}.
 The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for sniffing gases from the reactor volume.
-The reactor is sealed by anodic bonding of a pyrex lid to the silicon reactor and is able to operate at a pressure range of 0-2.5\,bar.
+The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate at a pressure range of 0-2.5\,bar.
 The reaction gases is supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min.
-The capillary flow is fed into a quadropole mass-spectrometer for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
-The design makes sure that all gases exposed to the catalyst under investigation is measured by the mass spectrometer ensuring an extremely high sensitivity of the system.
+The capillary flow is fed into a quadropole mass-spectrometer (QMA) for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
+The design makes sure that all gases exposed to the catalyst under investigation is measured by the QMA ensuring an extremely high sensitivity of the system.
 
 Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.
-When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the mass spectrometer chamber.
+When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMA chamber.
 
-The reactor is heated by joule heating of a platinum strip evaporated on the backside of the reactor volume.
-The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the platinum strip using it as a RTD for temperature measurement of the reactor.
+The reactor is heated by joule heating of a Pt strip evaporated on the backside of the reactor volume.
+The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the Pt strip using it as a RTD for temperature measurement of the reactor.
 An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
@@
 
-\subsection{Platinum nanoparticle deposition}
-Platinum nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
-Platinum clusters were formed by gas-phase condensation of platinum atoms produced by impinging argon ions on a 99.99\% platinum target in a magnetron sputter source.
+\subsection{Pt nanoparticle deposition}
+Pt nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
+Pt clusters were formed by gas-phase condensation of Pt atoms produced by impinging argon ions on a 99.99\% Pt target in a magnetron sputter source.
 After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
-Using this setup platinum nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2010,Nielsen2009}.
+Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2010,Nielsen2009}.
 The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor.
@@
 Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
-At O$_2$:CO ratio of $\sim0.08$ and a geometrical platinum coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C.
+At O$_2$:CO ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C.
 The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp.
-After the initial lightoff the sample is cooled to room temperature.
+After the initial light-off the sample is cooled to room temperature.
 When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur.
-A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen.
-Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
+A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical light-off ramp and the subsequent increase in temperature to achieve sustained oscillations is seen.
+Often the sample will show oscillations either directly upon light-off or on the falling temperature ramp.
 \begin{figure}[h]
@@
   \caption{A typical example of the initial treatment of a new sample.
-After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
+After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
   \label{fgr:initial_treatment}
@@
 The qualitative same behavior has been reproduced on a large number of samples.
-Nanoparticles with sizes ranging from 3\,nm to 9\,nm, have been tested but no clear size dependence was seen.
-3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations.
-Higher coverages also showed oscillations, but often only on the inital heating and cooling ramps, but only very rarely did they show prolonged oscillations at constant temperature.
+Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations.
+Higher coverages also showed oscillations but often only on the inital heating and cooling ramps.
+Only on rare occasions sustained oscillations were measured at constant temperature.
 
@@
 is shown.
-After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
+After 5900\,min.
+the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
 Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
@@
 A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered.
-At approximately 50\% conversion lightoff occurs and the sample is in full conversion.
+At approximately 50\% conversion light-off occurs and the sample is in full conversion.
 
@@
 The pressure dependence of the oscillations were also investigated.
-In the pressure range of 0.1\,bar to 1\,bar no change that could be attributed to the pressure was found.
-The oscillations do not change frequency nor qualitative behavior at different reactor pressures.
-Similarly, only a weak dependence on the CO/O$_2$ pressure was observed.
+In the pressure range of 0.1\,bar to 1\,bar no change of the oscillation frequency or qualitative behavior that could be attributed to the pressure was found.
+Similarly, only a weak dependence on the CO/O$_2$ ratio was observed.
 At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed.
@@
 Richer CO mixtures than 0.175 did not produce any oscillations in our system.
-This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
-The needed low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on platinum which poisons the nanoparticle surface during the low reactivity region of the cycle.
 
-Although oscillations have previously been observed on extended platinum thin films \cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric pressure no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
+Although oscillations have previously been observed on extended Pt thin films \cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric pressure no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
 
@@
 It is further suggested due to the general high adsorption energy of CO on metal surfaces that CO stabilizes a metal surface stable at low CO concentrations on high-density stepped surfaces.
-Contrary, a low concentration of steps will favour an oxidized surface.
-The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness.
+Contrary, a low concentration of steps will favour an oxidized surface and thus high activity.
+The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness and hence the rate.
 Thus, the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and lower the rate.
@@
 As the reaction runs, the conditions toward the outlet of the reactor will become more oxidizing and at the same time the reaction itself will smoothen the particles further pushing towards an oxidation of the particles.
-Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the mass-spectrometry as an increase in CO$_2$ and a decrease in CO.
+Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMA as an increase in CO$_2$ and a decrease in CO.
 
@@
 A possible explanation of the phenomenon could be sintering or roughening of the clusters.
+
+Oscillations were only seen in CO/O$_2$ ratio below 0.175.
+This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
+The needed low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on Pt which poisons the nanoparticle surface during the low reactivity region of the cycle.
 

### 2012-02-23 paper.tex
Re-write of most of the discussion

@@
 
-\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behavior of CO oxidation on SiO$_2$ supported Pt-nanoparticles at atmospheric pressure has been acquired.
+\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behavior of CO oxidation on SiO$_2$ supported Pt-nanoparticles at atmospheric pressure has been acquired as a function of pressure, coverage, gas composition and nanoparticle size.
 The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio.
-The frequency of the oscillations is very well defined and increases with time.
+The frequency of the oscillations is very well defined and increases over time.
 The oscillation frequency is furthermore strongly temperature dependent with increasing temperature resulting in increasing frequency.
@@
 A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
-Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active sites.
+Although single crystals surfaces are well suited model systems they can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active sites.
 
 Here we report on oscillatory behavior of CO oxidation on size-selected Pt nanoparticles supported on a SiO$_2$ substrate at atmospheric pressure.
-Oscillating reactions on Pt at UHV-conditions has been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
-This mechanism is, however, not relevant at atmospheric pressures and thus another mechanism is governing the oscillations at high pressures.
-It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures shows oscillatory behavior on single crystals of Pt, Pd and Ir.
-Recent studies have proposed a mechanism on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
-CO oxidation oscillations has also been observed on Pt thin-films\cite{Lund2000} and in macroscopic flow reactors\cite{Singh2010} but never on size selected Pt nanoparticles at atmospheric pressures for prolonged periods of time.
+Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
+It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows oscillatory behavior on single crystals of Pt, Pd and Ir.
+Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
+CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and by wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
+Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.
 
 \section{Experimental Methods}
-\subsection{Reactor}
-The experiments were performed in Si-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}.
-The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for sniffing gases from the reactor volume.
-The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate at a pressure range of 0-2.5\,bar.
-The reaction gases is supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min.
-The capillary flow is fed into a quadropole mass-spectrometer (QMA) for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
-The design makes sure that all gases exposed to the catalyst under investigation is measured by the QMA ensuring an extremely high sensitivity of the system.
+The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
+The reactor design makes sure that all gases exposed to the catalyst under investigation is measured by the QMA ensuring an extremely high sensitivity of the system.
 
-Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.
-When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMA chamber.
-
-The reactor is heated by joule heating of a Pt strip evaporated on the backside of the reactor volume.
-The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the Pt strip using it as a RTD for temperature measurement of the reactor.
-An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
-
-The gas handling including flow and pressured controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention allowing for self-consistent measurements of many samples.
-
-\subsection{Pt nanoparticle deposition}
-Pt nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
-Pt clusters were formed by gas-phase condensation of Pt atoms produced by impinging argon ions on a 99.99\% Pt target in a magnetron sputter source.
-After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
-Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2010,Nielsen2009}.
-The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor.
-The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition.
+Pt nanoparticles were deposited in the reactor using a gas-aggregation source.
+The nanoparticles were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
+Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2009}.
 After deposition the reactors were anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
@@
 \end{figure}
-The qualitative same behavior has been reproduced on a large number of samples.
 Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations.
-Higher coverages also showed oscillations but often only on the inital heating and cooling ramps.
-Only on rare occasions sustained oscillations were measured at constant temperature.
+No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.
 
@@
 An example of a single very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
-After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
+After a short on-cycle (at $\sim$1030\,min.) where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
 After the deactivation the sample quickly regains $\sim$30\% conversion.
-Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached.
+Hereafter the conversion increases slowly over time until approximately 50\% conversion is reached (at $\sim$1118\,min.).
 Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$.
@@
 Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time.
-Hereafter the oscillations are more irregular as shown in Figure~\ref{fgr:long_measurement}.
+Hereafter the oscillations become more irregular as shown in Figure~\ref{fgr:long_measurement}.
 At experiment end the oscillation period is between 45 and 20 minutes.
@@
 of oscillation time and after 5900\,min.
-is shown.
+are shown.
 After 5900\,min.
@@
   \caption{Extracts from the 4 day long experiment.
-The oscillation period become more irregular with time while the on/off ratio remains constant.
+The oscillation period become more irregular with time while the total integrated conversion remains constant.
 Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
@@
 
-The oscillation period becomes more irregular with progressing experiment time although the on/off ratio remains constant during the entire experiment time.
-Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure~\ref{fgr:full_oscillation}.
+The oscillation frequency becomes more irregular with progressing experiment time as shown in Figure \ref{fgr:extracts}.
+However, the ratio between CO and CO$_2$ integrated over an full period remains constant throughout the entire experiment time.
+
+%Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure~\ref{fgr:full_oscillation}.
 A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered.
@@
 
+%No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.
+
 \section{Discussion}
 Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.
-It is hence concluded that the oscillations is a feature related to the catalyst.
-It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theory \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
+Furthermore, a series of experiments was performed to exclude the oscillations as an instrumental artifact.
+Firstly, experiments were performed on larger volume reactor thus increasing the residence time in the reactor.
+Secondly, the oscillations were reproduced on a comparable but not identical setup.
+Both of these experiments suggests that the oscillations is a property of the Pt nanoparticles.
+
+It has previously been shown using STM \cite{Hendriksen2002}, FT-IR \cite{Carlsson2006}, Monte Carlo simulations \cite{Zhdanov2002} as well as DFT \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
 A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et.
 al.}\cite{Hendriksen2010} and our data is consistent with this model.
+We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task.
 
-According to the proposed model the bare metal surface is less active than the oxidized surface.
-It is further suggested due to the general high adsorption energy of CO on metal surfaces that CO stabilizes a metal surface stable at low CO concentrations on high-density stepped surfaces.
-Contrary, a low concentration of steps will favour an oxidized surface and thus high activity.
-The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness and hence the rate.
-Thus, the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and lower the rate.
-After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.
+According to the proposed model in ref.~\citenum{Hendriksen2010} the bare metal surface is less active than the oxidized surface.
+Oscillations originate from a switch between an oxidized surface and the bare metal surface.
+Initially, with CO present in the inlet gas a smooth metal surface is exposed due to the general high adsorption energy of CO on metal surfaces.
+As the Pt nanoparticles convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt oxide will start to form in the high partial pressures of O$_2$.
+According to \cite{Hendriksen2010} a slow roughening of the particles will occur when the reaction occurs on Pt-oxide resulting in the formation of an increasingly rough oxide surface.
+As the oxide becomes rougher the bare metal surface is increasingly favored resulting in a return to the lower rate rough metal state.
+As the rate decreases the CO partial pressure increases which results in a transition from rough metal surface to a smooth metal surface.
+When the sample is sufficiently smooth it will again oxidize and thus complete the oscillation cycle.
 
@@
 Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMA as an increase in CO$_2$ and a decrease in CO.
-
-Even though the temperature is kept constant the light-off temperature will decrease as the CO-concentration decreases.
-At a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion.
+As the CO-concentration decreases the light-off temperature will decrease hence approaching the temperature of the sample resulting in a steep increase in reactivity.
 If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration.
-The further increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion.
+The further increased rate will not be visible in the QMA since the reactor is already in full conversion.
 As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state.
-Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles.
-Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the deactivation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.
-It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of (Talværdier kommer lige om lidt...) ???/site/s corresponding to as little as ???
-nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
+Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing of the remaining active particles.
+Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the deactivation will happen very suddenly.
+Once these few particles eventually becomes sufficiently rough they will reduce and lose activity.
+It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of (Talværdier kommer lige om lidt...) ???/site/s corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
 
@@
 The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
-Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
+Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
 A possible explanation of the phenomenon could be sintering or roughening of the clusters.
+However, due to the fact that the overall conversion integrated over full oscillation periods is constant, we do not expect sintering to be cause, since this would also be expected to reduce the overall activity of the sample.
 
@@
 The needed low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on Pt which poisons the nanoparticle surface during the low reactivity region of the cycle.
+
+Nanoparticles of several difference sizes where tested which all showed oscillations.
+However, no change in duty cycle or frequency that could be attributed to the size of the nanoparticles was found.
+This may be due to the fact that even nominally identical samples also show a large variation in oscillation frequency and duty cycle thus possibly shadowing a nanoparticle size effect.
 

### 2012-02-23 supplementary.tex
Re-write of most of the discussion

--- 2012-02-20 paper.tex
@@
 \section{Introduction}
-
-%Footnotes
-%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
-
-%Please use \dag to cite the ESI in the main text of the article.
-%If you article does not have ESI please remove the the \dag symbol from the title and the above footnotetext.
-
-%\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
-%\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}
-
-%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
-
-%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \emph{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
-Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}
-
-CO oxidation is one of the most studied reactions due to its importance in both automotive catalysis and in the removal of trace CO in hydrogen streams.
-A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
-Single crystals surfaces, however, can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active sites.
-
-Here we report on oscillatory behavior of CO oxidation on size-selected Pt nanoparticles supported on a SiO$_2$ substrate at atmospheric pressure.
-Oscillating reactions on Pt at UHV-conditions has been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
-This mechanism is, however, not relevant at atmospheric pressures and thus another mechanism is governing the oscillations at high pressures.
-It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures shows oscillatory behavior on single crystals of Pt, Pd and Ir.
-Recent studies have proposed a mechanism on palladium \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
-CO oxidation oscillations has also been observed on Pt thin-films\cite{Lund2000} and in macroscopic flow reactors\cite{Singh2010} but never on size selected Pt nanoparticles at atmospheric pressures for prolonged periods of time.
-
-\section{Experimental Methods}
-\subsection{Reactor}
 The experiments were performed in Si-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}.
@@
 
-\section{Results}
-An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding.
-Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
-At O$_2$:CO ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C.
-The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp.
-After the initial light-off the sample is cooled to room temperature.
-When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur.
-A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical light-off ramp and the subsequent increase in temperature to achieve sustained oscillations is seen.
-Often the sample will show oscillations either directly upon light-off or on the falling temperature ramp.
-\begin{figure}[h]
-\centering
-  \includegraphics[width=9cm]{initial_treatment.png}
-  \caption{A typical example of the initial treatment of a new sample.
-After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
-  \label{fgr:initial_treatment}
-\end{figure}
-The qualitative same behavior has been reproduced on a large number of samples.
-Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations.
-Higher coverages also showed oscillations but often only on the inital heating and cooling ramps.
-Only on rare occasions sustained oscillations were measured at constant temperature.
-
-The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
-Once a sample start to oscillate consistently it will perform self-sustained oscillations for as long as the experiment is allowed to run.
-We have not observed a single sample stop oscillating once the self-sustained oscillations had started.
-
-An example of a single very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
-After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
-After the deactivation the sample quickly regains $\sim$30\% conversion.
-Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached.
-Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$.
-After a short full conversion period the sample again deactivates and the cycle repeats itself.
-The ratio between periods of high and low conversion are very different among samples, but for a given sample the ratio normally does not change even though the oscillation period consistently becomes longer as the experiment progresses.
-\begin{figure*}
-  \centering
-  \includegraphics[width=17cm]{single_full_oscillation.png}
-  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation.
-For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.
-This extremely long oscillation period is not commonly seen and was a result of carefull parameter tuning.
-Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.}
-  \label{fgr:full_oscillation}
-\end{figure*}
-
-After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}.
-Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time.
-Hereafter the oscillations are more irregular as shown in Figure~\ref{fgr:long_measurement}.
-At experiment end the oscillation period is between 45 and 20 minutes.
-\begin{figure}[h]
-\centering
-  \includegraphics[width=9cm]{summary_of_long_measurement.png}
-  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
-  \label{fgr:long_measurement}
-\end{figure}
-
-Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four day measurement.
-Data from shortly after the initial treatment, after 2800\,min.
-of oscillation time and after 5900\,min.
-is shown.
-After 5900\,min.
-the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
-Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
-  \caption{Extracts from the 4 day long experiment.
-The oscillation period become more irregular with time while the on/off ratio remains constant.
-Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
-  \label{fgr:extracts}
-\end{figure}
-
-The oscillation period becomes more irregular with progressing experiment time although the on/off ratio remains constant during the entire experiment time.
-Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure~\ref{fgr:full_oscillation}.
-A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered.
-At approximately 50\% conversion light-off occurs and the sample is in full conversion.
-
-\begin{figure}[h]
-\centering
-  \includegraphics[width=9cm]{temperature_dependence.png}
-  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C.
-Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
-  \label{fgr:temperature_dependence}
-\end{figure}
-A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}.
-By changing the temperature 5$^\circ$C the oscillation period was changed by more than a factor of 10.
-The magnitude of the change is not completely consistent across all measured samples but all samples do show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.
-
-The pressure dependence of the oscillations were also investigated.
-In the pressure range of 0.1\,bar to 1\,bar no change of the oscillation frequency or qualitative behavior that could be attributed to the pressure was found.
-Similarly, only a weak dependence on the CO/O$_2$ ratio was observed.
-At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed.
-Increasing the CO/O$_2$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
-Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.
-Richer CO mixtures than 0.175 did not produce any oscillations in our system.
-
-Although oscillations have previously been observed on extended Pt thin films \cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric pressure no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
-
-\section{Discussion}
-Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.
-It is hence concluded that the oscillations is a feature related to the catalyst.
-It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theory \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
-A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et.
-al.}\cite{Hendriksen2010} and our data is consistent with this model.
-
-According to the proposed model the bare metal surface is less active than the oxidized surface.
-It is further suggested due to the general high adsorption energy of CO on metal surfaces that CO stabilizes a metal surface stable at low CO concentrations on high-density stepped surfaces.
-Contrary, a low concentration of steps will favour an oxidized surface and thus high activity.
-The oscillating behavior is hence attributed to the shift between an oxidized surface which will increase surface roughness and a reduced surface which will decrease surface roughness and hence the rate.
-Thus, the reaction will only run a given time in the high-rate state before the catalyst will expose the reduced surface and lower the rate.
-After some time, the roughness will again be sufficiently low that the catalyst will again oxidize and increase the rate.
-
-In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface.
-It is to be expected that the particles will initially favor the reduced state.
-As the reaction runs, the conditions toward the outlet of the reactor will become more oxidizing and at the same time the reaction itself will smoothen the particles further pushing towards an oxidation of the particles.
-Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMA as an increase in CO$_2$ and a decrease in CO.
-
-Even though the temperature is kept constant the light-off temperature will decrease as the CO-concentration decreases.
-At a given point the CO concentration will become low enough that the light-off temperature drops below the sample temperature and the sample will show full conversion.
-If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration.
-The further increased rate will not be visible in the mass-spectrometer since the reactor is already in full conversion.
-As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state.
-Fewer and fewer oxidized particles will be responsible for the activity increasing the roughness rate of the remaining active particles.
-Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the deactivation will happen very suddenly once these few particles eventually becomes sufficiently rough that they will reduce and lose activity.
-It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of (Talværdier kommer lige om lidt...) ???/site/s corresponding to as little as ???
-nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
-
-The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}.
-This phenomena is consistent across all measured samples.
-The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
-Occasionally these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
-A possible explanation of the phenomenon could be sintering or roughening of the clusters.
-
-Oscillations were only seen in CO/O$_2$ ratio below 0.175.
-This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
-The needed low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on Pt which poisons the nanoparticle surface during the low reactivity region of the cycle.
-
-An interesting feature in the data is the very large temperature dependence.
-This property agrees well an earlier suggested model \cite{Hendriksen2010} and is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
-
-\section{Conclusion}
-Self-sustained CO oxidation oscillations at atmospheric pressure on Pt nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-quality mass-spectrometry.
-It was found that the samples increased the oscillation period over time and showed a strong temperature dependence.
-A model is proposed where the nanoparticles go through repetitive oxidation/reduction cycles which change the change rate of CO oxidation on the particles.
-
-%\subsection{This is the subsection heading style}
-%Section headings can be typeset with and without numbers.\cite{Gong2004} \cite{Hendriksen2010}
-
-%\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.
-
-%\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.
-
-%\section{Equations}
-
-%Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:
-
-% \[ A = \pi r^2 \]
-
-%\begin{equation}
-%  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
-%\end{equation}
-
-%\section{Graphics and tables}
-%\subsection{Graphics}
-%Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).
-
-%\subsection{Tables}
-%Tables typeset in RSC house style do not include vertical lines.
-Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table.
-Table captions do not end in a full point.
-
-%\begin{table}[h]
-%\small
-%  \caption{\ An example of a caption to accompany a table}
-%  \label{tbl:example}
-%  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
-%    \hline
-%    Header one/units & Header two & Header three \\
-%    \hline
-%    1 & 2 & 3 \\
-%    4 & 5 & 6 \\
-%    7 & 8 & 9 \\
-%    10 & 11 & 12 \\
-%    \hline
-%  \end{tabular*}
-%\end{table}
-
-%Adding notes to tables can be complicated.  Perhaps the easiest
-%method is to generate these manually.
-
-% an example of a two-column table
-%\begin{table*}
-%\small
-  %\caption{\ An example of a caption to accompany a table, table captions do not end in a full point}
-  %\label{tbl:example}
-  %\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllll}
-    %\hline
-    %Header one & Header two & Header three & Header four & Header five & Header six  & Header seven\\
-    %\hline
-    %1 & 2 & 3 & 4 & 5 & 6  & 7\\
-    %8 & 9 & 10 & 11 & 12 & 13 & 14 \\
-    %15 & 16 & 17 & 18 & 19 & 20 & 21\\
-    %\hline
-  %\end{tabular*}
-%\end{table*}
-
-%You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
-%The \texttt{mhchem} package can also be used so
-%that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.
-
-%\section{Conclusions}
-%The conclusions section should come at the end of article.
-For the reference section, the style file rsc.bst can be used to generate the correct reference style.\footnote[4]{Footnotes should appear here.
-These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
- %For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols.
-e.g.
-\footnote[num]{your text} the corresponding author \ast counts as footnote 1, ESI as footnote 2, e.g.
-if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] etc.
-Please also cite the ESI within the main body of the text using \dag.
-
-%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
-
-%\balance
-
-%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
-%\renewcommand\refname{Notes and references}
-
-\footnotesize{
-\bibliography{literature} %your .bib file
-\bibliographystyle{rsc} %the RSC's .bst file
-}
-
 \end{document}

### 2012-02-24 python_figures/summary_of_long_measurement.py
Added insert in the four-day summary

@@ -59,21 +59,23 @@ fig.set_size_inches(fig_width,fig_height)
 
 axis = fig.add_subplot(1,1,1)
 axis.plot(oscillations, periods, 'b.')
-axis.plot([750,6000],[1.8,17],'k-')
-axis.plot([750,5000],[5,43],'k-')
+axis.plot([750,6000],[1.8,17],'r-')
+axis.plot([750,5000],[5,43],'r-')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
 #axis.set_ylim(0,7)
 #axis.set_xlim(0,500)
 
 axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=3)
-axis.grid(True)    
+axis.grid(False)    
 
-#axis.set_ylabel('SEM Current / nA', fontsize=20)
 axis.set_ylabel('Oscil. period / minutes', fontsize=8)
 axis.set_xlabel('Time/minutes', fontsize=8)
 
-
+a = plt.axes([.18, .65, .3, .15], axisbg='w')
+a.plot(oscillations, periods, 'b,')
+a.tick_params(direction='in', length=3, width=1, colors='k',labelsize=6,axis='both',pad=3)
+plt.setp(a, xlim=(700,1500), ylim=(2,8),xticks=[900,1100,1300], yticks=[3,5,7])
 
 #plt.tight_layout()
 plt.show()

### 2012-02-24 python_figures/test_circle.py
Added first draft to code that will draw a schematic of the reactor with oxidation states

@@ -1,0 +1,31 @@
+#import matplotlib
+#import matplotlib.pyplot as plt
+#import numpy as np
+
+
+from pylab import *
+
+N = 1000
+
+R = rand(N)
+Theta = rand(N)*2*pi
+area = 25
+
+colors = zeros(N)
+
+
+for i in range(0,N):
+    if (R[i]>0.7) and (Theta[i] < 1):
+        colors[i] = 1
+    
+ax = subplot(111, polar=True)
+
+c = scatter(Theta, R, c=colors, s=area)
+
+c.set_alpha(0.75)
+
+
+ax.tick_params(direction='in', length=3, width=1, colors='k',labelsize=6,axis='both',pad=3)
+setp(ax, xticks=[], yticks=[])
+
+show()

### 2012-02-24 python_figures/single_full_oscillation.py
Started to integrate the oxidation-model into the oscillation zoom

@@ -5,6 +5,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
 
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
+
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
 except:
@@ -60,6 +62,33 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
 axis.set_xlabel('Time/minutes', fontsize=8)
+
+
+
+a = plt.axes([.18, .65, .3, .25], axisbg='w',polar=True)
+N = 500
+R = np.random.rand(N)
+Theta = np.random.rand(N)*2*np.pi
+area = 1
+
+colors = np.zeros(N)
+
+for i in range(0,N):
+    if (R[i]>0.7) and (Theta[i] < 1):
+        colors[i] = 1
+    
+#ax = plt.subplot(111, polar=True)
+
+c = plt.scatter(Theta, R, c=colors, s=area, linewidths=0)
+
+c.set_alpha(0.75)
+
+
+#ax.tick_params(direction='in', length=3, width=1, colors='k',labelsize=6,axis='both',pad=3)
+#plt.setp(ax, xticks=[], yticks=[])
+
+plt.setp(a, xticks=[], yticks=[])
+#plt.setp(a, xlim=(700,1500), ylim=(2,8),xticks=[900,1100,1300], yticks=[3,5,7])
 
 #plt.tight_layout()
 plt.show()

### 2012-02-24 python_figures/test_circle.py

@@ -1,31 +1,26 @@
-#import matplotlib
-#import matplotlib.pyplot as plt
-#import numpy as np
-
-
-from pylab import *
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
 
 N = 1000
-
-R = rand(N)
-Theta = rand(N)*2*pi
+R = np.random.rand(N)
+Theta = np.random.rand(N)*2*np.pi
 area = 25
 
-colors = zeros(N)
-
+colors = np.zeros(N)
 
 for i in range(0,N):
     if (R[i]>0.7) and (Theta[i] < 1):
         colors[i] = 1
     
-ax = subplot(111, polar=True)
+ax = plt.subplot(111, polar=True)
 
-c = scatter(Theta, R, c=colors, s=area)
+c = plt.scatter(Theta, R, c=colors, s=area)
 
 c.set_alpha(0.75)
 
 
 ax.tick_params(direction='in', length=3, width=1, colors='k',labelsize=6,axis='both',pad=3)
-setp(ax, xticks=[], yticks=[])
+plt.setp(ax, xticks=[], yticks=[])
 
-show()
+plt.show()

### 2012-02-26 paper.tex
Small typographic changes

@@
 A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
-Although single crystals surfaces are well suited model systems they can be very much different from industrial catalysts where supported nanoparticles are used to both increase surface area hence bringing material costs down and to increase the reactivity of the material by increasing the number of active sites.
+Single crystals surfaces are well suited model systems due to the high degree of achievable control of parameters compared to industrial catalysts.
+Here we report on studies in a microreactor model system of Pt nanoparticles.
+The size-selected nanoparticles supported on a SiO$_2$ substrate show oscillatory behavior of CO oxidation at atmospheric pressure.
 
-Here we report on oscillatory behavior of CO oxidation on size-selected Pt nanoparticles supported on a SiO$_2$ substrate at atmospheric pressure.
 Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
@@
 Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
-CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and by wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
+CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
 Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.
@@
 The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
-The reactor design makes sure that all gases exposed to the catalyst under investigation is measured by the QMA ensuring an extremely high sensitivity of the system.
+The reactor design makes sure that all gases exposed to the catalyst under investigation is measured by the quadropole mass spectrometer (QMA) ensuring an extremely high sensitivity of the system.
 
@@
 After a short on-cycle (at $\sim$1030\,min.) where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
-After the deactivation the sample quickly regains $\sim$30\% conversion.
+After the deactivation the sample quickly regains $\sim$30\% conversion (at $\sim$1040\,min.).
 Hereafter the conversion increases slowly over time until approximately 50\% conversion is reached (at $\sim$1118\,min.).
@@
 After a short full conversion period the sample again deactivates and the cycle repeats itself.
-The ratio between periods of high and low conversion are very different among samples, but for a given sample the ratio normally does not change even though the oscillation period consistently becomes longer as the experiment progresses.
 \begin{figure*}
@@
   \caption{Extracts from the 4 day long experiment.
-The oscillation period become more irregular with time while the total integrated conversion remains constant.
+The oscillation period becomes more irregular with time while the total integrated conversion remains constant.
 Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
@@
 The oscillation frequency becomes more irregular with progressing experiment time as shown in Figure \ref{fgr:extracts}.
-However, the ratio between CO and CO$_2$ integrated over an full period remains constant throughout the entire experiment time.
+However, the ratio between CO and CO$_2$ integrated over an full period remains constant throughout the entire experiment time, i.e.
+the samples produces the same amount of CO$_2$ independent of oscillation frequency.
 
@@
 By changing the temperature 5$^\circ$C the oscillation period was changed by more than a factor of 10.
-The magnitude of the change is not completely consistent across all measured samples but all samples do show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.
+The magnitude of the change is not completely consistent across all measured samples but all samples show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.
 
-The pressure dependence of the oscillations were also investigated.
+The pressure dependence of the oscillations was also investigated.
 In the pressure range of 0.1\,bar to 1\,bar no change of the oscillation frequency or qualitative behavior that could be attributed to the pressure was found.
 Similarly, only a weak dependence on the CO/O$_2$ ratio was observed.
-At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed.
+At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations was observed.
 Increasing the CO/O$_2$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
@@
 It has previously been shown using STM \cite{Hendriksen2002}, FT-IR \cite{Carlsson2006}, Monte Carlo simulations \cite{Zhdanov2002} as well as DFT \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
+We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task.
 A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et.
 al.}\cite{Hendriksen2010} and our data is consistent with this model.
-We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task.
 
@@
 As the Pt nanoparticles convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt oxide will start to form in the high partial pressures of O$_2$.
-According to \cite{Hendriksen2010} a slow roughening of the particles will occur when the reaction occurs on Pt-oxide resulting in the formation of an increasingly rough oxide surface.
+After the oxidation of the nanoparticles they will roughen slowly during CO oxidation resulting in the formation of an increasingly rough oxide surface.
 As the oxide becomes rougher the bare metal surface is increasingly favored resulting in a return to the lower rate rough metal state.
@@
 
-Nanoparticles of several difference sizes where tested which all showed oscillations.
+Nanoparticles of several different sizes where tested which all showed oscillations.
 However, no change in duty cycle or frequency that could be attributed to the size of the nanoparticles was found.

### 2012-02-27 supplementary.tex
Early work on the supplemental material

@@
 
+\begin{figure}[h]
+\centering
+  \includegraphics[width=13cm]{oscillations_gas_dependence_supplemental.png}
+  \caption{Complete series of oscillating sample. For every frame the CO-concentration is increased.}
+  \label{fgr:gas_dependence}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=9cm]{oscillations_gas_dependence_summary_supplemental.png}
+  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
+  \label{fgr:gas_dependence_summary}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{temperature_dependence_supplemental.png}
+  \caption{Another example of the very pronounced temperature dependence. In this case the oscillations are switched on and off by a step of 20$^\circ$C}
+  \label{fgr:temperature_dependence_supplemental}
+\end{figure}
+
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
+  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment}
+  \label{fgr:temperature_dependence_supplemental}
+\end{figure}
+
+\footnotesize{
+\bibliography{literature} %your .bib file
+\bibliographystyle{rsc} %the RSC's .bst file
+}
+
 \end{document}

### 2012-02-27 python_figures/duty_cycles_long_measurement.py

@@ -57,11 +57,16 @@ m44_average = []
 m44_average.append(0)
 m28_average = []
 m28_average.append(0)
+eff = []
+eff.append(0)
 for i in range(1,len(oscillations)):
     periods.append(oscillations[i]-oscillations[i-1])
     
-    m44_average.append(average(data['M44'][mass_indexes[i-i]:mass_indexes[i],1]))
-    m28_average.append(average(data['M28'][mass_indexes[i-i]:mass_indexes[i],1]))
+    m44_av = average(data['M44'][mass_indexes[i-i]:mass_indexes[i],1])
+    m44_average.append(m44_av)
+    m28_av = average(data['M28'][mass_indexes[i-i]:mass_indexes[i],1])
+    m28_average.append(m28_av)
+    eff.append(m44_av/m28_av)
 
 #print len(periods)
 
@@ -74,8 +79,9 @@ fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
 
 axis = fig.add_subplot(1,1,1)
-axis.plot(oscillations, m28_average, 'r-')
-axis.plot(oscillations, m44_average, 'b-')
+axis.plot(oscillations, m28_average, 'r.')
+axis.plot(oscillations, m44_average, 'b.')
+axis.plot(oscillations, eff, 'k.')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
 #axis.set_ylim(0,7)
@@ -91,5 +97,5 @@ axis.set_xlabel('Time/minutes', fontsize=8)
 
 
 #plt.tight_layout()
-plt.show()
+#plt.show()
 plt.savefig('../duty_cycles_long_measurement_supplemental.png',dpi=300)

### 2012-02-27 python_figures/oscillations_gas_dependence_summary.py

@@ -104,7 +104,7 @@ axis.set_xlabel('Time/minutes', fontsize=8)
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../oscillations_gas_dependence_supplemental.png',dpi=300)
+plt.savefig('../oscillations_gas_dependence_summary_supplemental.png',dpi=300)
 
 
 

### 2012-02-27 python_figures/single_full_oscillation.py

@@ -32,10 +32,10 @@ data['TEMPERATURE'] = np.array(cursor.fetchall())
 fig = plt.figure()
 fig.subplots_adjust(bottom=0.2) # Make room for x-label
 
-#ratio = 0.61803398           # Golden mean
-ratio = 0.4                  # This figure should be very wide to span two columns
+#ratio = 0.61803398             # Golden mean
+ratio = 0.4                     # This figure should be very wide to span two columns
 fig_width = 17
-fig_width = fig_width /2.54        # width in cm converted to inches
+fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
 
@@ -48,12 +48,12 @@ axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'b-')
 axis2.set_ylim(160,205)
 axis2.set_yticks((170,180,190,200))
 axis.set_xlim(1001,1133)
-axis.grid(True)    
+axis.grid(False)    
 
 #arrow = dict(facecolor='black', shrink=0.085,width=1)
 arrow = dict(facecolor='black',arrowstyle='->')
-axis.annotate('M28', xy=(1040, 0.83),  xycoords='data', xytext=(1058, 0.93), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
-axis.annotate('M44', xy=(1040, 0.41),  xycoords='data', xytext=(1058, 0.27), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('M28', xy=(1040, 0.82),  xycoords='data', xytext=(1055, 0.85), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('M44', xy=(1040, 0.5),  xycoords='data', xytext=(1050, 0.65), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
[…]

### 2012-02-27 supplementary.tex
The supplementary material is now much closer to being finished

@@
   \begin{@twocolumnfalse}
-\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure$^\dag$}}
+\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure\\ - Supplemental Material}}
 \vspace{0.6cm}
-
-\noindent\large{\textbf{Robert Jensen\textit{$^{a}$}, Thomas Andersen\textit{$^{a}$}, Anders Nierhoff\textit{$^{a}$}, Thomas Pedersen\textit{$^{b}$}, Ole Hansen\textit{$^{b}$}, Søren Dahl\textit{$^{a}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
-%Please note that \ast indicates the corresponding author(s) but no footnote text is required.
-
-%\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
-%First published on the web Xth XXXXXXXXXX 200X}}}
-
-%\noindent \textbf{\small{DOI: 10.1039/b000000x}}
-\vspace{0.6cm}
-%Please do not change this text.
-
-\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behavior of CO oxidation on SiO$_2$ supported Pt-nanoparticles at atmospheric pressure has been acquired as a function of pressure, coverage, gas composition and nanoparticle size.
-The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio.
-The frequency of the oscillations is very well defined and increases over time.
-The oscillation frequency is furthermore strongly temperature dependent with increasing temperature resulting in increasing frequency.
-A plausible mechanism for the oscillations is proposed based on a oxidation/reduction cycle of the nanoparticles which change the rate of CO oxidation on the particles.}  %on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
-\vspace{0.5cm}
  \end{@twocolumnfalse}
@@
 
-%\section{This is the section heading style}
-\section{Introduction}
+\section{The $\mu$-reactor platform}
 The experiments were performed in Si-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}.
@@
 The design makes sure that all gases exposed to the catalyst under investigation is measured by the QMA ensuring an extremely high sensitivity of the system.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=9cm]{reactor.jpg}
+  \caption{The Microreactor before the lid is anodicly bonded to the reactor}
+  \label{fgr:reactor}
+\end{figure}
 
@@
 
-\subsection{Pt nanoparticle deposition}
+\section{Pt nanoparticle deposition}
 Pt nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
@@
 
-\begin{figure}[h]
-\centering
-  \includegraphics[width=13cm]{oscillations_gas_dependence_supplemental.png}
-  \caption{Complete series of oscillating sample. For every frame the CO-concentration is increased.}
-  \label{fgr:gas_dependence}
-\end{figure}
+\section{CO concentration dependence}
+The dependence of the CO concentration on the period of the oscillations was investigated.
+The result show that the period increases slightly with increasing CO-concentration.
+However, the effect is small compared to the general trend of slower oscillations as the experiment progresses.
+In Figure~\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the actual masspectrometry data of the entire experiment is shown in Figure~\ref{fgr:gas_dependence}.
 
@@
 
+\begin{figure*}
+  \centering
+  \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
+  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$ (blue).
+The temperature is constant $210^\circ$C doing the entire measurement.
+For every frame the CO-concentration is increased.}
+  \label{fgr:gas_dependence}
+\end{figure*}
+
+\section{Temperature dependence}
+As mentioned in the main paper, the oscillations shows a very strong temperature dependence.
+In Figure~\ref{fgr:temperature_dependence_supplemental} we show an example where the oscillations are turned on and off by changing the temperature $20^\circ$C.
+
 \begin{figure}[h]
@@
   \includegraphics[width=9cm]{temperature_dependence_supplemental.png}
-  \caption{Another example of the very pronounced temperature dependence. In this case the oscillations are switched on and off by a step of 20$^\circ$C}
+  \caption{Another example of the very pronounced temperature dependence.}
   \label{fgr:temperature_dependence_supplemental}
 \end{figure}
+
+\section{Duty cycle}
+Even though the period of the oscillations increases with time, the total integrated conversion doing a complete cycle is almost constant.
+In Figure~\ref{fgr:duty_cycles_supplemental}, the value of the integral of CO and CO$_2$ is plotted for every oscillation in the four-day long experiment.
+It is evident that the ratio between CO and CO$_2$ is almost constant and thus the overall activity of the sample is almost unchanged despite the development in the oscillation frequency.
 
@@
   \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
-  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment}
-  \label{fgr:temperature_dependence_supplemental}
+  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment.
+The individual data-points is calculted as the integral of CO (red) or CO$_2$ (blue) doing the individual oscillations.
+The ratio between CO and CO$_2$ is drawn in black.}
+  \label{fgr:duty_cycles_supplemental}
 \end{figure}

### 2012-02-27 python_figures/duty_cycles_long_measurement.py

@@ -79,19 +79,19 @@ fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
 
 axis = fig.add_subplot(1,1,1)
-axis.plot(oscillations, m28_average, 'r.')
-axis.plot(oscillations, m44_average, 'b.')
-axis.plot(oscillations, eff, 'k.')
+axis.plot(oscillations, m28_average, 'r.',markersize=0.5)
+axis.plot(oscillations, m44_average, 'b.',markersize=0.5)
+axis.plot(oscillations, eff, 'k.',markersize=0.5)
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
-#axis.set_ylim(0,7)
-#axis.set_xlim(0,500)
+axis.set_ylim(1,4)
+axis.set_xlim(700,6000)
 
 axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=5)
-axis.grid(True)    
+axis.grid(False)    
 
 #axis.set_ylabel('SEM Current / nA', fontsize=20)
-axis.set_ylabel('Integrated charge (a.u.) / oscil.', fontsize=8)
+axis.set_ylabel('Integrated charge (a.u.)', fontsize=8)
 axis.set_xlabel('Time/minutes', fontsize=8)
 
 

### 2012-02-27 python_figures/oscillations_gas_dependence.py

@@ -46,8 +46,8 @@ fig = plt.figure()
 fig.subplots_adjust(bottom=0.05) # Make room for x-label
 fig.subplots_adjust(right=0.85) # Make room for right y-label
 #ratio = 0.61803398              # Golden mean
-ratio = 2
-fig_width = 13
+ratio = 1.4
+fig_width = 14
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -57,7 +57,7 @@ axis_array = []
 axis2_array = []
 
 for i in range(0,steps-1):
-    axis_array.append(fig.add_subplot((steps-1)/2,2,i+1))
+    axis_array.append(fig.add_subplot(6,3,i+1))
     axis_array[i].plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
     axis_array[i].plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'b-')
     #axis_array[i].set_ylim(0,0.1*(i+1)*1.85)
@@ -66,11 +66,21 @@ for i in range(0,steps-1):
     axis2_array.append(axis_array[i].twinx())
     axis2_array[i].plot(data['CO_FLOW'][:,0], data['CO_FLOW'][:,1]/(4+data['CO_FLOW'][:,1]), 'k-')
     axis2_array[i].set_ylim(0.01,0.25)
-    
-    if i%2 == 1:
+
+    if i%3 == 1:
+        axis2_array[i].set_yticks(())
+
+    if i%3 == 2:
+        axis2_array[i].set_ylabel('CO/O$_2$-ratio', fontsize=8)    
+
+    if i == 16:
+        axis_array[i].set_xlabel('Time / Hours', fontsize=8)    
+
+    if i%3 > 0:
         axis_array[i].set_yticks(())    
     else:
-        axis2_array[i].set_yticks(())    
+        axis2_array[i].set_yticks(())
+        axis_array[i].set_ylabel('SEM Current / nA', fontsize=8)    
     
     st = math.ceil(flow_sections[i])
     axis_array[i].set_xticks((st,st+1,st+2,st+3))

### 2012-02-28 paper.tex
Further corrections, send to external (Søren Dahl) read-through

@@
   \begin{@twocolumnfalse}
-\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure$^\dag$}}
+\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure}}
 \vspace{0.6cm}
 
-\noindent\large{\textbf{Robert Jensen\textit{$^{a}$}, Thomas Andersen\textit{$^{a}$}, Anders Nierhoff\textit{$^{a}$}, Thomas Pedersen\textit{$^{b}$}, Ole Hansen\textit{$^{b}$}, Søren Dahl\textit{$^{a}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
+\noindent\large{\textbf{Robert Jensen, Thomas Andersen, Anders Nierhoff, Thomas Pedersen, Ole Hansen, Søren Dahl and Ib Chorkendorff}}\vspace{0.5cm}
 %Please note that \ast indicates the corresponding author(s) but no footnote text is required.
@@
 The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
-The reactor design makes sure that all gases exposed to the catalyst under investigation is measured by the quadropole mass spectrometer (QMA) ensuring an extremely high sensitivity of the system.
+The reactor design makes sure that all gases exposed to the catalyst under investigation is measured by the quadropole mass spectrometer (QMS) ensuring an extremely high sensitivity of the system.
 
@@
   \caption{A typical example of the initial treatment of a new sample.
-After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
+After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.
+The non-zero value of CO during high conversion periods is consistent with the expected QMS background signals from CO$_2$ and O$_2$.}
   \label{fgr:initial_treatment}
@@
   \includegraphics[width=17cm]{single_full_oscillation.png}
-  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation.
+  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate deactivation.
 For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.
-This extremely long oscillation period is not commonly seen and was a result of carefull parameter tuning.
-Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.}
+This extremely long oscillation period is not commonly seen and was a result of careful parameter tuning.
+Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.
+Inserted circles illustrates the proposed model.
+At high conversion the platinum is oxidized (red) while in low conversion the sample is reduced (blue).}
   \label{fgr:full_oscillation}
@@
   \includegraphics[width=9cm]{summary_of_long_measurement.png}
-  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition. The sample went through a total of 439 oscillations in 4 days.}
+  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition.
+The sample went through a total of 439 oscillations in 4 days.
+Time is defined from experiment start and hence includes initial treatment.}
   \label{fgr:long_measurement}
@@
 However, the ratio between CO and CO$_2$ integrated over an full period remains constant throughout the entire experiment time, i.e.
-the samples produces the same amount of CO$_2$ independent of oscillation frequency.
+the samples maintains a constant overall rate independent of oscillation frequency.
 
@@
 It has previously been shown using STM \cite{Hendriksen2002}, FT-IR \cite{Carlsson2006}, Monte Carlo simulations \cite{Zhdanov2002} as well as DFT \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
-We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task.
 A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et.
@@
 Initially, with CO present in the inlet gas a smooth metal surface is exposed due to the general high adsorption energy of CO on metal surfaces.
-As the Pt nanoparticles convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt oxide will start to form in the high partial pressures of O$_2$.
-After the oxidation of the nanoparticles they will roughen slowly during CO oxidation resulting in the formation of an increasingly rough oxide surface.
+As the Pt nanoparticles convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt oxide will start to form in the high partial pressures of O$_2$ thus increasing the rate.
+The model\cite{Hendriksen2010} suggests that the oxidized nanoparticles will roughen during CO oxidation resulting in the formation of an increasingly rough oxide surface.
 As the oxide becomes rougher the bare metal surface is increasingly favored resulting in a return to the lower rate rough metal state.
@@
 It is to be expected that the particles will initially favor the reduced state.
-As the reaction runs, the conditions toward the outlet of the reactor will become more oxidizing and at the same time the reaction itself will smoothen the particles further pushing towards an oxidation of the particles.
-Gradually as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMA as an increase in CO$_2$ and a decrease in CO.
-As the CO-concentration decreases the light-off temperature will decrease hence approaching the temperature of the sample resulting in a steep increase in reactivity.
-If not all particles are oxidized at this point they will oxidize much faster after light-off due to the low CO-concentration.
-The further increased rate will not be visible in the QMA since the reactor is already in full conversion.
+As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles.
+Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO.
+As the CO concentration decreases the light-off temperature will decrease hence approaching the constant temperature of the sample resulting in a steep increase in reactivity.
+It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known.
+We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task.
+If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration.
+The further increased rate will not be visible in the QMS since the reactor is already in full conversion.
 As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state.
-Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing of the remaining active particles.
-Just before the overall activity drops only a very small fraction of the particles actually participates in the reaction and the deactivation will happen very suddenly.
-Once these few particles eventually becomes sufficiently rough they will reduce and lose activity.
-It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of (Talværdier kommer lige om lidt...) ???/site/s corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
+Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing rate of the remaining active particles.
+Just before the overall activity drops only a fraction of the particles participates in the reaction and the deactivation will happen very suddenly.
+Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle.
+It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of $10^{6}$/site/s corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
 
@@
 A possible explanation of the phenomenon could be sintering or roughening of the clusters.
-However, due to the fact that the overall conversion integrated over full oscillation periods is constant, we do not expect sintering to be cause, since this would also be expected to reduce the overall activity of the sample.
+However, due to the fact that the overall conversion integrated over full oscillation periods is constant we do not expect sintering to be cause since this would also be expected to reduce the overall activity of the sample.
 
@@
 
-Nanoparticles of several different sizes where tested which all showed oscillations.
+Nanoparticles of several different sizes were tested which all showed oscillations.
 However, no change in duty cycle or frequency that could be attributed to the size of the nanoparticles was found.
@@
 
-An interesting feature in the data is the very large temperature dependence.
+An interesting feature in the data is the very large temperature dependence on oscillation frequency.
 This property agrees well an earlier suggested model \cite{Hendriksen2010} and is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.

### 2012-02-28 supplementary.tex
Further corrections, send to external (Søren Dahl) read-through

@@
 \pagestyle{fancy}
+
+\renewcommand{\thefigure}{S\arabic{figure}}
 
@@
   \centering
-  \includegraphics[width=9cm]{reactor.jpg}
+  \includegraphics[width=8cm]{reactor.jpg}
   \caption{The Microreactor before the lid is anodicly bonded to the reactor}
@@
 \section{Duty cycle}
-Even though the period of the oscillations increases with time, the total integrated conversion doing a complete cycle is almost constant.
-In Figure~\ref{fgr:duty_cycles_supplemental}, the value of the integral of CO and CO$_2$ is plotted for every oscillation in the four-day long experiment.
+Even though the period of the oscillations increases with time, the total integrated conversion rate during a complete cycle is almost constant.
+In Figure~\ref{fgr:duty_cycles_supplemental}, the value of the mean value of CO and CO$_2$ is plotted for every oscillation in the four-day long experiment.
 It is evident that the ratio between CO and CO$_2$ is almost constant and thus the overall activity of the sample is almost unchanged despite the development in the oscillation frequency.

### 2012-02-28 python_figures/test_circle.py

@@ -1,26 +1,0 @@
-import matplotlib
-import matplotlib.pyplot as plt
-import numpy as np
-
-N = 1000
-R = np.random.rand(N)
-Theta = np.random.rand(N)*2*np.pi
-area = 25
-
-colors = np.zeros(N)
-
-for i in range(0,N):
-    if (R[i]>0.7) and (Theta[i] < 1):
-        colors[i] = 1
-    
-ax = plt.subplot(111, polar=True)
-
-c = plt.scatter(Theta, R, c=colors, s=area)
-
-c.set_alpha(0.75)
-
-
-ax.tick_params(direction='in', length=3, width=1, colors='k',labelsize=6,axis='both',pad=3)
-plt.setp(ax, xticks=[], yticks=[])
-
-plt.show()

### 2012-03-06 paper.tex
Included the simple corrections from Søren Dahl

@@
 It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows oscillatory behavior on single crystals of Pt, Pd and Ir.
-Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface.
+Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface formation.
 CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
@@
 Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
-At O$_2$:CO ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C.
+At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C.
 The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp.
@@
 However, the ratio between CO and CO$_2$ integrated over an full period remains constant throughout the entire experiment time, i.e.
-the samples maintains a constant overall rate independent of oscillation frequency.
+the samples maintains a constant average rate independent of oscillation frequency.
 
@@
 Secondly, the oscillations were reproduced on a comparable but not identical setup.
-Both of these experiments suggests that the oscillations is a property of the Pt nanoparticles.
+Finally attempts at reproducing the phenomenon on Pt-thin films of comparable covarage did not produce any oscillations.
+All of these experiments suggests that the oscillations is a true property of the Pt nanoparticles.
 
@@
 It is to be expected that the particles will initially favor the reduced state.
-As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles.
+As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles (illustrated in Figure~\ref{fgr:full_oscillation}).
 Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO.

### 2012-03-06 paper.tex
Small corrections before full author list read-through

@@
 Secondly, the oscillations were reproduced on a comparable but not identical setup.
-Finally attempts at reproducing the phenomenon on Pt-thin films of comparable covarage did not produce any oscillations.
-All of these experiments suggests that the oscillations is a true property of the Pt nanoparticles.
+Finally, attempts at reproducing the phenomenon on Pt-thin films of comparable coverage did not produce any oscillations.
+All of these experiments suggest that the oscillations is a property of the Pt nanoparticles.
 

### 2012-03-06 supplementary.tex
Included the simple corrections from Søren Dahl
Small corrections before full author list read-through

@@
 Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.
-When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMA chamber.
+When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMS chamber.
 
@@
 An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
+The measured RTD temperature is always compared to the thermocouple at room temperature both before and after an experiment to be sure the RTD did not change resistance due to annealing during the experiment.
 
-The gas handling including flow and pressured controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention allowing for self-consistent measurements of many samples.
+The gas handling including flow and pressure controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention allowing for self-consistent measurements of many samples.
 
@@
 The dependence of the CO concentration on the period of the oscillations was investigated.
-The result show that the period increases slightly with increasing CO-concentration.
+The result shows that the period increases slightly with increasing CO-concentration.
 However, the effect is small compared to the general trend of slower oscillations as the experiment progresses.
@@
 In Figure~\ref{fgr:duty_cycles_supplemental}, the value of the mean value of CO and CO$_2$ is plotted for every oscillation in the four-day long experiment.
-It is evident that the ratio between CO and CO$_2$ is almost constant and thus the overall activity of the sample is almost unchanged despite the development in the oscillation frequency.
+It is evident that the ratio between CO and CO$_2$ is almost constant and thus the average activity of the sample is almost unchanged despite the development in the oscillation frequency.
 

### 2012-03-07 paper.tex
Incorporated Ole Hansens suggestions

@@
 A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
-Single crystals surfaces are well suited model systems due to the high degree of achievable control of parameters compared to industrial catalysts.
+Single crystal surfaces are well suited model systems due to the high degree of achievable control of parameters compared to industrial catalysts.
 Here we report on studies in a microreactor model system of Pt nanoparticles.
@@
 Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2009}.
-After deposition the reactors were anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
+After deposition the reactors were anodically cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
 
@@
 
-The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour.
+The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s) up to more than an hour.
 Once a sample start to oscillate consistently it will perform self-sustained oscillations for as long as the experiment is allowed to run.
@@
   \includegraphics[width=9cm]{summary_of_long_measurement.png}
-  \caption{Summary of a sample oscillating under constant temperature, pressure and reactant composition.
+  \caption{Summary of the oscillation period as a function of time for a sample oscillating under constant temperature, pressure and reactant composition.
 The sample went through a total of 439 oscillations in 4 days.
-Time is defined from experiment start and hence includes initial treatment.}
+Time is defined from experiment start and hence includes initial treatment.
+The inset shows the initial steady increase in oscillation period.}
   \label{fgr:long_measurement}
@@
 
-Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four day measurement.
+Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four days measurement.
 Data from shortly after the initial treatment, after 2800\,min.
-of oscillation time and after 5900\,min.
-are shown.
-After 5900\,min.
-the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
+of oscillation time and after 5900\,min are shown.
+After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
 Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
@@
   \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
-  \caption{Extracts from the 4 day long experiment.
+  \caption{Extracts from the 4 days long experiment.
 The oscillation period becomes more irregular with time while the total integrated conversion remains constant.
@@
 Increasing the CO/O$_2$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
-Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.
+Generally, a tendency towards longer oscillation periods for higher CO/O$_2$ ratio was observed.
 Richer CO mixtures than 0.175 did not produce any oscillations in our system.
@@
 Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle.
-It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of $10^{6}$/site/s corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
+It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of $10^{6}$s$^{-1}$ per site corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
 
@@
 A possible explanation of the phenomenon could be sintering or roughening of the clusters.
-However, due to the fact that the overall conversion integrated over full oscillation periods is constant we do not expect sintering to be cause since this would also be expected to reduce the overall activity of the sample.
+However, due to the fact that the overall conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since this would also be expected to reduce the overall activity of the sample.
 
@@
 
-Nanoparticles of several different sizes were tested which all showed oscillations.
+Nanoparticles of several different sizes were tested and all showed oscillations.
 However, no change in duty cycle or frequency that could be attributed to the size of the nanoparticles was found.
@@
 An interesting feature in the data is the very large temperature dependence on oscillation frequency.
-This property agrees well an earlier suggested model \cite{Hendriksen2010} and is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
+This property agrees well an earlier suggested model \cite{Hendriksen2010} and it is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
 

### 2012-03-07 supplementary.tex
Incorporated Ole Hansens suggestions

@@
 \section{The $\mu$-reactor platform}
-The experiments were performed in Si-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}.
-The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for sniffing gases from the reactor volume.
-The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate at a pressure range of 0-2.5\,bar.
-The reaction gases is supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min.
-The capillary flow is fed into a quadropole mass-spectrometer (QMA) for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
-The design makes sure that all gases exposed to the catalyst under investigation is measured by the QMA ensuring an extremely high sensitivity of the system.
+The experiments were performed in Si-based 20x16\,mm $\mu$-reactors\cite{Henriksen2009}.
+The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume.
+The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0-2.5\,bar.
+The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min.
+The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
+The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system.
 
@@
   \includegraphics[width=8cm]{reactor.jpg}
-  \caption{The Microreactor before the lid is anodicly bonded to the reactor}
+  \caption{The Microreactor before the lid is anodically bonded to the reactor}
   \label{fgr:reactor}
@@
 
-The reactor is heated by joule heating of a Pt strip evaporated on the backside of the reactor volume.
+The reactor is heated by joule heating of a Pt strip evaporated on the backside of the reactor chip.
 The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the Pt strip using it as a RTD for temperature measurement of the reactor.
@@
 
-The gas handling including flow and pressure controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention allowing for self-consistent measurements of many samples.
+The gas handling including flow and pressure controllers and the mass spectrometer is fully automated allowing for measurements during several days without human intervention allowing for self-consistent measurements of many samples.
 

### 2012-03-07 paper.tex
Reformulation of a small paragraph

@@
 Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
-A possible explanation of the phenomenon could be sintering or roughening of the clusters.
-However, due to the fact that the overall conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since this would also be expected to reduce the overall activity of the sample.
+This could suggest either sintering or roughening of the clusters.
+However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause where an average loss in activity of the sample would be expected.
 

### 2012-03-07 paper.tex
Small change in the sintering paragraph

@@
 Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
-This could suggest either sintering or roughening of the clusters.
-However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause where an average loss in activity of the sample would be expected.
+A possible explanation of the phenomeonon could be sintering of the particles, during the many oxidation and reductions cycles.
+However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.
 

### 2012-03-07 paper.tex
Small corrections
Incorporated Anders Nierhoffs corrections

@@
 An example of a single very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
-After a short on-cycle (at $\sim$1030\,min.) where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
-After the deactivation the sample quickly regains $\sim$30\% conversion (at $\sim$1040\,min.).
-Hereafter the conversion increases slowly over time until approximately 50\% conversion is reached (at $\sim$1118\,min.).
+After a short on-cycle (at $\sim$1030\,min) where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
+After the deactivation the sample quickly regains $\sim$30\% conversion (at $\sim$1040\,min).
+Hereafter the conversion increases slowly over time until approximately 50\% conversion is reached (at $\sim$1118\,min).
 Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$.
@@
 This extremely long oscillation period is not commonly seen and was a result of careful parameter tuning.
-Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,minutes.
+Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,min.
 Inserted circles illustrates the proposed model.
@@
 After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}.
-Initially, the oscillation period is $\sim$2.5 minutes and increases linearly with time until 1500 minutes of total oscillation time.
+Initially, the oscillation period is $\sim$2.5 min and increases linearly with time until 1500 min of total oscillation time.
 Hereafter the oscillations become more irregular as shown in Figure~\ref{fgr:long_measurement}.
-At experiment end the oscillation period is between 45 and 20 minutes.
+At experiment end the oscillation period is between 20 and 45 min.
 \begin{figure}[h]
@@
 Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four days measurement.
-Data from shortly after the initial treatment, after 2800\,min.
-of oscillation time and after 5900\,min are shown.
+Data from shortly after the initial treatment, after 2800\,min of oscillation time and after 5900\,min are shown.
 After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
@@
 Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
-A possible explanation of the phenomeonon could be sintering of the particles, during the many oxidation and reductions cycles.
+A possible explanation of the phenomeonon could be sintering of the particles during the oxidation and reductions cycles.
 However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.

### 2012-03-12 paper.tex
Bringing the lay-out back to match guidelines for PhysChem ChemPhys...

@@
 \usepackage{times,mathptmx}
-% \usepackage{times}
+ \usepackage{times}
 % feel free not to use mathptmx if it causes difficulties
@@
 
-%\thispagestyle{plain}
-%\fancypagestyle{plain}{
-%\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
-%\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
-%\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
-%\renewcommand{\headrulewidth}{1pt}}
-%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-%\renewcommand\footnoterule{\vspace*{1pt}% 
-%\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
-%\setcounter{secnumdepth}{5}
+\thispagestyle{plain}
+\fancypagestyle{plain}{
+\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
+\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
+\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
+\renewcommand{\headrulewidth}{1pt}}
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+\renewcommand\footnoterule{\vspace*{1pt}% 
+\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
+\setcounter{secnumdepth}{5}
 
@@
 
-%\fancyfoot{}
-%\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
-%\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
-%\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
-%\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
-%\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
+\fancyfoot{}
+\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
+\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
+\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
+\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
+\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
 \fancyhead{}
@@
   \begin{@twocolumnfalse}
-\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure}}
+\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure$^\dag$}}
 \vspace{0.6cm}
 
-\noindent\large{\textbf{Robert Jensen, Thomas Andersen, Anders Nierhoff, Thomas Pedersen, Ole Hansen, Søren Dahl and Ib Chorkendorff}}\vspace{0.5cm}
+\noindent\large{\textbf{Robert Jensen,\textit{$^{a}$} Thomas Andersen,\textit{$^{a}$} Anders Nierhoff,\textit{$^{a}$} Thomas Pedersen,\textit{$^{b\ddag}$} Ole Hansen,\textit{$^{b\ddag}$} Søren Dahl,\textit{$^{a\ddag}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
 %Please note that \ast indicates the corresponding author(s) but no footnote text is required.
 
-%\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
-%First published on the web Xth XXXXXXXXXX 200X}}}
+\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
+First published on the web Xth XXXXXXXXXX 200X}}}
 
-%\noindent \textbf{\small{DOI: 10.1039/b000000x}}
+\noindent \textbf{\small{DOI: 10.1039/b000000x}}
 \vspace{0.6cm}
@@
 %Footnotes
-%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
+\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
 
@@
 
-%\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
+\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
+\footnotetext{\textit{$^{b}$~CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, Ørsteds Plads, B 345B, 2800 Lyngby, Denmark.
+Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
 %\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}

### 2012-03-12 paper.tex
Merged the supplementatry material into the main paper. Needs cleanup.

@@
 
-\noindent\large{\textbf{Robert Jensen,\textit{$^{a}$} Thomas Andersen,\textit{$^{a}$} Anders Nierhoff,\textit{$^{a}$} Thomas Pedersen,\textit{$^{b\ddag}$} Ole Hansen,\textit{$^{b\ddag}$} Søren Dahl,\textit{$^{a\ddag}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
+\noindent\large{\textbf{Robert Jensen,\textit{$^{a}$} Thomas Andersen,\textit{$^{a}$} Anders Nierhoff,\textit{$^{a}$} Thomas Pedersen,\textit{$^{b}$} Ole Hansen,\textit{$^{b}$} Søren Dahl,\textit{$^{a}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
 %Please note that \ast indicates the corresponding author(s) but no footnote text is required.
@@
 \section{Experimental Methods}
+\subsection{The $\mu$-reactor platform}
 The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
@@
 
-Pt nanoparticles were deposited in the reactor using a gas-aggregation source.
-The nanoparticles were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
-Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2009}.
+The experiments were performed in Si-based 20x16\,mm $\mu$-reactors\cite{Henriksen2009}.
+The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume.
+The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0-2.5\,bar.
+The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min.
+The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
+The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=8cm]{reactor.jpg}
+  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area and gas channel system}
+  \label{fgr:reactor}
+\end{figure}
+
+Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.
+When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMS chamber.
+
+The reactor is heated by joule heating of a Pt strip evaporated on the backside of the reactor chip.
+The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the Pt strip using it as a RTD for temperature measurement of the reactor.
+An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
+The measured RTD temperature is always compared to the thermocouple at room temperature both before and after an experiment to be sure the RTD did not change resistance due to annealing during the experiment.
+
+The gas handling including flow and pressure controllers and the mass spectrometer is fully automated allowing for measurements during several days without human intervention allowing for self-consistent measurements of many samples.
+
+\subsection{Pt nanoparticle deposition}
+Pt nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
+Pt clusters were formed by gas-phase condensation of Pt atoms produced by impinging argon ions on a 99.99\% Pt target in a magnetron sputter source.
+After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
+Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2010,Nielsen2009}.
+The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor.
+The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition.
 After deposition the reactors were anodically cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
@@
 %No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.
+
+\subsection{CO concentration dependence}
+The dependence of the CO concentration on the period of the oscillations was investigated.
+The result shows that the period increases slightly with increasing CO-concentration.
+However, the effect is small compared to the general trend of slower oscillations as the experiment progresses.
+In Figure~\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the actual masspectrometry data of the entire experiment is shown in Figure~\ref{fgr:gas_dependence}.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=9cm]{oscillations_gas_dependence_summary_supplemental.png}
+  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
+  \label{fgr:gas_dependence_summary}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
+  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$ (blue).
+The temperature is constant $210^\circ$C doing the entire measurement.
+For every frame the CO-concentration is increased.}
+  \label{fgr:gas_dependence}
+\end{figure*}
+
+\subsection{Temperature dependence}
+As mentioned in the main paper, the oscillations shows a very strong temperature dependence.
+In Figure~\ref{fgr:temperature_dependence_supplemental} we show an example where the oscillations are turned on and off by changing the temperature $20^\circ$C.
+
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{temperature_dependence_supplemental.png}
+  \caption{Another example of the very pronounced temperature dependence.}
+  \label{fgr:temperature_dependence_supplemental}
+\end{figure}
+
+\subsection{Duty cycle}
+Even though the period of the oscillations increases with time, the total integrated conversion rate during a complete cycle is almost constant.
+In Figure~\ref{fgr:duty_cycles_supplemental}, the value of the mean value of CO and CO$_2$ is plotted for every oscillation in the four-day long experiment.
+It is evident that the ratio between CO and CO$_2$ is almost constant and thus the average activity of the sample is almost unchanged despite the development in the oscillation frequency.
+
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
+  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment.
+The individual data-points is calculted as the integral of CO (red) or CO$_2$ (blue) doing the individual oscillations.
+The ratio between CO and CO$_2$ is drawn in black.}
+  \label{fgr:duty_cycles_supplemental}
+\end{figure}
 

### 2012-03-12 paper.tex
Started to integrate Ib changes

@@
 The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s) up to more than an hour.
-Once a sample start to oscillate consistently it will perform self-sustained oscillations for as long as the experiment is allowed to run.
+Once a sample start to oscillate it will perform self-sustained oscillations for as long as the experiment is allowed to run.
 We have not observed a single sample stop oscillating once the self-sustained oscillations had started.
@@
 An example of a single very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
-After a short on-cycle (at $\sim$1030\,min) where all CO is converted to CO$_2$ the reaction shows a fast deactivation.
+After a short on-cycle (at $\sim$1030\,min) where all CO is converted to CO$_2$ (notice the CO signal does not go to zero due to the cracking pattern of CO$_2$ and CO background in the QMS) the reaction shows a fast deactivation.
 After the deactivation the sample quickly regains $\sim$30\% conversion (at $\sim$1040\,min).
@@
 Initially, the oscillation period is $\sim$2.5 min and increases linearly with time until 1500 min of total oscillation time.
-Hereafter the oscillations become more irregular as shown in Figure~\ref{fgr:long_measurement}.
+Hereafter the oscillations become more irregular as shown in Figure~\ref{fgr:extracts} and lower panel Figure~\ref{fgr:long_measurement}.
 At experiment end the oscillation period is between 20 and 45 min.

### 2012-03-12 python_figures/summary_of_long_measurement.py

@@ -8,6 +8,7 @@ matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
+from scipy import optimize
 
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
@@ -59,8 +60,20 @@ fig.set_size_inches(fig_width,fig_height)
 
 axis = fig.add_subplot(1,1,1)
 axis.plot(oscillations, periods, 'b.')
-axis.plot([750,6000],[1.8,17],'r-')
-axis.plot([750,5000],[5,43],'r-')
+#axis.plot([750,6000],[1.8,17],'r-')
+#axis.plot([750,5000],[5,43],'r-')
+range = np.arange(700,6500)
+
+fitfunc = lambda p, x: p[0]*(x**p[1])+p[2]       # Target function
+errfunc = lambda p, x, y: fitfunc(p, x) - y # Distance to the target function
+p0 = [0.2,0.6,2] # Initial guess for the parameters
+p1, success = optimize.leastsq(errfunc, p0[:], args=([700,1000,2000,4000,6000],[4,6,20,37,45]),maxfev=1000)
+print p1, success
+axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r-')
+
+p1, success = optimize.leastsq(errfunc, p0[:], args=([500,1000,2000,4000,6000],[0,2,9,11,16]),maxfev=1000)
+print p1, success
+axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r-')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
 #axis.set_ylim(0,7)
@@ -78,5 +91,5 @@ a.tick_params(direction='in', length=3, width=1, colors='k',labelsize=6,axis='bo
 plt.setp(a, xlim=(700,1500), ylim=(2,8),xticks=[900,1100,1300], yticks=[3,5,7])
 
 #plt.tight_layout()
-plt.show()
+#plt.show()
 plt.savefig('../summary_of_long_measurement.png',dpi=300)

### 2012-03-19 paper.tex
Microscopic update

@@
 An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding.
-Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
+Initially a light-off CO-oxidation measurement is performed (shown in Figure~\ref{fgr:initial_treatment}) where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
 At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C.

### 2012-03-19 python_figures/duty_cycles_long_measurement.py
Small updates to several figures

@@ -9,6 +9,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
 
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
+
 def average(values):
     """Computes the arithmetic mean of a list of numbers.
 
@@ -80,10 +82,17 @@ fig.set_size_inches(fig_width,fig_height)
 
 axis = fig.add_subplot(1,1,1)
 axis.plot(oscillations, m28_average, 'r.',markersize=0.5)
-axis.plot(oscillations, m44_average, 'b.',markersize=0.5)
+axis.plot(oscillations, m44_average, 'g.',markersize=0.5)
 axis.plot(oscillations, eff, 'k.',markersize=0.5)
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
+
+arrow = dict(facecolor='black',arrowstyle='->')
+axis.annotate('CO$_2$', xy=(2500, 3.4),  xycoords='data', xytext=(2100, 3.1), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
+axis.annotate('CO', xy=(2500, 2.1),  xycoords='data', xytext=(2100, 2.4), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
+axis.annotate('CO$_2$/CO', xy=(2500, 1.6),  xycoords='data', xytext=(2100, 1.3), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
+
+
 axis.set_ylim(1,4)
 axis.set_xlim(700,6000)
 

### 2012-03-19 python_figures/single_full_oscillation.py

@@ -52,8 +52,8 @@ axis.grid(False)
 
 #arrow = dict(facecolor='black', shrink=0.085,width=1)
 arrow = dict(facecolor='black',arrowstyle='->')
-axis.annotate('M28', xy=(1040, 0.82),  xycoords='data', xytext=(1055, 0.85), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
-axis.annotate('M44', xy=(1040, 0.5),  xycoords='data', xytext=(1050, 0.65), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('CO', xy=(1040, 0.82),  xycoords='data', xytext=(1055, 0.85), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('CO$_2$', xy=(1040, 0.5),  xycoords='data', xytext=(1050, 0.65), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 axis.annotate('Temp.', xy=(1070, 1.08),  xycoords='data', xytext=(1095, 0.93), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)

### 2012-03-19 python_figures/summary_of_long_measurement.py

@@ -1,4 +1,3 @@
-
 #This will be a simple implementation of a program that summaries the oscillation period as a function of oscillation number
 #We will also need a simple program that summarises duty cycle as a function of oscillation
 
@@ -9,6 +8,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
 from scipy import optimize
+
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
 
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")

### 2012-03-20 paper.tex
First compiling version since move to ASC
Still need to fix the figures and the author list, but
the document compiles fine.

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%This is the article LaTeX template for RSC journals
-%Copyright The Royal Society of Chemistry 2010
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% This is a (brief) model paper using the achemso class
+%% The document class accepts keyval options, which should include
+%% the target journal and optionally the macuscript tye
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[journal=jacsat,manuscript=article]{achemso}
 
-\documentclass[8.5pt,twoside,twocolumn]{article}
-\oddsidemargin -1.2cm
-\evensidemargin -1.2cm
-\textwidth 18cm
-\headheight 1.0in
-\topmargin -3.5cm
-\textheight 22cm
-\usepackage[super,sort&compress,comma]{natbib} 
-\usepackage[version=3]{mhchem}
-\usepackage[utf8]{inputenc}
-\usepackage{times,mathptmx}
- \usepackage{times}
-% feel free not to use mathptmx if it causes difficulties
-\usepackage{sectsty}
-\usepackage{balance}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Place any additional packages needed here.  Only include packages
+%% which are essential, to avoid problems later.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
+\usepackage{graphicx}
 
-\usepackage{graphicx} %eps figures can be used instead
-\usepackage{lastpage}
-\usepackage[format=plain,justification=raggedright,singlelinecheck=false,font=small,labelfont=bf,labelsep=space]{caption} 
-\usepackage{fancyhdr}
-\pagestyle{fancy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% If issues arise when submitting your manuscript, you may want to
+%% un-comment the next line.  This provides information on the
+%% version of every file you have used.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%\listfiles
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Place any additional macros here.  Please use \newcommand* where
+%% possible, and avoid layout changing macros (which are not used
+%% when typesetting).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand*{\mycommand}[1]{\texttt{\emph{#1}}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Meta-data block
+%% ---------------
+%% Each author should be given as a separate \author command.
+%%
+%% Corresponding authors should have an e-mail given after the author
+%% name as an \email command.
+%%
+%% The affiliation of authors is given after the authors; each
+%% \affiliation command applies to all preceding authors not already
+%% assigned an affiliation.
+%%
+%% The affiliation takes an option argument for the short name.  This
+%% will typically be something like "University of Somewhere".
+%%
+%% The \altaffiliation macro should be used for new address, etc.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Robert Jensen}
+\author{Thomas Andersen}
+\author{Anders Nierhoff}
+\altaffiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark.}
+\author{Thomas Pedersen}
+\author{Ole Hansen}
+\affiliation{CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, Ørsteds Plads, B 345B, 2800 Lyngby, Denmark.
+Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}
+\author{Søren Dahl}
+\author{Ib Chorkendorff}
+\email{ibchork@fysik.dtu.dk}
+\altaffiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The document title should be given as usual
+%% A short title can be given as a *suggestion* for running headers.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title[Oxidation oscillations at atmospheric pressure]
+{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure}
 
 \begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The manuscript does not need to include \maketitle, which is
+%% executed automatically.  The document should begin with an
+%% abstract, if appropriate.  If one is given and should not be, the
+%% contents will be gobbled.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{abstract}
+  High-quality mass spectrometry data of the oscillatory behavior
+  of CO oxidation on SiO$_2$ supported Pt-nanoparticles at atmospheric
+  pressure has been acquired as a function of pressure, coverage, gas
+  composition and nanoparticle size. The oscillations are self-sustained
+  for several days at constant temperature, pressure and CO/O$_2$ ratio.
+  The frequency of the oscillations is very well defined and increases
+  over time. The oscillation frequency is furthermore strongly temperature
+  dependent with increasing temperature resulting in increasing frequency.
+  A plausible mechanism for the oscillations is proposed based on a
+  oxidation/reduction cycle of the nanoparticles which change the rate of
+  CO oxidation on the particles.
+\end{abstract}
 
-\thispagestyle{plain}
-\fancypagestyle{plain}{
-\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
-\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
-\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
-\renewcommand{\headrulewidth}{1pt}}
-\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-\renewcommand\footnoterule{\vspace*{1pt}% 
-\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
-\setcounter{secnumdepth}{5}
-
-\makeatletter 
-\def\subsubsection{\@startsection{subsubsection}{3}{10pt}{-1.25ex plus -1ex minus -.1ex}{0ex plus 0ex}{\normalsize\bf}} 
-\def\paragraph{\@startsection{paragraph}{4}{10pt}{-1.25ex plus -1ex minus -.1ex}{0ex plus 0ex}{\normalsize\textit}} 
-\renewcommand\@biblabel[1]{#1}            
-\renewcommand\@makefntext[1]% 
-{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
-\makeatother 
-\renewcommand{\figurename}{\small{Fig.}~}
-\sectionfont{\large}
-\subsectionfont{\normalsize}
-
-\fancyfoot{}
-\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
-\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
-\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
-\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
-\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
-\fancyhead{}
-\renewcommand{\headrulewidth}{1pt} 
-\renewcommand{\footrulewidth}{1pt}
-\setlength{\arrayrulewidth}{1pt}
-\setlength{\columnsep}{6.5mm}
-\setlength\bibsep{1pt}
-
-\twocolumn[
-  \begin{@twocolumnfalse}
-\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure$^\dag$}}
-\vspace{0.6cm}
-
-\noindent\large{\textbf{Robert Jensen,\textit{$^{a}$} Thomas Andersen,\textit{$^{a}$} Anders Nierhoff,\textit{$^{a}$} Thomas Pedersen,\textit{$^{b}$} Ole Hansen,\textit{$^{b}$} Søren Dahl,\textit{$^{a}$} and Ib Chorkendorff\textit{$^{a}$}}}\vspace{0.5cm}
-%Please note that \ast indicates the corresponding author(s) but no footnote text is required.
-
-\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
-First published on the web Xth XXXXXXXXXX 200X}}}
-
-\noindent \textbf{\small{DOI: 10.1039/b000000x}}
-\vspace{0.6cm}
-%Please do not change this text.
-
-\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behavior of CO oxidation on SiO$_2$ supported Pt-nanoparticles at atmospheric pressure has been acquired as a function of pressure, coverage, gas composition and nanoparticle size.
-The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio.
-The frequency of the oscillations is very well defined and increases over time.
-The oscillation frequency is furthermore strongly temperature dependent with increasing temperature resulting in increasing frequency.
-A plausible mechanism for the oscillations is proposed based on a oxidation/reduction cycle of the nanoparticles which change the rate of CO oxidation on the particles.}  %on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
-\vspace{0.5cm}
- \end{@twocolumnfalse}
-  ]
-
-%\section{This is the section heading style}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Start the main part of the manuscript here.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Introduction}
-
-%Footnotes
-\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
-
-%Please use \dag to cite the ESI in the main text of the article.
-%If you article does not have ESI please remove the the \dag symbol from the title and the above footnotetext.
-
-\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
-\footnotetext{\textit{$^{b}$~CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, Ørsteds Plads, B 345B, 2800 Lyngby, Denmark.
-Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
-%\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}
-
-%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
-
-%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \emph{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
-Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}
-
 CO oxidation is one of the most studied reactions due to its importance in both automotive catalysis and in the removal of trace CO in hydrogen streams.
@@
 
-%\subsection{This is the subsection heading style}
-%Section headings can be typeset with and without numbers.\cite{Gong2004} \cite{Hendriksen2010}
-
-%\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.
-
-%\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.
-
-%\section{Equations}
-
-%Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:
-
-% \[ A = \pi r^2 \]
-
-%\begin{equation}
-%  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
-%\end{equation}
-
-%\section{Graphics and tables}
-%\subsection{Graphics}
-%Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).
-
-%\subsection{Tables}
-%Tables typeset in RSC house style do not include vertical lines.
-Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table.
-Table captions do not end in a full point.
-
-%\begin{table}[h]
-%\small
-%  \caption{\ An example of a caption to accompany a table}
-%  \label{tbl:example}
-%  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
-%    \hline
-%    Header one/units & Header two & Header three \\
-%    \hline
-%    1 & 2 & 3 \\
-%    4 & 5 & 6 \\
-%    7 & 8 & 9 \\
-%    10 & 11 & 12 \\
-%    \hline
-%  \end{tabular*}
-%\end{table}
-
-%Adding notes to tables can be complicated.  Perhaps the easiest
-%method is to generate these manually.
-
-% an example of a two-column table
-%\begin{table*}
-%\small
-  %\caption{\ An example of a caption to accompany a table, table captions do not end in a full point}
-  %\label{tbl:example}
-  %\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllll}
-    %\hline
-    %Header one & Header two & Header three & Header four & Header five & Header six  & Header seven\\
-    %\hline
-    %1 & 2 & 3 & 4 & 5 & 6  & 7\\
-    %8 & 9 & 10 & 11 & 12 & 13 & 14 \\
-    %15 & 16 & 17 & 18 & 19 & 20 & 21\\
-    %\hline
-  %\end{tabular*}
-%\end{table*}
-
-%You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
-%The \texttt{mhchem} package can also be used so
-%that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.
-
-%\section{Conclusions}
-%The conclusions section should come at the end of article.
-For the reference section, the style file rsc.bst can be used to generate the correct reference style.\footnote[4]{Footnotes should appear here.
-These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
- %For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols.
-e.g.
-\footnote[num]{your text} the corresponding author \ast counts as footnote 1, ESI as footnote 2, e.g.
-if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] etc.
-Please also cite the ESI within the main body of the text using \dag.
-
-%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
-
-%\balance
-
-%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
-%\renewcommand\refname{Notes and references}
-
-\footnotesize{
 \bibliography{literature} %your .bib file
-\bibliographystyle{rsc} %the RSC's .bst file
-}
 

### 2012-03-20 paper.tex
Transition to ASC Nano complete

@@
 \author{Anders Nierhoff}
-\altaffiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark.}
+\affiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark.}
 \author{Thomas Pedersen}
 \author{Ole Hansen}
-\affiliation{CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, Ørsteds Plads, B 345B, 2800 Lyngby, Denmark.
-Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}
-\author{Søren Dahl}
+\affiliation{CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, \O rsteds Plads, B 345B, 2800 Lyngby, Denmark.}
+\author{S\o ren Dahl}
 \author{Ib Chorkendorff}
 \email{ibchork@fysik.dtu.dk}
-\altaffiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark.}
+\affiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark.}
 
@@
 
-\begin{figure}[h]
-  \centering
+\begin{scheme}
   \includegraphics[width=8cm]{reactor.jpg}
@@
   \label{fgr:reactor}
-\end{figure}
+\end{scheme}
 
@@
 Often the sample will show oscillations either directly upon light-off or on the falling temperature ramp.
-\begin{figure}[h]
-\centering
+
+\begin{scheme}
   \includegraphics[width=9cm]{initial_treatment.png}
@@
   \label{fgr:initial_treatment}
-\end{figure}
+\end{scheme}
+
 Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations.
@@
 After a short full conversion period the sample again deactivates and the cycle repeats itself.
-\begin{figure*}
-  \centering
+
+\begin{scheme}
   \includegraphics[width=17cm]{single_full_oscillation.png}
@@
   \label{fgr:full_oscillation}
-\end{figure*}
+\end{scheme}
 
@@
 At experiment end the oscillation period is between 20 and 45 min.
-\begin{figure}[h]
-\centering
+
+\begin{scheme}
   \includegraphics[width=9cm]{summary_of_long_measurement.png}
@@
   \label{fgr:long_measurement}
-\end{figure}
+\end{scheme}
 
@@
 Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
-\begin{figure}[h]
-  \centering
+\begin{scheme}
   \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
@@
   \label{fgr:extracts}
-\end{figure}
+\end{scheme}
 
@@
 
-%Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure~\ref{fgr:full_oscillation}.
-A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered.
-At approximately 50\% conversion light-off occurs and the sample is in full conversion.
-
-\begin{figure}[h]
-\centering
+\begin{scheme}
   \includegraphics[width=9cm]{temperature_dependence.png}
@@
   \label{fgr:temperature_dependence}
-\end{figure}
+\end{scheme}
+
 A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}.
@@
 
-\begin{figure}[h]
-  \centering
+\begin{scheme}
   \includegraphics[width=9cm]{oscillations_gas_dependence_summary_supplemental.png}
@@
   \label{fgr:gas_dependence_summary}
-\end{figure}
+\end{scheme}
 
-\begin{figure*}
-  \centering
+\begin{scheme}
   \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
@@
   \label{fgr:gas_dependence}
-\end{figure*}
+\end{scheme}
 
@@
 
-\begin{figure}[h]
+\begin{scheme}
 \centering
@@
   \label{fgr:temperature_dependence_supplemental}
-\end{figure}
+\end{scheme}
 
@@
 
-\begin{figure}[h]
-\centering
+\begin{scheme}
   \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
@@
   \label{fgr:duty_cycles_supplemental}
-\end{figure}
+\end{scheme}
 

### 2012-04-16 paper.tex
Started integrating Ibs introduction into main document

@@
 \section{Introduction}
-CO oxidation is one of the most studied reactions due to its importance in both automotive catalysis and in the removal of trace CO in hydrogen streams.
-A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
-Single crystal surfaces are well suited model systems due to the high degree of achievable control of parameters compared to industrial catalysts.
-Here we report on studies in a microreactor model system of Pt nanoparticles.
-The size-selected nanoparticles supported on a SiO$_2$ substrate show oscillatory behavior of CO oxidation at atmospheric pressure.
 
-Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
-It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows oscillatory behavior on single crystals of Pt, Pd and Ir.
-Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface formation.
-CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
-Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.
+Self-sustained oscillating systems are wide spread in nature and have been
+described both experimentally and theoretically. One of the maybe most famous
+biological examples is the oscillation in the lynx-hare population as
+reported through the number furs delivered to the Hudson Bay Company A).
+This was for some time was believed to be forced by the sunspot oscillations,
+however, this proved to be a coincidence B) and could be described alone
+by a close dynamical coupling in between the two populations. Similar very
+interesting observations have been made for our current climate changes
+\cite{Svensmark1997,Svensmark1998} suggesting that the sunspot activity could
+influences the level of cosmic rays and thus the cloud formation, but this
+currently a topic of controversy \cite{Lockwood2007}. A beautiful example of
+self-sustained oscillatory behavior in chemistry is the colorful
+Belousov-Zhabotinsky reaction which is rather easy to demonstrate for an
+audience\cite{ZAIKIN1970}. Such self-sustained oscillatory behavior has been
+explained for systems far from equilibrium in several theoretical works
+\cite{HakenBog,NicolisBog}. Similar behavior has been observed within
+heterogeneous catalysis where typically nanoparticles of a precious metal
+supported on an inexpensive oxide constitute the active phase \cite{IbsBog}.
+One of the very first examples was observed by Wicke for CO oxidation on a
+catalyst of highly dispersed Pt on γ−Al2O3 \cite{BEUSCH1972}. To gain a deeper
+insight into the fundamental aspects of such oscillatory reactions this work
+was followed up by Ertl on Pt(110) surfaces under well-defined conditions
+\cite{EISWIRTH1986}. Ertl demonstrated how the switching in between the
+unreconstructed Pt(110) surface and the reconstruction 2x1-Pt(110) surface
+combined with big changes of oxygen sticking coefficient on the two surfaces
+could drive the self-sustained oscillations. This and many other interesting
+aspects of self-sustained and forced oscillatory behavior and spatio–temporal
+self-organization were investigated by Ertl and coworkers on well-defined
+single crystals see for example reviews \cite{IMBIHL1995,JAKUBITH1990} and in
+particular the Nobel Lecture \cite{Ertl2008}. One of the reasons this has
+attracted so much interest is naturally the importance of such catalytic
+reactions and therefore a demand to gain a better understanding of their
+behavior with the goal of further improvement. CO oxidation is one of the most
+studied reactions due to its importance in both automotive catalysis and in
+the removal of trace CO in hydrogen streams \cite{IbsBog}. The oscillatory
+behavior is, however, limited to either Pt or the CO oxidation, but
+have been found for many other metallic catalyst like on for example Rh, Ir,
+and Pd and for oxidations reactions in general as well as for NO and CO
+reactions and even for hydrogenation reactions \cite{Lund2000,SALES1982}. Most
+of the studies are made on single crystal or poly crystalline films or
+filaments, mainly in conjunction with ultra-high vacuum equipment so that the
+surfaces can be characterized using the surface science methods. The amount of
+work described on supported catalyst seems more limited obviously because it
+is so much more difficult to characterize those systems and because additional
+complexities are present such as mass and heat transport. There even exist
+reports in the literature of how large scale facilities such as an industrial
+ammonia fixed-bed synthesis reactor in Germany in 1989 started oscillating for
+several hours. This could be modeled by a coupling of the exothermic process
+and the heat management in the reactor system \cite{Machado2005}, but one
+cannot rule out that the observed oscillations could in some systems also be
+created by inherent processes on the catalyst itself. In general such
+oscillations would be considered highly undesirable in industry since they
+could be difficult to control and result in run-away incidents in particular
+for exothermic reactions resulting in damaged catalyst due to sintering at
+higher temperatures. On the other hand there exist examples in the literature
+where forced oscillations seem to improve the overall activity
+\cite{IMBIHL1995,Machado2005} . One particular interesting process here could
+be the methanol synthesis where reducing the CO$_2$ contents for a shorter period
+of time result in a subsequent higher methanol rate over compensation for the
+lack of methanol production when running in the reducing H$_2$ and CO alone
+\cite{Dynamics-Bog}. This enhancement can be explained by extensive wetting
+and un-wetting of the active Copper catalyst dependent on the oxidation
+potential \cite{Hansen2002} i.e. the active area is strongly increased when
+reduced but slowly returns to the less active state when the CO$_2$ is present.
+
+As mentioned the understanding of self-sustained on supported catalyst is
+hampered by the fact that entirely different mechanism than those observed on
+single and polycrystalline samples may exist. For example on a Pt(110) crystal
+it was shown how waves of surface reconstruction could propagate on the
+surface ensuring a synchronization of the phenomena. This also have to occur
+for oscillation on supported catalyst, but here it is more likely to be due to
+coupling of mass or heat transport. There have been a few examples where such
+oscillations have been observed. Of these are the most prominent the work by
+Skoghlund \cite{Carlsson2006} where self-sustained oscillations were observed
+on supported Pt catalyst and simultaneous studied by in situ IR spectrometry.
+Similar studies were recently undertaken using EXAFS \cite{Singh2010} but here
+the oscillatory behavior was rather unstable and somewhat less convincible.
+
+In this work we demonstrate how a two-dimensional model system of Pt
+nanoparticles on a SiO2 support can be constructed that displays highly
+repeatable self-sustained oscillations when first started. The system consist
+of mass selected Pt nanoparticles in the range from 2 to 10\,nm Pt
+nanoparticles deposited in a microreactor with a surface area of 0.75\,cm$^2$
+specially designed to achieve high sensitivity \cite{Henriksen2009}. This
+method offers some advantages over the chemical synthesis methods, which also
+offers the possibility of size selected nanoparticles se for example 
+\cite{Tsang2008,Shao2011}, since in this case we do not have to bother with
+the surfactants required for these synthesis methods. The coverage of Pt
+nanoparticles could be varied from sub-percent to full coverage. It is
+demonstrated how the nanoparticles could provide self-sustained oscillations
+over extend of days and how various parameters could be mapped out inclusive
+the influence of the temperature dependence - an effect that could not be
+demonstrated for a continuous film of same area and similar conditions. By
+combining these results with previous studies \cite{Carlsson2006,Singh2010}
+and a recent detailed study of CO oxidation on Pd using STM
+\cite{Hendriksen2010} a plausible explanation of the oscillatory behaviors
+presented. The low coverage and extremely efficient Pt nanoparticles
+illuminates some of the pit falls that may have to be considered when making
+in situ investigations of such a system since extremely low coverages may
+provide the entire conversion.
+
+A) D. A. McLulich, Variations in the Number of Varying Hare,University of Toronto
+Press, Toronto, 1937. (we need to dig in for the correct ref here),
+B) I remember reading of this in a biology book back in the seventies, check)
 

### 2012-04-18 paper.tex
Updated the Lynx-hare references and fixed a few encoding errors

@@
 described both experimentally and theoretically. One of the maybe most famous
-biological examples is the oscillation in the lynx-hare population as
-reported through the number furs delivered to the Hudson Bay Company A).
-This was for some time was believed to be forced by the sunspot oscillations,
-however, this proved to be a coincidence B) and could be described alone
-by a close dynamical coupling in between the two populations. Similar very
-interesting observations have been made for our current climate changes
-\cite{Svensmark1997,Svensmark1998} suggesting that the sunspot activity could
-influences the level of cosmic rays and thus the cloud formation, but this
-currently a topic of controversy \cite{Lockwood2007}. A beautiful example of
-self-sustained oscillatory behavior in chemistry is the colorful
-Belousov-Zhabotinsky reaction which is rather easy to demonstrate for an
+biological examples is the oscillation in the lynx-hare population as reported
+through the number furs delivered to the Hudson Bay Company
+\cite{MacLulich,Elton1942}). This was for some time was believed to be forced
+by the sunspot oscillations \cite{Elton1924}, however, even though the
+realtionship has been debated even as recently as 1993\cite{SINCLAIR1993} the
+concensuss seems to be that this is not the case \cite{Elton1942,Kielland2010}
+and the periodic cycle can be explained by more classic wheather phenomena..
+Similar very interesting observations have been made for our current climate
+changes \cite{Svensmark1997,Svensmark1998} suggesting that the sunspot activity
+could influences the level of cosmic rays and thus the cloud formation, but
+this currently a topic of controversy \cite{Lockwood2007}. A beautiful example
+of self-sustained oscillatory behavior in chemistry is the colorful Belousov-
+Zhabotinsky reaction which is rather easy to demonstrate for an
 audience\cite{ZAIKIN1970}. Such self-sustained oscillatory behavior has been
@@
 One of the very first examples was observed by Wicke for CO oxidation on a
-catalyst of highly dispersed Pt on γ−Al2O3 \cite{BEUSCH1972}. To gain a deeper
-insight into the fundamental aspects of such oscillatory reactions this work
-was followed up by Ertl on Pt(110) surfaces under well-defined conditions
-\cite{EISWIRTH1986}. Ertl demonstrated how the switching in between the
-unreconstructed Pt(110) surface and the reconstruction 2x1-Pt(110) surface
-combined with big changes of oxygen sticking coefficient on the two surfaces
-could drive the self-sustained oscillations. This and many other interesting
-aspects of self-sustained and forced oscillatory behavior and spatio–temporal
-self-organization were investigated by Ertl and coworkers on well-defined
-single crystals see for example reviews \cite{IMBIHL1995,JAKUBITH1990} and in
-particular the Nobel Lecture \cite{Ertl2008}. One of the reasons this has
-attracted so much interest is naturally the importance of such catalytic
-reactions and therefore a demand to gain a better understanding of their
-behavior with the goal of further improvement. CO oxidation is one of the most
-studied reactions due to its importance in both automotive catalysis and in
-the removal of trace CO in hydrogen streams \cite{IbsBog}. The oscillatory
-behavior is, however, limited to either Pt or the CO oxidation, but
-have been found for many other metallic catalyst like on for example Rh, Ir,
-and Pd and for oxidations reactions in general as well as for NO and CO
-reactions and even for hydrogenation reactions \cite{Lund2000,SALES1982}. Most
-of the studies are made on single crystal or poly crystalline films or
-filaments, mainly in conjunction with ultra-high vacuum equipment so that the
-surfaces can be characterized using the surface science methods. The amount of
-work described on supported catalyst seems more limited obviously because it
-is so much more difficult to characterize those systems and because additional
-complexities are present such as mass and heat transport. There even exist
-reports in the literature of how large scale facilities such as an industrial
-ammonia fixed-bed synthesis reactor in Germany in 1989 started oscillating for
-several hours. This could be modeled by a coupling of the exothermic process
-and the heat management in the reactor system \cite{Machado2005}, but one
-cannot rule out that the observed oscillations could in some systems also be
-created by inherent processes on the catalyst itself. In general such
-oscillations would be considered highly undesirable in industry since they
-could be difficult to control and result in run-away incidents in particular
-for exothermic reactions resulting in damaged catalyst due to sintering at
-higher temperatures. On the other hand there exist examples in the literature
-where forced oscillations seem to improve the overall activity
-\cite{IMBIHL1995,Machado2005} . One particular interesting process here could
-be the methanol synthesis where reducing the CO$_2$ contents for a shorter period
-of time result in a subsequent higher methanol rate over compensation for the
-lack of methanol production when running in the reducing H$_2$ and CO alone
-\cite{Dynamics-Bog}. This enhancement can be explained by extensive wetting
-and un-wetting of the active Copper catalyst dependent on the oxidation
-potential \cite{Hansen2002} i.e. the active area is strongly increased when
-reduced but slowly returns to the less active state when the CO$_2$ is present.
+catalyst of highly dispersed Pt on $\gamma$−Al$_2$O$_3$ \cite{BEUSCH1972}. To
+gain a deeper insight into the fundamental aspects of such oscillatory
+reactions this work was followed up by Ertl on Pt(110) surfaces under well-
+defined conditions \cite{EISWIRTH1986}. Ertl demonstrated how the switching in
+between the unreconstructed Pt(110) surface and the reconstruction 2x1-Pt(110)
+surface combined with big changes of oxygen sticking coefficient on the two
+surfaces could drive the self-sustained oscillations. This and many other
+interesting aspects of self-sustained and forced oscillatory behavior and
+spatio--temporal self-organization were investigated by Ertl and coworkers on
+well-defined single crystals see for example reviews
+\cite{IMBIHL1995,JAKUBITH1990} and in particular the Nobel Lecture
+\cite{Ertl2008}. One of the reasons this has attracted so much interest is
+naturally the importance of such catalytic reactions and therefore a demand to
+gain a better understanding of their behavior with the goal of further
+improvement. CO oxidation is one of the most studied reactions due to its
+importance in both automotive catalysis and in the removal of trace CO in
+hydrogen streams \cite{IbsBog}. The oscillatory behavior is, however, limited
+to either Pt or the CO oxidation, but have been found for many other metallic
+catalyst like on for example Rh, Ir, and Pd and for oxidations reactions in
+general as well as for NO and CO reactions and even for hydrogenation reactions
+\cite{Lund2000,SALES1982}. Most of the studies are made on single crystal or
+poly crystalline films or filaments, mainly in conjunction with ultra-high
+vacuum equipment so that the surfaces can be characterized using the surface
+science methods. The amount of work described on supported catalyst seems more
+limited obviously because it is so much more difficult to characterize those
+systems and because additional complexities are present such as mass and heat
+transport. There even exist reports in the literature of how large scale
+facilities such as an industrial ammonia fixed-bed synthesis reactor in Germany
+in 1989 started oscillating for several hours. This could be modeled by a
+coupling of the exothermic process and the heat management in the reactor
+system \cite{Morud1998}, but one cannot rule out that the observed oscillations
+could in some systems also be created by inherent processes on the catalyst
+itself. In general such oscillations would be considered highly undesirable in
+industry since they could be difficult to control and result in run-away
+incidents in particular for exothermic reactions resulting in damaged catalyst
+due to sintering at higher temperatures. On the other hand there exist examples
+in the literature where forced oscillations seem to improve the overall
+activity \cite{IMBIHL1995,Machado2005} . One particular interesting process
+here could be the methanol synthesis where reducing the CO$_2$ contents for a
+shorter period of time result in a subsequent higher methanol rate over
+compensation for the lack of methanol production when running in the reducing
+H$_2$ and CO alone \cite{Dynamics-Bog}. This enhancement can be explained by
+extensive wetting and un-wetting of the active Copper catalyst dependent on the
+oxidation potential \cite{Hansen2002} i.e. the active area is strongly
+increased when reduced but slowly returns to the less active state when the
+CO$_2$ is present.
 
@@
 
-A) D. A. McLulich, Variations in the Number of Varying Hare,University of Toronto
-Press, Toronto, 1937. (we need to dig in for the correct ref here),
 B) I remember reading of this in a biology book back in the seventies, check)

### 2012-04-18 paper.tex
First corrections after inserting Ib's new introduction

--- 2012-03-20 paper.tex
@@
 \author{Anders Nierhoff}
-\affiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark.}
+\affiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej, Building 312, 2800 Kgs. Lyngby, Denmark.}
 \author{Thomas Pedersen}
 \author{Ole Hansen}
-\affiliation{CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, \O rsteds Plads, B 345B, 2800 Lyngby, Denmark.}
+\affiliation{CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, \O rsteds Plads, Building 345B, 2800 Kgs. Lyngby, Denmark.}
 \author{S\o ren Dahl}
@@
 \email{ibchork@fysik.dtu.dk}
-\affiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark.}
+\affiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej, Building 312, 2800 Kgs. Lyngby, Denmark.}
 
@@
 \section{Introduction}
-CO oxidation is one of the most studied reactions due to its importance in both automotive catalysis and in the removal of trace CO in hydrogen streams.
-A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
-Single crystal surfaces are well suited model systems due to the high degree of achievable control of parameters compared to industrial catalysts.
-Here we report on studies in a microreactor model system of Pt nanoparticles.
-The size-selected nanoparticles supported on a SiO$_2$ substrate show oscillatory behavior of CO oxidation at atmospheric pressure.
 
-Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
-It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows oscillatory behavior on single crystals of Pt, Pd and Ir.
-Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface formation.
-CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
-Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.
+Self-sustained oscillating systems are widespread in nature and have been
+described both experimentally and theoretically. One of the maybe most famous
+biological examples is the oscillation of the lynx-hare population as reported
+through the number furs delivered to the Hudson Bay
+Company\cite{MacLulich,Elton1942}. This was for some time believed to be forced
+by sunspot oscillations\cite{Elton1924}. Even though the correlation between
+sunspots and the lynx-hare population has been debated, even as recently as
+1993\cite{SINCLAIR1993}, this is not believed to determine the lynx-hare
+population\cite{Elton1942,Kielland2010}. Instead, the periodic population cycle
+can be explained by more classic weather phenomena. Similarly, very interesting
+observations have been made for our current climate
+changes\cite{Svensmark1997,Svensmark1998} suggesting that the sunspot activity
+influences the level of cosmic rays and thus the cloud formation. This topic
+is, however, a topic of controversy\cite{Lockwood2007}.
+
+A beautiful example of self-sustained oscillatory behavior in chemistry is the
+colorful Belousov- Zhabotinsky reaction\cite{ZAIKIN1970} which is rather easy
+to demonstrate for an audience. Such self-sustained oscillatory behavior has
+been explained for systems far from equilibrium in several theoretical
+works\cite{HakenBog,NicolisBog}. Similar behavior has been observed within
+heterogeneous catalysis where typically nanoparticles of a precious metal
+supported on an inexpensive oxide constitute the active phase\cite{IbsBog}. One
+of the very first examples was observed by Wicke for CO oxidation on a catalyst
+of highly dispersed Pt on $\gamma$-Al$_2$O$_3$\cite{BEUSCH1972}. To gain a
+deeper insight into the fundamental aspects of such oscillatory reactions this
+work was followed up by Ertl on Pt(110) surfaces under well-defined conditions
+\cite{EISWIRTH1986}. Ertl demonstrated how the switching between the
+unreconstructed Pt(110) surface and the reconstructed 2x1-Pt(110) surface
+combined with large changes of oxygen sticking coefficient on the two surfaces
+could drive the self-sustained oscillations. This and many other interesting
+aspects of self-sustained and forced oscillatory behavior and spatio-temporal
+self-organization were investigated by Ertl and coworkers on well-defined
+single crystals, see e.g. reviews\cite{IMBIHL1995,JAKUBITH1990} and in
+particular the Nobel Lecture\cite{Ertl2008}. One of the reasons this has
+attracted interest is the importance of such catalytic reactions demanding a
+better understanding of their behavior with the goal of further improvement.
+
+CO oxidation is one of the most studied reactions due to its importance in both
+automotive catalysis and in the removal of trace CO in hydrogen
+streams\cite{IbsBog}. The oscillatory behavior is not, however, limited to
+either Pt or CO oxidation but have been found for many other metallic catalysts
+like Rh, Ir, and Pd for oxidation reactions in general, NO and CO reactions and
+even for hydrogenation reactions \cite{Lund2000,SALES1982}. Most of the studies
+are made on single crystal or polycrystalline films or filaments mainly in
+conjunction with ultra-high vacuum equipment to be able to characterize the
+catalyst surfaces using surface science methods. The amount of work described
+on supported catalysts seems more limited due to the difficulty of
+characterizing those systems and because additional complexities are present
+such as mass and heat transport. Reports in the literature exist of how large
+scale facilities such as an industrial ammonia fixed-bed synthesis reactor in
+Germany in 1989 started oscillating for several hours. This could be modeled by
+coupling of the exothermic process and the heat management in the reactor
+system \cite{Morud1998} but one cannot rule out that the observed oscillations
+could in some systems also be created by inherent processes on the catalyst
+itself. In general such oscillations would be considered highly undesirable in
+industry since they would be difficult to control and result in run-away
+incidents for, in particular, exothermic reactions. This would result in
+damaged catalysts due to sintering at higher temperatures. On the other hand
+examples exist in literature where forced oscillations seem to improve the
+overall activity\cite{IMBIHL1995,Machado2005}. One particular interesting
+process here could be the methanol synthesis where a reduction of the CO$_2$
+content for a shorter period of time results in a subsequent higher methanol
+rate compensating for a lower methanol production while running in a
+reducing H$_2$ and CO mixture alone\cite{Dynamics-Bog}. This enhancement can
+be explained by an extensive wetting and un-wetting of the active Cu catalyst
+dependent on the oxidation potential\cite{Hansen2002}, i.e. the active area is
+strongly increased when reduced but slowly returns to the less active state
+when CO$_2$ is present.
+
+As mentioned the understanding of self-sustained oscillations on supported
+catalysts is hampered by the fact that entirely different mechanisms than those
+observed on single and polycrystalline samples may exist. For example it was
+shown on a Pt(110) crystal how waves of surface reconstruction could propagate
+on the surface ensuring a synchronization of the phenomena. This also have to
+occur for oscillations on supported catalysts but here it is more likely to be
+due to coupling of mass or heat transport. There have been a few examples where
+such oscillations have been observed. Of these the most prominent work is by
+Skoghlund\cite{Carlsson2006} where self-sustained oscillations were observed on
+a supported Pt catalyst while simultaneously studying the catalyst by in-situ
+IR spectrometry. Similar studies were recently undertaken using EXAFS
+\cite{Singh2010} but here the oscillatory behavior was unstable and less
+convincing.
+
+In this work we demonstrate how a two-dimensional model system of Pt
+nanoparticles on a SiO$_2$ support can be constructed that shows highly
+repeatable self-sustained oscillations when initially started. The system
+consist of mass selected Pt nanoparticles in the range from 2 to 10\,nm Pt
+nanoparticles deposited in a microreactor with a surface area of 0.75\,cm$^2$
+especially designed to achieve high sensitivity\cite{Henriksen2009}. This
+method offers some advantages over the chemical synthesis methods, which also
+offers the possibility of size selected nanoparticles, see e.g.
+\cite{Tsang2008,Shao2011}. Particularly, surfactants, which are required for
+chemical synthesis methods, are avoided with gas-aggregation formed particles
+while still being able to vary the coverage from sub-percent to full coverage.
+It is demonstrated how the nanoparticles could provide self-sustained
+oscillations over extend of days and how various parameters could be mapped out
+including the temperature dependence -- an effect that could
+not be demonstrated for a continuous film of same area and similar conditions.
+By combining these results with previous studies \cite{Carlsson2006,Singh2010}
+and a recent detailed study of CO oxidation on Pd using STM
+\cite{Hendriksen2010} a plausible explanation for the oscillatory behavior is
+presented. The low coverage and extremely efficient Pt nanoparticles illustrate
+some of the pit falls that may have to be considered when making in-situ
+investigations of such a system since extremely low coverages may provide the
+entire conversion.
 
@@
 The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume.
-The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0-2.5\,bar.
-The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min.
+The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0--2.5\,bar.
+The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0--10 mL/min.
 The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
 The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system.
-
 \begin{scheme}
@@
 \end{scheme}
-
 Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.

### 2012-04-18 paper.tex
Added Ibs reactor figure. Increased size of some figures.
Larger figures fits better in the layout used for manuscripts
used for submission to ACS-Nano.

@@
 \begin{scheme}
-  \includegraphics[width=8cm]{reactor.jpg}
+  \includegraphics[width=8cm]{Ib-reactor.png}
   \caption{Image of the 20x16\,mm microreactor showing the circular reactor area and gas channel system}
@@
 \begin{scheme}
-  \includegraphics[width=9cm]{initial_treatment.png}
+  \includegraphics[width=12cm]{initial_treatment.png}
   \caption{A typical example of the initial treatment of a new sample.
@@
 \begin{scheme}
-  \includegraphics[width=17cm]{single_full_oscillation.png}
+  \includegraphics[width=16cm]{single_full_oscillation.png}
   \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate deactivation.
@@
 \begin{scheme}
-  \includegraphics[width=9cm]{summary_of_long_measurement.png}
+  \includegraphics[width=12cm]{summary_of_long_measurement.png}
   \caption{Summary of the oscillation period as a function of time for a sample oscillating under constant temperature, pressure and reactant composition.
@@
 \begin{scheme}
-  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
+  \includegraphics[width=12cm]{extracts_from_very_long_oscillation.png}
   \caption{Extracts from the 4 days long experiment.
@@
 \begin{scheme}
-  \includegraphics[width=9cm]{temperature_dependence.png}
+  \includegraphics[width=12cm]{temperature_dependence.png}
   \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C.
@@
 \begin{scheme}
-  \includegraphics[width=9cm]{oscillations_gas_dependence_summary_supplemental.png}
+  \includegraphics[width=12cm]{oscillations_gas_dependence_summary_supplemental.png}
   \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
@@
 \centering
-  \includegraphics[width=9cm]{temperature_dependence_supplemental.png}
+  \includegraphics[width=12cm]{temperature_dependence_supplemental.png}
   \caption{Another example of the very pronounced temperature dependence.}
@@
 \begin{scheme}
-  \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
+  \includegraphics[width=12cm]{duty_cycles_long_measurement_supplemental.png}
   \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment.

### 2012-04-18 paper.tex
Further changes to the article

@@
   \includegraphics[width=12cm]{temperature_dependence.png}
-  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C.
-Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
+  \caption{Illustration of the strong temperature dependence.
+After about 10 hours of steady oscillations at 205$^\circ$C the temperature is lowered by 5$^\circ$C immediately decreasing the oscillation frequency.
+The temperature is hereafter increased by 2$^\circ$C resulting in an increase in oscillation frequency.
+At 205$^\circ$C the oscillation period was approximately 500\,s while the oscillation period period is approximately 5000\,s.
+at 203$^\circ$C}
   \label{fgr:temperature_dependence}
@@
 
-\begin{scheme}
+\begin{figure}
   \includegraphics[width=12cm]{oscillations_gas_dependence_summary_supplemental.png}
-  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
+  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is superimposed with small discontinuous steps when the CO concentration is increased.}
   \label{fgr:gas_dependence_summary}
-\end{scheme}
+\end{figure}
 
-\begin{scheme}
+\begin{figure}
   \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
@@
   \label{fgr:gas_dependence}
-\end{scheme}
+\end{figure}
 

### 2012-04-19 paper.tex
Added more ACS-Nano references and started to re-organize the structure

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Introduction}
+%\section{Introduction}
 
@@
 sunspots and the lynx-hare population has been debated, even as recently as
-1993\cite{SINCLAIR1993}, this is not believed to determine the lynx-hare
-population\cite{Elton1942,Kielland2010}. Instead, the periodic population cycle
+1993\cite{SINCLAIR1993}, this is not generally believed to be the case
+\cite{Elton1942,Kielland2010}. Instead, the periodic population cycle
 can be explained by more classic weather phenomena. Similarly, very interesting
@@
 works\cite{HakenBog,NicolisBog}. Similar behavior has been observed within
-heterogeneous catalysis where typically nanoparticles of a precious metal
-supported on an inexpensive oxide constitute the active phase\cite{IbsBog}. One
-of the very first examples was observed by Wicke for CO oxidation on a catalyst
+heterogeneous catalysis where one of very first examples was observed by Wicke
+for CO oxidation on a catalyst
 of highly dispersed Pt on $\gamma$-Al$_2$O$_3$\cite{BEUSCH1972}. To gain a
@@
 automotive catalysis and in the removal of trace CO in hydrogen
-streams\cite{IbsBog}. The oscillatory behavior is not, however, limited to
+streams\cite{IbsBog,Zhang2011}. The oscillatory behavior is not, however, limited to
 either Pt or CO oxidation but have been found for many other metallic catalysts
-like Rh, Ir, and Pd for oxidation reactions in general, NO and CO reactions and
-even for hydrogenation reactions \cite{Lund2000,SALES1982}. Most of the studies
+like Rh, Ir, and Pd for oxidation reactions in general, NO and CO reactions,
+hydrogenation reactions \cite{Lund2000,SALES1982} and redox
+systems\cite{Ibele2010}. Most of the studies
 are made on single crystal or polycrystalline films or filaments mainly in
-conjunction with ultra-high vacuum equipment to be able to characterize the
+conjunction with ultra-high vacuum equipment to be able to characterize
 catalyst surfaces using surface science methods. The amount of work described
@@
 characterizing those systems and because additional complexities are present
-such as mass and heat transport. Reports in the literature exist of how large
+such as mass and heat transport\cite{Meunier2008}. Reports in the literature
+exist of how large
 scale facilities such as an industrial ammonia fixed-bed synthesis reactor in
@@
 shown on a Pt(110) crystal how waves of surface reconstruction could propagate
-on the surface ensuring a synchronization of the phenomena. This also have to
+on the surface ensuring a synchronization of the phenomena. Synchronization also have to
 occur for oscillations on supported catalysts but here it is more likely to be
@@
 repeatable self-sustained oscillations when initially started. The system
-consist of mass selected Pt nanoparticles in the range from 2 to 10\,nm Pt
-nanoparticles deposited in a microreactor with a surface area of 0.75\,cm$^2$
+consist of mass selected Pt nanoparticles in the range from 2 to 10\,nm 
+deposited in a microreactor with a surface area of 0.75\,cm$^2$
 especially designed to achieve high sensitivity\cite{Henriksen2009}. This
@@
 offers the possibility of size selected nanoparticles, see e.g.
-\cite{Tsang2008,Shao2011}. Particularly, surfactants, which are required for
+\cite{Tsang2008,Shao2011}. Particularly, surfactants or solvents
+\cite{Biacchi2011}, which are required for
 chemical synthesis methods, are avoided with gas-aggregation formed particles
 while still being able to vary the coverage from sub-percent to full coverage.
-It is demonstrated how the nanoparticles could provide self-sustained
-oscillations over extend of days and how various parameters could be mapped out
+It is demonstrated how the nanoparticles provides self-sustained
+oscillations over extend of days and how various parameters can be mapped out
 including the temperature dependence -- an effect that could
@@
 
-\section{Experimental Methods}
-\subsection{The $\mu$-reactor platform}
-The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
-The reactor design makes sure that all gases exposed to the catalyst under investigation is measured by the quadropole mass spectrometer (QMS) ensuring an extremely high sensitivity of the system.
-
-The experiments were performed in Si-based 20x16\,mm $\mu$-reactors\cite{Henriksen2009}.
-The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume.
-The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0--2.5\,bar.
-The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0--10 mL/min.
-The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
-The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system.
-\begin{scheme}
-  \includegraphics[width=8cm]{Ib-reactor.png}
-  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area and gas channel system}
-  \label{fgr:reactor}
-\end{scheme}
-Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.
-When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMS chamber.
-
-The reactor is heated by joule heating of a Pt strip evaporated on the backside of the reactor chip.
-The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the Pt strip using it as a RTD for temperature measurement of the reactor.
-An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
-The measured RTD temperature is always compared to the thermocouple at room temperature both before and after an experiment to be sure the RTD did not change resistance due to annealing during the experiment.
-
-The gas handling including flow and pressure controllers and the mass spectrometer is fully automated allowing for measurements during several days without human intervention allowing for self-consistent measurements of many samples.
-
-\subsection{Pt nanoparticle deposition}
-Pt nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
-Pt clusters were formed by gas-phase condensation of Pt atoms produced by impinging argon ions on a 99.99\% Pt target in a magnetron sputter source.
-After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
-Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2010,Nielsen2009}.
-The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor.
-The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition.
-After deposition the reactors were anodically cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
-
-\section{Results}
+\section{Results and discussion}
 An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding.
@@
 
-\begin{scheme}
+\begin{figure}
   \includegraphics[width=12cm]{initial_treatment.png}
@@
   \label{fgr:initial_treatment}
-\end{scheme}
+\end{figure}
 
@@
 
-\begin{scheme}
+Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.
+Furthermore, a series of experiments was performed to exclude the oscillations as an instrumental artifact.
+Firstly, experiments were performed on larger volume reactor thus increasing the residence time in the reactor.
+Secondly, the oscillations were reproduced on a comparable but not identical setup.
+Finally, attempts at reproducing the phenomenon on Pt-thin films of comparable coverage did not produce any oscillations.
+All of these experiments suggest that the oscillations is a property of the Pt nanoparticles.
+
+\begin{figure}
   \includegraphics[width=16cm]{single_full_oscillation.png}
@@
   \label{fgr:full_oscillation}
-\end{scheme}
+\end{figure}
 
@@
 
-\begin{scheme}
+\begin{figure}
   \includegraphics[width=12cm]{summary_of_long_measurement.png}
@@
   \label{fgr:long_measurement}
-\end{scheme}
+\end{figure}
 
@@
 Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
-\begin{scheme}
+\begin{figure}
   \includegraphics[width=12cm]{extracts_from_very_long_oscillation.png}
@@
   \label{fgr:extracts}
-\end{scheme}
+\end{figure}
 
@@
 
-\begin{scheme}
+The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}.
+This phenomena is consistent across all measured samples.
+The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
+Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
+A possible explanation of the phenomeonon could be sintering of the particles during the oxidation and reductions cycles.
+However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.
+
+It has previously been shown using STM \cite{Hendriksen2002}, FT-IR \cite{Carlsson2006}, Monte Carlo simulations \cite{Zhdanov2002} as well as DFT \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
+A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et.
+al.}\cite{Hendriksen2010} and our data is consistent with this model.
+
+According to the proposed model in ref.~\citenum{Hendriksen2010} the bare metal surface is less active than the oxidized surface.
+Oscillations originate from a switch between an oxidized surface and the bare metal surface.
+Initially, with CO present in the inlet gas a smooth metal surface is exposed due to the general high adsorption energy of CO on metal surfaces.
+As the Pt nanoparticles convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt oxide will start to form in the high partial pressures of O$_2$ thus increasing the rate.
+The model\cite{Hendriksen2010} suggests that the oxidized nanoparticles will roughen during CO oxidation resulting in the formation of an increasingly rough oxide surface.
+As the oxide becomes rougher the bare metal surface is increasingly favored resulting in a return to the lower rate rough metal state.
+As the rate decreases the CO partial pressure increases which results in a transition from rough metal surface to a smooth metal surface.
+When the sample is sufficiently smooth it will again oxidize and thus complete the oscillation cycle.
+
+\begin{figure}
   \includegraphics[width=12cm]{temperature_dependence.png}
@@
   \label{fgr:temperature_dependence}
-\end{scheme}
+\end{figure}
 
@@
 By changing the temperature 5$^\circ$C the oscillation period was changed by more than a factor of 10.
-The magnitude of the change is not completely consistent across all measured samples but all samples show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.
+The magnitude of the change is not completely consistent across all measured samples but all samples show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations by changing the temperature $20^\circ$C, see Figure~\ref{fgr:temperature_dependence_supplemental}.
+
+\begin{figure}
+\centering
+  \includegraphics[width=12cm]{temperature_dependence_supplemental.png}
+  \caption{Another example of the very pronounced temperature dependence.}
+  \label{fgr:temperature_dependence_supplemental}
+\end{figure}
+
+An interesting feature in the data is the very large temperature dependence on oscillation frequency.
+This property agrees well an earlier suggested model \cite{Hendriksen2010} and it is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
 
@@
 
+Oscillations were only seen in CO/O$_2$ ratio below 0.175.
+This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
+The needed low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on Pt which poisons the nanoparticle surface during the low reactivity region of the cycle.
+
+Nanoparticles of several different sizes were tested and all showed oscillations.
+However, no change in duty cycle or frequency that could be attributed to the size of the nanoparticles was found.
+This may be due to the fact that even nominally identical samples also show a large variation in oscillation frequency and duty cycle thus possibly shadowing a nanoparticle size effect.
+
 \begin{figure}
@@
 
-\begin{scheme}
+\begin{figure}
 \centering
@@
   \label{fgr:temperature_dependence_supplemental}
-\end{scheme}
+\end{figure}
+
+An interesting feature in the data is the very large temperature dependence on oscillation frequency.
+This property agrees well an earlier suggested model \cite{Hendriksen2010} and it is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
 
@@
 
-\begin{scheme}
+\begin{figure}
   \includegraphics[width=12cm]{duty_cycles_long_measurement_supplemental.png}
@@
   \label{fgr:duty_cycles_supplemental}
-\end{scheme}
-
-\section{Discussion}
-Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.
-Furthermore, a series of experiments was performed to exclude the oscillations as an instrumental artifact.
-Firstly, experiments were performed on larger volume reactor thus increasing the residence time in the reactor.
-Secondly, the oscillations were reproduced on a comparable but not identical setup.
-Finally, attempts at reproducing the phenomenon on Pt-thin films of comparable coverage did not produce any oscillations.
-All of these experiments suggest that the oscillations is a property of the Pt nanoparticles.
-
-It has previously been shown using STM \cite{Hendriksen2002}, FT-IR \cite{Carlsson2006}, Monte Carlo simulations \cite{Zhdanov2002} as well as DFT \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
-A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et.
-al.}\cite{Hendriksen2010} and our data is consistent with this model.
-
-According to the proposed model in ref.~\citenum{Hendriksen2010} the bare metal surface is less active than the oxidized surface.
-Oscillations originate from a switch between an oxidized surface and the bare metal surface.
-Initially, with CO present in the inlet gas a smooth metal surface is exposed due to the general high adsorption energy of CO on metal surfaces.
-As the Pt nanoparticles convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt oxide will start to form in the high partial pressures of O$_2$ thus increasing the rate.
-The model\cite{Hendriksen2010} suggests that the oxidized nanoparticles will roughen during CO oxidation resulting in the formation of an increasingly rough oxide surface.
-As the oxide becomes rougher the bare metal surface is increasingly favored resulting in a return to the lower rate rough metal state.
-As the rate decreases the CO partial pressure increases which results in a transition from rough metal surface to a smooth metal surface.
-When the sample is sufficiently smooth it will again oxidize and thus complete the oscillation cycle.
+\end{figure}
 
@@
 
-The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}.
-This phenomena is consistent across all measured samples.
-The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
-Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
-A possible explanation of the phenomeonon could be sintering of the particles during the oxidation and reductions cycles.
-However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.
-
-Oscillations were only seen in CO/O$_2$ ratio below 0.175.
-This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
-The needed low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on Pt which poisons the nanoparticle surface during the low reactivity region of the cycle.
-
-Nanoparticles of several different sizes were tested and all showed oscillations.
-However, no change in duty cycle or frequency that could be attributed to the size of the nanoparticles was found.
-This may be due to the fact that even nominally identical samples also show a large variation in oscillation frequency and duty cycle thus possibly shadowing a nanoparticle size effect.
-
-An interesting feature in the data is the very large temperature dependence on oscillation frequency.
-This property agrees well an earlier suggested model \cite{Hendriksen2010} and it is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
-
-\section{Conclusion}
+\section{Conclusions}
 Self-sustained CO oxidation oscillations at atmospheric pressure on Pt nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-quality mass-spectrometry.
@@
 
+\section{Experimental Methods}
+\subsection{The $\mu$-reactor platform}
+The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
+The reactor design makes sure that all gases exposed to the catalyst under investigation is measured by the quadropole mass spectrometer (QMS) ensuring an extremely high sensitivity of the system.
+
+The experiments were performed in Si-based 20x16\,mm $\mu$-reactors\cite{Henriksen2009}.
+The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume.
+The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0--2.5\,bar.
+The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0--10 mL/min.
+The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
+The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system.
+\begin{figure}
+  \includegraphics[width=8cm]{Ib-reactor.png}
+  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area and gas channel system}
+  \label{fgr:reactor}
+\end{figure}
+Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.
+When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMS chamber.
+
+The reactor is heated by joule heating of a Pt strip evaporated on the backside of the reactor chip.
+The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the Pt strip using it as a RTD for temperature measurement of the reactor.
+An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
+The measured RTD temperature is always compared to the thermocouple at room temperature both before and after an experiment to be sure the RTD did not change resistance due to annealing during the experiment.
+
+The gas handling including flow and pressure controllers and the mass spectrometer is fully automated allowing for measurements during several days without human intervention allowing for self-consistent measurements of many samples.
+
+\subsection{Pt nanoparticle deposition}
+Pt nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
+Pt clusters were formed by gas-phase condensation of Pt atoms produced by impinging argon ions on a 99.99\% Pt target in a magnetron sputter source.
+After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
+Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2010,Nielsen2009}.
+The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor.
+The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition.
+After deposition the reactors were anodically cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
+
 \bibliography{literature} %your .bib file

### 2012-04-19 paper.tex
More adaptation to ASC-Nano

@@
 \section{Results and discussion}
-An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding.
-Initially a light-off CO-oxidation measurement is performed (shown in Figure~\ref{fgr:initial_treatment}) where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
-At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C.
-The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp.
-After the initial light-off the sample is cooled to room temperature.
-When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur.
-A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical light-off ramp and the subsequent increase in temperature to achieve sustained oscillations is seen.
-Often the sample will show oscillations either directly upon light-off or on the falling temperature ramp.
+An oscillation measurement is performed by mounting a sample in the setup
+directly after cluster deposition and anodic bonding. Initially a light-off CO-
+oxidation measurement is performed (shown in \ref{fgr:initial_treatment}) where
+the temperature is increased at 3\,$^\circ$C/min until the sample ignites and
+achieves full conversion of CO to CO$_2$. At CO:O$_2$ ratio of $\sim0.08$ and a
+geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately
+180\,$^\circ$C. The temperature ramp is typically continued up to
+260\,$^\circ$C whereafter the temperature is decreased at the same rate as the
+heating ramp. After the initial light-off the sample is cooled to room
+temperature. When at room temperature the temperature is again increased at
+3\,$^\circ$C/min until sustained oscillations occur. A typical initial
+treatment is seen in \ref{fgr:initial_treatment} where both the symmetrical
+light-off ramp and the subsequent increase in temperature to achieve sustained
+oscillations is seen. Often the sample will show oscillations either directly
+upon light-off or on the falling temperature ramp.
 
@@
   \includegraphics[width=12cm]{initial_treatment.png} 
-  \caption{A typical example of the initial treatment of a new sample.
-After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.
-The non-zero value of CO during high conversion periods is consistent with the expected QMS background signals from CO$_2$ and O$_2$.}
+  \caption{A typical example of the initial treatment of a new sample. After
+  performing a light- off ramp where oscillations can been seen the temperature
+  is increased to a constant value where sustained oscillations take place. The
+  non-zero value of CO during high conversion periods is consistent with the
+  expected QMS background signals from CO$_2$ and O$_2$.}
   \label{fgr:initial_treatment}
@@
 
-Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations.
-No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.
+Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm
+particles with a geometrical coverage of 0.1\% of the reactor area gave the
+most stable oscillations. No consistent dependency on oscillation frequency and
+duty cycle was found that could be attributed to the size of the particles.
 
-The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s) up to more than an hour.
-Once a sample start to oscillate it will perform self-sustained oscillations for as long as the experiment is allowed to run.
-We have not observed a single sample stop oscillating once the self-sustained oscillations had started.
+The oscillations on all samples are qualitatively similar but the oscillation
+period varies from a few seconds (the time-constant of the reactor is
+$\sim7\,$s) up to more than an hour. Once a sample start to oscillate it will
+perform self-sustained oscillations for as long as the experiment is allowed to
+run. We have not observed a single sample stop oscillating once the self-
+sustained oscillations had started.
 
-An example of a single very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
-After a short on-cycle (at $\sim$1030\,min) where all CO is converted to CO$_2$ (notice the CO signal does not go to zero due to the cracking pattern of CO$_2$ and CO background in the QMS) the reaction shows a fast deactivation.
-After the deactivation the sample quickly regains $\sim$30\% conversion (at $\sim$1040\,min).
-Hereafter the conversion increases slowly over time until approximately 50\% conversion is reached (at $\sim$1118\,min).
-Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$.
-After a short full conversion period the sample again deactivates and the cycle repeats itself.
+An example of a single very slow oscillation is seen in
+\ref{fgr:full_oscillation}. After a short on-cycle (at $\sim$1030\,min) where
+all CO is converted to CO$_2$ (notice the CO signal does not go to zero due to
+the cracking pattern of CO$_2$ and CO background in the QMS) the reaction shows
+a fast deactivation. After the deactivation the sample quickly regains
+$\sim$30\% conversion (at $\sim$1040\,min). Hereafter the conversion increases
+slowly over time until approximately 50\% conversion is reached (at
+$\sim$1118\,min). Shortly after reaching 50\% conversion the sample again
+ignites and convert all CO to CO$_2$. After a short full conversion period the
+sample again deactivates and the cycle repeats itself.
 
-Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.
-Furthermore, a series of experiments was performed to exclude the oscillations as an instrumental artifact.
-Firstly, experiments were performed on larger volume reactor thus increasing the residence time in the reactor.
-Secondly, the oscillations were reproduced on a comparable but not identical setup.
-Finally, attempts at reproducing the phenomenon on Pt-thin films of comparable coverage did not produce any oscillations.
-All of these experiments suggest that the oscillations is a property of the Pt nanoparticles.
+Due to the long timescales between full conversion and low conversion plateaus
+the oscillations cannot be attributed to the reactor setup itself which due to
+its small size has timescales on the order of seconds. Furthermore, a series of
+experiments was performed to exclude the oscillations as an instrumental
+artifact. Firstly, experiments were performed on a larger volume reactor thus
+increasing the residence time in the reactor. Secondly, the oscillations were
+reproduced on a comparable but not identical setup. Finally, attempts at
+reproducing the phenomenon on Pt-thin films of comparable coverage did not
+produce any oscillations. All of these experiments suggest that the
+oscillations is a property of the Pt nanoparticles.
 
@@
   \includegraphics[width=16cm]{single_full_oscillation.png}
-  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate deactivation.
-For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.
-This extremely long oscillation period is not commonly seen and was a result of careful parameter tuning.
-Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,min.
-Inserted circles illustrates the proposed model.
-At high conversion the platinum is oxidized (red) while in low conversion the sample is reduced (blue).}
-  \label{fgr:full_oscillation}
+  \caption{A full oscillation period first showing a steep ignition of the
+  sample followed by an almost immediate deactivation. For the next 65 minutes
+  the sample slowly recovers activity until full conversion is reached again
+  and the cycle repeats itself. This extremely long oscillation period is not
+  commonly seen and was a result of careful parameter tuning. Typical
+  oscillation periods are normally between $\sim$30\,s and $\sim$30\,min.
+  Inserted circles illustrates the proposed model. At high conversion the
+  platinum is oxidized (red) while in low conversion the sample is reduced
+  (blue).} \label{fgr:full_oscillation}
 \end{figure}
 
-After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}.
-Initially, the oscillation period is $\sim$2.5 min and increases linearly with time until 1500 min of total oscillation time.
-Hereafter the oscillations become more irregular as shown in Figure~\ref{fgr:extracts} and lower panel Figure~\ref{fgr:long_measurement}.
-At experiment end the oscillation period is between 20 and 45 min.
+After prolonged measurements over several days an increase in oscillation
+period was observed as shown in \ref{fgr:long_measurement}. Initially, the
+oscillation period is $\sim$2.5 min and increases linearly with time until 1500
+min of total oscillation time. Hereafter the oscillations become more irregular
+as shown in \ref{fgr:extracts} and lower panel \ref{fgr:long_measurement}. At
+experiment end the oscillation period is between 20 and 45 min.
 
@@
   \includegraphics[width=12cm]{summary_of_long_measurement.png}
-  \caption{Summary of the oscillation period as a function of time for a sample oscillating under constant temperature, pressure and reactant composition.
-The sample went through a total of 439 oscillations in 4 days.
-Time is defined from experiment start and hence includes initial treatment.
-The inset shows the initial steady increase in oscillation period.}
+  \caption{Summary of the oscillation period as a function of time for a sample
+  oscillating under constant temperature, pressure and reactant composition.
+  The sample went through a total of 439 oscillations in 4 days. Time is
+  defined from experiment start and hence includes initial treatment. The inset
+  shows the initial steady increase in oscillation period.}
   \label{fgr:long_measurement}
@@
 
-Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four days measurement.
-Data from shortly after the initial treatment, after 2800\,min of oscillation time and after 5900\,min are shown.
-After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
-Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
+\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations
+extracted from the same four days measurement. Data from shortly after the
+initial treatment, after 2800\,min of oscillation time and after 5900\,min are
+shown. After 5900\,min the oscillations are more irregular which is consistent
+with the data shown in \ref{fgr:long_measurement}. Also, oscillations in
+between full conversion oscillations with smaller amplitude and much higher
+frequency than the full on-off cycles become more visible as time progresses.
 \begin{figure}
   \includegraphics[width=12cm]{extracts_from_very_long_oscillation.png}
-  \caption{Extracts from the 4 days long experiment.
-The oscillation period becomes more irregular with time while the total integrated conversion remains constant.
-Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
-  \label{fgr:extracts}
+  \caption{Extracts from the 4 days long experiment. The oscillation period
+  becomes more irregular with time while the total integrated conversion
+  remains constant. Furthermore, small oscillations in between full conversion
+  cycles become more prominent as time progresses.} \label{fgr:extracts}
 \end{figure}
 
-The oscillation frequency becomes more irregular with progressing experiment time as shown in Figure \ref{fgr:extracts}.
-However, the ratio between CO and CO$_2$ integrated over an full period remains constant throughout the entire experiment time, i.e.
-the samples maintains a constant average rate independent of oscillation frequency.
+The oscillation period increases with time and becomes increasingly less stable
+as shown in \ref{fgr:extracts}. This phenomena is  consistent across all
+measured samples. The large scatter in oscillation period can be attributed to
+the smaller oscillations in between on/off cycles. Occasionally, these small
+amplitude oscillations will trigger a full switch thus introducing more short-
+period oscillations despite the trend of increasingly slower oscillation
+period. A possible explanation of the phenomeonon could be sintering of the
+particles during the oxidation and reductions cycles. However, the ratio
+between CO and CO$_2$ integrated over an full period remains constant
+throughout the entire experiment time, i.e. the samples maintains a constant
+average rate independent of oscillation frequency. Thus we do not expect
+sintering to be the cause since an average loss in activity of the sample would
+then be expected.
 
-The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}.
-This phenomena is consistent across all measured samples.
-The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
-Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
-A possible explanation of the phenomeonon could be sintering of the particles during the oxidation and reductions cycles.
-However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.
+It has previously been shown using STM \cite{Hendriksen2002}, FT-IR
+\cite{Carlsson2006}, Monte Carlo simulations \cite{Zhdanov2002} as well as DFT
+\cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric
+pressures is highly dependent on the oxidation state of the surface. A detailed
+proposal for the reaction mechanism on Pd has been developed by Hendriksen
+\textit{et. al.}\cite{Hendriksen2010} and our data is consistent with this
+model.
 
-It has previously been shown using STM \cite{Hendriksen2002}, FT-IR \cite{Carlsson2006}, Monte Carlo simulations \cite{Zhdanov2002} as well as DFT \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
-A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et.
-al.}\cite{Hendriksen2010} and our data is consistent with this model.
+According to the proposed model in ref.~\citenum{Hendriksen2010} the bare metal
+surface is less active than the oxidized surface. Oscillations originate from a
+switch between an oxidized surface and the bare metal surface. Initially, with
+CO present in the inlet gas a smooth metal surface is exposed due to the
+general high adsorption energy of CO on metal surfaces. As the Pt nanoparticles
+convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt
+oxide will start to form in the high partial pressures of O$_2$ thus increasing
+the rate. The model\cite{Hendriksen2010} suggests that the oxidized
+nanoparticles will roughen during CO oxidation resulting in the formation of an
+increasingly rough oxide surface. As the oxide becomes rougher the bare metal
+surface is increasingly favored resulting in a return to the lower rate rough
+metal state. As the rate decreases the CO partial pressure increases which
+results in a transition from rough metal surface to a smooth metal surface.
+When the sample is sufficiently smooth it will again oxidize and thus complete
+the oscillation cycle.
 
-According to the proposed model in ref.~\citenum{Hendriksen2010} the bare metal surface is less active than the oxidized surface.
-Oscillations originate from a switch between an oxidized surface and the bare metal surface.
-Initially, with CO present in the inlet gas a smooth metal surface is exposed due to the general high adsorption energy of CO on metal surfaces.
-As the Pt nanoparticles convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt oxide will start to form in the high partial pressures of O$_2$ thus increasing the rate.
-The model\cite{Hendriksen2010} suggests that the oxidized nanoparticles will roughen during CO oxidation resulting in the formation of an increasingly rough oxide surface.
-As the oxide becomes rougher the bare metal surface is increasingly favored resulting in a return to the lower rate rough metal state.
-As the rate decreases the CO partial pressure increases which results in a transition from rough metal surface to a smooth metal surface.
-When the sample is sufficiently smooth it will again oxidize and thus complete the oscillation cycle.
-
+\subsection{Temperature dependence}
 \begin{figure}
 \includegraphics[width=12cm]{temperature_dependence.png}
-  \caption{Illustration of the strong temperature dependence.
-After about 10 hours of steady oscillations at 205$^\circ$C the temperature is lowered by 5$^\circ$C immediately decreasing the oscillation frequency.
-The temperature is hereafter increased by 2$^\circ$C resulting in an increase in oscillation frequency.
-At 205$^\circ$C the oscillation period was approximately 500\,s while the oscillation period period is approximately 5000\,s.
-at 203$^\circ$C}
+\caption{Illustration of the strong temperature dependence. After about 10
+  hours of steady oscillations at 205$^\circ$C the temperature is lowered by
+  5$^\circ$C immediately decreasing the oscillation frequency. The temperature
+  is hereafter increased by 2$^\circ$C resulting in an increase in oscillation
+  frequency. At 205$^\circ$C the oscillation period was approximately 500\,s
+  while the oscillation period period is approximately 5000\,s. at
+  203$^\circ$C
   \label{fgr:temperature_dependence}
+}
 \end{figure}
 
-A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}.
-By changing the temperature 5$^\circ$C the oscillation period was changed by more than a factor of 10.
-The magnitude of the change is not completely consistent across all measured samples but all samples show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations by changing the temperature $20^\circ$C, see Figure~\ref{fgr:temperature_dependence_supplemental}.
-
+An interesting feature in the data is the very large temperature dependence on
+oscillation frequency, as shown in \ref{fgr:temperature_dependence}. By
+changing the temperature 5$^\circ$C the oscillation period was changed by more
+than a factor of 10. The magnitude of the change is not completely consistent
+across all measured samples but all samples show a very large temperature
+dependency where in some cases a provoked small change in temperature will
+consistently turn on and off the oscillations by changing the temperature
+$20^\circ$C, see \ref{fgr:temperature_dependence_supplemental}.
 \begin{figure}
@@
 \end{figure}
+This property agrees well an earlier suggested model \cite{Hendriksen2010} and
+it is, to our knowledge, the first time the temperature dependence of
+oscillations at atmospheric pressure has been measured.
 
-An interesting feature in the data is the very large temperature dependence on oscillation frequency.
-This property agrees well an earlier suggested model \cite{Hendriksen2010} and it is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
+\subsection{Pressure dependence}
+The pressure dependence of the oscillations was also investigated. In the
+pressure range of 0.1\,bar to 1\,bar no change of the oscillation frequency or
+qualitative behavior that could be attributed to the pressure was found.
+Similarly, only a weak dependence on the CO/O$_2$ ratio was observed. At a
+CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations was
+observed. Increasing the CO/O$_2$ showed clear oscillations with a significant
+increase in oscillation amplitude compared to lower CO concentrations.
+Generally, a tendency towards longer oscillation periods for higher CO/O$_2$
+ratio was observed. Richer CO mixtures than 0.175 did not produce any
+oscillations in our system.
 
-The pressure dependence of the oscillations was also investigated.
-In the pressure range of 0.1\,bar to 1\,bar no change of the oscillation frequency or qualitative behavior that could be attributed to the pressure was found.
-Similarly, only a weak dependence on the CO/O$_2$ ratio was observed.
-At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations was observed.
-Increasing the CO/O$_2$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
-Generally, a tendency towards longer oscillation periods for higher CO/O$_2$ ratio was observed.
-Richer CO mixtures than 0.175 did not produce any oscillations in our system.
-
-Although oscillations have previously been observed on extended Pt thin films \cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric pressure no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
+Although oscillations have previously been observed on extended Pt thin films
+\cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric
+pressure no oscillations could be provoked on thin films of comparable
+geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
 
@@
 \subsection{CO concentration dependence}
-The dependence of the CO concentration on the period of the oscillations was investigated.
-The result shows that the period increases slightly with increasing CO-concentration.
-However, the effect is small compared to the general trend of slower oscillations as the experiment progresses.
-In Figure~\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the actual masspectrometry data of the entire experiment is shown in Figure~\ref{fgr:gas_dependence}.
+The dependence of the CO concentration on the period of the oscillations was
+investigated. The result shows that the period increases slightly with
+increasing CO-concentration. However, the effect is small compared to the
+general trend of slower oscillations as the experiment progresses. In
+\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the
+actual masspectrometry data of the entire experiment is shown in
+\ref{fgr:gas_dependence}.
 
@@
   \includegraphics[width=12cm]{oscillations_gas_dependence_summary_supplemental.png}
-  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is superimposed with small discontinuous steps when the CO concentration is increased.}
-  \label{fgr:gas_dependence_summary}
+  \caption{Summary of the gas-dependence. The overall trend of increasing
+  oscillation period is superimposed with small discontinuous steps when the CO
+  concentration is increased.} \label{fgr:gas_dependence_summary}
 \end{figure}
 
-Oscillations were only seen in CO/O$_2$ ratio below 0.175.
-This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
-The needed low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on Pt which poisons the nanoparticle surface during the low reactivity region of the cycle.
-
-Nanoparticles of several different sizes were tested and all showed oscillations.
-However, no change in duty cycle or frequency that could be attributed to the size of the nanoparticles was found.
-This may be due to the fact that even nominally identical samples also show a large variation in oscillation frequency and duty cycle thus possibly shadowing a nanoparticle size effect.
+Oscillations were only seen in CO/O$_2$ ratio below 0.175. This ratio agrees
+well with literature \cite{Singh2010,Hendriksen2005} where oscillations have
+been observed in oxygen rich CO/O$_2$ mixtures. The needed low concentration of
+CO in the inlet gases can be attributed to the much higher sticking coefficient
+of CO on Pt which poisons the nanoparticle surface during the low reactivity
+region of the cycle.
 
@@
   \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
-  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$ (blue).
-The temperature is constant $210^\circ$C doing the entire measurement.
-For every frame the CO-concentration is increased.}
+  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$
+  (blue). The temperature is constant $210^\circ$C doing the entire
+  measurement. For every frame the CO-concentration is increased.}
   \label{fgr:gas_dependence}
@@
 
-\subsection{Temperature dependence}
-As mentioned in the main paper, the oscillations shows a very strong temperature dependence.
-In Figure~\ref{fgr:temperature_dependence_supplemental} we show an example where the oscillations are turned on and off by changing the temperature $20^\circ$C.
-
-\begin{figure}
-\centering
-  \includegraphics[width=12cm]{temperature_dependence_supplemental.png}
-  \caption{Another example of the very pronounced temperature dependence.}
-  \label{fgr:temperature_dependence_supplemental}
-\end{figure}
-
-An interesting feature in the data is the very large temperature dependence on oscillation frequency.
-This property agrees well an earlier suggested model \cite{Hendriksen2010} and it is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
-
 \subsection{Duty cycle}
-Even though the period of the oscillations increases with time, the total integrated conversion rate during a complete cycle is almost constant.
-In Figure~\ref{fgr:duty_cycles_supplemental}, the value of the mean value of CO and CO$_2$ is plotted for every oscillation in the four-day long experiment.
-It is evident that the ratio between CO and CO$_2$ is almost constant and thus the average activity of the sample is almost unchanged despite the development in the oscillation frequency.
+Even though the period of the oscillations increases with time, the total
+integrated conversion rate during a complete cycle is almost constant. In
+\ref{fgr:duty_cycles_supplemental}, the value of the mean value of CO and
+CO$_2$ is plotted for every oscillation in the four-day long experiment. It is
+evident that the ratio between CO and CO$_2$ is almost constant and thus the
+average activity of the sample is almost unchanged despite the development in
+the oscillation frequency.
 
@@
   \includegraphics[width=12cm]{duty_cycles_long_measurement_supplemental.png}
-  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment.
-The individual data-points is calculted as the integral of CO (red) or CO$_2$ (blue) doing the individual oscillations.
-The ratio between CO and CO$_2$ is drawn in black.}
-  \label{fgr:duty_cycles_supplemental}
+  \caption{A plot of the duty-cycle of the sample duing the 4-day long
+  experiment. The individual data-points is calculted as the integral of CO
+  (red) or CO$_2$ (blue) doing the individual oscillations. The ratio between
+  CO and CO$_2$ is drawn in black.} \label{fgr:duty_cycles_supplemental}
 \end{figure}
 
-In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface.
-It is to be expected that the particles will initially favor the reduced state.
-As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles (illustrated in Figure~\ref{fgr:full_oscillation}).
-Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO.
-As the CO concentration decreases the light-off temperature will decrease hence approaching the constant temperature of the sample resulting in a steep increase in reactivity.
-It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known.
-We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task.
-If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration.
-The further increased rate will not be visible in the QMS since the reactor is already in full conversion.
-As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state.
-Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing rate of the remaining active particles.
-Just before the overall activity drops only a fraction of the particles participates in the reaction and the deactivation will happen very suddenly.
-Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle.
-It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of $10^{6}$s$^{-1}$ per site corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
+\subsection{Size dependence}
+Nanoparticles of several different sizes were tested and all showed
+oscillations. However, no change in duty cycle or frequency that could be
+attributed to the size of the nanoparticles was found. This may be due to the
+fact that even nominally identical samples also show a large variation in
+oscillation frequency and duty cycle thus possibly shadowing a nanoparticle
+size effect.
+
+\subsection{Proposed mechanism}
+In this study Pt nanoparticles were investigated which, compared to a single
+crystal or a thin film, is a very rough surface. It is to be expected that the
+particles will initially favor the reduced state. As the reaction runs the gas
+composition towards the outlet of the reactor will become more oxidizing
+increasing the oxidation rate of the particles (illustrated in
+\ref{fgr:full_oscillation}). Gradually, as the particles towards the outlet
+oxidizes the turn-over will increase and the general CO concentration will
+decrease promoting more and more particles to oxidize which will gradually be
+seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO
+concentration decreases the light-off temperature will decrease hence
+approaching the constant temperature of the sample resulting in a steep
+increase in reactivity. It is important to note that the fraction of oxidized
+particles needed to achieve full conversion is not known. We are currently
+investigating new methods for gaining insight into the nature of the
+nanoparticles in the reactor but the low coverage and the design of the reactor
+makes this a challenging task. If not all particles are oxidized at light-off
+they will now oxidize much faster due to the low CO-concentration. The further
+increased rate will not be visible in the QMS since the reactor is already in
+full conversion. As most of the particles are now oxidized they will become
+more and more roughened and gradually return to the reduced state. Fewer and
+fewer oxidized particles will be responsible for the activity increasing the
+roughing rate of the remaining active particles. Just before the overall
+activity drops only a fraction of the particles participates in the reaction
+and the deactivation will happen very suddenly. Once these potentially few
+particles eventually becomes sufficiently rough they will reduce and lose
+activity hence completing the oscillation cycle. It should be noted that our
+group has recently measured turnover frequencies of CO oxidation on Pt in
+excess of $10^{6}$s$^{-1}$ per site corresponding to as little as $\sim$300 Pt
+nanoparticles contributing to the reactivity just before the end of the high-
+activity cycle.
 
 \section{Conclusions}
-Self-sustained CO oxidation oscillations at atmospheric pressure on Pt nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-quality mass-spectrometry.
-It was found that the samples increased the oscillation period over time and showed a strong temperature dependence.
-A model is proposed where the nanoparticles go through repetitive oxidation/reduction cycles which change the change rate of CO oxidation on the particles.
+Self-sustained CO oxidation oscillations at atmospheric pressure on Pt
+nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-
+quality mass-spectrometry. It was found that the samples increased the
+oscillation period over time and showed a strong temperature dependence. A
+model is proposed where the nanoparticles go through repetitive
+oxidation/reduction cycles which change the change rate of CO oxidation on the
+particles.
 
@@
 The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
-The reactor design makes sure that all gases exposed to the catalyst under investigation is measured by the quadropole mass spectrometer (QMS) ensuring an extremely high sensitivity of the system.
+The reactor design makes sure that all gases exposed to the catalyst under
+investigation is measured by the quadropole mass spectrometer (QMS) ensuring an
+extremely high sensitivity of the system.
 
-The experiments were performed in Si-based 20x16\,mm $\mu$-reactors\cite{Henriksen2009}.
-The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume.
-The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0--2.5\,bar.
-The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0--10 mL/min.
-The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
-The design makes sure that all gases exposed to the catalyst under investigation are measured by the QMS ensuring an extremely high sensitivity of the system.
-\begin{figure}
-  \includegraphics[width=8cm]{Ib-reactor.png}
-  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area and gas channel system}
-  \label{fgr:reactor}
-\end{figure}
-Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.
-When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMS chamber.
+The experiments were performed in Si-based 20x16\,mm
+$\mu$-reactors\cite{Henriksen2009}. The reactor consists of two inlets, a
+mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor
+volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m
+long capillary used for sniffing gases from the reactor volume. The reactor is
+sealed by anodic bonding of a pyrex lid to the Si reactor and is able to
+operate in a pressure range of 0--2.5\,bar. The reaction gases are supplied to
+the two inlets by flow controllers capable of controlling the gas flow from 0--
+10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer (QMS)
+for analysis while any surplus of gas from the inlets is passed directly
+through to the outlet via a pressure controller allowing control of reactor
+pressure. The design makes sure that all gases exposed to the catalyst under
+investigation are measured by the QMS ensuring an extremely high sensitivity of
+the system. \begin{figure} \includegraphics[width=8cm]{Ib-reactor.png}
+\caption{Image of the 20x16\,mm microreactor showing the circular reactor area
+and gas channel system} \label{fgr:reactor} \end{figure} Before any
+measurements are performed the reactor is pumped by a turbopump to minimize
+contaminants in the system. When an evacuated reactor is mounted the base
+pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in
+operation at $1\,$bar in the reactor volume the pressure is
+$\sim5\times10^{-7}\,$mbar in the QMS chamber.
 
-The reactor is heated by joule heating of a Pt strip evaporated on the backside of the reactor chip.
-The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the Pt strip using it as a RTD for temperature measurement of the reactor.
-An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
-The measured RTD temperature is always compared to the thermocouple at room temperature both before and after an experiment to be sure the RTD did not change resistance due to annealing during the experiment.
+The reactor is heated by joule heating of a Pt strip evaporated on the backside
+of the reactor chip. The introduction of two additional contacts on the
+backside of the reactor allows for 4 wire measurements of the resistance of the
+Pt strip using it as a RTD for temperature measurement of the reactor. An
+external thermocouple acts as room-temperature calibration of the RTD as well
+as sanity check of the RTD measurement during operation. The measured RTD
+temperature is always compared to the thermocouple at room temperature both
+before and after an experiment to be sure the RTD did not change resistance due
+to annealing during the experiment.
 
-The gas handling including flow and pressure controllers and the mass spectrometer is fully automated allowing for measurements during several days without human intervention allowing for self-consistent measurements of many samples.
+The gas handling including flow and pressure controllers and the mass
+spectrometer is fully automated allowing for measurements during several days
+without human intervention allowing for self-consistent measurements of many
+samples.
 
 \subsection{Pt nanoparticle deposition}
-Pt nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
-Pt clusters were formed by gas-phase condensation of Pt atoms produced by impinging argon ions on a 99.99\% Pt target in a magnetron sputter source.
-After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
-Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2010,Nielsen2009}.
-The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor.
-The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition.
-After deposition the reactors were anodically cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
+Pt nanoparticles were deposited in the reactor using a gas-aggregation source
+(Mantis Deposition Ltd., Nanogen 50). Pt clusters were formed by gas-phase
+condensation of Pt atoms produced by impinging argon ions on a 99.99\% Pt
+target in a magnetron sputter source. After condensation the ionised fraction
+(60-80\%) of the clusters were size-selected by a quadropole mass selection
+filter according to their mass-to-charge ratio. Using this setup Pt
+nanoparticles with diameters in the range of 2--16\,nm can be produced
+\cite{Nielsen2010,Nielsen2009}. The size-selected nanoparticles were after
+size-selection soft-landed in the reactor volume of the microreactor. The
+coverage was kept at approximately 0.1\% geometric coverage determined by
+measuring the current on the reactor during deposition. After deposition the
+reactors were anodically cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid
+sintering of the nanoparticles while bonding.
 

### 2012-04-19 python_figures/duty_cycles_long_measurement.py

@@ -101,7 +101,7 @@ axis.grid(False)
 
 #axis.set_ylabel('SEM Current / nA', fontsize=20)
 axis.set_ylabel('Integrated charge (a.u.)', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / minutes', fontsize=8)
 
 
 

### 2012-04-19 python_figures/extracts_from_very_long_oscillation.py

@@ -70,8 +70,8 @@ axis_array[0].annotate('CO$_2$', xy=(725, 1.7),  xycoords='data', xytext=(715, 0
 axis_array[0].annotate('T', xy=(728, 4.9),  xycoords='data', xytext=(720, 5.3), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
 
 axis_array[1].set_ylabel('SEM Current / nA', fontsize=8)
-axis2_array[1].set_ylabel('Temperature', fontsize=8)
-axis_array[2].set_xlabel('Time/minutes', fontsize=8)
+axis2_array[1].set_ylabel('Temperature / $^\circ$C', fontsize=8)
+axis_array[2].set_xlabel('Time / minutes', fontsize=8)
 
 
 #plt.tight_layout()

### 2012-04-19 python_figures/initial_treatment.py

@@ -76,7 +76,7 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / minutes', fontsize=8)
 
 
 
@@ -98,7 +98,7 @@ axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('', fontsize=8)
 axis.set_xticks((465,475,485))
 axis2.set_yticks(())
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / minutes', fontsize=8)
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 
@@ -121,7 +121,7 @@ axis.text(718,4.3,"T",fontsize=8,)
 axis.set_xlim(710,740)
 axis.set_yticks(())
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / minutes', fontsize=8)
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 

### 2012-04-19 python_figures/oscillations_gas_dependence_summary.py

@@ -94,8 +94,8 @@ axis.set_xlim(0,3100)
 axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=3)
 axis.grid(True)    
 
-axis.set_ylabel('Oscillations periods / minutes', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_ylabel('Oscillation periods / minutes', fontsize=8)
+axis.set_xlabel('Time / minutes', fontsize=8)
 
 
 

### 2012-04-19 python_figures/single_full_oscillation.py

@@ -61,7 +61,7 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / minutes', fontsize=8)
 
 
 positions = []

### 2012-04-19 python_figures/summary_of_long_measurement.py

@@ -84,7 +84,7 @@ axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis=
 axis.grid(False)    
 
 axis.set_ylabel('Oscil. period / minutes', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / minutes', fontsize=8)
 
 a = plt.axes([.18, .65, .3, .15], axisbg='w')
 a.plot(oscillations, periods, 'b,')

### 2012-04-19 python_figures/temperature_dependence.py

@@ -60,7 +60,7 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / minutes', fontsize=8)
 
 #plt.tight_layout()
 #plt.show()

### 2012-04-19 python_figures/temperature_dependence_supplemental.py

@@ -60,7 +60,7 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / minutes', fontsize=8)
 
 #plt.tight_layout()
 plt.show()

### 2012-04-20 paper.tex
Final corrections before sending to author-list

@@
 
-As mentioned the understanding of self-sustained oscillations on supported
+The understanding of self-sustained oscillations on supported
 catalysts is hampered by the fact that entirely different mechanisms than those
@@
 repeatable self-sustained oscillations when initially started. The system
-consist of mass selected Pt nanoparticles in the range from 2 to 10\,nm 
+consists of mass selected Pt nanoparticles in the range from 2 to 10\,nm 
 deposited in a microreactor with a surface area of 0.75\,cm$^2$
@@
 It is demonstrated how the nanoparticles provides self-sustained
-oscillations over extend of days and how various parameters can be mapped out
-including the temperature dependence -- an effect that could
+oscillations stable in course of several days and how various parameters can be mapped out
+including the temperature dependence -- an effect that, to our knowledge, has
+never been measured before and that could
 not be demonstrated for a continuous film of same area and similar conditions.
@@
 An oscillation measurement is performed by mounting a sample in the setup
-directly after cluster deposition and anodic bonding. Initially a light-off CO-
-oxidation measurement is performed (shown in \ref{fgr:initial_treatment}) where
+directly after cluster deposition and anodic bonding. Initially a light-off
+CO-oxidation measurement is performed (shown in \ref{fgr:initial_treatment}) where
 the temperature is increased at 3\,$^\circ$C/min until the sample ignites and
-achieves full conversion of CO to CO$_2$. At CO:O$_2$ ratio of $\sim0.08$ and a
-geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately
+achieves full conversion of CO to CO$_2$. At a CO:O$_2$ ratio of $\sim0.08$ and a
+geometrical Pt coverage of the reactor area of $\sim0.1\%$ light-off occurs at approximately
 180\,$^\circ$C. The temperature ramp is typically continued up to
@@
 
-Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm
-particles with a geometrical coverage of 0.1\% of the reactor area gave the
-most stable oscillations. No consistent dependency on oscillation frequency and
-duty cycle was found that could be attributed to the size of the particles.
-
 The oscillations on all samples are qualitatively similar but the oscillation
-period varies from a few seconds (the time-constant of the reactor is
+period varies from a few seconds (the time constant of the reactor is
 $\sim7\,$s) up to more than an hour. Once a sample start to oscillate it will
 perform self-sustained oscillations for as long as the experiment is allowed to
-run. We have not observed a single sample stop oscillating once the self-
-sustained oscillations had started.
+run. We have not observed a single sample stop oscillating once the self-sustained oscillations had started.
 
@@
 \ref{fgr:full_oscillation}. After a short on-cycle (at $\sim$1030\,min) where
-all CO is converted to CO$_2$ (notice the CO signal does not go to zero due to
-the cracking pattern of CO$_2$ and CO background in the QMS) the reaction shows
-a fast deactivation. After the deactivation the sample quickly regains
+all CO is converted to CO$_2$ the reaction shows a fast deactivation. 
+Notice the CO signal does not go to zero due to the cracking pattern of
+CO$_2$ and CO background in the Quadrupole Mass Spectrometer (QMS).
+After the deactivation the sample quickly regains
 $\sim$30\% conversion (at $\sim$1040\,min). Hereafter the conversion increases
@@
 its small size has timescales on the order of seconds. Furthermore, a series of
-experiments was performed to exclude the oscillations as an instrumental
+experiments were performed to exclude the oscillations as an instrumental
 artifact. Firstly, experiments were performed on a larger volume reactor thus
@@
 reproduced on a comparable but not identical setup. Finally, attempts at
-reproducing the phenomenon on Pt-thin films of comparable coverage did not
+reproducing the phenomenon on Pt thin films of comparable coverage did not
 produce any oscillations. All of these experiments suggest that the
-oscillations is a property of the Pt nanoparticles.
+oscillations is a property of the Pt nanoparticles. However, 
+although oscillations have previously been observed on extended Pt thin films
+\cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric
+pressure no oscillations could be provoked on thin films of comparable
+geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
 
@@
 period was observed as shown in \ref{fgr:long_measurement}. Initially, the
-oscillation period is $\sim$2.5 min and increases linearly with time until 1500
-min of total oscillation time. Hereafter the oscillations become more irregular
-as shown in \ref{fgr:extracts} and lower panel \ref{fgr:long_measurement}. At
-experiment end the oscillation period is between 20 and 45 min.
+oscillation period is $\sim$2.5 min and increases linearly with time until 1500\,min
+of total oscillation time. Hereafter the oscillations become more irregular
+as shown in \ref{fgr:long_measurement} and in the lower panel of \ref{fgr:extracts}. At
+experiment end the oscillation period is between 20\,min and 45\,min.
 
@@
 extracted from the same four days measurement. Data from shortly after the
-initial treatment, after 2800\,min of oscillation time and after 5900\,min are
+initial treatment, after 2800\,min of oscillation time and after 5900\,min is
 shown. After 5900\,min the oscillations are more irregular which is consistent
@@
   \includegraphics[width=12cm]{extracts_from_very_long_oscillation.png}
-  \caption{Extracts from the 4 days long experiment. The oscillation period
+  \caption{Extracts from a 4 day long experiment. The oscillation period
   becomes more irregular with time while the total integrated conversion
@@
 the smaller oscillations in between on/off cycles. Occasionally, these small
-amplitude oscillations will trigger a full switch thus introducing more short-
-period oscillations despite the trend of increasingly slower oscillation
+amplitude oscillations will trigger a full switch thus introducing more
+short-period oscillations despite the trend of increasingly slower oscillation
 period. A possible explanation of the phenomeonon could be sintering of the
@@
 between CO and CO$_2$ integrated over an full period remains constant
-throughout the entire experiment time, i.e. the samples maintains a constant
+throughout the entire experiment time, i.e. the samples maintain a constant
 average rate independent of oscillation frequency. Thus we do not expect
 sintering to be the cause since an average loss in activity of the sample would
-then be expected.
+be expected.
 
@@
 \caption{Illustration of the strong temperature dependence. After about 10
-  hours of steady oscillations at 205$^\circ$C the temperature is lowered by
-  5$^\circ$C immediately decreasing the oscillation frequency. The temperature
-  is hereafter increased by 2$^\circ$C resulting in an increase in oscillation
-  frequency. At 205$^\circ$C the oscillation period was approximately 500\,s
+  hours of steady oscillations at 205\,$^\circ$C the temperature is lowered by
+  5\,$^\circ$C immediately decreasing the oscillation frequency. The temperature
+  is hereafter increased by 2\,$^\circ$C resulting in an increase in oscillation
+  frequency. At 205\,$^\circ$C the oscillation period was approximately 500\,s
   while the oscillation period period is approximately 5000\,s. at
-  203$^\circ$C
+  203\,$^\circ$C
   \label{fgr:temperature_dependence}
@@
 An interesting feature in the data is the very large temperature dependence on
-oscillation frequency, as shown in \ref{fgr:temperature_dependence}. By
-changing the temperature 5$^\circ$C the oscillation period was changed by more
+oscillation frequency as shown in \ref{fgr:temperature_dependence}. By
+changing the temperature 5\,$^\circ$C the oscillation period was changed by more
 than a factor of 10. The magnitude of the change is not completely consistent
 across all measured samples but all samples show a very large temperature
-dependency where in some cases a provoked small change in temperature will
-consistently turn on and off the oscillations by changing the temperature
-$20^\circ$C, see \ref{fgr:temperature_dependence_supplemental}.
+dependence where in some cases a provoked small change in temperature will
+consistently turn on and off the oscillations, see \ref{fgr:temperature_dependence_supplemental}.
 \begin{figure}
@@
   \includegraphics[width=12cm]{temperature_dependence_supplemental.png}
-  \caption{Another example of the very pronounced temperature dependence.}
+  \caption{Another example of the very pronounced temperature dependence.
+  here the oscillations are turned on and off by changing the temperature
+  $20^\circ$C,}
   \label{fgr:temperature_dependence_supplemental}
@@
 oscillations in our system.
-
-Although oscillations have previously been observed on extended Pt thin films
-\cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric
-pressure no oscillations could be provoked on thin films of comparable
-geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
 
@@
 \subsection{Duty cycle}
-Even though the period of the oscillations increases with time, the total
+Even though the period of the oscillations increases with time the total
 integrated conversion rate during a complete cycle is almost constant. In
-\ref{fgr:duty_cycles_supplemental}, the value of the mean value of CO and
+\ref{fgr:duty_cycles_supplemental} the mean value of CO and
 CO$_2$ is plotted for every oscillation in the four-day long experiment. It is
-evident that the ratio between CO and CO$_2$ is almost constant and thus the
-average activity of the sample is almost unchanged despite the development in
+evident that the ratio between CO and CO$_2$ is almost constant. The
+average activity of the sample is thus almost unchanged despite the development in
 the oscillation frequency.
@@
 \subsection{Size dependence}
-Nanoparticles of several different sizes were tested and all showed
-oscillations. However, no change in duty cycle or frequency that could be
+Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm
+particles with a geometrical coverage of 0.1\% of the reactor area gave the
+most stable oscillations. 
+However, no change in duty cycle or frequency that could be
 attributed to the size of the nanoparticles was found. This may be due to the
@@
 \ref{fgr:full_oscillation}). Gradually, as the particles towards the outlet
-oxidizes the turn-over will increase and the general CO concentration will
+oxidizes the turn-over frequency will increase and the general CO concentration will
 decrease promoting more and more particles to oxidize which will gradually be
@@
 group has recently measured turnover frequencies of CO oxidation on Pt in
-excess of $10^{6}$s$^{-1}$ per site corresponding to as little as $\sim$300 Pt
+excess of $10^{6}$\,s$^{-1}$ per site corresponding to as little as $\sim$300 Pt
 nanoparticles contributing to the reactivity just before the end of the high-
@@
 Self-sustained CO oxidation oscillations at atmospheric pressure on Pt
-nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-
-quality mass-spectrometry. It was found that the samples increased the
+nanoparticles ranging from from 3\,nm to 9\,nm have been measured with
+high-quality mass-spectrometry. Full conversion was achieved on 0.1\,\%
+geometrical Pt coverage and it is found likely that full conversion can be obtained on
+extremely small amounts of Pt. It was found that the samples increased the
 oscillation period over time and showed a strong temperature dependence. A
@@
 \subsection{The $\mu$-reactor platform}
-The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
-The reactor design makes sure that all gases exposed to the catalyst under
-investigation is measured by the quadropole mass spectrometer (QMS) ensuring an
-extremely high sensitivity of the system.
-
 The experiments were performed in Si-based 20x16\,mm
@@
 the two inlets by flow controllers capable of controlling the gas flow from 0--
-10 mL/min. The capillary flow is fed into a quadropole mass-spectrometer (QMS)
+10 mL/min The capillary flow is fed into a QMS
 for analysis while any surplus of gas from the inlets is passed directly
@@
 target in a magnetron sputter source. After condensation the ionised fraction
-(60-80\%) of the clusters were size-selected by a quadropole mass selection
+(60-80\%) of the clusters is size-selected by a quadropole mass selection
 filter according to their mass-to-charge ratio. Using this setup Pt

### 2012-04-23 paper.tex
Incorporated many of Ib and Oles corrections

@@
   High-quality mass spectrometry data of the oscillatory behavior
-  of CO oxidation on SiO$_2$ supported Pt-nanoparticles at atmospheric
+  of CO oxidation on SiO$_2$ supported mass selected Pt-nanoparticles at atmospheric
   pressure has been acquired as a function of pressure, coverage, gas
@@
 1993\cite{SINCLAIR1993}, this is not generally believed to be the case
-\cite{Elton1942,Kielland2010}. Instead, the periodic population cycle
-can be explained by more classic weather phenomena. Similarly, very interesting
+\cite{Elton1942,Kielland2010}. Nevertheless, very interesting oscillation
 observations have been made for our current climate
@@
 works\cite{HakenBog,NicolisBog}. Similar behavior has been observed within
-heterogeneous catalysis where one of very first examples was observed by Wicke
+heterogeneous catalysis where one of the very first examples was observed by Wicke
 for CO oxidation on a catalyst
@@
 strongly increased when reduced but slowly returns to the less active state
-when CO$_2$ is present.
+when CO$_2$ is present. This suggest that an increased activity could be
+obtained by oscillating between oxidizing and reducing conditions or CO$_2$
+rich/lean conditions respectively.
 
@@
 Skoghlund\cite{Carlsson2006} where self-sustained oscillations were observed on
-a supported Pt catalyst while simultaneously studying the catalyst by in-situ
+a supported Pt catalyst while the catalyst was simultaneously studied by in-situ
 IR spectrometry. Similar studies were recently undertaken using EXAFS
@@
 chemical synthesis methods, are avoided with gas-aggregation formed particles
-while still being able to vary the coverage from sub-percent to full coverage.
+while it is still possible to vary the coverage from sub-percent to full coverage.
 It is demonstrated how the nanoparticles provides self-sustained
@@
 never been measured before and that could
-not be demonstrated for a continuous film of same area and similar conditions.
+not be demonstrated for a continuous film of same area in similar conditions.
 By combining these results with previous studies \cite{Carlsson2006,Singh2010}
@@
 directly after cluster deposition and anodic bonding. Initially a light-off
-CO-oxidation measurement is performed (shown in \ref{fgr:initial_treatment}) where
+CO-oxidation measurement is performed (shown in Figure~\ref{fgr:initial_treatment}) where
 the temperature is increased at 3\,$^\circ$C/min until the sample ignites and
@@
 3\,$^\circ$C/min until sustained oscillations occur. A typical initial
-treatment is seen in \ref{fgr:initial_treatment} where both the symmetrical
+treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical
 light-off ramp and the subsequent increase in temperature to achieve sustained
@@
   \caption{A typical example of the initial treatment of a new sample. After
-  performing a light- off ramp where oscillations can been seen the temperature
+  performing a light-off ramp, where oscillations can been seen, the temperature
   is increased to a constant value where sustained oscillations take place. The
@@
 period varies from a few seconds (the time constant of the reactor is
-$\sim7\,$s) up to more than an hour. Once a sample start to oscillate it will
+$\sim7\,$s) up to more than an hour. Once a sample starts to oscillate it will
 perform self-sustained oscillations for as long as the experiment is allowed to
@@
 An example of a single very slow oscillation is seen in
-\ref{fgr:full_oscillation}. After a short on-cycle (at $\sim$1030\,min) where
+Figure~\ref{fgr:full_oscillation}. After a short on-cycle (at $\sim$1030\,min) where
 all CO is converted to CO$_2$ the reaction shows a fast deactivation. 
@@
 $\sim$1118\,min). Shortly after reaching 50\% conversion the sample again
-ignites and convert all CO to CO$_2$. After a short full conversion period the
+ignites and converts all CO to CO$_2$. After a short full conversion period the
 sample again deactivates and the cycle repeats itself.
@@
 experiments were performed to exclude the oscillations as an instrumental
-artifact. Firstly, experiments were performed on a larger volume reactor thus
-increasing the residence time in the reactor. Secondly, the oscillations were
+artifact. Firstly, experiments were performed on a reactor with five times larger volume and thus
+five times increased residence time in the reactor. Secondly, the oscillations were
 reproduced on a comparable but not identical setup. Finally, attempts at
@@
 After prolonged measurements over several days an increase in oscillation
-period was observed as shown in \ref{fgr:long_measurement}. Initially, the
-oscillation period is $\sim$2.5 min and increases linearly with time until 1500\,min
+period was observed as shown in Figure~\ref{fgr:long_measurement}. Initially, the
+oscillation period is $\sim$2.5 min and it increases linearly with time until 1500\,min
 of total oscillation time. Hereafter the oscillations become more irregular
-as shown in \ref{fgr:long_measurement} and in the lower panel of \ref{fgr:extracts}. At
+as shown in Figure~\ref{fgr:long_measurement} and in the lower panel of Figure~\ref{fgr:extracts}. At
 experiment end the oscillation period is between 20\,min and 45\,min.
@@
   oscillating under constant temperature, pressure and reactant composition.
-  The sample went through a total of 439 oscillations in 4 days. Time is
+  The sample went through a total of 439 oscillations in 4 days. For details on on
+  the oscillations over this period please consult supplementary Figure ????. Time is
   defined from experiment start and hence includes initial treatment. The inset
-  shows the initial steady increase in oscillation period.}
+  shows the initial steady increase in oscillation period. The red lines indicate
+  max and min oscillation time to guide the eye.}
   \label{fgr:long_measurement}
@@
 
-\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations
+Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations
 extracted from the same four days measurement. Data from shortly after the
-initial treatment, after 2800\,min of oscillation time and after 5900\,min is
+initial treatment, after 2800\,min of oscillation time and after 5900\,min are
 shown. After 5900\,min the oscillations are more irregular which is consistent
-with the data shown in \ref{fgr:long_measurement}. Also, oscillations in
+with the data shown in Figure~\ref{fgr:long_measurement}. Also, oscillations in
 between full conversion oscillations with smaller amplitude and much higher
@@
   \includegraphics[width=12cm]{extracts_from_very_long_oscillation.png}
-  \caption{Extracts from a 4 day long experiment. The oscillation period
+  \caption{Extracts from a 4 days long experiment. The oscillation period
   becomes more irregular with time while the total integrated conversion
@@
 The oscillation period increases with time and becomes increasingly less stable
-as shown in \ref{fgr:extracts}. This phenomena is  consistent across all
+as shown in Figure~\ref{fgr:extracts}. This phenomenon is consistent across all
 measured samples. The large scatter in oscillation period can be attributed to
@@
 amplitude oscillations will trigger a full switch thus introducing more
-short-period oscillations despite the trend of increasingly slower oscillation
-period. A possible explanation of the phenomeonon could be sintering of the
+short-period oscillations despite the trend of increasingly longer oscillation
+period. A possible explanation of the phenomenon could be sintering of the
 particles during the oxidation and reductions cycles. However, the ratio
@@
 proposal for the reaction mechanism on Pd has been developed by Hendriksen
-\textit{et. al.}\cite{Hendriksen2010} and our data is consistent with this
+\textit{et. al.}\cite{Hendriksen2010} and our data are consistent with this
 model.
@@
 convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt
-oxide will start to form in the high partial pressures of O$_2$ thus increasing
+oxide will start to form in the high partial pressure of O$_2$ thus increasing
 the rate. The model\cite{Hendriksen2010} suggests that the oxidized
@@
 \includegraphics[width=12cm]{temperature_dependence.png}
-\caption{Illustration of the strong temperature dependence. After about 10
+\caption{Illustration of the strong temperature dependence of the oscillation period. After about 10
   hours of steady oscillations at 205\,$^\circ$C the temperature is lowered by
@@
   while the oscillation period period is approximately 5000\,s. at
-  203\,$^\circ$C
+  203\,$^\circ$C.
   \label{fgr:temperature_dependence}
@@
 
-An interesting feature in the data is the very large temperature dependence on
-oscillation frequency as shown in \ref{fgr:temperature_dependence}. By
+An interesting feature in the data is the very large temperature dependence of the
+oscillation frequency as shown in Figure~\ref{fgr:temperature_dependence}. By
 changing the temperature 5\,$^\circ$C the oscillation period was changed by more
@@
 across all measured samples but all samples show a very large temperature
-dependence where in some cases a provoked small change in temperature will
-consistently turn on and off the oscillations, see \ref{fgr:temperature_dependence_supplemental}.
+dependence. In some cases a provoked change in temperature will
+consistently turn on and off the oscillations. This is illustrated in the supplementary
+material, Figure ??????\ref{fgr:temperature_dependence_supplemental}.
 \begin{figure}
@@
   \includegraphics[width=12cm]{temperature_dependence_supplemental.png}
-  \caption{Another example of the very pronounced temperature dependence.
-  here the oscillations are turned on and off by changing the temperature
-  $20^\circ$C,}
+  \caption{Another example of the very pronounced temperature dependence of the oscillation period.
+  Here the oscillations are turned on and off by changing the temperature by
+  $20^\circ$C.}
   \label{fgr:temperature_dependence_supplemental}
@@
 Similarly, only a weak dependence on the CO/O$_2$ ratio was observed. At a
-CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations was
-observed. Increasing the CO/O$_2$ showed clear oscillations with a significant
+CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were
+observed. Increasing the CO/O$_2$ ratio showed clear oscillations with a significant
 increase in oscillation amplitude compared to lower CO concentrations.
@@
 \subsection{CO concentration dependence}
-The dependence of the CO concentration on the period of the oscillations was
+The dependence of period of the oscillations on the the CO concentration was
 investigated. The result shows that the period increases slightly with
@@
 general trend of slower oscillations as the experiment progresses. In
-\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the
-actual masspectrometry data of the entire experiment is shown in
-\ref{fgr:gas_dependence}.
+Figure~\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the
+actual mass spectrometry data of the entire experiment are shown in Figure~\ref{fgr:gas_dependence}.
 
@@
   \includegraphics[width=12cm]{oscillations_gas_dependence_summary_supplemental.png}
-  \caption{Summary of the gas-dependence. The overall trend of increasing
-  oscillation period is superimposed with small discontinuous steps when the CO
-  concentration is increased.} \label{fgr:gas_dependence_summary}
+  \caption{Oscillation period (blue) as a function of time and CO concentration (black). The
+  overall trend of increasing oscillation period with time is superimposed with small
+  discontinuous steps when the CO concentration is increased.} 
+  \label{fgr:gas_dependence_summary}
 \end{figure}
@@
   \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
-  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$
-  (blue). The temperature is constant $210^\circ$C doing the entire
+  \caption{Complete series of data from an oscillating sample, showing CO (red) and CO$_2$
+  (blue). The temperature is constant at $210^\circ$C during the entire
   measurement. For every frame the CO-concentration is increased.}
@@
 integrated conversion rate during a complete cycle is almost constant. In
-\ref{fgr:duty_cycles_supplemental} the mean value of CO and
-CO$_2$ is plotted for every oscillation in the four-day long experiment. It is
+Figure~\ref{fgr:duty_cycles_supplemental} the mean value of CO and
+CO$_2$ is plotted for every oscillation in a four-day long experiment. It is
 evident that the ratio between CO and CO$_2$ is almost constant. The
@@
   \includegraphics[width=12cm]{duty_cycles_long_measurement_supplemental.png}
-  \caption{A plot of the duty-cycle of the sample duing the 4-day long
-  experiment. The individual data-points is calculted as the integral of CO
-  (red) or CO$_2$ (blue) doing the individual oscillations. The ratio between
+  \caption{Running average of the CO and CO$_2$ concentrations and their ratio during a 4-day long
+  experiment. The individual data-points is calculated as the integral of CO
+  (red) or CO$_2$ (green) during the individual oscillation periods. The ratio between
   CO and CO$_2$ is drawn in black.} \label{fgr:duty_cycles_supplemental}
@@
 In this study Pt nanoparticles were investigated which, compared to a single
-crystal or a thin film, is a very rough surface. It is to be expected that the
+crystal or a thin film, have a very rough surface. It is to be expected that the
 particles will initially favor the reduced state. As the reaction runs the gas
 composition towards the outlet of the reactor will become more oxidizing
-increasing the oxidation rate of the particles (illustrated in
-\ref{fgr:full_oscillation}). Gradually, as the particles towards the outlet
+increasing the oxidation rate of the particles (illustrated in the bottom of
+Figure~\ref{fgr:full_oscillation}). Gradually, as the particles towards the outlet
 oxidizes the turn-over frequency will increase and the general CO concentration will
@@
 nanoparticles in the reactor but the low coverage and the design of the reactor
-makes this a challenging task. If not all particles are oxidized at light-off
+makes this a challenging task. If all particles are not oxidized at light-off
 they will now oxidize much faster due to the low CO-concentration. The further
@@
 nanoparticles contributing to the reactivity just before the end of the high-
-activity cycle.
+activity cycle. This would correspond to an area of ????? ppm of the reactor
+area suggesting that in situ studies are becoming a challenges as such a
+minority of the reactor volume could account for all the reactivity. Attempts
+to see any thermal signal from such small areas has so far been in vain.
 
@@
 Self-sustained CO oxidation oscillations at atmospheric pressure on Pt
-nanoparticles ranging from from 3\,nm to 9\,nm have been measured with
+nanoparticles ranging from from 3\,nm to 9\,nm in diameter have been measured with
 high-quality mass-spectrometry. Full conversion was achieved on 0.1\,\%
@@
 extremely small amounts of Pt. It was found that the samples increased the
-oscillation period over time and showed a strong temperature dependence. A
-model is proposed where the nanoparticles go through repetitive
+oscillation period over time and showed a strong temperature dependence of the
+oscillation period. A model is proposed where the nanoparticles go through repetitive
 oxidation/reduction cycles which change the change rate of CO oxidation on the
-particles.
+particles. The fact that extremely few NP may account for the activity make in
+situ investigations a challenge.
 
@@
 long capillary used for sniffing gases from the reactor volume. The reactor is
-sealed by anodic bonding of a pyrex lid to the Si reactor and is able to
+sealed by anodic bonding of a Pyrex lid to the Si reactor and is able to
 operate in a pressure range of 0--2.5\,bar. The reaction gases are supplied to
 the two inlets by flow controllers capable of controlling the gas flow from 0--
-10 mL/min The capillary flow is fed into a QMS
+10 mL/min. The capillary flow is fed into a QMS
 for analysis while any surplus of gas from the inlets is passed directly
@@
 investigation are measured by the QMS ensuring an extremely high sensitivity of
-the system. \begin{figure} \includegraphics[width=8cm]{Ib-reactor.png}
+the system.
+
+\begin{figure}
+ \includegraphics[width=8cm]{Ib-reactor.png}
  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area
-and gas channel system} \label{fgr:reactor} \end{figure} Before any
-measurements are performed the reactor is pumped by a turbopump to minimize
+and the gas channel system.}
+  \label{fgr:reactor}
+\end{figure}
+
+Before any measurements are performed the reactor is evacuated by a turbopump to minimize
 contaminants in the system. When an evacuated reactor is mounted the base
@@
 external thermocouple acts as room-temperature calibration of the RTD as well
-as sanity check of the RTD measurement during operation. The measured RTD
-temperature is always compared to the thermocouple at room temperature both
+as a sanity check of the RTD measurement during operation. The measured RTD
+temperature is always compared to the thermocouple temperature at room temperature both
 before and after an experiment to be sure the RTD did not change resistance due
@@
 reactors were anodically cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid
-sintering of the nanoparticles while bonding.
+sintering of the nanoparticles while bonding in air.
+
+\section{Acknowledgments}
+This work was carried out as part of the Catalysis for Sustainable Energy
+initiative, which is funded by the Danish Ministry of Science, Technology and
+Innovation. The Center for Individual Nanoparticle Functionality is funded by
+the Danish National Research Foundation.
 

### 2012-04-23 python_figures/duty_cycles_long_measurement.py

@@ -101,7 +101,7 @@ axis.grid(False)
 
 #axis.set_ylabel('SEM Current / nA', fontsize=20)
 axis.set_ylabel('Integrated charge (a.u.)', fontsize=8)
-axis.set_xlabel('Time / minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
 
 

### 2012-04-23 python_figures/extracts_from_very_long_oscillation.py

@@ -33,7 +33,7 @@ fig.subplots_adjust(bottom=0.1) # Make room for x-label
 fig.subplots_adjust(right=0.85) # Make room for right y-label
 #ratio = 0.61803398              # Golden mean
 ratio = 1
-fig_width = 9
+fig_width = 12
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -71,7 +71,7 @@ axis_array[0].annotate('T', xy=(728, 4.9),  xycoords='data', xytext=(720, 5.3), 
 
 axis_array[1].set_ylabel('SEM Current / nA', fontsize=8)
 axis2_array[1].set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis_array[2].set_xlabel('Time / minutes', fontsize=8)
+axis_array[2].set_xlabel('Time / min', fontsize=8)
 
 
 #plt.tight_layout()

### 2012-04-23 python_figures/initial_treatment.py

@@ -36,7 +36,7 @@ fig.subplots_adjust(right=0.85) # Make room for second y-label
 
 #ratio = 0.61803398           # Golden mean
 ratio = 0.9
-fig_width = 9
+fig_width = 12
 fig_width = fig_width /2.54        # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -76,7 +76,7 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis.set_xlabel('Time / minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
 
 
@@ -88,7 +88,7 @@ axis.set_ylim(0,6)
 axis.set_yticks((1,3,5))
 axis.text(463,1.2,"CO",fontsize=8,)
 axis.text(465,2.3,"CO$_2$",fontsize=8,)
-axis.text(470,4.9,"T",fontsize=8,)
+axis.text(470,4.9,"Temp.",fontsize=8,)
 axis2 = axis.twinx()
 axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'b-')
 axis2.set_ylim(0,300)
@@ -98,7 +98,7 @@ axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('', fontsize=8)
 axis.set_xticks((465,475,485))
 axis2.set_yticks(())
-axis.set_xlabel('Time / minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)
 
@@ -117,11 +117,11 @@ axis2.set_yticks((50,150,250))
 axis.set_xticks((715,725,735))
 axis.text(715,0.8,"CO",fontsize=8,)
 axis.text(722,3.4,"CO$_2$",fontsize=8,)
-axis.text(718,4.3,"T",fontsize=8,)
+axis.text(718,4.3,"Temp.",fontsize=8,)
 axis.set_xlim(710,740)
 axis.set_yticks(())
[…]

### 2012-04-23 python_figures/oscillations_gas_dependence.py

@@ -59,7 +59,7 @@ axis2_array = []
 for i in range(0,steps-1):
     axis_array.append(fig.add_subplot(6,3,i+1))
     axis_array[i].plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
-    axis_array[i].plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'b-')
+    axis_array[i].plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
     #axis_array[i].set_ylim(0,0.1*(i+1)*1.85)
     axis_array[i].set_ylim(0,1.5)
     axis_array[i].set_yticks((0.25,0.5,0.75,1,1.25))

### 2012-04-23 python_figures/oscillations_gas_dependence_summary.py

@@ -74,8 +74,9 @@ for i in range(1,len(oscillations)):
 
 fig = plt.figure()
 fig.subplots_adjust(bottom=0.2) # Make room for x-label
+fig.subplots_adjust(right=0.9) # Make room for second y-label
 ratio = 0.61803398              # Golden mean
-fig_width = 9
+fig_width = 12
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -92,13 +93,19 @@ axis.set_ylim(0,50)
 axis.set_xlim(0,3100)
 
 axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=3)
-axis.grid(True)    
+axis.grid(False)    
 
-axis.set_ylabel('Oscillation periods / minutes', fontsize=8)
-axis.set_xlabel('Time / minutes', fontsize=8)
+axis.set_ylabel('Oscillation period / minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
-
-
+axis2 = axis.twinx()
+#axis2.plot(data['CO_FLOW'][:,0], data['CO_FLOW'][:,1], 'r-')
+axis2.plot(data['CO_FLOW'][:,0], data['CO_FLOW'][:,1]/(4+data['CO_FLOW'][:,1]), 'k-')
+axis2.set_xlim(0,3100)
+axis2.set_ylim(0,0.15)
+axis2.set_ylabel('CO/O$_2$-ratio', fontsize=8)    
+#axis2.set_yticks((0.025,0.05,0.075,0.1,0.125))
+axis2.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=3)
 
 
 

### 2012-04-23 python_figures/single_full_oscillation.py

@@ -34,7 +34,7 @@ fig.subplots_adjust(bottom=0.2) # Make room for x-label
 
 #ratio = 0.61803398             # Golden mean
 ratio = 0.4                     # This figure should be very wide to span two columns
-fig_width = 17
+fig_width = 16
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -61,7 +61,7 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis.set_xlabel('Time / minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
 
 positions = []

### 2012-04-23 python_figures/summary_of_long_measurement.py

@@ -84,7 +84,7 @@ axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis=
 axis.grid(False)    
 
 axis.set_ylabel('Oscil. period / minutes', fontsize=8)
-axis.set_xlabel('Time / minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
 a = plt.axes([.18, .65, .3, .15], axisbg='w')
 a.plot(oscillations, periods, 'b,')

### 2012-04-23 python_figures/temperature_dependence.py

@@ -33,7 +33,7 @@ fig.subplots_adjust(bottom=0.2) # Make room for x-label
 fig.subplots_adjust(right=0.85) # Make room for second y-label
 
 ratio = 0.61803398           # Golden mean
-fig_width = 9
+fig_width = 12
 fig_width = fig_width /2.54        # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -60,7 +60,7 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis.set_xlabel('Time / minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
 #plt.tight_layout()
 #plt.show()

### 2012-04-23 python_figures/temperature_dependence_supplemental.py

@@ -33,7 +33,7 @@ fig.subplots_adjust(bottom=0.2) # Make room for x-label
 fig.subplots_adjust(right=0.85) # Make room for second y-label
 
 ratio = 0.61803398           # Golden mean
-fig_width = 9
+fig_width = 12
 fig_width = fig_width /2.54        # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -60,7 +60,7 @@ axis2.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis
 
 axis.set_ylabel('SEM Current / nA', fontsize=8)
 axis2.set_ylabel('Temperature / $^\circ$C', fontsize=8)
-axis.set_xlabel('Time / minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
 #plt.tight_layout()
 plt.show()

### 2012-04-27 paper.tex
Incorporated Sørens corrections

@@
 deeper insight into the fundamental aspects of such oscillatory reactions this
-work was followed up by Ertl on Pt(110) surfaces under well-defined conditions
+work was followed up by Ertl and coworkers on Pt(110) surfaces under well-defined conditions
 \cite{EISWIRTH1986}. Ertl demonstrated how the switching between the
 unreconstructed Pt(110) surface and the reconstructed 2x1-Pt(110) surface
-combined with large changes of oxygen sticking coefficient on the two surfaces
+combined with large differences in oxygen sticking coefficient on the two surfaces
 could drive the self-sustained oscillations. This and many other interesting
@@
 systems\cite{Ibele2010}. Most of the studies
-are made on single crystal or polycrystalline films or filaments mainly in
-conjunction with ultra-high vacuum equipment to be able to characterize
+are made on single crystal surfaces or polycrystalline films or filaments mainly in
+conjunction with ultra-high vacuum equipment to be able to characterize the
 catalyst surfaces using surface science methods. The amount of work described
@@
 some of the pit falls that may have to be considered when making in-situ
-investigations of such a system since extremely low coverages may provide the
+investigations of such a system since a small fraction of the active sites may provide the
 entire conversion.
@@
 180\,$^\circ$C. The temperature ramp is typically continued up to
-260\,$^\circ$C whereafter the temperature is decreased at the same rate as the
-heating ramp. After the initial light-off the sample is cooled to room
+260\,$^\circ$C whereafter the temperature is decreased at 3\,$^\circ$C/min.
+After the initial light-off the sample is cooled to room
 temperature. When at room temperature the temperature is again increased at
 3\,$^\circ$C/min until sustained oscillations occur. A typical initial
-treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical
-light-off ramp and the subsequent increase in temperature to achieve sustained
-oscillations is seen. Often the sample will show oscillations either directly
-upon light-off or on the falling temperature ramp.
+treatment is seen in Figure~\ref{fgr:initial_treatment}. Often the sample will
+show oscillations either directly upon light-off or on the falling temperature
+ramp.
 

### 2012-04-30 paper.tex
Moved two figures to supplementary

@@
   The sample went through a total of 439 oscillations in 4 days. For details on on
-  the oscillations over this period please consult supplementary Figure ????. Time is
+  the oscillations over this period please consult Figure~\ref{fgr:extracts}. Time is
   defined from experiment start and hence includes initial treatment. The inset
@@
 consistently turn on and off the oscillations. This is illustrated in the supplementary
-material, Figure ??????\ref{fgr:temperature_dependence_supplemental}.
-\begin{figure}
-\centering
-  \includegraphics[width=12cm]{temperature_dependence_supplemental.png}
-  \caption{Another example of the very pronounced temperature dependence of the oscillation period.
-  Here the oscillations are turned on and off by changing the temperature by
-  $20^\circ$C.}
-  \label{fgr:temperature_dependence_supplemental}
-\end{figure}
+material, Figure~S1.
 This property agrees well an earlier suggested model \cite{Hendriksen2010} and
@@
 \begin{figure}
-  \includegraphics[width=12cm]{oscillations_gas_dependence_summary_supplemental.png}
+  \includegraphics[width=12cm]{oscil_gas_dependence_summary.png}
   \caption{Oscillation period (blue) as a function of time and CO concentration (black). The
@@
 \begin{figure}
-  \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
+  \includegraphics[width=14cm]{oscil_gas_dependence.png}
   \caption{Complete series of data from an oscillating sample, showing CO (red) and CO$_2$
@@
   \label{fgr:gas_dependence}
-\end{figure}
-
-\subsection{Duty cycle}
-Even though the period of the oscillations increases with time the total
-integrated conversion rate during a complete cycle is almost constant. In
-Figure~\ref{fgr:duty_cycles_supplemental} the mean value of CO and
-CO$_2$ is plotted for every oscillation in a four-day long experiment. It is
-evident that the ratio between CO and CO$_2$ is almost constant. The
-average activity of the sample is thus almost unchanged despite the development in
-the oscillation frequency.
-
-\begin{figure}
-  \includegraphics[width=12cm]{duty_cycles_long_measurement_supplemental.png}
-  \caption{Running average of the CO and CO$_2$ concentrations and their ratio during a 4-day long
-  experiment. The individual data-points is calculated as the integral of CO
-  (red) or CO$_2$ (green) during the individual oscillation periods. The ratio between
-  CO and CO$_2$ is drawn in black.} \label{fgr:duty_cycles_supplemental}
 \end{figure}
@@
 nanoparticles contributing to the reactivity just before the end of the high-
-activity cycle. This would correspond to an area of ????? ppm of the reactor
+activity cycle. This would correspond to an area of 14\,ppm of the reactor
 area suggesting that in situ studies are becoming a challenges as such a

### 2012-04-30 supplementary.tex
Incorporated small correction from Thomas Pedersen
Moved two figures to supplementary

--- 2012-02-28 supplementary.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%This is the article LaTeX template for RSC journals
-%Copyright The Royal Society of Chemistry 2010
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% This is a (brief) model paper using the achemso class
+%% The document class accepts keyval options, which should include
+%% the target journal and optionally the macuscript tye
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[journal=jacsat,manuscript=article]{achemso}
 
-\documentclass[8.5pt,twoside,twocolumn]{article}
-\oddsidemargin -1.2cm
-\evensidemargin -1.2cm
-\textwidth 18cm
-\headheight 1.0in
-\topmargin -3.5cm
-\textheight 22cm
-\usepackage[super,sort&compress,comma]{natbib} 
-\usepackage[version=3]{mhchem}
-\usepackage[utf8]{inputenc}
-\usepackage{times,mathptmx}
-% \usepackage{times}
-% feel free not to use mathptmx if it causes difficulties
-\usepackage{sectsty}
-\usepackage{balance}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Place any additional packages needed here.  Only include packages
+%% which are essential, to avoid problems later.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
+\usepackage{graphicx}
 
-\usepackage{graphicx} %eps figures can be used instead
-\usepackage{lastpage}
-\usepackage[format=plain,justification=raggedright,singlelinecheck=false,font=small,labelfont=bf,labelsep=space]{caption} 
-\usepackage{fancyhdr}
-\pagestyle{fancy}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% If issues arise when submitting your manuscript, you may want to
+%% un-comment the next line.  This provides information on the
+%% version of every file you have used.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%\listfiles
 
-\renewcommand{\thefigure}{S\arabic{figure}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Place any additional macros here.  Please use \newcommand* where
+%% possible, and avoid layout changing macros (which are not used
+%% when typesetting).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand*{\mycommand}[1]{\texttt{\emph{#1}}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Meta-data block
+%% ---------------
+%% Each author should be given as a separate \author command.
+%%
+%% Corresponding authors should have an e-mail given after the author
+%% name as an \email command.
+%%
+%% The affiliation of authors is given after the authors; each
+%% \affiliation command applies to all preceding authors not already
+%% assigned an affiliation.
+%%
+%% The affiliation takes an option argument for the short name.  This
+%% will typically be something like "University of Somewhere".
+%%
+%% The \altaffiliation macro should be used for new address, etc.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\author{Robert Jensen}
+\author{Thomas Andersen}
+\author{Anders Nierhoff}
+\author{Thomas Pedersen}
+\author{Ole Hansen}
+\author{S\o ren Dahl}
+\author{Ib Chorkendorff}
+\email{ibchork@fysik.dtu.dk}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The document title should be given as usual
+%% A short title can be given as a *suggestion* for running headers.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title[Oxidation oscillations at atmospheric pressure]
+{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure - Supplementaty materials}
 
 \begin{document}
-
-%\thispagestyle{plain}
-%\fancypagestyle{plain}{
-%\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
-%\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
-%\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
-%\renewcommand{\headrulewidth}{1pt}}
-%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
-%\renewcommand\footnoterule{\vspace*{1pt}% 
-%\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
-%\setcounter{secnumdepth}{5}
-
-\makeatletter 
-\def\subsubsection{\@startsection{subsubsection}{3}{10pt}{-1.25ex plus -1ex minus -.1ex}{0ex plus 0ex}{\normalsize\bf}} 
-\def\paragraph{\@startsection{paragraph}{4}{10pt}{-1.25ex plus -1ex minus -.1ex}{0ex plus 0ex}{\normalsize\textit}} 
-\renewcommand\@biblabel[1]{#1}            
-\renewcommand\@makefntext[1]% 
-{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
-\makeatother 
-\renewcommand{\figurename}{\small{Fig.}~}
-\sectionfont{\large}
-\subsectionfont{\normalsize}
-
-%\fancyfoot{}
-%\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
-%\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
-%\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
-%\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
-%\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
-\fancyhead{}
-\renewcommand{\headrulewidth}{1pt} 
-\renewcommand{\footrulewidth}{1pt}
-\setlength{\arrayrulewidth}{1pt}
-\setlength{\columnsep}{6.5mm}
-\setlength\bibsep{1pt}
-
-\twocolumn[
-  \begin{@twocolumnfalse}
-\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure\\ - Supplemental Material}}
-\vspace{0.6cm}
- \end{@twocolumnfalse}
-  ]
-
-\section{The $\mu$-reactor platform}
-The experiments were performed in Si-based 20x15 mm $\mu$-reactors\cite{Henriksen2009}.
-The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide capillary used for sniffing gases from the reactor volume.
-The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate at a pressure range of 0-2.5\,bar.
-The reaction gases is supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min.
-The capillary flow is fed into a quadropole mass-spectrometer (QMA) for analysis while any surplus of gas from the inlets are passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
-The design makes sure that all gases exposed to the catalyst under investigation is measured by the QMA ensuring an extremely high sensitivity of the system.
+\section{Temperature dependence}
+As mentioned in the main paper, the oscillations shows a very strong
+temperature dependence. In Figure~\ref{fgr:temperature_dependence_supplemental}
+we show an example where the oscillations are turned on and off by changing the
+temperature $20^\circ$C.
 
@@
 \centering
-  \includegraphics[width=8cm]{reactor.jpg}
-  \caption{The Microreactor before the lid is anodicly bonded to the reactor}
-  \label{fgr:reactor}
-\end{figure}
-
-Before any measurements are performed the reactor is pumped by a turbopump to minimize contaminants in the system.
-When an evacuated reactor is mounted the base pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in operation at $1\,$bar in the reactor volume the pressure is $\sim5\times10^{-7}\,$mbar in the QMA chamber.
-
-The reactor is heated by joule heating of a Pt strip evaporated on the backside of the reactor volume.
-The introduction of two additional contacts on the backside of the reactor allows for 4 wire measurements of the resistance of the Pt strip using it as a RTD for temperature measurement of the reactor.
-An external thermocouple acts as room-temperature calibration of the RTD as well as sanity check of the RTD measurement during operation.
-
-The gas handling including flow and pressured controllers and the mass spectrometer is fully automized allowing for measurements of several days without human intervention allowing for self-consistent measurements of many samples.
-
-\section{Pt nanoparticle deposition}
-Pt nanoparticles were deposited in the reactor using a gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
-Pt clusters were formed by gas-phase condensation of Pt atoms produced by impinging argon ions on a 99.99\% Pt target in a magnetron sputter source.
-After condensation the ionised fraction (60-80\%) of the clusters were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
-Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2010,Nielsen2009}.
-The size-selected nanoparticles were after size-selection soft-landed in the reactor volume of the microreactor.
-The coverage was kept at approximately 0.1\% geometric coverage determined by measuring the current on the reactor during deposition.
-After deposition the reactors were anodicly cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
-
-\section{CO concentration dependence}
-The dependence of the CO concentration on the period of the oscillations was investigated.
-The result show that the period increases slightly with increasing CO-concentration.
-However, the effect is small compared to the general trend of slower oscillations as the experiment progresses.
-In Figure~\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the actual masspectrometry data of the entire experiment is shown in Figure~\ref{fgr:gas_dependence}.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=9cm]{oscillations_gas_dependence_summary_supplemental.png}
-  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
-  \label{fgr:gas_dependence_summary}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
-  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$ (blue).
-The temperature is constant $210^\circ$C doing the entire measurement.
-For every frame the CO-concentration is increased.}
-  \label{fgr:gas_dependence}
-\end{figure*}
-
-\section{Temperature dependence}
-As mentioned in the main paper, the oscillations shows a very strong temperature dependence.
-In Figure~\ref{fgr:temperature_dependence_supplemental} we show an example where the oscillations are turned on and off by changing the temperature $20^\circ$C.
-
-\begin{figure}[h]
-\centering
-  \includegraphics[width=9cm]{temperature_dependence_supplemental.png}
+  \includegraphics[width=12cm]{temperature_dependence_supplemental.png}
   \caption{Another example of the very pronounced temperature dependence.}
@@
 
-\section{Duty cycle}
-Even though the period of the oscillations increases with time, the total integrated conversion rate during a complete cycle is almost constant.
-In Figure~\ref{fgr:duty_cycles_supplemental}, the value of the mean value of CO and CO$_2$ is plotted for every oscillation in the four-day long experiment.
-It is evident that the ratio between CO and CO$_2$ is almost constant and thus the overall activity of the sample is almost unchanged despite the development in the oscillation frequency.
+\subsection{Duty cycle}
+Even though the period of the oscillations increases with time the total
+integrated conversion rate during a complete cycle is almost constant. In
+Figure~\ref{fgr:duty_cycles_supplemental} the mean value of CO and
+CO$_2$ is plotted for every oscillation in a four-day long experiment. It is
+evident that the ratio between CO and CO$_2$ is almost constant. The
+average activity of the sample is thus almost unchanged despite the development in
+the oscillation frequency.
 
-\begin{figure}[h]
-\centering
-  \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
-  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment.
-The individual data-points is calculted as the integral of CO (red) or CO$_2$ (blue) doing the individual oscillations.
-The ratio between CO and CO$_2$ is drawn in black.}
+\begin{figure}
+  \includegraphics[width=12cm]{duty_cycles_long_measurement_supplemental.png}
+  \caption{Running average of the CO and CO$_2$ concentrations and their ratio
+  during a 4-day long experiment. The individual data-points is calculated as
+  the integral of CO (red) or CO$_2$ (green) during the individual oscillation
+  periods. The ratio between CO and CO$_2$ is drawn in black.}
   \label{fgr:duty_cycles_supplemental}
@@
 
-\footnotesize{
-\bibliography{literature} %your .bib file
-\bibliographystyle{rsc} %the RSC's .bst file
-}
-
 \end{document}

### 2012-04-30 python_figures/oscillations_gas_dependence.py

@@ -95,4 +95,4 @@ for i in range(0,steps-1):
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../oscillations_gas_dependence_supplemental.png',dpi=300)
+plt.savefig('../oscillations_gas_dependence.png',dpi=300)

### 2012-04-30 python_figures/oscillations_gas_dependence_summary.py

@@ -111,7 +111,7 @@ axis2.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../oscillations_gas_dependence_summary_supplemental.png',dpi=300)
+plt.savefig('../oscil_gas_dependence_summary.png',dpi=300)
 
 
 

### 2012-04-30 supplementary.tex
Changed supplemantry figure labels to S1, S2, etc...

@@
 
+\renewcommand{\thefigure}{S\arabic{figure}}
+
 \begin{document}
@@
 As mentioned in the main paper, the oscillations shows a very strong
-temperature dependence. In Figure~\ref{fgr:temperature_dependence_supplemental}
+temperature dependence. In \ref{fgr:temperature_dependence_supplemental}
 we show an example where the oscillations are turned on and off by changing the
@@
 integrated conversion rate during a complete cycle is almost constant. In
-Figure~\ref{fgr:duty_cycles_supplemental} the mean value of CO and
+\ref{fgr:duty_cycles_supplemental} the mean value of CO and
 CO$_2$ is plotted for every oscillation in a four-day long experiment. It is

### 2012-04-30 paper.tex
Ready to go to Ib again

@@
 directly after cluster deposition and anodic bonding. Initially a light-off
-CO-oxidation measurement is performed (shown in Figure~\ref{fgr:initial_treatment}) where
+CO-oxidation measurement is performed (shown in \ref{fgr:initial_treatment}) where
 the temperature is increased at 3\,$^\circ$C/min until the sample ignites and
@@
 3\,$^\circ$C/min until sustained oscillations occur. A typical initial
-treatment is seen in Figure~\ref{fgr:initial_treatment}. Often the sample will
+treatment is seen in \ref{fgr:initial_treatment}. Often the sample will
 show oscillations either directly upon light-off or on the falling temperature
@@
 An example of a single very slow oscillation is seen in
-Figure~\ref{fgr:full_oscillation}. After a short on-cycle (at $\sim$1030\,min) where
+\ref{fgr:full_oscillation}. After a short on-cycle (at $\sim$1030\,min) where
 all CO is converted to CO$_2$ the reaction shows a fast deactivation. 
@@
 After prolonged measurements over several days an increase in oscillation
-period was observed as shown in Figure~\ref{fgr:long_measurement}. Initially, the
+period was observed as shown in \ref{fgr:long_measurement}. Initially, the
 oscillation period is $\sim$2.5 min and it increases linearly with time until 1500\,min
 of total oscillation time. Hereafter the oscillations become more irregular
-as shown in Figure~\ref{fgr:long_measurement} and in the lower panel of Figure~\ref{fgr:extracts}. At
+as shown in \ref{fgr:long_measurement} and in the lower panel of \ref{fgr:extracts}. At
 experiment end the oscillation period is between 20\,min and 45\,min.
@@
   The sample went through a total of 439 oscillations in 4 days. For details on on
-  the oscillations over this period please consult Figure~\ref{fgr:extracts}. Time is
+  the oscillations over this period please consult \ref{fgr:extracts}. Time is
   defined from experiment start and hence includes initial treatment. The inset
@@
 shown. After 5900\,min the oscillations are more irregular which is consistent
-with the data shown in Figure~\ref{fgr:long_measurement}. Also, oscillations in
+with the data shown in \ref{fgr:long_measurement}. Also, oscillations in
 between full conversion oscillations with smaller amplitude and much higher
@@
 The oscillation period increases with time and becomes increasingly less stable
-as shown in Figure~\ref{fgr:extracts}. This phenomenon is consistent across all
+as shown in \ref{fgr:extracts}. This phenomenon is consistent across all
 measured samples. The large scatter in oscillation period can be attributed to
@@
 between CO and CO$_2$ integrated over an full period remains constant
-throughout the entire experiment time, i.e. the samples maintain a constant
+throughout the entire experiment time (supplementary, Figure~S2), i.e. the samples maintain a constant
 average rate independent of oscillation frequency. Thus we do not expect
@@
 oxide will start to form in the high partial pressure of O$_2$ thus increasing
-the rate. The model\cite{Hendriksen2010} suggests that the oxidized
+the rate. The model suggests that the oxidized
 nanoparticles will roughen during CO oxidation resulting in the formation of an
@@
 surface is increasingly favored resulting in a return to the lower rate rough
-metal state. As the rate decreases the CO partial pressure increases which
-results in a transition from rough metal surface to a smooth metal surface.
+metal state. Since the surface mobility is higher for the reduced surface\cite{Hendriksen2010},
+the roughness of the surface will gradually decrease and result
+in a transition from rough metal surface to a smooth metal surface.
 When the sample is sufficiently smooth it will again oxidize and thus complete
@@
 An interesting feature in the data is the very large temperature dependence of the
-oscillation frequency as shown in Figure~\ref{fgr:temperature_dependence}. By
+oscillation frequency as shown in \ref{fgr:temperature_dependence}. By
 changing the temperature 5\,$^\circ$C the oscillation period was changed by more
@@
 general trend of slower oscillations as the experiment progresses. In
-Figure~\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the
-actual mass spectrometry data of the entire experiment are shown in Figure~\ref{fgr:gas_dependence}.
+\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the
+actual mass spectrometry data of the entire experiment are shown in \ref{fgr:gas_dependence}.
 
@@
 increasing the oxidation rate of the particles (illustrated in the bottom of
-Figure~\ref{fgr:full_oscillation}). Gradually, as the particles towards the outlet
+\ref{fgr:full_oscillation}). Gradually, as the particles towards the outlet
 oxidizes the turn-over frequency will increase and the general CO concentration will
@@
 \section{Conclusions}
+Self-sustained oscillations have been found to be of great interest in nature
+and here we demonstrate a systems that shows how nanoparticles can be brought
+into this regime with high reliability forming a basis for further deep
+understanding of this phenomena.
+
 Self-sustained CO oxidation oscillations at atmospheric pressure on Pt

### 2012-05-03 python_figures/summary_of_long_measurement.py
Added dashed lines to the summary plot

@@ -70,11 +70,11 @@ errfunc = lambda p, x, y: fitfunc(p, x) - y # Distance to the target function
 p0 = [0.2,0.6,2] # Initial guess for the parameters
 p1, success = optimize.leastsq(errfunc, p0[:], args=([700,1000,2000,4000,6000],[4,6,20,37,45]),maxfev=1000)
 print p1, success
-axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r-')
+axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r--')
 
 p1, success = optimize.leastsq(errfunc, p0[:], args=([500,1000,2000,4000,6000],[0,2,9,11,16]),maxfev=1000)
 print p1, success
-axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r-')
+axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r--')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
 #axis.set_ylim(0,7)

### 2012-05-15 paper.tex
Finished the manuscript for submission

@@
 \begin{figure}
-  \includegraphics[width=12cm]{initial_treatment.png} 
+  \includegraphics[width=12cm]{initial_treatment.eps} 
   \caption{A typical example of the initial treatment of a new sample. After
@@
 \begin{figure}
-  \includegraphics[width=16cm]{single_full_oscillation.png}
+  \includegraphics[width=16cm]{single_full_oscillation.eps}
   \caption{A full oscillation period first showing a steep ignition of the
@@
 \begin{figure}
-  \includegraphics[width=12cm]{summary_of_long_measurement.png}
+  \includegraphics[width=12cm]{summary_of_long_measurement.eps}
   \caption{Summary of the oscillation period as a function of time for a sample
@@
 \begin{figure}
-  \includegraphics[width=12cm]{extracts_from_very_long_oscillation.png}
+  \includegraphics[width=12cm]{extracts_from_very_long_oscillation.eps}
   \caption{Extracts from a 4 days long experiment. The oscillation period
@@
 \begin{figure}
-\includegraphics[width=12cm]{temperature_dependence.png}
+\includegraphics[width=12cm]{temperature_dependence.eps}
 \caption{Illustration of the strong temperature dependence of the oscillation period. After about 10
@@
 \begin{figure}
-  \includegraphics[width=12cm]{oscil_gas_dependence_summary.png}
+  \includegraphics[width=12cm]{oscil_gas_dependence_summary.eps}
   \caption{Oscillation period (blue) as a function of time and CO concentration (black). The
@@
 \begin{figure}
-  \includegraphics[width=14cm]{oscil_gas_dependence.png}
+  \includegraphics[width=14cm]{oscil_gas_dependence.eps}
   \caption{Complete series of data from an oscillating sample, showing CO (red) and CO$_2$
@@
 \begin{figure}
- \includegraphics[width=8cm]{Ib-reactor.png}
+ \includegraphics[width=8cm]{reactor.eps}
  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area

### 2012-05-15 python_figures/extracts_from_very_long_oscillation.py

@@ -76,4 +76,4 @@ axis_array[2].set_xlabel('Time / min', fontsize=8)
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../extracts_from_very_long_oscillation.png',dpi=300)
+plt.savefig('../extracts_from_very_long_oscillation.eps')

### 2012-05-15 python_figures/initial_treatment.py

@@ -131,4 +131,4 @@ axis.grid(False)
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../initial_treatment.png',dpi=300)
+plt.savefig('../initial_treatment.eps')

### 2012-05-15 python_figures/oscillations_gas_dependence.py

@@ -95,4 +95,4 @@ for i in range(0,steps-1):
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../oscillations_gas_dependence.png',dpi=300)
+plt.savefig('../oscillations_gas_dependence.eps')

### 2012-05-15 python_figures/oscillations_gas_dependence_summary.py

@@ -111,7 +111,7 @@ axis2.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../oscil_gas_dependence_summary.png',dpi=300)
+plt.savefig('../oscil_gas_dependence_summary.eps')
 
 
 

### 2012-05-15 python_figures/single_full_oscillation.py

@@ -103,4 +103,4 @@ for pos in positions:
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../single_full_oscillation.png',dpi=300)
+plt.savefig('../single_full_oscillation.eps')

### 2012-05-15 python_figures/summary_of_long_measurement.py

@@ -93,4 +93,4 @@ plt.setp(a, xlim=(700,1500), ylim=(2,8),xticks=[900,1100,1300], yticks=[3,5,7])
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../summary_of_long_measurement.png',dpi=300)
+plt.savefig('../summary_of_long_measurement.eps')

### 2012-05-15 python_figures/temperature_dependence.py

@@ -64,4 +64,4 @@ axis.set_xlabel('Time / min', fontsize=8)
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../temperature_dependence.png',dpi=300)
+plt.savefig('../temperature_dependence.eps')

### 2012-06-28 paper.tex
Updated the Angewandte version
The version with lay-out for Angewandte is now updated with the
corrections originally intended for PhycChem ChecmPhys

--- 2012-04-30 paper.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% This is a (brief) model paper using the achemso class
-%% The document class accepts keyval options, which should include
-%% the target journal and optionally the macuscript tye
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[journal=jacsat,manuscript=article]{achemso}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%This is the article LaTeX template for RSC journals
+%Copyright The Royal Society of Chemistry 2010
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional packages needed here.  Only include packages
-%% which are essential, to avoid problems later.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
-\usepackage{graphicx}
+\documentclass[8.5pt,twoside,twocolumn]{article}
+\oddsidemargin -1.2cm
+\evensidemargin -1.2cm
+\textwidth 18cm
+\headheight 1.0in
+\topmargin -3.5cm
+\textheight 22cm
+\usepackage[super,sort&compress,comma]{natbib} 
+\usepackage[version=3]{mhchem}
+\usepackage[utf8]{inputenc}
+\usepackage{times,mathptmx}
+% \usepackage{times}
+% feel free not to use mathptmx if it causes difficulties
+\usepackage{sectsty}
+\usepackage{balance}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% If issues arise when submitting your manuscript, you may want to
-%% un-comment the next line.  This provides information on the
-%% version of every file you have used.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\listfiles
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Place any additional macros here.  Please use \newcommand* where
-%% possible, and avoid layout changing macros (which are not used
-%% when typesetting).
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand*{\mycommand}[1]{\texttt{\emph{#1}}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Meta-data block
-%% ---------------
-%% Each author should be given as a separate \author command.
-%%
-%% Corresponding authors should have an e-mail given after the author
-%% name as an \email command.
-%%
-%% The affiliation of authors is given after the authors; each
-%% \affiliation command applies to all preceding authors not already
-%% assigned an affiliation.
-%%
-%% The affiliation takes an option argument for the short name.  This
-%% will typically be something like "University of Somewhere".
-%%
-%% The \altaffiliation macro should be used for new address, etc.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\author{Robert Jensen}
-\author{Thomas Andersen}
-\author{Anders Nierhoff}
-\affiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej, Building 312, 2800 Kgs. Lyngby, Denmark.}
-\author{Thomas Pedersen}
-\author{Ole Hansen}
-\affiliation{CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, \O rsteds Plads, Building 345B, 2800 Kgs. Lyngby, Denmark.}
-\author{S\o ren Dahl}
-\author{Ib Chorkendorff}
-\email{ibchork@fysik.dtu.dk}
-\affiliation{CINF, Department of Physics, Technical University of Denmark, Fysikvej, Building 312, 2800 Kgs. Lyngby, Denmark.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The document title should be given as usual
-%% A short title can be given as a *suggestion* for running headers.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title[Oxidation oscillations at atmospheric pressure]
-{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure}
+\usepackage{graphicx} %eps figures can be used instead
+\usepackage{lastpage}
+\usepackage[format=plain,justification=raggedright,singlelinecheck=false,font=small,labelfont=bf,labelsep=space]{caption} 
+\usepackage{fancyhdr}
+\pagestyle{fancy}
 
 \begin{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% The manuscript does not need to include \maketitle, which is
-%% executed automatically.  The document should begin with an
-%% abstract, if appropriate.  If one is given and should not be, the
-%% contents will be gobbled.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-  High-quality mass spectrometry data of the oscillatory behavior
-  of CO oxidation on SiO$_2$ supported mass selected Pt-nanoparticles at atmospheric
-  pressure has been acquired as a function of pressure, coverage, gas
-  composition and nanoparticle size. The oscillations are self-sustained
-  for several days at constant temperature, pressure and CO/O$_2$ ratio.
-  The frequency of the oscillations is very well defined and increases
-  over time. The oscillation frequency is furthermore strongly temperature
-  dependent with increasing temperature resulting in increasing frequency.
-  A plausible mechanism for the oscillations is proposed based on a
-  oxidation/reduction cycle of the nanoparticles which change the rate of
-  CO oxidation on the particles.
-\end{abstract}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Start the main part of the manuscript here.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Introduction}
+%\thispagestyle{plain}
+%\fancypagestyle{plain}{
+%\fancyhead[L]{\includegraphics[height=8pt]{headers/LH}}
+%\fancyhead[C]{\hspace{-1cm}\includegraphics[height=20pt]{headers/CH}}
+%\fancyhead[R]{\includegraphics[height=10pt]{headers/RH}\vspace{-0.2cm}}
+%\renewcommand{\headrulewidth}{1pt}}
+%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
+%\renewcommand\footnoterule{\vspace*{1pt}% 
+%\hrule width 3.4in height 0.4pt \vspace*{5pt}} 
+%\setcounter{secnumdepth}{5}
 
-Self-sustained oscillating systems are widespread in nature and have been
-described both experimentally and theoretically. One of the maybe most famous
-biological examples is the oscillation of the lynx-hare population as reported
-through the number furs delivered to the Hudson Bay
-Company\cite{MacLulich,Elton1942}. This was for some time believed to be forced
-by sunspot oscillations\cite{Elton1924}. Even though the correlation between
-sunspots and the lynx-hare population has been debated, even as recently as
-1993\cite{SINCLAIR1993}, this is not generally believed to be the case
-\cite{Elton1942,Kielland2010}. Nevertheless, very interesting oscillation
-observations have been made for our current climate
-changes\cite{Svensmark1997,Svensmark1998} suggesting that the sunspot activity
-influences the level of cosmic rays and thus the cloud formation. This topic
-is, however, a topic of controversy\cite{Lockwood2007}.
+\makeatletter 
+\def\subsubsection{\@startsection{subsubsection}{3}{10pt}{-1.25ex plus -1ex minus -.1ex}{0ex plus 0ex}{\normalsize\bf}} 
+\def\paragraph{\@startsection{paragraph}{4}{10pt}{-1.25ex plus -1ex minus -.1ex}{0ex plus 0ex}{\normalsize\textit}} 
+\renewcommand\@biblabel[1]{#1}            
+\renewcommand\@makefntext[1]% 
+{\noindent\makebox[0pt][r]{\@thefnmark\,}#1}
+\makeatother 
+\renewcommand{\figurename}{\small{Fig.}~}
+\sectionfont{\large}
+\subsectionfont{\normalsize}
 
-A beautiful example of self-sustained oscillatory behavior in chemistry is the
-colorful Belousov- Zhabotinsky reaction\cite{ZAIKIN1970} which is rather easy
-to demonstrate for an audience. Such self-sustained oscillatory behavior has
-been explained for systems far from equilibrium in several theoretical
-works\cite{HakenBog,NicolisBog}. Similar behavior has been observed within
-heterogeneous catalysis where one of the very first examples was observed by Wicke
-for CO oxidation on a catalyst
-of highly dispersed Pt on $\gamma$-Al$_2$O$_3$\cite{BEUSCH1972}. To gain a
-deeper insight into the fundamental aspects of such oscillatory reactions this
-work was followed up by Ertl and coworkers on Pt(110) surfaces under well-defined conditions
-\cite{EISWIRTH1986}. Ertl demonstrated how the switching between the
-unreconstructed Pt(110) surface and the reconstructed 2x1-Pt(110) surface
-combined with large differences in oxygen sticking coefficient on the two surfaces
-could drive the self-sustained oscillations. This and many other interesting
-aspects of self-sustained and forced oscillatory behavior and spatio-temporal
-self-organization were investigated by Ertl and coworkers on well-defined
-single crystals, see e.g. reviews\cite{IMBIHL1995,JAKUBITH1990} and in
-particular the Nobel Lecture\cite{Ertl2008}. One of the reasons this has
-attracted interest is the importance of such catalytic reactions demanding a
-better understanding of their behavior with the goal of further improvement.
+%\fancyfoot{}
+%\fancyfoot[LO,RE]{\vspace{-7pt}\includegraphics[height=9pt]{headers/LF}}
+%\fancyfoot[CO]{\vspace{-7.2pt}\hspace{12.2cm}\includegraphics{headers/RF}}
+%\fancyfoot[CE]{\vspace{-7.5pt}\hspace{-13.5cm}\includegraphics{headers/RF}}
+%\fancyfoot[RO]{\footnotesize{\sffamily{1--\pageref{LastPage} ~\textbar  \hspace{2pt}\thepage}}}
+%\fancyfoot[LE]{\footnotesize{\sffamily{\thepage~\textbar\hspace{3.45cm} 1--\pageref{LastPage}}}}
+\fancyhead{}
+\renewcommand{\headrulewidth}{1pt} 
+\renewcommand{\footrulewidth}{1pt}
+\setlength{\arrayrulewidth}{1pt}
+\setlength{\columnsep}{6.5mm}
+\setlength\bibsep{1pt}
+
+\twocolumn[
+  \begin{@twocolumnfalse}
+\noindent\LARGE{\textbf{Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure}}
+\vspace{0.6cm}
+
+\noindent\large{\textbf{Robert Jensen, Thomas Andersen, Anders Nierhoff, Thomas Pedersen, Ole Hansen, Søren Dahl and Ib Chorkendorff}}\vspace{0.5cm}
+%Please note that \ast indicates the corresponding author(s) but no footnote text is required.
+
+%\noindent\textit{\small{\textbf{Received Xth XXXXXXXXXX 20XX, Accepted Xth XXXXXXXXX 20XX\newline
+%First published on the web Xth XXXXXXXXXX 200X}}}
+
+%\noindent \textbf{\small{DOI: 10.1039/b000000x}}
+\vspace{0.6cm}
+%Please do not change this text.
+
+\noindent \normalsize{High-quality mass spectrometry data of the oscillatory behavior of CO oxidation on SiO$_2$ supported Pt-nanoparticles at atmospheric pressure has been acquired as a function of pressure, coverage, gas composition and nanoparticle size.
+The oscillations are self-sustained for several days at constant temperature, pressure and CO/O$_2$ ratio.
+The frequency of the oscillations is very well defined and increases over time.
+The oscillation frequency is furthermore strongly temperature dependent with increasing temperature resulting in increasing frequency.
+A plausible mechanism for the oscillations is proposed based on a oxidation/reduction cycle of the nanoparticles which change the rate of CO oxidation on the particles.}  %on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
+\vspace{0.5cm}
+ \end{@twocolumnfalse}
+  ]
+
+%\section{This is the section heading style}
+\section{Introduction}
+
+%Footnotes
+%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
+
+%Please use \dag to cite the ESI in the main text of the article.
+%If you article does not have ESI please remove the the \dag symbol from the title and the above footnotetext.
+
+%\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
+%\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}
+
+%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
+
+%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \emph{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
+Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}
 
 CO oxidation is one of the most studied reactions due to its importance in both
-automotive catalysis and in the removal of trace CO in hydrogen
-streams\cite{IbsBog,Zhang2011}. The oscillatory behavior is not, however, limited to
-either Pt or CO oxidation but have been found for many other metallic catalysts
-like Rh, Ir, and Pd for oxidation reactions in general, NO and CO reactions,
-hydrogenation reactions \cite{Lund2000,SALES1982} and redox
-systems\cite{Ibele2010}. Most of the studies
-are made on single crystal surfaces or polycrystalline films or filaments mainly in
-conjunction with ultra-high vacuum equipment to be able to characterize the
-catalyst surfaces using surface science methods. The amount of work described
-on supported catalysts seems more limited due to the difficulty of
-characterizing those systems and because additional complexities are present
-such as mass and heat transport\cite{Meunier2008}. Reports in the literature
-exist of how large
-scale facilities such as an industrial ammonia fixed-bed synthesis reactor in
-Germany in 1989 started oscillating for several hours. This could be modeled by
-coupling of the exothermic process and the heat management in the reactor
-system \cite{Morud1998} but one cannot rule out that the observed oscillations
-could in some systems also be created by inherent processes on the catalyst
-itself. In general such oscillations would be considered highly undesirable in
-industry since they would be difficult to control and result in run-away
-incidents for, in particular, exothermic reactions. This would result in
-damaged catalysts due to sintering at higher temperatures. On the other hand
-examples exist in literature where forced oscillations seem to improve the
-overall activity\cite{IMBIHL1995,Machado2005}. One particular interesting
-process here could be the methanol synthesis where a reduction of the CO$_2$
-content for a shorter period of time results in a subsequent higher methanol
-rate compensating for a lower methanol production while running in a
-reducing H$_2$ and CO mixture alone\cite{Dynamics-Bog}. This enhancement can
-be explained by an extensive wetting and un-wetting of the active Cu catalyst
-dependent on the oxidation potential\cite{Hansen2002}, i.e. the active area is
-strongly increased when reduced but slowly returns to the less active state
-when CO$_2$ is present. This suggest that an increased activity could be
-obtained by oscillating between oxidizing and reducing conditions or CO$_2$
-rich/lean conditions respectively.
+automotive catalysis and in the removal of trace CO in hydrogen streams. A
+large effort and a large number of experiments with a variety of surface
+sensitive techniques have been conducted on single crystal surfaces greatly
+improving the understanding of this reaction. Single crystal surfaces are well
+suited model systems due to the high degree of achievable control of parameters
+compared to industrial catalysts. Here we report on studies in a microreactor
+model system of Pt nanoparticles. The size-selected nanoparticles supported on
+a SiO$_2$ substrate show oscillatory behavior of CO oxidation at atmospheric
+pressure.
 
-The understanding of self-sustained oscillations on supported
-catalysts is hampered by the fact that entirely different mechanisms than those
-observed on single and polycrystalline samples may exist. For example it was
-shown on a Pt(110) crystal how waves of surface reconstruction could propagate
-on the surface ensuring a synchronization of the phenomena. Synchronization also have to
-occur for oscillations on supported catalysts but here it is more likely to be
-due to coupling of mass or heat transport. There have been a few examples where
-such oscillations have been observed. Of these the most prominent work is by
-Skoghlund\cite{Carlsson2006} where self-sustained oscillations were observed on
-a supported Pt catalyst while the catalyst was simultaneously studied by in-situ
-IR spectrometry. Similar studies were recently undertaken using EXAFS
-\cite{Singh2010} but here the oscillatory behavior was unstable and less
-convincing.
+Oscillating reactions on single crystals at UHV conditions have been studied
+extensively and is know to originate from surface reconstructions of the
+surface during the oscillations\cite{Ertl2008}. It has previously been
+shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows
+oscillatory behavior on single crystals of Pt, Pd and Ir. Recent studies have
+proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of
+surface oxide formation, oxide roughening and clean metal surface formation. CO
+oxidation oscillations has also been observed on Pt thin films\cite{Lund2000},
+in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles
+synthesized from wet chemical synthesis and subsequent annealing
+\cite{Carlsson2006}. Here we investigate CO oscillations in a microreactor
+model system on size selected Pt nanoparticles by high sensitivity mass
+spectrometry.
 
-In this work we demonstrate how a two-dimensional model system of Pt
-nanoparticles on a SiO$_2$ support can be constructed that shows highly
-repeatable self-sustained oscillations when initially started. The system
-consists of mass selected Pt nanoparticles in the range from 2 to 10\,nm 
-deposited in a microreactor with a surface area of 0.75\,cm$^2$
-especially designed to achieve high sensitivity\cite{Henriksen2009}. This
-method offers some advantages over the chemical synthesis methods, which also
-offers the possibility of size selected nanoparticles, see e.g.
-\cite{Tsang2008,Shao2011}. Particularly, surfactants or solvents
-\cite{Biacchi2011}, which are required for
-chemical synthesis methods, are avoided with gas-aggregation formed particles
-while it is still possible to vary the coverage from sub-percent to full coverage.
-It is demonstrated how the nanoparticles provides self-sustained
-oscillations stable in course of several days and how various parameters can be mapped out
-including the temperature dependence -- an effect that, to our knowledge, has
-never been measured before and that could
-not be demonstrated for a continuous film of same area in similar conditions.
-By combining these results with previous studies \cite{Carlsson2006,Singh2010}
-and a recent detailed study of CO oxidation on Pd using STM
-\cite{Hendriksen2010} a plausible explanation for the oscillatory behavior is
-presented. The low coverage and extremely efficient Pt nanoparticles illustrate
-some of the pit falls that may have to be considered when making in-situ
-investigations of such a system since a small fraction of the active sites may provide the
-entire conversion.
+\section{Experimental Methods}
+The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
+The reactor design makes sure that all gases exposed to the catalyst under
+investigation is measured by the quadropole mass spectrometer (QMS) ensuring an
+extremely high sensitivity of the system.
 
-\section{Results and discussion}
+Pt nanoparticles were deposited in the reactor using a gas-aggregation source.
+The nanoparticles were size-selected by a quadropole mass selection filter
+according to their mass-to-charge ratio. Using this setup Pt nanoparticles with
+diameters in the range of 2--16\,nm can be produced \cite{Nielsen2009}. After
+deposition the reactors were anodically cold-bonded \cite{Vesborg2010} to a
+pyrex lid to avoid sintering of the nanoparticles while bonding.
+
+\section{Results}
 An oscillation measurement is performed by mounting a sample in the setup
-directly after cluster deposition and anodic bonding. Initially a light-off
-CO-oxidation measurement is performed (shown in Figure~\ref{fgr:initial_treatment}) where
-the temperature is increased at 3\,$^\circ$C/min until the sample ignites and
-achieves full conversion of CO to CO$_2$. At a CO:O$_2$ ratio of $\sim0.08$ and a
-geometrical Pt coverage of the reactor area of $\sim0.1\%$ light-off occurs at approximately
-180\,$^\circ$C. The temperature ramp is typically continued up to
-260\,$^\circ$C whereafter the temperature is decreased at 3\,$^\circ$C/min.
-After the initial light-off the sample is cooled to room
-temperature. When at room temperature the temperature is again increased at
-3\,$^\circ$C/min until sustained oscillations occur. A typical initial
-treatment is seen in Figure~\ref{fgr:initial_treatment}. Often the sample will
-show oscillations either directly upon light-off or on the falling temperature
-ramp.
+directly after cluster deposition and anodic bonding. Initially a light-off CO-
+oxidation measurement is performed (shown in
+Figure~\ref{fgr:initial_treatment}) where the temperature is increased at
+3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to
+CO$_2$. At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of
+$\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C. The temperature
+ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is
+decreased at the same rate as the heating ramp. After the initial light-off the
+sample is cooled to room temperature. When at room temperature the temperature
+is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A
+typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where
+both the symmetrical light-off ramp and the subsequent increase in temperature
+to achieve sustained oscillations is seen. Often the sample will show
+oscillations either directly upon light-off or on the falling temperature ramp.
 
-\begin{figure}
-  \includegraphics[width=12cm]{initial_treatment.png} 
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{initial_treatment.png}
   \caption{A typical example of the initial treatment of a new sample. After
-  performing a light-off ramp, where oscillations can been seen, the temperature
+ performing a light-off ramp where oscillations can been seen the temperature
  is increased to a constant value where sustained oscillations take place. The
@@
 
+Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm
+particles with a geometrical coverage of 0.1\% of the reactor area gave the
+most stable oscillations. No consistent dependency on oscillation frequency and
+duty cycle was found that could be attributed to the size of the particles.
+
 The oscillations on all samples are qualitatively similar but the oscillation
-period varies from a few seconds (the time constant of the reactor is
-$\sim7\,$s) up to more than an hour. Once a sample starts to oscillate it will
+period varies from a few seconds (the time-constant of the reactor is
+$\sim7\,$s) up to more than an hour. Once a sample start to oscillate it will
 perform self-sustained oscillations for as long as the experiment is allowed to
-run. We have not observed a single sample stop oscillating once the self-sustained oscillations had started.
+run. We have not observed a single sample stop oscillating once the self-
+sustained oscillations had started.
 
 An example of a single very slow oscillation is seen in
-Figure~\ref{fgr:full_oscillation}. After a short on-cycle (at $\sim$1030\,min) where
-all CO is converted to CO$_2$ the reaction shows a fast deactivation. 
-Notice the CO signal does not go to zero due to the cracking pattern of
-CO$_2$ and CO background in the Quadrupole Mass Spectrometer (QMS).
-After the deactivation the sample quickly regains
-$\sim$30\% conversion (at $\sim$1040\,min). Hereafter the conversion increases
-slowly over time until approximately 50\% conversion is reached (at
+Figure~\ref{fgr:full_oscillation}. After a short on-cycle (at $\sim$1030\,min)
+where all CO is converted to CO$_2$ (notice the CO signal does not go to zero
+due to the cracking pattern of CO$_2$ and CO background in the QMS) the
+reaction shows a fast deactivation. After the deactivation the sample quickly
+regains $\sim$30\% conversion (at $\sim$1040\,min). Hereafter the conversion
+increases slowly over time until approximately 50\% conversion is reached (at
 $\sim$1118\,min). Shortly after reaching 50\% conversion the sample again
-ignites and converts all CO to CO$_2$. After a short full conversion period the
+ignites and convert all CO to CO$_2$. After a short full conversion period the
 sample again deactivates and the cycle repeats itself.
 
-Due to the long timescales between full conversion and low conversion plateaus
-the oscillations cannot be attributed to the reactor setup itself which due to
-its small size has timescales on the order of seconds. Furthermore, a series of
-experiments were performed to exclude the oscillations as an instrumental
-artifact. Firstly, experiments were performed on a reactor with five times larger volume and thus
-five times increased residence time in the reactor. Secondly, the oscillations were
-reproduced on a comparable but not identical setup. Finally, attempts at
-reproducing the phenomenon on Pt thin films of comparable coverage did not
-produce any oscillations. All of these experiments suggest that the
-oscillations is a property of the Pt nanoparticles. However, 
-although oscillations have previously been observed on extended Pt thin films
-\cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric
-pressure no oscillations could be provoked on thin films of comparable
-geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
-
-\begin{figure}
-  \includegraphics[width=16cm]{single_full_oscillation.png}
+\begin{figure*}
+  \centering
+  \includegraphics[width=17cm]{single_full_oscillation.png}
   \caption{A full oscillation period first showing a steep ignition of the
@@
   platinum is oxidized (red) while in low conversion the sample is reduced
-  (blue).} \label{fgr:full_oscillation}
-\end{figure}
+  (blue).}
+  \label{fgr:full_oscillation}
+\end{figure*}
 
 After prolonged measurements over several days an increase in oscillation
-period was observed as shown in Figure~\ref{fgr:long_measurement}. Initially, the
-oscillation period is $\sim$2.5 min and it increases linearly with time until 1500\,min
-of total oscillation time. Hereafter the oscillations become more irregular
-as shown in Figure~\ref{fgr:long_measurement} and in the lower panel of Figure~\ref{fgr:extracts}. At
-experiment end the oscillation period is between 20\,min and 45\,min.
+period was observed as shown in Figure \ref{fgr:long_measurement}. Initially,
+the oscillation period is $\sim$2.5 min and increases linearly with time until
+1500 min of total oscillation time. Hereafter the oscillations become more
+irregular as shown in Figure~\ref{fgr:extracts} and lower panel
+Figure~\ref{fgr:long_measurement}. At experiment end the oscillation period is
+between 20 and 45 min.
 
-\begin{figure}
-  \includegraphics[width=12cm]{summary_of_long_measurement.png}
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{summary_of_long_measurement.png}
   \caption{Summary of the oscillation period as a function of time for a sample
   oscillating under constant temperature, pressure and reactant composition.
-  The sample went through a total of 439 oscillations in 4 days. For details on on
-  the oscillations over this period please consult Figure~\ref{fgr:extracts}. Time is
+  The sample went through a total of 439 oscillations in 4 days. Time is
   defined from experiment start and hence includes initial treatment. The inset
-  shows the initial steady increase in oscillation period. The red lines indicate
-  max and min oscillation time to guide the eye.}
+  shows the initial steady increase in oscillation period.}
   \label{fgr:long_measurement}
@@
 
-Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations
-extracted from the same four days measurement. Data from shortly after the
-initial treatment, after 2800\,min of oscillation time and after 5900\,min are
-shown. After 5900\,min the oscillations are more irregular which is consistent
-with the data shown in Figure~\ref{fgr:long_measurement}. Also, oscillations in
-between full conversion oscillations with smaller amplitude and much higher
-frequency than the full on-off cycles become more visible as time progresses.
-\begin{figure}
-  \includegraphics[width=12cm]{extracts_from_very_long_oscillation.png}
-  \caption{Extracts from a 4 days long experiment. The oscillation period
+Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of
+oscillations extracted from the same four days measurement. Data from shortly
+after the initial treatment, after 2800\,min of oscillation time and after
+5900\,min are shown. After 5900\,min the oscillations are more irregular which
+is consistent with the data shown in Figure \ref{fgr:long_measurement}. Also,
+oscillations in between full conversion oscillations with smaller amplitude and
+much higher frequency than the full on-off cycles become more visible as time
+progresses.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
+  \caption{Extracts from the 4 days long experiment. The oscillation period
   becomes more irregular with time while the total integrated conversion
   remains constant. Furthermore, small oscillations in between full conversion
-  cycles become more prominent as time progresses.} \label{fgr:extracts}
+  cycles become more prominent as time progresses.}
+  \label{fgr:extracts}
 \end{figure}
 
-The oscillation period increases with time and becomes increasingly less stable
-as shown in Figure~\ref{fgr:extracts}. This phenomenon is consistent across all
-measured samples. The large scatter in oscillation period can be attributed to
-the smaller oscillations in between on/off cycles. Occasionally, these small
-amplitude oscillations will trigger a full switch thus introducing more
-short-period oscillations despite the trend of increasingly longer oscillation
-period. A possible explanation of the phenomenon could be sintering of the
-particles during the oxidation and reductions cycles. However, the ratio
-between CO and CO$_2$ integrated over an full period remains constant
-throughout the entire experiment time, i.e. the samples maintain a constant
-average rate independent of oscillation frequency. Thus we do not expect
-sintering to be the cause since an average loss in activity of the sample would
-be expected.
+The oscillation frequency becomes more irregular with progressing experiment
+time as shown in Figure \ref{fgr:extracts}. However, the ratio between CO and
+CO$_2$ integrated over an full period remains constant throughout the entire
+experiment time, i.e. the samples maintains a constant average rate independent
+of oscillation frequency.
+
+%Furthermore, the oscillations have the qualitatively identical behavior as
+%shown in Figure~\ref{fgr:full_oscillation}. A short full conversion period is
+%followed by a fast deactivation from where reactivity is slowly recovered. At
+%approximately 50\% conversion light-off occurs and the sample is in full
+%conversion.
+
+\begin{figure}[h]
+\centering
+  \includegraphics[width=9cm]{temperature_dependence.png}
+  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature
+  is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before
+  the temperature step the oscillation period was approximately 500\,s and
+  after the step the period is approximately 5000\,s.}
+  \label{fgr:temperature_dependence}
+\end{figure}
+
+A very strong temperature dependence on the oscillation frequency was also
+found as shown in Figure~\ref{fgr:temperature_dependence}. By changing the
+temperature 5$^\circ$C the oscillation period was changed by more than a factor
+of 10. The magnitude of the change is not completely consistent across all
+measured samples but all samples show a very large temperature dependency where
+in some cases a provoked small change in temperature will consistently turn on
+and off the oscillations.
+
+The pressure dependence of the oscillations was also investigated. In the
+pressure range of 0.1\,bar to 1\,bar no change of the oscillation frequency or
+qualitative behavior that could be attributed to the pressure was found.
+Similarly, only a weak dependence on the CO/O$_2$ ratio was observed. At a
+CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations was
+observed. Increasing the CO/O$_2$ showed clear oscillations with a significant
+increase in oscillation amplitude compared to lower CO concentrations.
+Generally, a tendency towards longer oscillation periods for higher CO/O$_2$
+ratio was observed. Richer CO mixtures than 0.175 did not produce any
+oscillations in our system.
+
+Although oscillations have previously been observed on extended Pt thin films
+\cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric
+pressure no oscillations could be provoked on thin films of comparable
+geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
+
+%No consistent dependency on oscillation frequency and duty cycle was found
+%that could be attributed to the size of the particles.
+
+\section{Discussion}
+Due to the long timescales between full conversion and low conversion plateaus
+the oscillations cannot be attributed to the reactor setup itself which due to
+its small size has timescales on the order of seconds. Furthermore, a series of
+experiments was performed to exclude the oscillations as an instrumental
+artifact. Firstly, experiments were performed on larger volume reactor thus
+increasing the residence time in the reactor. Secondly, the oscillations were
+reproduced on a comparable but not identical setup. Finally, attempts at
+reproducing the phenomenon on Pt-thin films of comparable coverage did not
+produce any oscillations. All of these experiments suggest that the
+oscillations is a property of the Pt nanoparticles.
 
@@
 proposal for the reaction mechanism on Pd has been developed by Hendriksen
-\textit{et. al.}\cite{Hendriksen2010} and our data are consistent with this
+\textit{et. al.}\cite{Hendriksen2010} and our data is consistent with this
 model.
@@
 convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt
-oxide will start to form in the high partial pressure of O$_2$ thus increasing
+oxide will start to form in the high partial pressures of O$_2$ thus increasing
 the rate. The model\cite{Hendriksen2010} suggests that the oxidized
@@
 
-\subsection{Temperature dependence}
-\begin{figure}
-\includegraphics[width=12cm]{temperature_dependence.png}
-\caption{Illustration of the strong temperature dependence of the oscillation period. After about 10
-  hours of steady oscillations at 205\,$^\circ$C the temperature is lowered by
-  5\,$^\circ$C immediately decreasing the oscillation frequency. The temperature
-  is hereafter increased by 2\,$^\circ$C resulting in an increase in oscillation
-  frequency. At 205\,$^\circ$C the oscillation period was approximately 500\,s
-  while the oscillation period period is approximately 5000\,s. at
-  203\,$^\circ$C.
-  \label{fgr:temperature_dependence}
-}
-\end{figure}
-
-An interesting feature in the data is the very large temperature dependence of the
-oscillation frequency as shown in Figure~\ref{fgr:temperature_dependence}. By
-changing the temperature 5\,$^\circ$C the oscillation period was changed by more
-than a factor of 10. The magnitude of the change is not completely consistent
-across all measured samples but all samples show a very large temperature
-dependence. In some cases a provoked change in temperature will
-consistently turn on and off the oscillations. This is illustrated in the supplementary
-material, Figure~S1.
-This property agrees well an earlier suggested model \cite{Hendriksen2010} and
-it is, to our knowledge, the first time the temperature dependence of
-oscillations at atmospheric pressure has been measured.
-
-\subsection{Pressure dependence}
-The pressure dependence of the oscillations was also investigated. In the
-pressure range of 0.1\,bar to 1\,bar no change of the oscillation frequency or
-qualitative behavior that could be attributed to the pressure was found.
-Similarly, only a weak dependence on the CO/O$_2$ ratio was observed. At a
-CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were
-observed. Increasing the CO/O$_2$ ratio showed clear oscillations with a significant
-increase in oscillation amplitude compared to lower CO concentrations.
-Generally, a tendency towards longer oscillation periods for higher CO/O$_2$
-ratio was observed. Richer CO mixtures than 0.175 did not produce any
-oscillations in our system.
-
-%No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.
-
-\subsection{CO concentration dependence}
-The dependence of period of the oscillations on the the CO concentration was
-investigated. The result shows that the period increases slightly with
-increasing CO-concentration. However, the effect is small compared to the
-general trend of slower oscillations as the experiment progresses. In
-Figure~\ref{fgr:gas_dependence_summary} the oscillation periods are summarized and the
-actual mass spectrometry data of the entire experiment are shown in Figure~\ref{fgr:gas_dependence}.
-
-\begin{figure}
-  \includegraphics[width=12cm]{oscil_gas_dependence_summary.png}
-  \caption{Oscillation period (blue) as a function of time and CO concentration (black). The
-  overall trend of increasing oscillation period with time is superimposed with small
-  discontinuous steps when the CO concentration is increased.} 
-  \label{fgr:gas_dependence_summary}
-\end{figure}
-
-Oscillations were only seen in CO/O$_2$ ratio below 0.175. This ratio agrees
-well with literature \cite{Singh2010,Hendriksen2005} where oscillations have
-been observed in oxygen rich CO/O$_2$ mixtures. The needed low concentration of
-CO in the inlet gases can be attributed to the much higher sticking coefficient
-of CO on Pt which poisons the nanoparticle surface during the low reactivity
-region of the cycle.
-
-\begin{figure}
-  \includegraphics[width=14cm]{oscil_gas_dependence.png}
-  \caption{Complete series of data from an oscillating sample, showing CO (red) and CO$_2$
-  (blue). The temperature is constant at $210^\circ$C during the entire
-  measurement. For every frame the CO-concentration is increased.}
-  \label{fgr:gas_dependence}
-\end{figure}
-
-\subsection{Size dependence}
-Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm
-particles with a geometrical coverage of 0.1\% of the reactor area gave the
-most stable oscillations. 
-However, no change in duty cycle or frequency that could be
-attributed to the size of the nanoparticles was found. This may be due to the
-fact that even nominally identical samples also show a large variation in
-oscillation frequency and duty cycle thus possibly shadowing a nanoparticle
-size effect.
-
-\subsection{Proposed mechanism}
 In this study Pt nanoparticles were investigated which, compared to a single
-crystal or a thin film, have a very rough surface. It is to be expected that the
+crystal or a thin film, is a very rough surface. It is to be expected that the
 particles will initially favor the reduced state. As the reaction runs the gas
 composition towards the outlet of the reactor will become more oxidizing
-increasing the oxidation rate of the particles (illustrated in the bottom of
-Figure~\ref{fgr:full_oscillation}). Gradually, as the particles towards the outlet
-oxidizes the turn-over frequency will increase and the general CO concentration will
-decrease promoting more and more particles to oxidize which will gradually be
-seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO
+increasing the oxidation rate of the particles (illustrated in
+Figure~\ref{fgr:full_oscillation}). Gradually, as the particles toward the
+outlet oxidizes the turn-over will increase and the general CO concentration
+will decrease promoting more and more particles to oxidize which will gradually
+be seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO
 concentration decreases the light-off temperature will decrease hence
@@
 nanoparticles in the reactor but the low coverage and the design of the reactor
-makes this a challenging task. If all particles are not oxidized at light-off
+makes this a challenging task. If not all particles are oxidized at light-off
 they will now oxidize much faster due to the low CO-concentration. The further
@@
 group has recently measured turnover frequencies of CO oxidation on Pt in
-excess of $10^{6}$\,s$^{-1}$ per site corresponding to as little as $\sim$300 Pt
+excess of $10^{6}$s$^{-1}$ per site corresponding to as little as $\sim$300 Pt
 nanoparticles contributing to the reactivity just before the end of the high-
-activity cycle. This would correspond to an area of 14\,ppm of the reactor
-area suggesting that in situ studies are becoming a challenges as such a
-minority of the reactor volume could account for all the reactivity. Attempts
-to see any thermal signal from such small areas has so far been in vain.
+activity cycle.
 
-\section{Conclusions}
+The oscillation period increases with time and becomes increasingly less stable
+as shown in Figure~\ref{fgr:extracts}. This phenomena is consistent across all
+measured samples. The large scatter in oscillation period can be attributed to
+the smaller oscillations in between on/off cycles. Occasionally, these small
+amplitude oscillations will trigger a full switch thus introducing more short-
+period oscillations despite the trend of increasingly slower oscillation
+period. A possible explanation of the phenomeonon could be sintering of the
+particles during the oxidation and reductions cycles. However, since the
+average conversion integrated over full oscillation periods is constant we do
+not expect sintering to be the cause since an average loss in activity of the
+sample would then be expected.
+
+Oscillations were only seen in CO/O$_2$ ratio below 0.175. This ratio agrees
+well with literature \cite{Singh2010,Hendriksen2005} where oscillations have
+been observed in oxygen rich CO/O$_2$ mixtures. The needed low concentration of
+CO in the inlet gases can be attributed to the much higher sticking coefficient
+of CO on Pt which poisons the nanoparticle surface during the low reactivity
+region of the cycle.
+
+Nanoparticles of several different sizes were tested and all showed
+oscillations. However, no change in duty cycle or frequency that could be
+attributed to the size of the nanoparticles was found. This may be due to the
+fact that even nominally identical samples also show a large variation in
+oscillation frequency and duty cycle thus possibly shadowing a nanoparticle
+size effect.
+
+An interesting feature in the data is the very large temperature dependence on
+oscillation frequency. This property agrees well an earlier suggested model
+\cite{Hendriksen2010} and it is, to our knowledge, the first time the
+temperature dependence of oscillations at atmospheric pressure has been
+measured.
+
+\section{Conclusion}
 Self-sustained CO oxidation oscillations at atmospheric pressure on Pt
-nanoparticles ranging from from 3\,nm to 9\,nm in diameter have been measured with
-high-quality mass-spectrometry. Full conversion was achieved on 0.1\,\%
-geometrical Pt coverage and it is found likely that full conversion can be obtained on
-extremely small amounts of Pt. It was found that the samples increased the
-oscillation period over time and showed a strong temperature dependence of the
-oscillation period. A model is proposed where the nanoparticles go through repetitive
+nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-
+quality mass-spectrometry. It was found that the samples increased the
+oscillation period over time and showed a strong temperature dependence. A
+model is proposed where the nanoparticles go through repetitive
 oxidation/reduction cycles which change the change rate of CO oxidation on the
-particles. The fact that extremely few NP may account for the activity make in
-situ investigations a challenge.
+particles.
 
-\section{Experimental Methods}
-\subsection{The $\mu$-reactor platform}
-The experiments were performed in Si-based 20x16\,mm
-$\mu$-reactors\cite{Henriksen2009}. The reactor consists of two inlets, a
-mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor
-volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m
-long capillary used for sniffing gases from the reactor volume. The reactor is
-sealed by anodic bonding of a Pyrex lid to the Si reactor and is able to
-operate in a pressure range of 0--2.5\,bar. The reaction gases are supplied to
-the two inlets by flow controllers capable of controlling the gas flow from 0--
-10 mL/min. The capillary flow is fed into a QMS
-for analysis while any surplus of gas from the inlets is passed directly
-through to the outlet via a pressure controller allowing control of reactor
-pressure. The design makes sure that all gases exposed to the catalyst under
-investigation are measured by the QMS ensuring an extremely high sensitivity of
-the system.
+%\subsection{This is the subsection heading style}
+%Section headings can be typeset with and without numbers.\cite{Gong2004} \cite{Hendriksen2010}
 
-\begin{figure}
- \includegraphics[width=8cm]{Ib-reactor.png}
- \caption{Image of the 20x16\,mm microreactor showing the circular reactor area
-and the gas channel system.}
-  \label{fgr:reactor}
-\end{figure}
+%\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.
 
-Before any measurements are performed the reactor is evacuated by a turbopump to minimize
-contaminants in the system. When an evacuated reactor is mounted the base
-pressure of the mass spectrometer chamber is $\sim5\times10^{-9}\,$mbar and in
-operation at $1\,$bar in the reactor volume the pressure is
-$\sim5\times10^{-7}\,$mbar in the QMS chamber.
+%\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.
 
-The reactor is heated by joule heating of a Pt strip evaporated on the backside
-of the reactor chip. The introduction of two additional contacts on the
-backside of the reactor allows for 4 wire measurements of the resistance of the
-Pt strip using it as a RTD for temperature measurement of the reactor. An
-external thermocouple acts as room-temperature calibration of the RTD as well
-as a sanity check of the RTD measurement during operation. The measured RTD
-temperature is always compared to the thermocouple temperature at room temperature both
-before and after an experiment to be sure the RTD did not change resistance due
-to annealing during the experiment.
+%\section{Equations}
 
-The gas handling including flow and pressure controllers and the mass
-spectrometer is fully automated allowing for measurements during several days
-without human intervention allowing for self-consistent measurements of many
-samples.
+%Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:
 
-\subsection{Pt nanoparticle deposition}
-Pt nanoparticles were deposited in the reactor using a gas-aggregation source
-(Mantis Deposition Ltd., Nanogen 50). Pt clusters were formed by gas-phase
-condensation of Pt atoms produced by impinging argon ions on a 99.99\% Pt
-target in a magnetron sputter source. After condensation the ionised fraction
-(60-80\%) of the clusters is size-selected by a quadropole mass selection
-filter according to their mass-to-charge ratio. Using this setup Pt
-nanoparticles with diameters in the range of 2--16\,nm can be produced
-\cite{Nielsen2010,Nielsen2009}. The size-selected nanoparticles were after
-size-selection soft-landed in the reactor volume of the microreactor. The
-coverage was kept at approximately 0.1\% geometric coverage determined by
-measuring the current on the reactor during deposition. After deposition the
-reactors were anodically cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid
-sintering of the nanoparticles while bonding in air.
+% \[ A = \pi r^2 \]
 
-\section{Acknowledgments}
-This work was carried out as part of the Catalysis for Sustainable Energy
-initiative, which is funded by the Danish Ministry of Science, Technology and
-Innovation. The Center for Individual Nanoparticle Functionality is funded by
-the Danish National Research Foundation.
+%\begin{equation}
+%  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
+%\end{equation}
 
+%\section{Graphics and tables}
+%\subsection{Graphics}
+%Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).
+
+%\subsection{Tables}
+%Tables typeset in RSC house style do not include vertical lines.
+Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table.
+Table captions do not end in a full point.
+
+%\begin{table}[h]
+%\small
+%  \caption{\ An example of a caption to accompany a table}
+%  \label{tbl:example}
+%  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
+%    \hline
+%    Header one/units & Header two & Header three \\
+%    \hline
+%    1 & 2 & 3 \\
+%    4 & 5 & 6 \\
+%    7 & 8 & 9 \\
+%    10 & 11 & 12 \\
+%    \hline
+%  \end{tabular*}
+%\end{table}
+
+%Adding notes to tables can be complicated.  Perhaps the easiest
+%method is to generate these manually.
+
+% an example of a two-column table
+%\begin{table*}
+%\small
+  %\caption{\ An example of a caption to accompany a table, table captions do not end in a full point}
+  %\label{tbl:example}
+  %\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllll}
+    %\hline
+    %Header one & Header two & Header three & Header four & Header five & Header six  & Header seven\\
+    %\hline
+    %1 & 2 & 3 & 4 & 5 & 6  & 7\\
+    %8 & 9 & 10 & 11 & 12 & 13 & 14 \\
+    %15 & 16 & 17 & 18 & 19 & 20 & 21\\
+    %\hline
+  %\end{tabular*}
+%\end{table*}
+
+%You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
+%The \texttt{mhchem} package can also be used so
+%that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.
+
+%\section{Conclusions}
+%The conclusions section should come at the end of article.
+For the reference section, the style file rsc.bst can be used to generate the correct reference style.\footnote[4]{Footnotes should appear here.
+These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
+ %For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols.
+e.g.
+\footnote[num]{your text} the corresponding author \ast counts as footnote 1, ESI as footnote 2, e.g.
+if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] etc.
+Please also cite the ESI within the main body of the text using \dag.
+
+%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
+
+%\balance
+
+%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
+%\renewcommand\refname{Notes and references}
+
+\footnotesize{
 \bibliography{literature} %your .bib file
+\bibliographystyle{rsc} %the RSC's .bst file
+}
 

### 2012-06-28 python_figures/initial_treatment.py

@@ -6,6 +6,7 @@ import numpy as np
 import MySQLdb
 from matplotlib.patches import Rectangle
 
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
 
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
@@ -59,16 +60,16 @@ axis2 = axis.twinx()
 axis2.plot(data['TEMPERATURE'][:,0], data['TEMPERATURE'][:,1], 'b-')
 axis2.set_ylim(0,300)
 axis2.set_yticks((50,150,250))
-axis.set_xlim(100,800)
+axis.set_xlim(250,800)
 axis.grid(False)    
 
 
 
 #arrow = dict(facecolor='black', shrink=0.085,width=1)
 arrow = dict(facecolor='black',arrowstyle='->')
-axis.annotate('M28', xy=(260, 2.6),  xycoords='data', xytext=(185, 3.5), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
-axis.annotate('M44', xy=(440, 4.4),  xycoords='data', xytext=(390, 5.6), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
-axis.annotate('Temp.', xy=(440, 6.6),  xycoords='data', xytext=(270, 7.2), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('CO', xy=(375, 2.4),  xycoords='data', xytext=(350, 1.1), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
+axis.annotate('CO$_2$', xy=(420, 3.7),  xycoords='data', xytext=(460, 5.4), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
+axis.annotate('Temp.', xy=(440, 6.6),  xycoords='data', xytext=(380, 7.2), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
 
[…]

### 2012-06-28 python_figures/temperature_dependence_supplemental.py

@@ -4,6 +4,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
 
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
+
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
 except:
@@ -49,8 +51,8 @@ axis.grid(False)
 
 arrow = dict(facecolor='black',arrowstyle='->')
 #arrow = dict(facecolor='black', shrink=0.085,width=1)
-axis.annotate('M28', xy=(80, 3.5),  xycoords='data', xytext=(120, 4.5), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
-axis.annotate('M44', xy=(80, 1.2),  xycoords='data', xytext=(120, 2.25), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('CO', xy=(80, 3.5),  xycoords='data', xytext=(120, 4.5), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('CO$_2$', xy=(80, 1.2),  xycoords='data', xytext=(120, 2.25), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 axis.annotate('Temp.', xy=(70, 5.7),  xycoords='data', xytext=(120, 7), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)

### 2012-10-18 paper.tex
Backporting from later versions
Since this document is now checkout from rather long ago
because it fits with pccp, it will be necessary to backport
some newer corrections into this document. Some of this
work has been done in this commit.

@@
 
-CO oxidation is one of the most studied reactions due to its importance in both
-automotive catalysis and in the removal of trace CO in hydrogen streams. A
-large effort and a large number of experiments with a variety of surface
-sensitive techniques have been conducted on single crystal surfaces greatly
-improving the understanding of this reaction. Single crystal surfaces are well
-suited model systems due to the high degree of achievable control of parameters
-compared to industrial catalysts. Here we report on studies in a microreactor
-model system of Pt nanoparticles. The size-selected nanoparticles supported on
-a SiO$_2$ substrate show oscillatory behavior of CO oxidation at atmospheric
-pressure.
+CO oxidation is one of the most studied reactions due to its importance in both automotive catalysis and in the removal of trace CO in hydrogen streams.
+A large effort and a large number of experiments with a variety of surface sensitive techniques have been conducted on single crystal surfaces greatly improving the understanding of this reaction.
+Single crystal surfaces are well suited model systems due to the high degree of achievable control of parameters compared to industrial catalysts.
+Here we report on studies in a microreactor model system of Pt nanoparticles.
+The size-selected nanoparticles supported on a SiO$_2$ substrate show oscillatory behavior of CO oxidation at atmospheric pressure.
 
-Oscillating reactions on single crystals at UHV conditions have been studied
-extensively and is know to originate from surface reconstructions of the
-surface during the oscillations\cite{Ertl2008}. It has previously been
-shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows
-oscillatory behavior on single crystals of Pt, Pd and Ir. Recent studies have
-proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of
-surface oxide formation, oxide roughening and clean metal surface formation. CO
-oxidation oscillations has also been observed on Pt thin films\cite{Lund2000},
-in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles
-synthesized from wet chemical synthesis and subsequent annealing
-\cite{Carlsson2006}. Here we investigate CO oscillations in a microreactor
-model system on size selected Pt nanoparticles by high sensitivity mass
-spectrometry.
+Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
+It has previously been shown\cite{SALES1982} that CO oxidation at atmospheric pressures also shows oscillatory behavior on single crystals of Pt, Pd and Ir.
+Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface formation.
+CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
+Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.
 
@@
 The experiments were performed in Si-based $\mu$-reactors\cite{Henriksen2009}.
-The reactor design makes sure that all gases exposed to the catalyst under
-investigation is measured by the quadropole mass spectrometer (QMS) ensuring an
-extremely high sensitivity of the system.
+The reactor design makes sure that all gases exposed to the catalyst under investigation is measured by the quadropole mass spectrometer (QMS) ensuring an extremely high sensitivity of the system.
 
 Pt nanoparticles were deposited in the reactor using a gas-aggregation source.
-The nanoparticles were size-selected by a quadropole mass selection filter
-according to their mass-to-charge ratio. Using this setup Pt nanoparticles with
-diameters in the range of 2--16\,nm can be produced \cite{Nielsen2009}. After
-deposition the reactors were anodically cold-bonded \cite{Vesborg2010} to a
-pyrex lid to avoid sintering of the nanoparticles while bonding.
+The nanoparticles were size-selected by a quadropole mass selection filter according to their mass-to-charge ratio.
+Using this setup Pt nanoparticles with diameters in the range of 2--16\,nm can be produced \cite{Nielsen2009}.
+After deposition the reactors were anodically cold-bonded \cite{Vesborg2010} to a pyrex lid to avoid sintering of the nanoparticles while bonding.
 
 \section{Results}
-An oscillation measurement is performed by mounting a sample in the setup
-directly after cluster deposition and anodic bonding. Initially a light-off CO-
-oxidation measurement is performed (shown in
-Figure~\ref{fgr:initial_treatment}) where the temperature is increased at
-3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to
-CO$_2$. At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of
-$\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C. The temperature
-ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is
-decreased at the same rate as the heating ramp. After the initial light-off the
-sample is cooled to room temperature. When at room temperature the temperature
-is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A
-typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where
-both the symmetrical light-off ramp and the subsequent increase in temperature
-to achieve sustained oscillations is seen. Often the sample will show
-oscillations either directly upon light-off or on the falling temperature ramp.
-
+An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding.
+Initially a light-off CO-oxidation measurement is performed (shown in Figure~\ref{fgr:initial_treatment}) where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
+At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C.
+The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating ramp.
+After the initial light-off the sample is cooled to room temperature.
+When at room temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur.
+A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical light-off ramp and the subsequent increase in temperature to achieve sustained oscillations is seen.
+Often the sample will show oscillations either directly upon light-off or on the falling temperature ramp.
 \begin{figure}[h]
@@
   \includegraphics[width=9cm]{initial_treatment.png}
-  \caption{A typical example of the initial treatment of a new sample. After
- performing a light-off ramp where oscillations can been seen the temperature
- is increased to a constant value where sustained oscillations take place. The
- non-zero value of CO during high conversion periods is consistent with the
- expected QMS background signals from CO$_2$ and O$_2$.}
+  \caption{A typical example of the initial treatment of a new sample.
+After performing a light-off ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.
+The non-zero value of CO during high conversion periods is consistent with the expected QMS background signals from CO$_2$ and O$_2$.}
   \label{fgr:initial_treatment}
 \end{figure}
+Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm particles with a geometrical coverage of 0.1\% of the reactor area gave the most stable oscillations.
+No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.
 
-Nanoparticles with sizes ranging from 3\,nm to 9\,nm have been tested but 3\,nm
-particles with a geometrical coverage of 0.1\% of the reactor area gave the
-most stable oscillations. No consistent dependency on oscillation frequency and
-duty cycle was found that could be attributed to the size of the particles.
+The oscillations on all samples are qualitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s) up to more than an hour.
+Once a sample start to oscillate it will perform self-sustained oscillations for as long as the experiment is allowed to run.
+We have not observed a single sample stop oscillating once the self-sustained oscillations had started.
 
-The oscillations on all samples are qualitatively similar but the oscillation
-period varies from a few seconds (the time-constant of the reactor is
-$\sim7\,$s) up to more than an hour. Once a sample start to oscillate it will
-perform self-sustained oscillations for as long as the experiment is allowed to
-run. We have not observed a single sample stop oscillating once the self-
-sustained oscillations had started.
-
-An example of a single very slow oscillation is seen in
-Figure~\ref{fgr:full_oscillation}. After a short on-cycle (at $\sim$1030\,min)
-where all CO is converted to CO$_2$ (notice the CO signal does not go to zero
-due to the cracking pattern of CO$_2$ and CO background in the QMS) the
-reaction shows a fast deactivation. After the deactivation the sample quickly
-regains $\sim$30\% conversion (at $\sim$1040\,min). Hereafter the conversion
-increases slowly over time until approximately 50\% conversion is reached (at
-$\sim$1118\,min). Shortly after reaching 50\% conversion the sample again
-ignites and convert all CO to CO$_2$. After a short full conversion period the
-sample again deactivates and the cycle repeats itself.
-
+An example of a single very slow oscillation is seen in Figure~\ref{fgr:full_oscillation}.
+After a short on-cycle (at $\sim$1030\,min) where all CO is converted to CO$_2$ (notice the CO signal does not go to zero due to the cracking pattern of CO$_2$ and CO background in the QMS) the reaction shows a fast deactivation.
+After the deactivation the sample quickly regains $\sim$30\% conversion (at $\sim$1040\,min).
+Hereafter the conversion increases slowly over time until approximately 50\% conversion is reached (at $\sim$1118\,min).
+Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$.
+After a short full conversion period the sample again deactivates and the cycle repeats itself.
 \begin{figure*}
@@
   \includegraphics[width=17cm]{single_full_oscillation.png}
-  \caption{A full oscillation period first showing a steep ignition of the
-  sample followed by an almost immediate deactivation. For the next 65 minutes
-  the sample slowly recovers activity until full conversion is reached again
-  and the cycle repeats itself. This extremely long oscillation period is not
-  commonly seen and was a result of careful parameter tuning. Typical
-  oscillation periods are normally between $\sim$30\,s and $\sim$30\,min.
-  Inserted circles illustrates the proposed model. At high conversion the
-  platinum is oxidized (red) while in low conversion the sample is reduced
-  (blue).}
+  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate deactivation.
+For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.
+This extremely long oscillation period is not commonly seen and was a result of careful parameter tuning.
+Typical oscillation periods are normally between $\sim$30\,s and $\sim$30\,min.
+Inserted circles illustrates the proposed model.
+At high conversion the platinum is oxidized (red) while in low conversion the sample is reduced (blue).}
   \label{fgr:full_oscillation}
@@
 
-After prolonged measurements over several days an increase in oscillation
-period was observed as shown in Figure \ref{fgr:long_measurement}. Initially,
-the oscillation period is $\sim$2.5 min and increases linearly with time until
-1500 min of total oscillation time. Hereafter the oscillations become more
-irregular as shown in Figure~\ref{fgr:extracts} and lower panel
-Figure~\ref{fgr:long_measurement}. At experiment end the oscillation period is
-between 20 and 45 min.
-
+After prolonged measurements over several days an increase in oscillation period was observed as shown in Figure \ref{fgr:long_measurement}.
+Initially, the oscillation period is $\sim$2.5 min and increases linearly with time until 1500 min of total oscillation time.
+Hereafter the oscillations become more irregular as shown in Figure~\ref{fgr:extracts} and lower panel Figure~\ref{fgr:long_measurement}.
+At experiment end the oscillation period is between 20 and 45 min.
 \begin{figure}[h]
@@
   \includegraphics[width=9cm]{summary_of_long_measurement.png}
-  \caption{Summary of the oscillation period as a function of time for a sample
-  oscillating under constant temperature, pressure and reactant composition.
-  The sample went through a total of 439 oscillations in 4 days. Time is
-  defined from experiment start and hence includes initial treatment. The inset
-  shows the initial steady increase in oscillation period.}
+  \caption{Summary of the oscillation period as a function of time for a sample oscillating under constant temperature, pressure and reactant composition.
+The sample went through a total of 439 oscillations in 4 days.
+Time is defined from experiment start and hence includes initial treatment.
+The inset shows the initial steady increase in oscillation period.}
   \label{fgr:long_measurement}
@@
 
-Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of
-oscillations extracted from the same four days measurement. Data from shortly
-after the initial treatment, after 2800\,min of oscillation time and after
-5900\,min are shown. After 5900\,min the oscillations are more irregular which
-is consistent with the data shown in Figure \ref{fgr:long_measurement}. Also,
-oscillations in between full conversion oscillations with smaller amplitude and
-much higher frequency than the full on-off cycles become more visible as time
-progresses.
-
+Figure~\ref{fgr:extracts} shows extracts of mass spectrometry data of oscillations extracted from the same four days measurement.
+Data from shortly after the initial treatment, after 2800\,min of oscillation time and after 5900\,min are shown.
+After 5900\,min the oscillations are more irregular which is consistent with the data shown in Figure \ref{fgr:long_measurement}.
+Also, oscillations in between full conversion oscillations with smaller amplitude and much higher frequency than the full on-off cycles become more visible as time progresses.
 \begin{figure}[h]
@@
   \includegraphics[width=9cm]{extracts_from_very_long_oscillation.png}
-  \caption{Extracts from the 4 days long experiment. The oscillation period
-  becomes more irregular with time while the total integrated conversion
-  remains constant. Furthermore, small oscillations in between full conversion
-  cycles become more prominent as time progresses.}
+  \caption{Extracts from the 4 days long experiment.
+The oscillation period becomes more irregular with time while the total integrated conversion remains constant.
+Furthermore, small oscillations in between full conversion cycles become more prominent as time progresses.}
   \label{fgr:extracts}
@@
 
-The oscillation frequency becomes more irregular with progressing experiment
-time as shown in Figure \ref{fgr:extracts}. However, the ratio between CO and
-CO$_2$ integrated over an full period remains constant throughout the entire
-experiment time, i.e. the samples maintains a constant average rate independent
-of oscillation frequency.
+The oscillation frequency becomes more irregular with progressing experiment time as shown in Figure \ref{fgr:extracts}.
+However, the ratio between CO and CO$_2$ integrated over an full period remains constant throughout the entire experiment time, i.e.
+the samples maintains a constant average rate independent of oscillation frequency.
 
-%Furthermore, the oscillations have the qualitatively identical behavior as
-%shown in Figure~\ref{fgr:full_oscillation}. A short full conversion period is
-%followed by a fast deactivation from where reactivity is slowly recovered. At
-%approximately 50\% conversion light-off occurs and the sample is in full
-%conversion.
+%Furthermore, the oscillations have the qualitatively identical behavior as shown in Figure~\ref{fgr:full_oscillation}.
+A short full conversion period is followed by a fast deactivation from where reactivity is slowly recovered.
+At approximately 50\% conversion light-off occurs and the sample is in full conversion.
 
@@
   \includegraphics[width=9cm]{temperature_dependence.png}
-  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature
-  is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before
-  the temperature step the oscillation period was approximately 500\,s and
-  after the step the period is approximately 5000\,s.}
+  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C.
+Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
   \label{fgr:temperature_dependence}
 \end{figure}
+A very strong temperature dependence on the oscillation frequency was also found as shown in Figure~\ref{fgr:temperature_dependence}.
+By changing the temperature 5$^\circ$C the oscillation period was changed by more than a factor of 10.
+The magnitude of the change is not completely consistent across all measured samples but all samples show a very large temperature dependency where in some cases a provoked small change in temperature will consistently turn on and off the oscillations.
 
-A very strong temperature dependence on the oscillation frequency was also
-found as shown in Figure~\ref{fgr:temperature_dependence}. By changing the
-temperature 5$^\circ$C the oscillation period was changed by more than a factor
-of 10. The magnitude of the change is not completely consistent across all
-measured samples but all samples show a very large temperature dependency where
-in some cases a provoked small change in temperature will consistently turn on
-and off the oscillations.
+The pressure dependence of the oscillations was also investigated.
+In the pressure range of 0.1\,bar to 1\,bar no change of the oscillation frequency or qualitative behavior that could be attributed to the pressure was found.
+Similarly, only a weak dependence on the CO/O$_2$ ratio was observed.
+At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations was observed.
+Increasing the CO/O$_2$ showed clear oscillations with a significant increase in oscillation amplitude compared to lower CO concentrations.
+Generally, a tendency towards longer oscillation periods for higher CO/O$_2$ ratio was observed.
+Richer CO mixtures than 0.175 did not produce any oscillations in our system.
 
-The pressure dependence of the oscillations was also investigated. In the
-pressure range of 0.1\,bar to 1\,bar no change of the oscillation frequency or
-qualitative behavior that could be attributed to the pressure was found.
-Similarly, only a weak dependence on the CO/O$_2$ ratio was observed. At a
-CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations was
-observed. Increasing the CO/O$_2$ showed clear oscillations with a significant
-increase in oscillation amplitude compared to lower CO concentrations.
-Generally, a tendency towards longer oscillation periods for higher CO/O$_2$
-ratio was observed. Richer CO mixtures than 0.175 did not produce any
-oscillations in our system.
+Although oscillations have previously been observed on extended Pt thin films \cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric pressure no oscillations could be provoked on thin films of comparable geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
 
-Although oscillations have previously been observed on extended Pt thin films
-\cite{Singh2010} as well as single crystals\cite{Hendriksen2005} at atmospheric
-pressure no oscillations could be provoked on thin films of comparable
-geometrical coverage to the nanoparticles in our system at any CO/O$_2$ ratio.
-
-%No consistent dependency on oscillation frequency and duty cycle was found
-%that could be attributed to the size of the particles.
+%No consistent dependency on oscillation frequency and duty cycle was found that could be attributed to the size of the particles.
 
 \section{Discussion}
-Due to the long timescales between full conversion and low conversion plateaus
-the oscillations cannot be attributed to the reactor setup itself which due to
-its small size has timescales on the order of seconds. Furthermore, a series of
-experiments was performed to exclude the oscillations as an instrumental
-artifact. Firstly, experiments were performed on larger volume reactor thus
-increasing the residence time in the reactor. Secondly, the oscillations were
-reproduced on a comparable but not identical setup. Finally, attempts at
-reproducing the phenomenon on Pt-thin films of comparable coverage did not
-produce any oscillations. All of these experiments suggest that the
-oscillations is a property of the Pt nanoparticles.
+Due to the long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the reactor setup itself which due to its small size has timescales on the order of seconds.
+Furthermore, a series of experiments was performed to exclude the oscillations as an instrumental artifact.
+Firstly, experiments were performed on larger volume reactor thus increasing the residence time in the reactor.
+Secondly, the oscillations were reproduced on a comparable but not identical setup.
+Finally, attempts at reproducing the phenomenon on Pt-thin films of comparable coverage did not produce any oscillations.
+All of these experiments suggest that the oscillations is a property of the Pt nanoparticles.
 
-It has previously been shown using STM \cite{Hendriksen2002}, FT-IR
-\cite{Carlsson2006}, Monte Carlo simulations \cite{Zhdanov2002} as well as DFT
-\cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric
-pressures is highly dependent on the oxidation state of the surface. A detailed
-proposal for the reaction mechanism on Pd has been developed by Hendriksen
-\textit{et. al.}\cite{Hendriksen2010} and our data is consistent with this
-model.
+It has previously been shown using STM \cite{Hendriksen2002}, FT-IR \cite{Carlsson2006}, Monte Carlo simulations \cite{Zhdanov2002} as well as DFT \cite{Gong2004} that the activity of Pt towards CO oxidation at atmospheric pressures is highly dependent on the oxidation state of the surface.
+A detailed proposal for the reaction mechanism on Pd has been developed by Hendriksen \textit{et.
+al.}\cite{Hendriksen2010} and our data is consistent with this model.
 
-According to the proposed model in ref.~\citenum{Hendriksen2010} the bare metal
-surface is less active than the oxidized surface. Oscillations originate from a
-switch between an oxidized surface and the bare metal surface. Initially, with
-CO present in the inlet gas a smooth metal surface is exposed due to the
-general high adsorption energy of CO on metal surfaces. As the Pt nanoparticles
-convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt
-oxide will start to form in the high partial pressures of O$_2$ thus increasing
-the rate. The model\cite{Hendriksen2010} suggests that the oxidized
-nanoparticles will roughen during CO oxidation resulting in the formation of an
-increasingly rough oxide surface. As the oxide becomes rougher the bare metal
-surface is increasingly favored resulting in a return to the lower rate rough
-metal state. As the rate decreases the CO partial pressure increases which
-results in a transition from rough metal surface to a smooth metal surface.
-When the sample is sufficiently smooth it will again oxidize and thus complete
-the oscillation cycle.
+According to the proposed model in ref.~\citenum{Hendriksen2010} the bare metal surface is less active than the oxidized surface.
+Oscillations originate from a switch between an oxidized surface and the bare metal surface.
+Initially, with CO present in the inlet gas a smooth metal surface is exposed due to the general high adsorption energy of CO on metal surfaces.
+As the Pt nanoparticles convert the CO to CO$_2$ the partial pressure of CO will decrease and a Pt oxide will start to form in the high partial pressures of O$_2$ thus increasing the rate.
+The model\cite{Hendriksen2010} suggests that the oxidized nanoparticles will roughen during CO oxidation resulting in the formation of an increasingly rough oxide surface.
+As the oxide becomes rougher the bare metal surface is increasingly favored resulting in a return to the lower rate rough metal state.
+As the rate decreases the CO partial pressure increases which results in a transition from rough metal surface to a smooth metal surface.
+When the sample is sufficiently smooth it will again oxidize and thus complete the oscillation cycle.
 
-In this study Pt nanoparticles were investigated which, compared to a single
-crystal or a thin film, is a very rough surface. It is to be expected that the
-particles will initially favor the reduced state. As the reaction runs the gas
-composition towards the outlet of the reactor will become more oxidizing
-increasing the oxidation rate of the particles (illustrated in
-Figure~\ref{fgr:full_oscillation}). Gradually, as the particles toward the
-outlet oxidizes the turn-over will increase and the general CO concentration
-will decrease promoting more and more particles to oxidize which will gradually
-be seen in the QMS as an increase in CO$_2$ and a decrease in CO. As the CO
-concentration decreases the light-off temperature will decrease hence
-approaching the constant temperature of the sample resulting in a steep
-increase in reactivity. It is important to note that the fraction of oxidized
-particles needed to achieve full conversion is not known. We are currently
-investigating new methods for gaining insight into the nature of the
-nanoparticles in the reactor but the low coverage and the design of the reactor
-makes this a challenging task. If not all particles are oxidized at light-off
-they will now oxidize much faster due to the low CO-concentration. The further
-increased rate will not be visible in the QMS since the reactor is already in
-full conversion. As most of the particles are now oxidized they will become
-more and more roughened and gradually return to the reduced state. Fewer and
-fewer oxidized particles will be responsible for the activity increasing the
-roughing rate of the remaining active particles. Just before the overall
-activity drops only a fraction of the particles participates in the reaction
-and the deactivation will happen very suddenly. Once these potentially few
-particles eventually becomes sufficiently rough they will reduce and lose
-activity hence completing the oscillation cycle. It should be noted that our
-group has recently measured turnover frequencies of CO oxidation on Pt in
-excess of $10^{6}$s$^{-1}$ per site corresponding to as little as $\sim$300 Pt
-nanoparticles contributing to the reactivity just before the end of the high-
-activity cycle.
+In this study Pt nanoparticles were investigated which, compared to a single crystal or a thin film, is a very rough surface.
+It is to be expected that the particles will initially favor the reduced state.
+As the reaction runs the gas composition towards the outlet of the reactor will become more oxidizing increasing the oxidation rate of the particles (illustrated in Figure~\ref{fgr:full_oscillation}).
+Gradually, as the particles toward the outlet oxidizes the turn-over will increase and the general CO concentration will decrease promoting more and more particles to oxidize which will gradually be seen in the QMS as an increase in CO$_2$ and a decrease in CO.
+As the CO concentration decreases the light-off temperature will decrease hence approaching the constant temperature of the sample resulting in a steep increase in reactivity.
+It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known.
+We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task.
+If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration.
+The further increased rate will not be visible in the QMS since the reactor is already in full conversion.
+As most of the particles are now oxidized they will become more and more roughened and gradually return to the reduced state.
+Fewer and fewer oxidized particles will be responsible for the activity increasing the roughing rate of the remaining active particles.
+Just before the overall activity drops only a fraction of the particles participates in the reaction and the deactivation will happen very suddenly.
+Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle.
+It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of $10^{6}$s$^{-1}$ per site corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
 
-The oscillation period increases with time and becomes increasingly less stable
-as shown in Figure~\ref{fgr:extracts}. This phenomena is consistent across all
-measured samples. The large scatter in oscillation period can be attributed to
-the smaller oscillations in between on/off cycles. Occasionally, these small
-amplitude oscillations will trigger a full switch thus introducing more short-
-period oscillations despite the trend of increasingly slower oscillation
-period. A possible explanation of the phenomeonon could be sintering of the
-particles during the oxidation and reductions cycles. However, since the
-average conversion integrated over full oscillation periods is constant we do
-not expect sintering to be the cause since an average loss in activity of the
-sample would then be expected.
+The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}.
+This phenomena is consistent across all measured samples.
+The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles.
+Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period.
+A possible explanation of the phenomeonon could be sintering of the particles during the oxidation and reductions cycles.
+However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.
 
-Oscillations were only seen in CO/O$_2$ ratio below 0.175. This ratio agrees
-well with literature \cite{Singh2010,Hendriksen2005} where oscillations have
-been observed in oxygen rich CO/O$_2$ mixtures. The needed low concentration of
-CO in the inlet gases can be attributed to the much higher sticking coefficient
-of CO on Pt which poisons the nanoparticle surface during the low reactivity
-region of the cycle.
+Oscillations were only seen in CO/O$_2$ ratio below 0.175.
+This ratio agrees well with literature \cite{Singh2010,Hendriksen2005} where oscillations have been observed in oxygen rich CO/O$_2$ mixtures.
+The needed low concentration of CO in the inlet gases can be attributed to the much higher sticking coefficient of CO on Pt which poisons the nanoparticle surface during the low reactivity region of the cycle.
 
-Nanoparticles of several different sizes were tested and all showed
-oscillations. However, no change in duty cycle or frequency that could be
-attributed to the size of the nanoparticles was found. This may be due to the
-fact that even nominally identical samples also show a large variation in
-oscillation frequency and duty cycle thus possibly shadowing a nanoparticle
-size effect.
+Nanoparticles of several different sizes were tested and all showed oscillations.
+However, no change in duty cycle or frequency that could be attributed to the size of the nanoparticles was found.
+This may be due to the fact that even nominally identical samples also show a large variation in oscillation frequency and duty cycle thus possibly shadowing a nanoparticle size effect.
 
-An interesting feature in the data is the very large temperature dependence on
-oscillation frequency. This property agrees well an earlier suggested model
-\cite{Hendriksen2010} and it is, to our knowledge, the first time the
-temperature dependence of oscillations at atmospheric pressure has been
-measured.
+An interesting feature in the data is the very large temperature dependence on oscillation frequency.
+This property agrees well an earlier suggested model \cite{Hendriksen2010} and it is, to our knowledge, the first time the temperature dependence of oscillations at atmospheric pressure has been measured.
 
 \section{Conclusion}
-Self-sustained CO oxidation oscillations at atmospheric pressure on Pt
-nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-
-quality mass-spectrometry. It was found that the samples increased the
-oscillation period over time and showed a strong temperature dependence. A
-model is proposed where the nanoparticles go through repetitive
-oxidation/reduction cycles which change the change rate of CO oxidation on the
-particles.
+Self-sustained CO oxidation oscillations at atmospheric pressure on Pt nanoparticles ranging from from 3\,nm to 9\,nm have been measured with high-quality mass-spectrometry.
+It was found that the samples increased the oscillation period over time and showed a strong temperature dependence.
+A model is proposed where the nanoparticles go through repetitive oxidation/reduction cycles which change the change rate of CO oxidation on the particles.
 

### 2012-10-18 python_figures/extracts_from_very_long_oscillation.py

@@ -5,6 +5,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
 
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
+
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
 except:
@@ -61,6 +63,11 @@ for i in range(0,3):
     axis_array[i].tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=2)
     axis2_array[i].tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='y',pad=2)
     axis_array[i].grid(False)    
+
+arrow = dict(facecolor='black',arrowstyle='->')
+axis_array[0].annotate('CO', xy=(710, 3.9),  xycoords='data', xytext=(710, 5.7), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
+axis_array[0].annotate('CO$_2$', xy=(725, 1.7),  xycoords='data', xytext=(715, 0.5), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
+axis_array[0].annotate('T', xy=(728, 4.9),  xycoords='data', xytext=(720, 5.3), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=8,)
 
 axis_array[1].set_ylabel('SEM Current / nA', fontsize=8)
 axis2_array[1].set_ylabel('Temperature', fontsize=8)

### 2012-10-18 python_figures/summary_of_long_measurement.py

@@ -1,4 +1,3 @@
-
 #This will be a simple implementation of a program that summaries the oscillation period as a function of oscillation number
 #We will also need a simple program that summarises duty cycle as a function of oscillation
 
@@ -8,6 +7,9 @@ matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
+from scipy import optimize
+
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
 
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
@@ -59,8 +61,20 @@ fig.set_size_inches(fig_width,fig_height)
 
 axis = fig.add_subplot(1,1,1)
 axis.plot(oscillations, periods, 'b.')
-axis.plot([750,6000],[1.8,17],'r-')
-axis.plot([750,5000],[5,43],'r-')
+#axis.plot([750,6000],[1.8,17],'r-')
+#axis.plot([750,5000],[5,43],'r-')
+range = np.arange(700,6500)
+
+fitfunc = lambda p, x: p[0]*(x**p[1])+p[2]       # Target function
+errfunc = lambda p, x, y: fitfunc(p, x) - y # Distance to the target function
+p0 = [0.2,0.6,2] # Initial guess for the parameters
+p1, success = optimize.leastsq(errfunc, p0[:], args=([700,1000,2000,4000,6000],[4,6,20,37,45]),maxfev=1000)
+print p1, success
+axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r-')
+
+p1, success = optimize.leastsq(errfunc, p0[:], args=([500,1000,2000,4000,6000],[0,2,9,11,16]),maxfev=1000)
+print p1, success
+axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r-')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
 #axis.set_ylim(0,7)
@@ -78,5 +92,5 @@ a.tick_params(direction='in', length=3, width=1, colors='k',labelsize=6,axis='bo
 plt.setp(a, xlim=(700,1500), ylim=(2,8),xticks=[900,1100,1300], yticks=[3,5,7])
 
 #plt.tight_layout()
-plt.show()
+#plt.show()
 plt.savefig('../summary_of_long_measurement.png',dpi=300)

### 2012-10-18 python_figures/temperature_dependence.py

@@ -4,6 +4,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 import MySQLdb
 
+matplotlib.rc('text',usetex=True) # Magic fix for the font warnings
+
 try:
     db = MySQLdb.connect(host="servcinf", user="cinf_reader",passwd = "cinf_reader", db = "cinfdata")
 except:
@@ -49,8 +51,8 @@ axis.grid(False)
 
 arrow = dict(facecolor='black',arrowstyle='->')
 #arrow = dict(facecolor='black', shrink=0.085,width=1)
-axis.annotate('M28', xy=(830, 0.85),  xycoords='data', xytext=(800, 0.95), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
-axis.annotate('M44', xy=(830, 0.4),  xycoords='data', xytext=(800, 0.25), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('CO', xy=(830, 0.85),  xycoords='data', xytext=(800, 0.95), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
+axis.annotate('CO$_2$', xy=(830, 0.4),  xycoords='data', xytext=(800, 0.25), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 axis.annotate('Temp.', xy=(855, 1.15),  xycoords='data', xytext=(810, 1.2), textcoords='data', arrowprops=arrow, horizontalalignment='right', verticalalignment='center',fontsize=9,)
 
 axis.tick_params(direction='in', length=6, width=1, colors='k',labelsize=8,axis='both',pad=3)

### 2012-10-18 paper.tex
Added a missing figure, updated a few wrong numbers

@@
 
-\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
-\footnotetext{\textit{$^{b}$~CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, Ørsteds Plads, B 345B, 2800 Lyngby, Denmark.
-Fax: XX XXXX XXXX; Tel: XX XXXX XXXX; E-mail: ibchork@fysik.dtu.dk}}
+\footnotetext{\textit{$^{a}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark. E-mail: ibchork@fysik.dtu.dk}}
+\footnotetext{\textit{$^{b}$~CINF, Department of Micro- and Nanotechnology, Technical University of Denmark, Ørsteds Plads, B 345B, 2800 Lyngby, Denmark.}}
 %\footnotetext{\textit{$^{b}$~CINF, Department of Physics, Technical University of Denmark, Fysikvej 312, 2800 Lyngby, Denmark}}
@@
 Once these potentially few particles eventually becomes sufficiently rough they will reduce and lose activity hence completing the oscillation cycle.
-It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt in excess of $10^{6}$s$^{-1}$ per site corresponding to as little as $\sim$300 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
+It should be noted that our group has recently measured turnover frequencies of CO oxidation on Pt of almost $10^{5}$s$^{-1}$ per site corresponding to as little as $\sim$50000 Pt nanoparticles contributing to the reactivity just before the end of the high-activity cycle.
+This corresponds to an area of $\sim$0.5 ppm of the reactor area suggesting that in situ studies become challenging as such a minority of the reactor volume could account for all the reactivity.
+Attempts to see any thermal signal from such small areas has so far been in vain.
 
@@
 
-%\subsection{This is the subsection heading style}
-%Section headings can be typeset with and without numbers.\cite{Gong2004} \cite{Hendriksen2010}
-
-%\subsubsection{This is the subsubsection style.~~} These headings should end in a full point.
-
-%\paragraph{This is the next level heading.~~} For this level please use \texttt{\textbackslash paragraph}. These headings should also end in a full point.
-
-%\section{Equations}
-
-%Equations can be typeset inline \textit{e.g.} $ y = mx + c$ or displayed with and without numbers:
-
-% \[ A = \pi r^2 \]
-
-%\begin{equation}
-%  \frac{\mathrm{\gamma}}{\mathrm{\epsilon}x} r^2 = 2r
-%\end{equation}
-
-%\section{Graphics and tables}
-%\subsection{Graphics}
-%Graphics should be inserted on the page where they are first mentioned (unless they are equations, which appear in the flow of the text).
-
-%\subsection{Tables}
-%Tables typeset in RSC house style do not include vertical lines.
-Table footnote symbols are lower-case italic letters and are typeset at the bottom of the table.
-Table captions do not end in a full point.
-
-%\begin{table}[h]
-%\small
-%  \caption{\ An example of a caption to accompany a table}
-%  \label{tbl:example}
-%  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}lll}
-%    \hline
-%    Header one/units & Header two & Header three \\
-%    \hline
-%    1 & 2 & 3 \\
-%    4 & 5 & 6 \\
-%    7 & 8 & 9 \\
-%    10 & 11 & 12 \\
-%    \hline
-%  \end{tabular*}
-%\end{table}
-
-%Adding notes to tables can be complicated.  Perhaps the easiest
-%method is to generate these manually.
-
-% an example of a two-column table
-%\begin{table*}
-%\small
-  %\caption{\ An example of a caption to accompany a table, table captions do not end in a full point}
-  %\label{tbl:example}
-  %\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lllllll}
-    %\hline
-    %Header one & Header two & Header three & Header four & Header five & Header six  & Header seven\\
-    %\hline
-    %1 & 2 & 3 & 4 & 5 & 6  & 7\\
-    %8 & 9 & 10 & 11 & 12 & 13 & 14 \\
-    %15 & 16 & 17 & 18 & 19 & 20 & 21\\
-    %\hline
-  %\end{tabular*}
-%\end{table*}
-
-%You can also put lists into the text. You can have bulleted or numbered lists of almost any kind. 
-%The \texttt{mhchem} package can also be used so
-%that formulae are easy to input: \texttt{\textbackslash ce\{H2SO4\}} gives \ce{H2SO4}.
-
-%\section{Conclusions}
-%The conclusions section should come at the end of article.
-For the reference section, the style file rsc.bst can be used to generate the correct reference style.\footnote[4]{Footnotes should appear here.
-These might include comments relevant to but not central to the matter under discussion, limited experimental and spectral data, and crystallographic data.}
- %For footnotes in the main text of the article please number the footnotes to avoid duplicate symbols.
-e.g.
-\footnote[num]{your text} the corresponding author \ast counts as footnote 1, ESI as footnote 2, e.g.
-if there is no ESI, please start at [num]=[2], if ESI is cited in the title please start at [num]=[3] etc.
-Please also cite the ESI within the main body of the text using \dag.
-
-%The \balance command can be used to balance the columns on the final page if desired. It should be placed anywhere within the first column of the last page.
-
-%\balance
-
-%If notes are included in your references you can change the title from 'References' to 'Notes and references' using the following command:
-%\renewcommand\refname{Notes and references}
-
 \footnotesize{

### 2012-10-18 paper.tex
Final small changes before submission

@@
 The oscillation frequency is furthermore strongly temperature dependent with increasing temperature resulting in increasing frequency.
-A plausible mechanism for the oscillations is proposed based on a oxidation/reduction cycle of the nanoparticles which change the rate of CO oxidation on the particles.}  %on an earlier model on Pd single crystals [Hendriksen \textit{et al., Nature Chemistry}, 2010, \textbf{9}, 730]}
+A plausible mechanism for the oscillations is proposed based on a oxidation/reduction cycle of the nanoparticles which change the rate of CO oxidation on the particles.}
 \vspace{0.5cm}

### 2012-11-19 paper.tex
Started to modify paper according to referee's whishes

@@
 
+Already the early theretical descriptions of the possibility of oscillationary beheaviour even very simple catalytic systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}) noticed that even though oscillation can theoretically occur in many catalytic systems, the details are extremely specific to the given system, and it can thus be diffuctult to predict how and if a given system will oscillate.
+
+Oscillations in catalytic systems can be quite complex and the parameter space can be very large\cite{Ferino1999}.
+In the system investigated in this paper, oscillations could be dependant on morphologic parameres of the nanoparticels such as size, shape and exposed facets.
+Also the oxidation state and possible carbon pollution on the surface could have impact on the system.
+More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will influcence the systems' ability to show kinetic oscillations.
+
 Oscillating reactions on single crystals at UHV conditions have been studied extensively and is know to originate from surface reconstructions of the surface during the oscillations\cite{Ertl2008}.
@@
 Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface formation.
-CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
+CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, Pd zeolites\cite{Liauw1996,Slinko2001}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
 Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.
@@
 An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding.
-Initially a light-off CO-oxidation measurement is performed (shown in Figure~\ref{fgr:initial_treatment}) where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$.
+Initially a light-off CO-oxidation measurement is performed (shown in Figure~\ref{fgr:initial_treatment}) where the temperature is increased at 3\,$^\circ$C/min until the sample reaches the light-off tempereature and achieves full conversion of CO to CO$_2$.
 At CO:O$_2$ ratio of $\sim0.08$ and a geometrical Pt coverage of $\sim0.1\%$ light-off occurs at approximately 180\,$^\circ$C.
@@
 Hereafter the conversion increases slowly over time until approximately 50\% conversion is reached (at $\sim$1118\,min).
-Shortly after reaching 50\% conversion the sample again ignites and convert all CO to CO$_2$.
+Shortly after reaching 50\% conversion the sample again reach light-off and convert all CO to CO$_2$.
 After a short full conversion period the sample again deactivates and the cycle repeats itself.
@@
   \includegraphics[width=17cm]{single_full_oscillation.png}
-  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate deactivation.
+  \caption{A full oscillation period first showing a steep increase in activity followed by an almost immediate deactivation.
 For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.
@@
 It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known.
-We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor makes this a challenging task.
+We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor !!!
+and the fact that the lid can only be removed by mechanically breaking the reactor!!!
+makes this a challenging task.
 If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration.

### 2012-11-23 paper.tex
A bit closer towards reply to reviewers

@@
 However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.
+!!!
+Another possible mechanism behind the increasing oscillation period, could be morphology changes of the nano particles.
+However, the fact that the oscillations show no clear size dependence in the range of 3 to 9\,nm suggest that the oscillations are not very dependent on the exact particle morphology.!!!
 

### 2012-11-23 supplementary.tex
A bit closer towards reply to reviewers

--- 2012-03-07 supplementary.tex
@@
 The reactor consists of two inlets, a mixing zone allowing for diffusional mixing of reactants, an outlet, a reactor volume of $240\,$nL and a $5.4\,\mu$m wide, 3\,$\mu$m high and 1500\,$\mu$m long capillary used for sniffing gases from the reactor volume.
-The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0-2.5\,bar.
-The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0-10 mL/min.
+The reactor is sealed by anodic bonding of a pyrex lid to the Si reactor and is able to operate in a pressure range of 0--2.5\,bar.
+The reaction gases are supplied to the two inlets by flow controllers capable of controlling the gas flow from 0--10 mL/min.
 The capillary flow is fed into a quadropole mass-spectrometer (QMS) for analysis while any surplus of gas from the inlets is passed directly through to the outlet via a pressure controller allowing control of reactor pressure.
@@
   \includegraphics[width=8cm]{reactor.jpg}
-  \caption{The Microreactor before the lid is anodically bonded to the reactor}
+  \caption{Image of the 20x16\,mm microreactor showing the circular reactor area and gas channel system}
   \label{fgr:reactor}
@@
   \centering
-  \includegraphics[width=9cm]{oscillations_gas_dependence_summary_supplemental.png}
-  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
+  \includegraphics[width=9cm]{oscil_gas_dependence_summary.png}
+  \caption{Oscillation period (blue) as a function of time and CO concentration (black).
+The overall trend of increasing oscillation period with time is superimposed with small discontinuous steps when the CO concentration is increased.}
   \label{fgr:gas_dependence_summary}
@@
   \centering
-  \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
-  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$ (blue).
-The temperature is constant $210^\circ$C doing the entire measurement.
+  \includegraphics[width=14cm]{oscil_gas_dependence.png}
+  \caption{Complete series of data from an oscillating sample, showing CO (red) and CO$_2$ (blue).
+The temperature is constant at $210^\circ$C during the entire measurement.
 For every frame the CO-concentration is increased.}
@@
   \includegraphics[width=9cm]{duty_cycles_long_measurement_supplemental.png}
-  \caption{A plot of the duty-cycle of the sample duing the 4-day long experiment.
-The individual data-points is calculted as the integral of CO (red) or CO$_2$ (blue) doing the individual oscillations.
+  \caption{Running average of the CO and CO$_2$ concentrations and their ratio during a 4-day long experiment.
+The individual data-points is calculated as the integral of CO (red) or CO$_2$ (green) during the individual oscillation periods.
 The ratio between CO and CO$_2$ is drawn in black.}

### 2012-11-23 python_figures/duty_cycles_long_measurement.py

@@ -101,7 +101,7 @@ axis.grid(False)
 
 #axis.set_ylabel('SEM Current / nA', fontsize=20)
 axis.set_ylabel('Integrated charge (a.u.)', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
 
 

### 2012-11-23 python_figures/oscillations_gas_dependence.py

@@ -59,7 +59,7 @@ axis2_array = []
 for i in range(0,steps-1):
     axis_array.append(fig.add_subplot(6,3,i+1))
     axis_array[i].plot(data['M28'][:,0], data['M28'][:,1]*1e9, 'r-')
-    axis_array[i].plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'b-')
+    axis_array[i].plot(data['M44'][:,0], data['M44'][:,1]*1e9, 'g-')
     #axis_array[i].set_ylim(0,0.1*(i+1)*1.85)
     axis_array[i].set_ylim(0,1.5)
     axis_array[i].set_yticks((0.25,0.5,0.75,1,1.25))
@@ -95,4 +95,4 @@ for i in range(0,steps-1):
 
 #plt.tight_layout()
 #plt.show()
-plt.savefig('../oscillations_gas_dependence_supplemental.png',dpi=300)
+plt.savefig('../oscillations_gas_dependence.png',dpi=300)

### 2012-11-23 python_figures/oscillations_gas_dependence_summary.py

@@ -74,8 +74,9 @@ for i in range(1,len(oscillations)):
 
 fig = plt.figure()
 fig.subplots_adjust(bottom=0.2) # Make room for x-label
+fig.subplots_adjust(right=0.9) # Make room for second y-label
 ratio = 0.61803398              # Golden mean
-fig_width = 9
+fig_width = 12
 fig_width = fig_width /2.54     # width in cm converted to inches
 fig_height = fig_width*ratio
 fig.set_size_inches(fig_width,fig_height)
@@ -92,19 +93,25 @@ axis.set_ylim(0,50)
 axis.set_xlim(0,3100)
 
 axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=3)
-axis.grid(True)    
+axis.grid(False)    
 
-axis.set_ylabel('Oscillations periods / minutes', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_ylabel('Oscillation period / minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
-
-
+axis2 = axis.twinx()
+#axis2.plot(data['CO_FLOW'][:,0], data['CO_FLOW'][:,1], 'r-')
+axis2.plot(data['CO_FLOW'][:,0], data['CO_FLOW'][:,1]/(4+data['CO_FLOW'][:,1]), 'k-')
+axis2.set_xlim(0,3100)
+axis2.set_ylim(0,0.15)
+axis2.set_ylabel('CO/O$_2$-ratio', fontsize=8)    
+#axis2.set_yticks((0.025,0.05,0.075,0.1,0.125))
+axis2.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis='both',pad=3)
 
 
 
 #plt.tight_layout()
 plt.show()
-plt.savefig('../oscillations_gas_dependence_summary_supplemental.png',dpi=300)
+plt.savefig('../oscil_gas_dependence_summary.png',dpi=300)
 
 
 

### 2012-11-23 python_figures/summary_of_long_measurement.py

@@ -70,11 +70,11 @@ errfunc = lambda p, x, y: fitfunc(p, x) - y # Distance to the target function
 p0 = [0.2,0.6,2] # Initial guess for the parameters
 p1, success = optimize.leastsq(errfunc, p0[:], args=([700,1000,2000,4000,6000],[4,6,20,37,45]),maxfev=1000)
 print p1, success
-axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r-')
+axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r--')
 
 p1, success = optimize.leastsq(errfunc, p0[:], args=([500,1000,2000,4000,6000],[0,2,9,11,16]),maxfev=1000)
 print p1, success
-axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r-')
+axis.plot(range,p1[0]*(range**(p1[1]))+p1[2],'r--')
 #axis.plot(data['M28'][:,0], data['M28'][:,1], 'r-')
 #axis.plot(data['M44'][:,0], data['M44'][:,1], 'b-')
 #axis.set_ylim(0,7)
@@ -84,7 +84,7 @@ axis.tick_params(direction='in', length=6, width=2, colors='k',labelsize=8,axis=
 axis.grid(False)    
 
 axis.set_ylabel('Oscil. period / minutes', fontsize=8)
-axis.set_xlabel('Time/minutes', fontsize=8)
+axis.set_xlabel('Time / min', fontsize=8)
 
 a = plt.axes([.18, .65, .3, .15], axisbg='w')
 a.plot(oscillations, periods, 'b,')

### 2012-11-24 paper.tex
First version of reply to referees sent to Ib

@@
 
+!!!!
 Already the early theretical descriptions of the possibility of oscillationary beheaviour even very simple catalytic systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}) noticed that even though oscillation can theoretically occur in many catalytic systems, the details are extremely specific to the given system, and it can thus be diffuctult to predict how and if a given system will oscillate.
+!!!!
 
+!!!
 Oscillations in catalytic systems can be quite complex and the parameter space can be very large\cite{Ferino1999}.
@@
 Also the oxidation state and possible carbon pollution on the surface could have impact on the system.
-More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will influcence the systems' ability to show kinetic oscillations.
+More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will influcence the systems ability to show kinetic oscillations.
+!!!
 
@@
 Recent studies have proposed a mechanism on Pd \cite{Hendriksen2010} attributed to a cycle of surface oxide formation, oxide roughening and clean metal surface formation.
-CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, Pd zeolites\cite{Liauw1996,Slinko2001}, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
+CO oxidation oscillations has also been observed on Pt thin films\cite{Lund2000}, !!!
+Pd zeolites\cite{Liauw1996,Slinko2001} !!!, in macroscopic flow reactors\cite{Singh2010} and on Pt nanoparticles synthesized from wet chemical synthesis and subsequent annealing \cite{Carlsson2006}.
 Here we investigate CO oscillations in a microreactor model system on size selected Pt nanoparticles by high sensitivity mass spectrometry.
@@
 This corresponds to an area of $\sim$0.5 ppm of the reactor area suggesting that in situ studies become challenging as such a minority of the reactor volume could account for all the reactivity.
-Attempts to see any thermal signal from such small areas has so far been in vain.
+Attempts to see any thermal signal from such small areas has so far been in vain, !!!
+which would point towards a constant temperature even on the microscopic scale, however the experimental data are so far not good enough to make final conclusions.!!!
 

### 2012-11-24 supplementary.tex
First version of reply to referees sent to Ib

@@
 
+\section{TEM Imaging}
+!!!
+It is quite obvious that it would be very interesting to aquire good TEM images of the nanoparticles  before and after a long oscillation measurement.
+However, due to the design of the $\mu$-reactor platform it is extremely difficult to get TEM images after reaction.
+This is partly due to the very thick substrate of seveal hundred $\mu$m, as well as the anodic bonding.
+The lid can only be removed by mechanically breaking the device.
+Figure ????
+show a TEM image of a cluster ......
+!!!
+
 \section{CO concentration dependence}

### 2012-11-28 supplementary.tex
Added the TEM to the supplementary + a little bit to the reply

@@
 However, due to the design of the $\mu$-reactor platform it is extremely difficult to get TEM images after reaction.
-This is partly due to the very thick substrate of seveal hundred $\mu$m, as well as the anodic bonding.
-The lid can only be removed by mechanically breaking the device.
-Figure ????
-show a TEM image of a cluster ......
-!!!
+This is partly due to the very thick substrate of seveal hundred $\mu$m, as well as the anodic bonding, which cannot be reversed and thus the lid can only be removed by mechanically breaking the device.
+Images of the as-deposited particles are on the other hand quite easy to acquire by depositing on a substrate more suitable for TEM under conditions identical to those of the deposition into the $\mu$-reactor.
+Such an image is shown in Figure~\ref{fgr:gas_dependence}.
+Images of this kind confirms that our particles actually look like we expect them to do, but does not bring any insight into the oscillation mechanism or an explanation of the decrease in oscillation period as time progresses.!!!!
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=9cm]{3nm_Pt_on_SiO2.png}
+  \caption{Image of as-deposited nanoparticles deposited on a thin substrate of SiO$_2$.}
+  \label{fgr:tem_3nm}
+\end{figure}
 

### 2012-11-30 paper.tex
Now we are close to being able to re-submit

--- 2012-11-19 paper.tex
@@
 
-Already the early theretical descriptions of the possibility of oscillationary beheaviour even very simple catalytic systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}) noticed that even though oscillation can theoretically occur in many catalytic systems, the details are extremely specific to the given system, and it can thus be diffuctult to predict how and if a given system will oscillate.
+Already the early theoretical descriptions of the possibility of oscillationary behavior of even very simple catalytic systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}) noticed that even though oscillation can theoretically occur in many catalytic systems, the details are extremely specific to the given system, and it can thus be difficult to predict how and if a given system will oscillate.
 
 Oscillations in catalytic systems can be quite complex and the parameter space can be very large\cite{Ferino1999}.
-In the system investigated in this paper, oscillations could be dependant on morphologic parameres of the nanoparticels such as size, shape and exposed facets.
+In the system investigated in this paper, oscillations could be dependant on morphologic parameters of the nanoparticels such as size, shape and exposed facets.
 Also the oxidation state and possible carbon pollution on the surface could have impact on the system.
-More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will influcence the systems' ability to show kinetic oscillations.
+More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will also influcence the systems ability to show kinetic oscillations.
 
@@
 It is important to note that the fraction of oxidized particles needed to achieve full conversion is not known.
-We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor !!!
-and the fact that the lid can only be removed by mechanically breaking the reactor!!!
-makes this a challenging task.
+We are currently investigating new methods for gaining insight into the nature of the nanoparticles in the reactor but the low coverage and the design of the reactor and the fact that the lid can only be removed by mechanically breaking the reactor makes this a challenging task.
 If not all particles are oxidized at light-off they will now oxidize much faster due to the low CO-concentration.
@@
 This corresponds to an area of $\sim$0.5 ppm of the reactor area suggesting that in situ studies become challenging as such a minority of the reactor volume could account for all the reactivity.
-Attempts to see any thermal signal from such small areas has so far been in vain.
+Attempts to see any thermal signal from such small areas has so far been in vain, which would point towards a constant temperature even on the microscopic scale, however the experimental data are so far not good enough to make final conclusions.
 
@@
 However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.
+Another possible mechanism behind the increasing oscillation period, could be morphology changes of the nano particles.
+However, the fact that the oscillations show no clear size dependence in the range of 3 to 9\,nm suggests that the oscillations are not very dependent on the exact particle morphology.
 

### 2012-11-30 paper.tex
Almost done...

@@
 
-Already the early theoretical descriptions of the possibility of oscillationary behavior of even very simple catalytic systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}) noticed that even though oscillation can theoretically occur in many catalytic systems, the details are extremely specific to the given system, and it can thus be difficult to predict how and if a given system will oscillate.
-
-Oscillations in catalytic systems can be quite complex and the parameter space can be very large\cite{Ferino1999}.
-In the system investigated in this paper, oscillations could be dependant on morphologic parameters of the nanoparticels such as size, shape and exposed facets.
-Also the oxidation state and possible carbon pollution on the surface could have impact on the system.
-More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will also influcence the systems ability to show kinetic oscillations.
+Already early theoretical descriptions of the oscillatory behavior, on even very simple catalytic systems, noticed that oscillations can occur in many systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}).
+The details of the oscillations are, however, extremely specific to the given system and it can thus be difficult to predict how and if a given system will oscillate.
+Oscillations in catalytic systems can be quite complex and the parameter space can be very large.
+In the system investigated in this paper oscillations could be dependent on morphological parameters of the nanoparticles such as size, shape and exposed facets.
+Also, the oxidation state and possible pollution on the surface could have impact on the system.
+More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will also influence the systems ability to show kinetic oscillations.
 
@@
 This corresponds to an area of $\sim$0.5 ppm of the reactor area suggesting that in situ studies become challenging as such a minority of the reactor volume could account for all the reactivity.
-Attempts to see any thermal signal from such small areas has so far been in vain, which would point towards a constant temperature even on the microscopic scale, however the experimental data are so far not good enough to make final conclusions.
+Attempts to see any thermal signal from such small areas has so far been in vain, which would point towards a constant temperature even on the microscopic scale.
+However, the experimental data are so far not good enough to make final conclusions.
 
@@
 However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since an average loss in activity of the sample would then be expected.
-Another possible mechanism behind the increasing oscillation period, could be morphology changes of the nano particles.
+Another possible mechanism behind the increasing oscillation period, could be morphology changes of the nanoparticles.
 However, the fact that the oscillations show no clear size dependence in the range of 3 to 9\,nm suggests that the oscillations are not very dependent on the exact particle morphology.

### 2012-12-03 paper.tex
Integrated most of Ibs and Oles corrections

@@
 
-Already early theoretical descriptions of the oscillatory behavior, on even very simple catalytic systems, noticed that oscillations can occur in many systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}).
+Already early theoretical descriptions of the oscillatory behavior, even on very simple catalytic systems, noticed that oscillations can occur in many systems (eg \cite{LAGOS1979,IVANOV1980,TAKOUDIS1981,SONG1991}).
 The details of the oscillations are, however, extremely specific to the given system and it can thus be difficult to predict how and if a given system will oscillate.
@@
 Also, the oxidation state and possible pollution on the surface could have impact on the system.
-More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor will also influence the systems ability to show kinetic oscillations.
+More macroscopic parameters such as the geometry of the reactor, the temperature distribution and the distribution of the particles throughout the reactor may also influence the systems ability to show kinetic oscillations.
 
@@
 Another possible mechanism behind the increasing oscillation period, could be morphology changes of the nanoparticles.
-However, the fact that the oscillations show no clear size dependence in the range of 3 to 9\,nm suggests that the oscillations are not very dependent on the exact particle morphology.
+However, the fact that the oscillations show no clear size dependence in the range of 3 to 9\,nm suggests that the oscillations are not very dependent on the size.
 

### 2012-12-03 supplementary.tex
Integrated most of Ibs and Oles corrections

@@
 \section{TEM Imaging}
-!!!
 It is quite obvious that it would be very interesting to aquire good TEM images of the nanoparticles  before and after a long oscillation measurement.
@@
 Such an image is shown in Figure~\ref{fgr:gas_dependence}.
-Images of this kind confirms that our particles actually look like we expect them to do, but does not bring any insight into the oscillation mechanism or an explanation of the decrease in oscillation period as time progresses.!!!!
+Images of this kind confirms that our particles actually look like we expect them to do, but does not bring any insight into the oscillation mechanism or an explanation of the decrease in oscillation period as time progresses.
 \begin{figure}[h]

### 2012-12-04 paper.tex
Added an extra reference and completed the reply to referees.
Updated the color scheme to allow printing in PCCP

@@
 Inserted circles illustrates the proposed model.
-At high conversion the platinum is oxidized (red) while in low conversion the sample is reduced (blue).}
+At high conversion the platinum is oxidized (bright spots) while in low conversion the sample is reduced (dark spots).}
   \label{fgr:full_oscillation}
@@
 Attempts to see any thermal signal from such small areas has so far been in vain, which would point towards a constant temperature even on the microscopic scale.
+Also a recent thereoretical study shows that heat transport is very efficient in systems like the $\mu$-reactors\cite{Zhdanov2012}.
 However, the experimental data are so far not good enough to make final conclusions.

### 2012-12-04 python_figures/single_full_oscillation.py

@@ -73,7 +73,7 @@ positions.append([.6, .25, .15, .15])
 positions.append([.69, .25, .15, .15])
 
 oxide = []
-oxide.append([0.001,3.14])
+oxide.append([0.002,3.14])
 oxide.append([1,0])
 oxide.append([0.7,0.5])
 oxide.append([0.5,1])
@@ -84,17 +84,19 @@ N = 500
 R = np.random.rand(N)
 Theta = np.random.rand(N)*2*np.pi
 area = 0.8
-colors = np.zeros((N,len(positions)))
 
 j = 0
 for pos in positions:
+    colors = []
     a = plt.axes(pos, axisbg='w',polar=True)
     print oxide[j][0]
     for i in range(0,N):
         if (R[i]>oxide[j][0]) and ((Theta[i] < oxide[j][1]) or (Theta[i] > 2*np.pi - oxide[j][1])):
-            colors[i][j] = 1
+            colors.append((1,0.2,0.2))
+        else:
+            colors.append((0,0,0.25))
             
-    c = plt.scatter(Theta, R, c=colors[:,j], s=area, linewidths=0)
+    c = plt.scatter(Theta, R, c=colors, s=area, linewidths=0)
     c.set_alpha(0.75)
     plt.setp(a, xticks=[], yticks=[])
     j = j + 1
